### 2016-11-28 reports/Effects_of_AWD_N_on_SB.rmd
Initial commit
Add data;

Add README.md files;

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Development/svm-r-markdown-templates/svm-latex-ms.tex
title: "Effects of Alternate Wetting and Drying Irrigation and Nitrogen Fertilization on Sheath Blight of Rice"
thanks: "Replication files are available on the author's Github account (http://github.com/adamhsparks/AWD_N_SB). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Adam.Sparks@usq.edu.au"
author:
- name: Adam H. Sparks
  affiliation: Centre for Crop Health, University of Southern Queensland, West St., Toowoomba, QLD 4350, Australia
- name: Nancy P. Castilla
  affiliation: Crop and Environmental Sciences Division, International Rice Research Institute, Los Baños, Laguna 4031, Philippines
abstract: "Abstract limited to 200 words in one paragraph."
keywords: "*Rhizoctonia solani*"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt

# spacing: double
bibliography: ~/Dropbox/master.bib
biblio-style: apsr
---

Introduction goes here with no heading

# Materials and Methods

# Results

## Data analysis

\pagebreak

# Discussion

# Acknowledgements

<!--
# Literature Cited
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\vspace*{-0.2in}
\noindent
-->

### 2016-11-28 munge/01-fill_na_2016_data.R

@@ -1,0 +1,60 @@
+# Preprocess 2016 data for all assessments
+#
+# 1. Cleanup date format and fill empty dates
+# 2. Fill empty NTIL (for same hill, not missing values)
+# 3. Fill empty NTShB (for same hill, not missing values)
+
+library(tidyr)
+library(readr)
+
+# First assessment -------------------------------------------------------------
+DS2016_A1 <- read_csv("data/DS2016_1.csv")
+# Fill missing values in NTIL and NTShB
+DS2016_A1 <-
+  DS2016_A1 %>% fill(NTIL)
+DS2016_A1 <-
+  DS2016_A1 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A1[, 1] <- as.Date("2016-03-15", origin = "1970-01-01")
+
+# Second assessement -----------------------------------------------------------
+DS2016_A2 <- read_csv("data/DS2016_2.csv")
+DS2016_A2 <-
+  DS2016_A2 %>% fill(NTIL)
+DS2016_A2 <-
+  DS2016_A2 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A2[, 1] <- as.Date("2016-03-29", origin = "1970-01-01")
+
+
+# Third assessement ------------------------------------------------------------
+DS2016_A3 <- read_csv("data/DS2016_3.csv")
+DS2016_A3 <-
+  DS2016_A3 %>% fill(NTIL)
+DS2016_A3 <-
+  DS2016_A3 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A3[, 1] <- as.Date("2016-04-12", origin = "1970-01-01")
+
+# Fourth assessment ------------------------------------------------------------
+DS2016_A4 <- read_csv("data/DS2016_4.csv")
+DS2016_A4 <-
+  DS2016_A4 %>% fill(NTIL)
+DS2016_A4 <-
+  DS2016_A4 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A4[, 1] <- as.Date("2016-04-26", origin = "1970-01-01")
+
+DS2016 <- rbind(as.data.frame(DS2016_A1),
+                as.data.frame(DS2016_A2),
+                as.data.frame(DS2016_A3),
+                as.data.frame(DS2016_A4))
+
+# write CSV to cache -----------------------------------------------------------
+write_csv(DS2016, "./cache/AWD_2016_Data.csv")
+
+# eos

### 2017-03-23 Analysis.Rmd
Continued edits and additions
Add Rmd files for checking probability distribution for analysis and
for analysis

Change N rates to reflect actual kg/ha rather than just a 0-4 number.

---
title: "Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ProjectTemplate)
load.project()
```
# 2015

## Leaf Sheath Blight Severity Model
```{r}
(LShB_lmm_2015 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2015))
summary(LShB_lmm_2015)

plot(LShB_lmm_2015)
qqnorm(resid(LShB_lmm_2015))

```

## Tiller Sheath Blight Severity Model
```{r}
(TShB_lmm_2015 <- lmer(TShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2015))
summary(TShB_lmm_2015)

plot(TShB_lmm_2015)
qqnorm(resid(TShB_lmm_2015))

```

*******

# 2016

## Leaf Sheath Blight Severity Model
```{r}
(LShB_lmm_2016 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2016))
summary(LShB_lmm_2016)

plot(LShB_lmm_2016)
qqnorm(resid(LShB_lmm_2016))

```

## Tiller Sheath Blight Severity Model
```{r}
(TShB_lmm_2016 <- lmer(TShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
                       data = AUDPS_2016))
summary(TShB_lmm_2016)

plot(TShB_lmm_2016)
qqnorm(resid(TShB_lmm_2016))

```

### 2017-03-23 Probability_distribution_checks.Rmd
Continued edits and additions
Add Rmd files for checking probability distribution for analysis and
for analysis

Change N rates to reflect actual kg/ha rather than just a 0-4 number.

---
title: "Probability Distribution Checks"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ProjectTemplate)
load.project()
```
# 2015
## Check probability distribution fit for leaf sheath blight

```{r, results='hide', message=FALSE, warning=FALSE}

AUDPS_2015$LShB_rating_t <- AUDPS_2015$LShB_rating + 1

qqp(AUDPS_2015$LShB_rating_t, "norm")

qqp(AUDPS_2015$LShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2015$LShB_rating_t, "Poisson")
qqp(AUDPS_2015$LShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2015$LShB_rating_t, "gamma")
qqp(AUDPS_2015$LShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

## Check probability distribution fit for tiller sheath blight

```{r, results='hide', message=FALSE, warning=FALSE}

AUDPS_2015$TShB_rating_t <- AUDPS_2015$TShB_rating + 1

qqp(AUDPS_2015$TShB_rating_t, "norm")

qqp(AUDPS_2015$TShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2015$TShB_rating_t, "Poisson")
qqp(AUDPS_2015$TShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2015$TShB_rating_t, "gamma")
qqp(AUDPS_2015$TShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

*******

# 2016

## Check probability distribution fit for leaf sheath blight

```{r, results='hide', message=FALSE, warning=FALSE}

AUDPS_2016$LShB_rating_t <- AUDPS_2016$LShB_rating + 1

qqp(AUDPS_2016$LShB_rating_t, "norm")

qqp(AUDPS_2016$LShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2016$LShB_rating_t, "Poisson")
qqp(AUDPS_2016$LShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2016$LShB_rating_t, "gamma")
qqp(AUDPS_2016$LShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

## Check probability distribution fit for tiller sheath blight

```{r, results='hide', message=FALSE, warning=FALSE}

AUDPS_2016$TShB_rating_t <- AUDPS_2016$TShB_rating + 1

qqp(AUDPS_2016$TShB_rating_t, "norm")

qqp(AUDPS_2016$TShB_rating_t, "lnorm")

poisson <- fitdistr(AUDPS_2016$TShB_rating_t, "Poisson")
qqp(AUDPS_2016$TShB_rating_t, "pois", poisson$estimate)

gamma <- fitdistr(AUDPS_2016$TShB_rating_t, "gamma")
qqp(AUDPS_2016$TShB_rating_t, "gamma",
    shape = gamma$estimate[[1]], 
    rate = gamma$estimate[[2]])
```

### 2017-03-23 munge/01_preprocess_2015_data.R

@@ -68,13 +68,19 @@ reformat <- function(files) {
 
 DS2015 <- ldply(.data = files, .fun = reformat)
 
+# Replace "N*" with a number for NRTE ------------------------------------------
+DS2015$NRTE[which(DS2015$NRTE == "N0")] = 0
+DS2015$NRTE[which(DS2015$NRTE == "N1")] = 120
+DS2015$NRTE[which(DS2015$NRTE == "N2")] = 150
+
+# Add treatment numbers --------------------------------------------------------
 DS2015$TRT <- NA
-DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == "N0")] = "FLD_N0"
-DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == "N1")] = "FLD_N1"
-DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == "N2")] = "FLD_N2"
-DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == "N0")] = "AWD_N0"
-DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == "N1")] = "AWD_N1"
-DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == "N2")] = "AWD_N2"
+DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 0)] = "FLD_N0"
+DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 120)] = "FLD_N120"
+DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 150)] = "FLD_N150"
+DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 0)] = "AWD_N0"
+DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 120)] = "AWD_N120"
+DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 150)] = "AWD_N150"
 
 DS2015 <-
   as_tibble(DS2015) %>% dplyr::select(DATE,

### 2017-03-23 munge/02-preprocess_2016_data.R

@@ -82,12 +82,16 @@ DS2016[is.na(DS2016)] <- 0
 # Replace "Flooded" with "FLD" -------------------------------------------------
 DS2016$WMGT[which(DS2016$WMGT == "Flooded")] = "FLD"
 
+# Replace "N*" with a number for NRTE ------------------------------------------
+DS2016$NRTE[which(DS2016$NRTE == "N1")] = 60
+DS2016$NRTE[which(DS2016$NRTE == "N2")] = 180
+
 # Add treatment numbers --------------------------------------------------------
 DS2016$TRT <- NA
-DS2016$TRT[which(DS2016$WMGT == "FLD" & DS2016$NRTE == "N1")] = "FLD_N3"
-DS2016$TRT[which(DS2016$WMGT == "FLD" & DS2016$NRTE == "N2")] = "FLD_N4"
-DS2016$TRT[which(DS2016$WMGT == "AWD" & DS2016$NRTE == "N1")] = "AWD_N3"
-DS2016$TRT[which(DS2016$WMGT == "AWD" & DS2016$NRTE == "N2")] = "AWD_N4"
+DS2016$TRT[which(DS2016$WMGT == "FLD" & DS2016$NRTE == 60)] = "FLD_N60"
+DS2016$TRT[which(DS2016$WMGT == "FLD" & DS2016$NRTE == 180)] = "FLD_N180"
+DS2016$TRT[which(DS2016$WMGT == "AWD" & DS2016$NRTE == 60)] = "AWD_N60"
+DS2016$TRT[which(DS2016$WMGT == "AWD" & DS2016$NRTE == 180)] = "AWD_N180"
 
 # Rename columns for consistency with 2015 -------------------------------------
 DS2016 <- dplyr::rename(DS2016, TShB_rating = NSHShB)

### 2017-03-23 munge/visualise_data.R

@@ -201,62 +201,3 @@ ggplot(AUDPS, aes(x = TRT, y = TShB_rating)) +
   geom_boxplot() +
   theme_tufte()
 ggsave("graphs/TShB_AUDPS.png", width = 4, height = 4)
-
-
-# qqplots ----------------------------------------------------------------------
-#2015
-
-gg_qq <- function(x, distribution = "norm", ..., line.estimate = NULL, conf = 0.95,
-                  labels = names(x)){
-  q.function <- eval(parse(text = paste0("q", distribution)))
-  d.function <- eval(parse(text = paste0("d", distribution)))
-  x <- na.omit(x)
-  ord <- order(x)
-  n <- length(x)
-  P <- ppoints(length(x))
-  df <- data.frame(ord.x = x[ord], z = q.function(P, ...))
-
-  if (is.null(line.estimate)) {
-    Q.x <- quantile(df$ord.x, c(0.25, 0.75))
-    Q.z <- q.function(c(0.25, 0.75), ...)
-    b <- diff(Q.x)/diff(Q.z)
-    coef <- c(Q.x[1] - b * Q.z[1], b)
-  } else {
-    coef <- coef(line.estimate(ord.x ~ z))
-  }
-
-  zz <- qnorm(1 - (1 - conf)/2)
-  SE <- (coef[2]/d.function(df$z)) * sqrt(P * (1 - P)/n)
-  fit.value <- coef[1] + coef[2] * df$z
-  df$upper <- fit.value + zz * SE
-  df$lower <- fit.value - zz * SE
-
-  if (!is.null(labels)) {
-    df$label <- ifelse(df$ord.x > df$upper | df$ord.x < df$lower, labels[ord],"")
-  }
-
-  p <- ggplot(df, aes(x = z, y = ord.x)) +
-    geom_point() +
-    geom_abline(intercept = coef[1], slope = coef[2]) +
-    geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2)
-  if (!is.null(labels)) p <- p + geom_text(aes(label = label))
-  print(p)
-  coef
-}
-
-Animals2 <- data(Animals2, package = "robustbase")
-mod.lm <- lm(log(Animals2$brain) ~ log(Animals2$body))
-x <- rstudent(mod.lm)
-gg_qq(x)
-
[…]

### 2017-03-23 Probability_distribution_checks.Rmd
Make probability distribution checks more readable

@@
 # 2015
-## Check probability distribution fit for leaf sheath blight
+## 2015 Check probability distribution fit for leaf sheath blight
 
@@
 
-## Check probability distribution fit for tiller sheath blight
+## 2015 Check probability distribution fit for tiller sheath blight
 
@@
 
-## Check probability distribution fit for leaf sheath blight
+## 2016 Check probability distribution fit for leaf sheath blight
 
@@
 
-## Check probability distribution fit for tiller sheath blight
+## 2016 Check probability distribution fit for tiller sheath blight
 

### 2017-03-23 Probability_distribution_checks.Rmd
Edits for clarity

@@
 ```
-# 2015
+
 ## 2015 Check probability distribution fit for leaf sheath blight
@@
 
-# 2016
-
 ## 2016 Check probability distribution fit for leaf sheath blight

### 2017-03-23 Probability_distribution_checks.Rmd
Clean up and clarify probability distribution checks

@@
 
+Here we check the probability distribution that best fits these data.
+I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
+As you see in that guide, there are several distributions that can be checked, for my purposes normal or lognormal are enough so I won't check the others.
+
 ## 2015 Check probability distribution fit for leaf sheath blight
@@
 
-AUDPS_2015$LShB_rating_t <- AUDPS_2015$LShB_rating + 1
+qqp(AUDPS_2015$LShB_rating, "norm")
 
-qqp(AUDPS_2015$LShB_rating_t, "norm")
+qqp(AUDPS_2015$LShB_rating, "lnorm")
 
-qqp(AUDPS_2015$LShB_rating_t, "lnorm")
-
-poisson <- fitdistr(AUDPS_2015$LShB_rating_t, "Poisson")
-qqp(AUDPS_2015$LShB_rating_t, "pois", poisson$estimate)
-
-gamma <- fitdistr(AUDPS_2015$LShB_rating_t, "gamma")
-qqp(AUDPS_2015$LShB_rating_t, "gamma",
-    shape = gamma$estimate[[1]], 
-    rate = gamma$estimate[[2]])
 ```
@@
 
-AUDPS_2015$TShB_rating_t <- AUDPS_2015$TShB_rating + 1
+AUDPS_2015$TShB_rating <- AUDPS_2015$TShB_rating + 1
 
-qqp(AUDPS_2015$TShB_rating_t, "norm")
+qqp(AUDPS_2015$TShB_rating, "norm")
 
-qqp(AUDPS_2015$TShB_rating_t, "lnorm")
+qqp(AUDPS_2015$TShB_rating, "lnorm")
 
-poisson <- fitdistr(AUDPS_2015$TShB_rating_t, "Poisson")
-qqp(AUDPS_2015$TShB_rating_t, "pois", poisson$estimate)
-
-gamma <- fitdistr(AUDPS_2015$TShB_rating_t, "gamma")
-qqp(AUDPS_2015$TShB_rating_t, "gamma",
-    shape = gamma$estimate[[1]], 
-    rate = gamma$estimate[[2]])
 ```
@@
 
-AUDPS_2016$LShB_rating_t <- AUDPS_2016$LShB_rating + 1
+qqp(AUDPS_2016$LShB_rating, "norm")
 
-qqp(AUDPS_2016$LShB_rating_t, "norm")
+qqp(AUDPS_2016$LShB_rating, "lnorm")
 
-qqp(AUDPS_2016$LShB_rating_t, "lnorm")
-
-poisson <- fitdistr(AUDPS_2016$LShB_rating_t, "Poisson")
-qqp(AUDPS_2016$LShB_rating_t, "pois", poisson$estimate)
-
-gamma <- fitdistr(AUDPS_2016$LShB_rating_t, "gamma")
-qqp(AUDPS_2016$LShB_rating_t, "gamma",
-    shape = gamma$estimate[[1]], 
-    rate = gamma$estimate[[2]])
 ```
@@
 
-AUDPS_2016$TShB_rating_t <- AUDPS_2016$TShB_rating + 1
+qqp(AUDPS_2016$TShB_rating, "norm")
 
-qqp(AUDPS_2016$TShB_rating_t, "norm")
+qqp(AUDPS_2016$TShB_rating, "lnorm")
 
-qqp(AUDPS_2016$TShB_rating_t, "lnorm")
+```
 
-poisson <- fitdistr(AUDPS_2016$TShB_rating_t, "Poisson")
-qqp(AUDPS_2016$TShB_rating_t, "pois", poisson$estimate)
+## Conclusions
 
-gamma <- fitdistr(AUDPS_2016$TShB_rating_t, "gamma")
-qqp(AUDPS_2016$TShB_rating_t, "gamma",
-    shape = gamma$estimate[[1]], 
-    rate = gamma$estimate[[2]])
-```
+To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines.
+In this case, for the 2015 data, the leaf data fit a lognormal distribution best, for all others a normal distribution appears to be fine.

### 2017-03-23 Analysis.Rmd
Cleanup graphs

@@
 ```{r}
-(LShB_lmm_2015 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
-                       data = AUDPS_2015))
+(LShB_lmm_2015 <- glmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
+                          family = binomial(link = "logit"), data = AUDPS_2015))
 summary(LShB_lmm_2015)

### 2017-03-23 munge/01_preprocess_2015_data.R

@@ -13,7 +13,7 @@ reformat <- function(files) {
 
   x <-
     x %>%
-    group_by(REP, WMGT, NRTE, HILL, SMPL) %>%
+    group_by(REP, WMGT, NRTE) %>%
     gather(LShB, LShB_rating, starts_with("SL")) %>%
     gather(TShB, TShB_rating, starts_with("SHB")) %>%
     gather(GL, GL_value, starts_with("GL")) %>%
@@ -25,18 +25,8 @@ reformat <- function(files) {
                    TShB_rating,
                    GL_value,
                    DL_value)
-  x <-
-    x %>%
-    group_by(REP, WMGT, NRTE) %>%
-    summarise_each(funs(mean),
-                   NTIL,
-                   NTShB,
-                   LShB_rating,
-                   TShB_rating,
-                   GL_value,
-                   DL_value)
 
-  x[, 4:14] <- round(x[, 4:9], 2)
+  x[, 4:9] <- round(x[, 4:9], 2)
 
   if (files == "data/DS2015_Raw_22DAI.csv") {
     DATE <- rep(as.Date("2015-02-12", origin = "1970-01-01"),

### 2017-03-23 munge/03_preprocess_data.R

@@ -26,26 +26,19 @@ DATE_2 <- na.omit(DATE_2_2016)
 DAYS_2016 <- difftime(DATE_1, DATE_2)
 DS2016$DAYS <- c(rep(0, 16), DAYS_2016)
 
-# Calculate AUDPS (Simco and Piepho 2012, DOI: 10.1094/PHYTO-07-11-0216) -------
-
-AUDPS_2015 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
-  summarise_each(funs(audps(., dates = DAYS)),
-                 LShB_rating,
-                 TShB_rating)
-
-AUDPS_2016 <-
-  DS2016 %>%
-  group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
-  summarise_each(funs(audps(., dates = DAYS)),
-                 LShB_rating,
-                 TShB_rating)
-
 # Join 2015 and 2016 AUDPS data to make next few steps quicker -----------------
 
-AUDPS <- as_tibble(rbind(as.data.frame(AUDPS_2015),
-                         as.data.frame(AUDPS_2016)))
+RAW_data <- AUDPS <- as_tibble(rbind(as.data.frame(DS2015),
+                                     as.data.frame(DS2016)))
+
+# Calculate AUDPS (Simco and Piepho 2012, DOI: 10.1094/PHYTO-07-11-0216) -------
+
+AUDPS <-
+  AUDPS %>%
+  group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
+  summarise_each(funs(audps(., dates = DAYS)),
+                 LShB_rating,
+                 TShB_rating)
 
 AUDPS$LShB_rating <- round(AUDPS$LShB_rating, 2)
 
@@ -54,11 +47,10 @@ AUDPS$WMGT <- as.factor(AUDPS$WMGT)
 AUDPS$NRTE <- as.factor(AUDPS$NRTE)
 AUDPS$REP <- as.factor(AUDPS$REP)
 
+AUDPS <- plyr::rename(AUDPS, c("LShB_rating" = "LShB_AUDPS",
+                               "TShB_rating" = "TShB_AUDPS"))
+
 # Split the 2015 and 2016 AUDPS data for easier analysis -----------------------
 
 AUDPS_2015 <- AUDPS[which(AUDPS$YEAR == "2015"), ]
[…]

### 2017-03-23 munge/04_visualise_data.R

@@ -1,0 +1,129 @@
+# density plot of LShB_rating data ---------------------------------------------
+ggplot(RAW_data, aes(x = LShB_rating, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+                   alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  ggtitle("Leaf Sheath Blight Severity Rating") +
+  theme_tufte()
+ggsave("graphs/LShB_rating.png", width = 4, height = 4)
+
+# density plot of TShB_rating data ---------------------------------------------
+ggplot(RAW_data, aes(x = TShB_rating, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  ggtitle("Tiller Sheath Blight Severity Rating") +
+  theme_tufte()
+ggsave("graphs/TShB_rating.png", width = 4, height = 4)
+
+# density plot of green leaf data ----------------------------------------------
+ggplot(RAW_data, aes(x = GL_value, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  xlab("Count") +
+  ggtitle("Green Leaf Values") +
+  theme_tufte()
+ggsave("graphs/GL_value.png", width = 4, height = 4)
+
+# density plot of dead leaf data -----------------------------------------------
+ggplot(RAW_data, aes(x = DL_value, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  ggtitle("DL_value") +
+  theme_tufte()
+ggsave("graphs/DL_value.png", width = 4, height = 4)
+
+# line plot of leaf sheath blight AUDPS data -----------------------------------
+ggplot(RAW_data, aes(x = ASMT, y = LShB_rating, group = LShB_rating)) +
[…]

### 2017-03-23 munge/visualise_data.R

@@ -1,203 +1,0 @@
-# density plots of raw data -------------------------------------------------------
-
-# check density plot of LShB_rating data
-ggplot(AWD, aes(x = LShB_rating, linetype = as.factor(YEAR))) +
-  geom_density(aes(fill = as.factor(YEAR)),
-                   alpha = 0.5) +
-  viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
-  scale_linetype(name = "Year") +
-  ggtitle("LShB_rating") +
-  theme_tufte()
-ggsave("graphs/LShB_rating.png", width = 4, height = 4)
-
-ggplot(AWD, aes(x = TShB_rating, linetype = as.factor(YEAR))) +
-  geom_density(aes(fill = as.factor(YEAR)),
-               alpha = 0.5) +
-  viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
-  scale_linetype(name = "Year") +
-  ggtitle("TShB_rating") +
-  theme_tufte()
-ggsave("graphs/TShB_rating.png", width = 4, height = 4)
-
-ggplot(AWD, aes(x = GL_value, linetype = as.factor(YEAR))) +
-  geom_density(aes(fill = as.factor(YEAR)),
-               alpha = 0.5) +
-  viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
-  scale_linetype(name = "Year") +
-  ggtitle("GL_value") +
-  theme_tufte()
-ggsave("graphs/GL_value.png", width = 4, height = 4)
-
-ggplot(AWD, aes(x = DL_value, linetype = as.factor(YEAR))) +
-  geom_density(aes(fill = as.factor(YEAR)),
-               alpha = 0.5) +
-  viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
-  scale_linetype(name = "Year") +
-  ggtitle("DL_value") +
-  theme_tufte()
-ggsave("graphs/DL_value.png", width = 4, height = 4)
-
-ggplot(AUDPS, aes(x = LShB_rating, linetype = as.factor(YEAR))) +
-  geom_density(aes(fill = as.factor(YEAR)),
-               alpha = 0.5) +
-  viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
-  scale_linetype(name = "Year") +
-  ggtitle("LShB_AUDPS") +
-  theme_tufte()
-ggsave("graphs/LShB_AUDPS.png", width = 4, height = 4)
-
[…]

### 2017-03-23 munge/01_preprocess_2015_data.R
Correct N rate values in graphs/add ratings over time

@@ -60,17 +60,17 @@ DS2015 <- ldply(.data = files, .fun = reformat)
 
 # Replace "N*" with a number for NRTE ------------------------------------------
 DS2015$NRTE[which(DS2015$NRTE == "N0")] = 0
-DS2015$NRTE[which(DS2015$NRTE == "N1")] = 120
-DS2015$NRTE[which(DS2015$NRTE == "N2")] = 150
+DS2015$NRTE[which(DS2015$NRTE == "N1")] = 100
+DS2015$NRTE[which(DS2015$NRTE == "N2")] = 120
 
 # Add treatment numbers --------------------------------------------------------
 DS2015$TRT <- NA
 DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 0)] = "FLD_N0"
+DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 100)] = "FLD_N100"
 DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 120)] = "FLD_N120"
-DS2015$TRT[which(DS2015$WMGT == "FLD" & DS2015$NRTE == 150)] = "FLD_N150"
 DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 0)] = "AWD_N0"
+DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 100)] = "AWD_N100"
 DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 120)] = "AWD_N120"
-DS2015$TRT[which(DS2015$WMGT == "AWD" & DS2015$NRTE == 150)] = "AWD_N150"
 
 DS2015 <-
   as_tibble(DS2015) %>% dplyr::select(DATE,

### 2017-03-23 munge/04_visualise_data.R

@@ -59,24 +59,19 @@ ggplot(RAW_data, aes(x = ASMT, y = LShB_rating, group = LShB_rating)) +
   theme_tufte()
 ggsave("graphs/LShB_over_time.png", width = 4, height = 4)
 
-
+# line plot of tiller sheath blight AUDPS data ---------------------------------
 ggplot(RAW_data, aes(x = ASMT, y = GL_value, group = GL_value)) +
   stat_summary(fun.y = "mean", geom = "line",
                aes(group = factor(TRT),
                    colour = TRT,
-                   linetype = TRT),
-               size = .5) +
-  stat_summary(fun.y = "mean", geom = "point",
-               aes(group = factor(TRT),
-                   colour = TRT),
+                   linetype = as.factor(YEAR)),
                size = 1) +
-  ylab("Green Leaves (count)") +
-  xlab("Assessment") +
-  facet_grid(. ~ YEAR) +
   viridis::scale_color_viridis(discrete = TRUE,
                                name = "Treatment") +
-  scale_linetype(name = "Treatment") +
+  scale_linetype(name = "Year") +
+  xlab("Assessment") +
   theme_tufte()
+ggsave("graphs/TShB_over_time.png", width = 4, height = 4)
 
 ggplot(RAW_data, aes(x = ASMT, y = DL_value, group = DL_value)) +
   stat_summary(fun.y = "mean", geom = "line",

### 2017-03-23 Analysis.Rmd
Reorder factors and add new graphs; update analysis

--- 2017-03-23 Analysis.Rmd
@@
 ```{r}
-(LShB_lmm_2015 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
-                       data = AUDPS_2015))
-summary(LShB_lmm_2015)
 
-plot(LShB_lmm_2015)
-qqnorm(resid(LShB_lmm_2015))
+# 2015 model goes here
 
@@
 ```{r}
-(TShB_lmm_2015 <- lmer(TShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
-                       data = AUDPS_2015))
+TShB_lmm_2015 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
+                      data = AUDPS_2015,
+                      REML = FALSE)
 summary(TShB_lmm_2015)
@@
 ```{r}
-(LShB_lmm_2016 <- lmer(LShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
-                       data = AUDPS_2016))
+LShB_lmm_2016 <- lmer(LShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
+                      data = AUDPS_2016,
+                      REML = FALSE)
 summary(LShB_lmm_2016)
@@
 ```{r}
-(TShB_lmm_2016 <- lmer(TShB_rating ~ WMGT * NRTE + (1 | REP/WMGT),
-                       data = AUDPS_2016))
+TShB_lmm_2016 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
+                      data = AUDPS_2016,
+                      REML = FALSE)
 summary(TShB_lmm_2016)

### 2017-03-23 munge/03_preprocess_data.R

@@ -45,10 +45,17 @@ AUDPS$LShB_rating <- round(AUDPS$LShB_rating, 2)
 AUDPS$YEAR <- as.factor(AUDPS$YEAR)
 AUDPS$WMGT <- as.factor(AUDPS$WMGT)
 AUDPS$NRTE <- as.factor(AUDPS$NRTE)
+AUDPS$TRT <- as.factor(AUDPS$TRT)
 AUDPS$REP <- as.factor(AUDPS$REP)
 
 AUDPS <- plyr::rename(AUDPS, c("LShB_rating" = "LShB_AUDPS",
                                "TShB_rating" = "TShB_AUDPS"))
+
+AUDPS$NRTE <- factor(AUDPS$NRTE, levels = c(0, 100, 120, 60, 180))
+AUDPS$TRT <- factor(AUDPS$TRT, levels = c("AWD_N0", "AWD_N100", "AWD_N120",
+                                          "AWD_N60", "AWD_N180", "FLD_N0",
+                                          "FLD_N100", "FLD_N120", "FLD_N60",
+                                          "FLD_N180"))
 
 # Split the 2015 and 2016 AUDPS data for easier analysis -----------------------
 

### 2017-03-23 munge/04_visualise_data.R

@@ -5,6 +5,7 @@ ggplot(RAW_data, aes(x = LShB_rating, linetype = as.factor(YEAR))) +
   viridis::scale_fill_viridis(discrete = TRUE,
                               name = "Year") +
   scale_linetype(name = "Year") +
+  facet_grid(WMGT ~ NRTE) +
   ggtitle("Leaf Sheath Blight Severity Rating") +
   theme_tufte()
 ggsave("graphs/LShB_rating.png", width = 4, height = 4)
@@ -16,6 +17,7 @@ ggplot(RAW_data, aes(x = TShB_rating, linetype = as.factor(YEAR))) +
   viridis::scale_fill_viridis(discrete = TRUE,
                               name = "Year") +
   scale_linetype(name = "Year") +
+  facet_grid(WMGT ~ NRTE) +
   ggtitle("Tiller Sheath Blight Severity Rating") +
   theme_tufte()
 ggsave("graphs/TShB_rating.png", width = 4, height = 4)
@@ -73,23 +75,31 @@ ggplot(RAW_data, aes(x = ASMT, y = GL_value, group = GL_value)) +
   theme_tufte()
 ggsave("graphs/TShB_over_time.png", width = 4, height = 4)
 
-ggplot(RAW_data, aes(x = ASMT, y = DL_value, group = DL_value)) +
-  stat_summary(fun.y = "mean", geom = "line",
-               aes(group = factor(TRT),
-                   colour = TRT,
-                   linetype = TRT),
-               size = .5) +
-  stat_summary(fun.y = "mean", geom = "point",
-               aes(group = factor(TRT),
-                   colour = TRT),
-               size = 1) +
-  ylab("Dead Leaves (count)") +
-  xlab("Assessment") +
-  facet_grid(. ~ YEAR) +
-  viridis::scale_color_viridis(discrete = TRUE,
-                               name = "Treatment") +
-  scale_linetype(name = "Treatment") +
+# density plot of leaf sheath blight AUDPS data --------------------------------
+ggplot(AUDPS, aes(x = LShB_AUDPS, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  facet_grid(WMGT ~ NRTE) +
[…]

### 2017-03-23 Analysis.Rmd
Clean up output in Analysis.Rmd/md and add resources to main README.md

@@
                       REML = FALSE)
-summary(TShB_lmm_2015)
+summary(TShB_lmm_2015, correlation = FALSE)
 
@@
                       REML = FALSE)
-summary(LShB_lmm_2016)
+summary(LShB_lmm_2016, correlation = FALSE)
 
@@
                       REML = FALSE)
-summary(TShB_lmm_2016)
+summary(TShB_lmm_2016, correlation = FALSE)
 

### 2017-03-25 Analysis.Rmd
Diagnostics and Analysis
Update diagnostic plots, check exponential fit rather than lognormal

First draft analysis is complete using `MCMCglmm` with diagnostic plots

--- 2017-03-23 Analysis.Rmd
@@
 ```
-# 2015
 
-## Leaf Sheath Blight Severity Model
+## 2015 Leaf Sheath Blight Severity Model
 ```{r}
 
-# 2015 model goes here
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE, ~REP, 
+                 data = as.data.frame(AUDPS_2015),
+                 verbose = FALSE,
+                 prior = eprior,
+                 pr = TRUE)
+
+summary(LShB_lmm_2015)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
+names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
+names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(LShB_lmm_2015$Sol)
+
+# Diagnostic line plots for replicate
+ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for replicate
+ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# Diagnostic line plots for treatements
+ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for treatment
+ggplot(trts, aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# joint distibution of error
+rdf <- data.frame(LShB_lmm_2015$VCV)
+ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
+  geom_density2d() + 
+  geom_abline(intercept = 0, slope = 1)
+```
+
+## 2015 Tiller Sheath Blight Severity Model
+```{r}
+
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+TShB_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
+                 data = as.data.frame(AUDPS_2015),
+                 verbose = FALSE,
+                 prior = eprior,
+                 pr = TRUE)
+
+summary(TShB_lmm_2015)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(TShB_lmm_2015$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(TShB_lmm_2015$Sol[, 2:6])
+names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
+names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(TShB_lmm_2015$Sol)
+
+# Diagnostic line plots for replicate
+ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for replicate
+ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# Diagnostic line plots for treatments
+ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for treatment
+ggplot(trts, aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# joint distibution of error
+rdf <- data.frame(TShB_lmm_2015$VCV)
+ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
+  geom_density2d() + 
+  geom_abline(intercept = 0, slope = 1)
+```
+
+*******
+
+## 2016 Leaf Sheath Blight Severity Model
+```{r}
+
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE, ~REP, 
+                 data = as.data.frame(AUDPS_2016),
+                 verbose = FALSE,
+                 prior = eprior,
+                 pr = TRUE)
+
+summary(LShB_lmm_2016)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:8)])
+reps <- melt(reps)
+
+trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
+names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(LShB_lmm_2016$Sol)
+
+# Diagnostic line plots for replicate
+ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for replicate
+ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# Diagnostic line plots for treatments
+ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for treatment
+ggplot(trts, aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# joint distibution of error
+rdf <- data.frame(TShB_lmm_2015$VCV)
+ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
+  geom_density2d() + 
+  geom_abline(intercept = 0, slope = 1)
 
@@
 ```{r}
-TShB_lmm_2015 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
-                      data = AUDPS_2015,
-                      REML = FALSE)
-summary(TShB_lmm_2015)
 
-plot(TShB_lmm_2015)
-qqnorm(resid(TShB_lmm_2015))
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+TShB_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
+                 data = as.data.frame(AUDPS_2016),
+                 verbose = FALSE,
+                 prior = eprior,
+                 pr = TRUE)
 
-```
-
-*******
-
-# 2016
-
-## Leaf Sheath Blight Severity Model
-```{r}
-LShB_lmm_2016 <- lmer(LShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
-                      data = AUDPS_2016,
-                      REML = FALSE)
-summary(LShB_lmm_2016)
-
-plot(LShB_lmm_2016)
-qqnorm(resid(LShB_lmm_2016))
-
-```
-
-## Tiller Sheath Blight Severity Model
-```{r}
-TShB_lmm_2016 <- lmer(TShB_AUDPS ~ WMGT * NRTE + (1 | REP/WMGT),
-                      data = AUDPS_2016,
-                      REML = FALSE)
 summary(TShB_lmm_2016)
 
-plot(TShB_lmm_2016)
-qqnorm(resid(TShB_lmm_2016))
+# create data frames for generating diagnostic plots
+reps <- data.frame(TShB_lmm_2016$Sol[, c(1, 5:8)])
+reps <- melt(reps)
 
+trts <-  data.frame(TShB_lmm_2016$Sol[, 2:4])
+names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(TShB_lmm_2016$Sol)
+
+# Diagnostic line plots for replicate
+ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for replicate
+ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# Diagnostic line plots for treatments
+ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
+  geom_line() +
+  theme_tufte() +
+  xlab("Iteration Number") +
+  ylab(NULL) +
+  facet_grid(variable ~ .)
+
+# Posterior distributions for treatment
+ggplot(trts, aes(x = value, color = variable)) + 
+  geom_density() +
+  theme_tufte()
+
+# joint distibution of error
+rdf <- data.frame(TShB_lmm_2015$VCV)
+ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
+  geom_density2d() + 
+  geom_abline(intercept = 0, slope = 1)
 ```

### 2017-03-25 Probability_distribution_checks.Rmd
Update probability distribution checks to use new data frame names
Diagnostics and Analysis
Update diagnostic plots, check exponential fit rather than lognormal

First draft analysis is complete using `MCMCglmm` with diagnostic plots

@@
 I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
-As you see in that guide, there are several distributions that can be checked, for my purposes normal or lognormal are enough so I won't check the others.
+As you see in that guide, there are several distributions that can be checked, for my purposes normal or exponential are enough so I won't check the others.
 
@@
 
-qqp(AUDPS_2015$LShB_rating, "norm")
+f1 <- fitdist(AUDPS_2015$LShB_AUDPS, "norm")
+plot(f1)
+qqp(AUDPS_2015$LShB_AUDPS, "norm")
 
-qqp(AUDPS_2015$LShB_rating, "lnorm")
+f2 <- fitdist(AUDPS_2015$LShB_AUDPS, "exp")
+plot(f2)
+qqp(AUDPS_2015$LShB_AUDPS, "exp")
 
@@
 
-AUDPS_2015$TShB_rating <- AUDPS_2015$TShB_rating + 1
+f1 <- fitdist(AUDPS_2015$TShB_AUDPS, "norm")
+plot(f1)
+qqp(AUDPS_2015$TShB_AUDPS, "norm")
 
-qqp(AUDPS_2015$TShB_rating, "norm")
-
-qqp(AUDPS_2015$TShB_rating, "lnorm")
+f2 <- fitdist(AUDPS_2015$TShB_AUDPS, "exp")
+plot(f2)
+qqp(AUDPS_2015$TShB_AUDPS, "exp")
 
@@
 
-qqp(AUDPS_2016$LShB_rating, "norm")
+f1 <- fitdist(AUDPS_2016$LShB_AUDPS, "norm")
+plot(f1)
+qqp(AUDPS_2016$LShB_AUDPS, "norm")
 
-qqp(AUDPS_2016$LShB_rating, "lnorm")
+f2 <- fitdist(AUDPS_2016$LShB_AUDPS, "exp")
+plot(f2)
+qqp(AUDPS_2015$LShB_AUDPS, "exp")
 
@@
 
-qqp(AUDPS_2016$TShB_rating, "norm")
+f1 <- fitdist(AUDPS_2016$TShB_AUDPS, "norm")
+plot(f1)
+qqp(AUDPS_2016$TShB_AUDPS, "norm")
 
-qqp(AUDPS_2016$TShB_rating, "lnorm")
+f2 <- fitdist(AUDPS_2016$TShB_AUDPS, "exp")
+plot(f2)
+qqp(AUDPS_2015$LShB_AUDPS, "exp")
 
@@
 To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines.
-In this case, for the 2015 data, the leaf data fit a lognormal distribution best, for all others a normal distribution appears to be fine.
+On the y-axis are the observations and on the x-axis the quantiles modelled by the distribution.
+A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit.
+In this case, for the 2015 data, the leaf data fit a lognormal distribution best or exponential, for all others a normal distribution appears to be fine.
+Because of the non-normal residuals of the 2015 leaf sheath blight data we'll look at using something that can handle these data like `MCMCglmm`.

### 2017-03-25 munge/03_preprocess_data.R

@@ -59,5 +59,5 @@ AUDPS$TRT <- factor(AUDPS$TRT, levels = c("AWD_N0", "AWD_N100", "AWD_N120",
 
 # Split the 2015 and 2016 AUDPS data for easier analysis -----------------------
 
-AUDPS_2015 <- AUDPS[which(AUDPS$YEAR == "2015"), ]
-AUDPS_2016 <- AUDPS[which(AUDPS$YEAR == "2016"), ]
+AUDPS_2015 <- droplevels(AUDPS[AUDPS$YEAR == 2015, ])
+AUDPS_2016 <- droplevels(AUDPS[AUDPS$YEAR == 2016, ])

### 2017-03-25 Analysis.Rmd
Correct errors in Analysis.Rmd

@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2015 Leaf Sheath Blight Replicates")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2015 Replicate Posteriors for Leaf Sheath Blight")
 
-# Diagnostic line plots for treatements
+# Diagnostic line plots for treatments
 ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2015 Leaf Sheath Blight Treatments")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2015 Treatment Posteriors for Leaf Sheath Blight")
 
@@
   geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+  geom_abline(intercept = 0, slope = 1) +
+  ggtitle("2015 Leaf Blight Error") +
+  theme_tufte()
 ```
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2015 Tiller Sheath Blight Replicates")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2015 Replicate Posteriors for Tiller Sheath Blight")
 
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2015 Tiller Sheath Blight Treatments")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2015 Treatment Posteriors for Tiller Sheath Blight")
 
@@
   geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+  geom_abline(intercept = 0, slope = 1) +
+  ggtitle("2015 Tiller Blight Error") +
+  theme_tufte()
 ```
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2016 Leaf Sheath Blight Replicates")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2016 Replicate Posteriors for Leaf Sheath Blight")
 
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2016 Leaf Sheath Blight Treatments")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2016 Treatment Posteriors for Leaf Sheath Blight")
 
 # joint distibution of error
-rdf <- data.frame(TShB_lmm_2015$VCV)
+rdf <- data.frame(LShB_lmm_2016$VCV)
 ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
   geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+  geom_abline(intercept = 0, slope = 1) +
+  ggtitle("2016 Leaf Blight Error") +
+  theme_tufte()
 
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2016 Tiller Sheath Blight Replicates")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2016 Replicate Posteriors for Tiller Sheath Blight")
 
@@
   ylab(NULL) +
-  facet_grid(variable ~ .)
+  facet_grid(variable ~ .) +
+  ggtitle("Diagnostic Plots for 2016 Tiller Sheath Blight Treatments")
 
@@
   geom_density() +
-  theme_tufte()
+  theme_tufte() +
+  ggtitle("2016 Treatement Posteriors")
 
 # joint distibution of error
-rdf <- data.frame(TShB_lmm_2015$VCV)
+rdf <- data.frame(TShB_lmm_2016$VCV)
 ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
   geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+  geom_abline(intercept = 0, slope = 1) +
+  ggtitle("2016 Tiller Sheath Blight Error") +
+  theme_tufte()
 ```

### 2017-03-26 Analysis.Rmd
Add notes about analysis to Analysis.Rmd

@@
 ```
+
+Before the analysis, note that due to changes between the years, the analysis
+must be carried out on each year separately. The 2015 data and 2016 data cannot
+be combined due to changes in inoculation methods; there are other changes too,
+but the main one is this. Therefore, the analyses will be conducted separately for
+leaf severity and tiller severity for 2015 dry season and 2016 dry season.
+Comparisons will only be observational and cannot be statistically compared.
 
@@
 
-## Tiller Sheath Blight Severity Model
+## 2016 Tiller Sheath Blight Severity Model
 ```{r}

### 2017-03-26 Analysis.Rmd
Run several iterations of the models for better random errors
Add new custom functions for graphing

Add new diagnostic graphs for random errors

--- 2017-03-25 Analysis.Rmd
@@
 ```
+## Notes on this analysis before starting
 
-## 2015 Leaf Sheath Blight Severity Model
+#### Changes between 2015 and 2016
+
+Before the analysis, note that due to changes between the years, the analysis
+must be carried out on each year separately. The 2015 data and 2016 data cannot
+be combined due to changes in inoculation methods; there are other changes too,
+but the main one is this. Therefore, the analyses will be conducted separately for
+leaf severity and Leaf severity for 2015 dry season and 2016 dry season.
+Comparisons will only be observational and cannot be statistically compared.
+
+#### Random effects
+Fitting the models with the default iterations resulted in some less than
+acceptable models. Because of this, the number of iterations has been increased,
+`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
+smaller errors for random effects and better models.
+
+## 2015
+### 2015 Leaf Sheath Blight Severity Model
 ```{r}
@@
                           prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
                           pr = TRUE)
@@
 reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:10)])
+x <- 1:nrow(reps)
 reps <- melt(reps)
@@
 
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(LShB_lmm_2015$Sol)
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Leaf ShB Reps")
 
-# Diagnostic line plots for replicate
-ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2015 Replicate Posteriors for Leaf ShB Reps")
 
-# Posterior distributions for replicate
-ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
-
-# Diagnostic line plots for treatements
-ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")
 
 # Posterior distributions for treatment
-ggplot(trts, aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+plot_treatment_posteriors(d = trts,
+                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")
 
-# joint distibution of error
+# check random effects
+plotTrace(LShB_lmm_2015$VCV, log = TRUE)
+
+# plot joint distibution of error
 rdf <- data.frame(LShB_lmm_2015$VCV)
-ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
-  geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2015 Leaf ShB Random Error Distribution"))
 ```
 
-## 2015 Tiller Sheath Blight Severity Model
+### 2015 Tiller Sheath Blight Severity Model
 ```{r}
@@
 
-# Diagnostic line plots for replicate
-ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Leaf ShB Reps")
 
-# Posterior distributions for replicate
-ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2015 Replicate Posteriors for Leaf ShB Reps")
 
-# Diagnostic line plots for treatments
-ggplot(data = trts, aes(x = rep(x, 5), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")
 
 # Posterior distributions for treatment
-ggplot(trts, aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+plot_treatment_posteriors(d = trts,
+                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")
 
-# joint distibution of error
+# check random effects
+plotTrace(TShB_lmm_2015$VCV, log = TRUE)
+
+# plot joint distibution of error
 rdf <- data.frame(TShB_lmm_2015$VCV)
-ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
-  geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2015 Leaf ShB Random Error Distribution"))
 ```
@@
 
-## 2016 Leaf Sheath Blight Severity Model
+## 2016
+
+### 2016 Leaf Sheath Blight Severity Model
 ```{r}
@@
                           verbose = FALSE,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
                           prior = eprior,
@@
 
-# Diagnostic line plots for replicate
-ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Leaf ShB Reps")
 
-# Posterior distributions for replicate
-ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2016 Replicate Posteriors for Leaf ShB Reps")
 
-# Diagnostic line plots for treatments
-ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Leaf ShB Treatments")
 
 # Posterior distributions for treatment
-ggplot(trts, aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+plot_treatment_posteriors(d = trts,
+                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")
 
-# joint distibution of error
-rdf <- data.frame(TShB_lmm_2015$VCV)
-ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
-  geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+# check random effects
+plotTrace(LShB_lmm_2016$VCV, log = TRUE)
 
+# plot joint distibution of error
+rdf <- data.frame(LShB_lmm_2015$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2016 Leaf ShB Random Error Distribution"))
 ```
 
-## Tiller Sheath Blight Severity Model
+### 2016 Tiller Sheath Blight Severity Model
 ```{r}
@@
 
-# Diagnostic line plots for replicate
-ggplot(data = reps, aes(x = rep(x, 5), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Leaf ShB Reps")
 
-# Posterior distributions for replicate
-ggplot(reps[reps$variable != "X.Intercept.", ], aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2016 Replicate Posteriors for Leaf ShB Reps")
 
-# Diagnostic line plots for treatments
-ggplot(data = trts, aes(x = rep(x, 3), y = value, group = variable)) +
-  geom_line() +
-  theme_tufte() +
-  xlab("Iteration Number") +
-  ylab(NULL) +
-  facet_grid(variable ~ .)
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2106 Diagnostic Plots for Leaf ShB Treatments")
 
 # Posterior distributions for treatment
-ggplot(trts, aes(x = value, color = variable)) + 
-  geom_density() +
-  theme_tufte()
+plot_treatment_posteriors(d = trts,
+                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")
 
-# joint distibution of error
-rdf <- data.frame(TShB_lmm_2015$VCV)
-ggplot(rdf, aes(x = sqrt(REP), y = sqrt(units))) + 
-  geom_density2d() + 
-  geom_abline(intercept = 0, slope = 1)
+# check random effects
+plotTrace(TShB_lmm_2016$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(TShB_lmm_2016$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2016 Leaf ShB Random Error Distribution"))
 ```
+
+# Conclusions
+
+The models all appear to be good fits after increasing the number of iterations.
+None of the treatments in either year, 2015 or 2016, were significant. The
+see `pMCMC` values and also posterior graphs. There is a large amount of overlap
+in all of the posterior graphs.

### 2017-03-26 lib/helpers.R

@@ -2,3 +2,42 @@ helper.function <- function()
 {
   return(1)
 }
+
+plot_diagnostic_lines <- function(d, x, title) {
+
+  # Diagnostic line plots for replicate
+  ggplot(data = d, aes(
+    x = rep(x, length(unique(d$variable))),
+    y = value,
+    group = variable
+  )) +
+    geom_line() +
+    theme_tufte() +
+    xlab("Iteration Number") +
+    ylab(NULL) +
+    facet_grid(variable ~ .) +
+    ggtitle(paste(title))
+}
+
+plot_replicate_posteriors <- function(d, title) {
+  ggplot(d[d$variable != "X.Intercept.",], aes(x = value, color = variable)) +
+    geom_density() +
+    theme_tufte() +
+    ggtitle(paste(title))
+}
+
+
+plot_treatment_posteriors <- function(d, title) {
+  ggplot(data = d, aes(x = value, color = variable)) +
+    geom_density() +
+    theme_tufte() +
+    ggtitle(paste(title))
+}
+
+plot_joint_random_error_dist <- function(d, title) {
+  ggplot(d, aes(x = sqrt(REP), y = sqrt(units))) +
+    geom_density2d() +
+    geom_abline(intercept = 0, slope = 1) +
+    ggtitle(paste(title)) +
+    theme_tufte()
+}

### 2017-03-27 Analysis.Rmd
Add standard deviation
sd for blight evaluations is now in final data frames and initial data
visualisations

Remove "TODO" file

Fix plot titles that were incorrectly labeled "Leaf" when they should
read "Tiller"

@@
                       x = x,
-                      title = "2015 Diagnostic Plots for Leaf ShB Reps")
+                      title = "2015 Diagnostic Plots for Tiller ShB Reps")
 
@@
 plot_replicate_posteriors(d = reps,
-                          title = "2015 Replicate Posteriors for Leaf ShB Reps")
+                          title = "2015 Replicate Posteriors for Tiller ShB Reps")
 
@@
                       x = x,
-                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")
+                      title = "2015 Diagnostic Plots for Tiller ShB Treatments")
 
@@
 plot_treatment_posteriors(d = trts,
-                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")
+                          title = "2015 Treatment Posteriors for Tiller ShB Treatments")
 
@@
 plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Leaf ShB Random Error Distribution"))
+                             title = ("2015 Tiller ShB Random Error Distribution"))
 ```
@@
                       x = x,
-                      title = "2016 Diagnostic Plots for Leaf ShB Reps")
+                      title = "2016 Diagnostic Plots for Tiller ShB Reps")
 
@@
 plot_replicate_posteriors(d = reps,
-                          title = "2016 Replicate Posteriors for Leaf ShB Reps")
+                          title = "2016 Replicate Posteriors for Tiller ShB Reps")
 
@@
                       x = x,
-                      title = "2106 Diagnostic Plots for Leaf ShB Treatments")
+                      title = "2106 Diagnostic Plots for Tiller ShB Treatments")
 
@@
 plot_treatment_posteriors(d = trts,
-                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")
+                          title = "2016 Treatment Posteriors for Tiller ShB Treatments")
 
@@
 plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Leaf ShB Random Error Distribution"))
+                             title = ("2016 Tiller ShB Random Error Distribution"))
 ```

### 2017-03-27 munge/01_preprocess_2015_data.R

@@ -18,7 +18,7 @@ reformat <- function(files) {
     gather(TShB, TShB_rating, starts_with("SHB")) %>%
     gather(GL, GL_value, starts_with("GL")) %>%
     gather(DL, DL_value, starts_with("DL")) %>%
-    summarise_each(funs(mean),
+    summarise_each(funs(mean, sd),
                    NTIL,
                    NTShB,
                    LShB_rating,
@@ -26,7 +26,7 @@ reformat <- function(files) {
                    GL_value,
                    DL_value)
 
-  x[, 4:9] <- round(x[, 4:9], 2)
+  x[, 4:9] <- round(x[, 4:15], 2)
 
   if (files == "data/DS2015_Raw_22DAI.csv") {
     DATE <- rep(as.Date("2015-02-12", origin = "1970-01-01"),
@@ -79,12 +79,14 @@ DS2015 <-
                                       NRTE,
                                       REP,
                                       TRT,
-                                      NTIL,
-                                      NTShB,
-                                      LShB_rating,
-                                      TShB_rating,
-                                      GL_value,
-                                      DL_value)
+                                      NTIL_mean,
+                                      NTShB_mean,
+                                      LShB_rating_mean,
+                                      LShB_rating_sd,
+                                      TShB_rating_mean,
+                                      TShB_rating_sd,
+                                      GL_value_mean,
+                                      DL_value_mean)
 
 DS2015$YEAR <- year(DS2015$DATE)
 

### 2017-03-27 munge/02-preprocess_2016_data.R

@@ -113,7 +113,7 @@ DS2016 <-
   gather(LShB, LShB_rating, starts_with("SL")) %>%
   gather(GL, GL_value, starts_with("GL")) %>%
   gather(DL, DL_value, starts_with("DL")) %>%
-  summarise_each(funs(mean),
+  summarise_each(funs(mean, sd),
                  NTIL,
                  NTShB,
                  LShB_rating,
@@ -125,12 +125,14 @@ DS2016 <-
   DS2016 %>%
   group_by(DATE, ASMT, REP, TRT, WMGT, NRTE) %>%
   summarise_each(funs(mean),
-                 NTIL,
-                 NTShB,
-                 LShB_rating,
-                 TShB_rating,
-                 GL_value,
-                 DL_value)
+                 NTIL_mean,
+                 NTShB_mean,
+                 LShB_rating_mean,
+                 LShB_rating_sd,
+                 TShB_rating_mean,
+                 TShB_rating_sd,
+                 GL_value_mean,
+                 DL_value_mean)
 
 # arrange columns to be in same order in both data frames
 DS2016 <-
@@ -140,15 +142,17 @@ DS2016 <-
                            NRTE,
                            REP,
                            TRT,
-                           NTIL,
-                           NTShB,
-                           LShB_rating,
-                           TShB_rating,
-                           GL_value,
-                           DL_value)
+                           NTIL_mean,
+                           NTShB_mean,
+                           LShB_rating_mean,
+                           LShB_rating_sd,
+                           TShB_rating_mean,
+                           TShB_rating_sd,
+                           GL_value_mean,
+                           DL_value_mean)
 
-cols <- c(7:12)
-DS2016[, cols] = apply(DS2016[, cols], 2, function(x)
+cols <- c(7:14)
+DS2016[, cols] <- apply(DS2016[, cols], 2, function(x)
   round(x, 2))
 
 DS2016$YEAR <- year(DS2016$DATE)

### 2017-03-27 munge/03_preprocess_data.R

@@ -33,14 +33,27 @@ RAW_data <- AUDPS <- as_tibble(rbind(as.data.frame(DS2015),
 
 # Calculate AUDPS (Simco and Piepho 2012, DOI: 10.1094/PHYTO-07-11-0216) -------
 
+mean_sd <-
+  AUDPS %>%
+  group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
+  summarise_each(funs(mean),
+                 LShB_rating_sd,
+                 TShB_rating_sd)
+
+cols <- c(7:8)
+mean_sd[, cols] <- apply(mean_sd[, cols], 2, function(x)
+  round(x, 2))
+
 AUDPS <-
   AUDPS %>%
   group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
   summarise_each(funs(audps(., dates = DAYS)),
-                 LShB_rating,
-                 TShB_rating)
+                 LShB_rating_mean,
+                 TShB_rating_mean)
 
-AUDPS$LShB_rating <- round(AUDPS$LShB_rating, 2)
+AUDPS$LShB_rating_mean <- round(AUDPS$LShB_rating_mean, 2)
+
+AUDPS <- left_join(AUDPS, mean_sd)
 
 AUDPS$YEAR <- as.factor(AUDPS$YEAR)
 AUDPS$WMGT <- as.factor(AUDPS$WMGT)
@@ -48,8 +61,8 @@ AUDPS$NRTE <- as.factor(AUDPS$NRTE)
 AUDPS$TRT <- as.factor(AUDPS$TRT)
 AUDPS$REP <- as.factor(AUDPS$REP)
 
-AUDPS <- plyr::rename(AUDPS, c("LShB_rating" = "LShB_AUDPS",
-                               "TShB_rating" = "TShB_AUDPS"))
+AUDPS <- plyr::rename(AUDPS, c("LShB_rating_mean" = "LShB_AUDPS",
+                               "TShB_rating_mean" = "TShB_AUDPS"))
 
 AUDPS$NRTE <- factor(AUDPS$NRTE, levels = c(0, 100, 120, 60, 180))
 AUDPS$TRT <- factor(AUDPS$TRT, levels = c("AWD_N0", "AWD_N100", "AWD_N120",

### 2017-03-27 munge/04_visualise_data.R

@@ -1,5 +1,5 @@
-# density plot of LShB_rating data ---------------------------------------------
-ggplot(RAW_data, aes(x = LShB_rating, linetype = as.factor(YEAR))) +
+# density plot of LShB_rating_mean data ----------------------------------------
+ggplot(RAW_data, aes(x = LShB_rating_mean, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                    alpha = 0.5) +
   viridis::scale_fill_viridis(discrete = TRUE,
@@ -8,10 +8,26 @@ ggplot(RAW_data, aes(x = LShB_rating, linetype = as.factor(YEAR))) +
   facet_grid(WMGT ~ NRTE) +
   ggtitle("Leaf Sheath Blight Severity Rating") +
   theme_tufte()
-ggsave("graphs/LShB_rating.png", width = 4, height = 4)
+ggsave("graphs/LShB_rating_mean.png", width = 4, height = 4)
 
-# density plot of TShB_rating data ---------------------------------------------
-ggplot(RAW_data, aes(x = TShB_rating, linetype = as.factor(YEAR))) +
+# density plot of LShB_rating_sd data ------------------------------------------
+
+ggplot(RAW_data, aes(x = LShB_rating_sd, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  facet_grid(WMGT ~ NRTE) +
+  ggtitle("Leaf Sheath Blight Severity Rating Std Dev.") +
+  theme_tufte() +
+  theme(axis.text.x = element_text(size = 8,
+                                   angle = 45,
+                                   hjust = 1))
+ggsave("graphs/LShB_rating_sd.png", width = 4, height = 4)
+
+# density plot of TShB_rating_mean data ----------------------------------------
+ggplot(RAW_data, aes(x = TShB_rating_mean, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                alpha = 0.5) +
   viridis::scale_fill_viridis(discrete = TRUE,
@@ -20,10 +36,22 @@ ggplot(RAW_data, aes(x = TShB_rating, linetype = as.factor(YEAR))) +
[…]

### 2017-03-27 munge/04_visualise_data.R
Correct graphs/README.md; remove extra graphs
Fix the url of the image files for the standard deviation and mean
density plots

@@ -11,7 +11,6 @@ ggplot(RAW_data, aes(x = LShB_rating_mean, linetype = as.factor(YEAR))) +
 ggsave("graphs/LShB_rating_mean.png", width = 4, height = 4)
 
 # density plot of LShB_rating_sd data ------------------------------------------
-
 ggplot(RAW_data, aes(x = LShB_rating_sd, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                alpha = 0.5) +

### 2017-03-28 Analysis.Rmd
Minor edits to text in Analysis and main README
Add analysis for tiller sheath blight incidence and corresponding graphs

--- 2017-03-26 Analysis.Rmd
@@
 
-#### Random effects
+#### Iterations
 Fitting the models with the default iterations resulted in some less than
@@
 
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(LShB_lmm_2015$Sol)
+
 # diagnostic line plots for replicate
@@
                       x = x,
-                      title = "2015 Diagnostic Plots for Leaf ShB Reps")
+                      title = "2015 Diagnostic Plots for Replicates, Leaf ShB Severity")
 
@@
 plot_replicate_posteriors(d = reps,
-                          title = "2015 Replicate Posteriors for Leaf ShB Reps")
+                          title = "2015 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
 
@@
                       x = x,
-                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")
+                      title = "2015 Diagnostic Plots for Treatments, Leaf ShB Severity")
 
@@
 plot_treatment_posteriors(d = trts,
-                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")
+                          title = "2015 Posteriors for Treatments, Leaf ShB Severity")
 
@@
 plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Leaf ShB Random Error Distribution"))
+                             title = ("2015 Random Error Distribution for Leaf ShB Severity"))
 ```
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
+TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 
-summary(TShB_lmm_2015)
+summary(TShB_severity_lmm_2015)
 
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_lmm_2015$Sol[, 2:6])
+trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
 names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
@@
 # Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_lmm_2015$Sol)
+x <- 1:nrow(TShB_severity_lmm_2015$Sol)
 
@@
                       x = x,
-                      title = "2015 Diagnostic Plots for Leaf ShB Reps")
+                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Severity")
 
@@
 plot_replicate_posteriors(d = reps,
-                          title = "2015 Replicate Posteriors for Leaf ShB Reps")
+                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
 
@@
                       x = x,
-                      title = "2015 Diagnostic Plots for Leaf ShB Treatments")
+                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Severity")
 
@@
 plot_treatment_posteriors(d = trts,
-                          title = "2015 Treatment Posteriors for Leaf ShB Treatments")
+                          title = "2015 Posteriors for Treatments, Tiller ShB Severity")
 
 # check random effects
-plotTrace(TShB_lmm_2015$VCV, log = TRUE)
+plotTrace(TShB_severity_lmm_2015$VCV, log = TRUE)
 
 # plot joint distibution of error
-rdf <- data.frame(TShB_lmm_2015$VCV)
+rdf <- data.frame(TShB_severity_lmm_2015$VCV)
 plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Leaf ShB Random Error Distribution"))
+                             title = ("2015 Random Error Distribution for Tiller ShB Severity"))
+```
+
+### 2015 Tiller Sheath Blight Incidence Model
+```{r}
+
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, ~REP, 
+                          data = as.data.frame(AUDPS_2015),
+                          verbose = FALSE,
+                          prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
+                          pr = TRUE)
+
+summary(TShB_incidence_lmm_2015)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
+names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
+names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(TShB_incidence_lmm_2015$Sol)
+
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Incidence")
+
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")
+
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Incidence")
+
+# Posterior distributions for treatment
+plot_treatment_posteriors(d = trts,
+                          title = "2015 Posteriors for Treatments, Tiller ShB Incidence")
+
+# check random effects
+plotTrace(TShB_incidence_lmm_2015$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(TShB_incidence_lmm_2015$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2015 Random Error Distribution for Tiller ShB Incidence"))
 ```
@@
                       x = x,
-                      title = "2016 Diagnostic Plots for Leaf ShB Reps")
+                      title = "2016 Diagnostic Plots for Replicates, Leaf ShB Severity")
 
@@
 plot_replicate_posteriors(d = reps,
-                          title = "2016 Replicate Posteriors for Leaf ShB Reps")
+                          title = "2016 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
 
@@
                       x = x,
-                      title = "2016 Diagnostic Plots for Leaf ShB Treatments")
+                      title = "2016 Diagnostic Plots for Treatments, Leaf ShB Severity")
 
@@
 plot_treatment_posteriors(d = trts,
-                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")
+                          title = "2016 Posteriors for Treatments, Leaf ShB Severity")
 
@@
 # plot joint distibution of error
-rdf <- data.frame(LShB_lmm_2015$VCV)
+rdf <- data.frame(LShB_lmm_2016$VCV)
 plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Leaf ShB Random Error Distribution"))
+                             title = ("2016 Random Error Distribution for Leaf ShB Severity"))
 ```
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
+TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
                           data = as.data.frame(AUDPS_2016),
@@
 
-summary(TShB_lmm_2016)
+summary(TShB_severity_lmm_2016)
 
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_lmm_2016$Sol[, 2:4])
+trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
 names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
@@
 # Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_lmm_2016$Sol)
+x <- 1:nrow(TShB_severity_lmm_2016$Sol)
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Severity")
+
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
+
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Severity")
+
+# Posterior distributions for treatment
+plot_treatment_posteriors(d = trts,
+                          title = "2016 Posteriors for Treatments, Tiller ShB Severity")
+
+# check random effects
+plotTrace(TShB_severity_lmm_2016$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(TShB_severity_lmm_2016$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2016 Random Error Distribution for Tiller ShB Severity"))
+```
+
+### 2016 Tiller Sheath Blight Incidence Model
+```{r}
+
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, ~REP, 
+                          data = as.data.frame(AUDPS_2016),
+                          verbose = FALSE,
+                          prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
+                          pr = TRUE)
+
+summary(TShB_incidence_lmm_2016)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:8)])
+reps <- melt(reps)
+
+trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
+names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
+names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(TShB_incidence_lmm_2016$Sol)
 
@@
                       x = x,
-                      title = "2016 Diagnostic Plots for Leaf ShB Reps")
+                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Incidence")
 
@@
 plot_replicate_posteriors(d = reps,
-                          title = "2016 Replicate Posteriors for Leaf ShB Reps")
+                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")
 
@@
                       x = x,
-                      title = "2106 Diagnostic Plots for Leaf ShB Treatments")
+                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Incidence")
 
@@
 plot_treatment_posteriors(d = trts,
-                          title = "2016 Treatment Posteriors for Leaf ShB Treatments")
+                          title = "2016 Posteriors for Treatments, Tiller ShB Incidence")
 
 # check random effects
-plotTrace(TShB_lmm_2016$VCV, log = TRUE)
+plotTrace(TShB_incidence_lmm_2016$VCV, log = TRUE)
 
 # plot joint distibution of error
-rdf <- data.frame(TShB_lmm_2016$VCV)
+rdf <- data.frame(TShB_incidence_lmm_2016$VCV)
 plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Leaf ShB Random Error Distribution"))
+                             title = ("2016 Random Error Distribution for Tiller ShB Incidence"))
 ```

### 2017-03-28 munge/01_preprocess_2015_data.R

@@ -4,7 +4,7 @@ files <-
   list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)
 
 reformat <- function(files) {
-  x <- read_csv(files)
+  x <- read_csv(files[1])
   x[is.na(x)] <- 0
 
   # ensure that all leaf sheath blight observations are numeric, not character
@@ -14,6 +14,7 @@ reformat <- function(files) {
   x <-
     x %>%
     group_by(REP, WMGT, NRTE) %>%
+    mutate(TShB_incidence = NTShB/NTIL) %>%
     gather(LShB, LShB_rating, starts_with("SL")) %>%
     gather(TShB, TShB_rating, starts_with("SHB")) %>%
     gather(GL, GL_value, starts_with("GL")) %>%
@@ -23,10 +24,11 @@ reformat <- function(files) {
                    NTShB,
                    LShB_rating,
                    TShB_rating,
+                   TShB_incidence,
                    GL_value,
                    DL_value)
 
-  x[, 4:9] <- round(x[, 4:15], 2)
+  x[, 4:17] <- round(x[, 4:17], 2)
 
   if (files == "data/DS2015_Raw_22DAI.csv") {
     DATE <- rep(as.Date("2015-02-12", origin = "1970-01-01"),
@@ -85,6 +87,8 @@ DS2015 <-
                                       LShB_rating_sd,
                                       TShB_rating_mean,
                                       TShB_rating_sd,
+                                      TShB_incidence_mean,
+                                      TShB_incidence_sd,
                                       GL_value_mean,
                                       DL_value_mean)
 

### 2017-03-28 munge/02-preprocess_2016_data.R

@@ -110,6 +110,7 @@ DS2016[, cols] = apply(DS2016[, cols], 2, function(x)
 DS2016 <-
   DS2016 %>%
   group_by(DATE, ASMT, REP, TRT, WMGT, NRTE, SMPL, HILL) %>%
+  mutate(TShB_incidence = NTShB/NTIL) %>%
   gather(LShB, LShB_rating, starts_with("SL")) %>%
   gather(GL, GL_value, starts_with("GL")) %>%
   gather(DL, DL_value, starts_with("DL")) %>%
@@ -118,6 +119,7 @@ DS2016 <-
                  NTShB,
                  LShB_rating,
                  TShB_rating,
+                 TShB_incidence,
                  GL_value,
                  DL_value)
 
@@ -131,6 +133,8 @@ DS2016 <-
                  LShB_rating_sd,
                  TShB_rating_mean,
                  TShB_rating_sd,
+                 TShB_incidence_mean,
+                 TShB_incidence_sd,
                  GL_value_mean,
                  DL_value_mean)
 
@@ -148,8 +152,11 @@ DS2016 <-
                            LShB_rating_sd,
                            TShB_rating_mean,
                            TShB_rating_sd,
+                           TShB_incidence_mean,
+                           TShB_incidence_sd,
                            GL_value_mean,
                            DL_value_mean)
+
 
 cols <- c(7:14)
 DS2016[, cols] <- apply(DS2016[, cols], 2, function(x)

### 2017-03-28 munge/03_preprocess_data.R

@@ -38,7 +38,8 @@ mean_sd <-
   group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
   summarise_each(funs(mean),
                  LShB_rating_sd,
-                 TShB_rating_sd)
+                 TShB_rating_sd,
+                 TShB_incidence_sd)
 
 cols <- c(7:8)
 mean_sd[, cols] <- apply(mean_sd[, cols], 2, function(x)
@@ -49,9 +50,8 @@ AUDPS <-
   group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
   summarise_each(funs(audps(., dates = DAYS)),
                  LShB_rating_mean,
-                 TShB_rating_mean)
-
-AUDPS$LShB_rating_mean <- round(AUDPS$LShB_rating_mean, 2)
+                 TShB_rating_mean,
+                 TShB_incidence_mean)
 
 AUDPS <- left_join(AUDPS, mean_sd)
 

### 2017-03-28 munge/04_visualise_data.R

@@ -49,6 +49,36 @@ ggplot(RAW_data, aes(x = TShB_rating_sd, linetype = as.factor(YEAR))) +
   theme_tufte()
 ggsave("graphs/TShB_rating_sd.png", width = 4, height = 4)
 
+# density plot of TShB_incidence_mean data ----------------------------------------
+ggplot(RAW_data, aes(x = TShB_incidence_mean, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  facet_grid(WMGT ~ NRTE) +
+  ggtitle("Tiller Sheath Blight Incidence") +
+  theme_tufte() +
+theme(axis.text.x = element_text(size = 8,
+                                 angle = 45,
+                                 hjust = 1)) +
+ggsave("graphs/TShB_incidence_mean.png", width = 4, height = 4)
+
+# density plot of TShB_incidence_sd data ------------------------------------------
+ggplot(RAW_data, aes(x = TShB_incidence_sd, linetype = as.factor(YEAR))) +
+  geom_density(aes(fill = as.factor(YEAR)),
+               alpha = 0.5) +
+  viridis::scale_fill_viridis(discrete = TRUE,
+                              name = "Year") +
+  scale_linetype(name = "Year") +
+  facet_grid(WMGT ~ NRTE) +
+  ggtitle("Tiller Sheath Blight Incidence Std Dev.") +
+  theme_tufte() +
+  theme(axis.text.x = element_text(size = 8,
+                                   angle = 45,
+                                   hjust = 1)) +
+ggsave("graphs/TShB_incidence_sd.png", width = 4, height = 4)
+
 # density plot of green leaf data ----------------------------------------------
 ggplot(RAW_data, aes(x = GL_value_mean, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
@@ -150,7 +180,8 @@ ggplot(AUDPS, aes(x = TRT, y = TShB_AUDPS)) +
   viridis::scale_color_viridis(discrete = TRUE,
                                name = "Year") +
   viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
+                              name = "Year",
+                              option = "A") +
   theme_tufte() +
[…]

### 2017-03-28 Probability_distribution_checks.Rmd
add probability plots for tiller sheath blight incidence

@@
 
-## 2015 Check probability distribution fit for tiller sheath blight
+## 2015 Check probability distribution fit for tiller sheath blight severity
 
@@
 qqp(AUDPS_2015$TShB_AUDPS, "exp")
+
+```
+
+## 2015 Check probability distribution fit for tiller sheath blight incidence
+
+```{r, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS_2015$TShB_incidence_mean, "norm")
+plot(f1)
+qqp(AUDPS_2015$TShB_incidence_mean, "norm")
+
+f2 <- fitdist(AUDPS_2015$TShB_incidence_mean, "exp")
+plot(f2)
+qqp(AUDPS_2015$TShB_incidence_mean, "exp")
 
@@
 
+## 2016 Check probability distribution fit for tiller sheath blight incidence
+
+```{r, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS_2016$TShB_incidence_mean, "norm")
+plot(f1)
+qqp(AUDPS_2016$TShB_incidence_mean, "norm")
+
+f2 <- fitdist(AUDPS_2016$TShB_incidence_mean, "exp")
+plot(f2)
+qqp(AUDPS_2016$TShB_incidence_mean, "exp")
+
+```
+
 ## Conclusions

### 2017-03-28 munge/04_visualise_data.R

@@ -212,7 +212,7 @@ ggplot(AUDPS, aes(x = TRT, y = TShB_AUDPS)) +
 ggsave("graphs/TShB_AUDPS_boxplot.png", width = 6, height = 4)
 
 
-# boxplots of tiller sheath blight AUDPS data ----------------------------------
+# boxplots of tiller sheath blight incidence data ------------------------------
 ggplot(AUDPS, aes(x = as.factor(TRT), y = TShB_incidence_mean)) +
   geom_boxplot(aes(fill = YEAR, colour = YEAR)) +
   viridis::scale_color_viridis(discrete = TRUE,

### 2017-04-05 reports/Effects_of_AWD_N_on_SB.rmd
Start fleshing out M&M; add references for analysis

@@
 ---
-output: 
-  pdf_document:
-    citation_package: natbib
-    keep_tex: true
-    fig_caption: true
-    latex_engine: pdflatex
-    template: ~/Development/svm-r-markdown-templates/svm-latex-ms.tex
 title: "Effects of Alternate Wetting and Drying Irrigation and Nitrogen Fertilization on Sheath Blight of Rice"
@@
 author:
-- name: Adam H. Sparks
-  affiliation: Centre for Crop Health, University of Southern Queensland, West St., Toowoomba, QLD 4350, Australia
-- name: Nancy P. Castilla
-  affiliation: Crop and Environmental Sciences Division, International Rice Research Institute, Los Baños, Laguna 4031, Philippines
-abstract: "Abstract limited to 200 words in one paragraph."
-keywords: "*Rhizoctonia solani*"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
-geometry: margin=1in
-fontfamily: mathpazo
-fontsize: 12pt
-
-# spacing: double
-bibliography: ~/Dropbox/master.bib
-biblio-style: apsr
+  - A.H. Sparks and N.P. Castilla
+keywords: "_Rhizoctonia solani_, Irrigation"
+abstract: "First author: University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350, Australia; and second author: International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna 4031, Philippines."
+output:
+  word_document:
+    keep_md: yes
+    reference_docx: Phytopathology_Style_Reference.docx
+  html_document: default
+csl: phytopathology.csl
+bibliography: AWD_N_ShB.bib
 ---
 
-Introduction goes here with no heading
+Corresponding author: Adam H. Sparks; E-mail address: Adam.Sparks@usq.edu.au
+
+______
+
+# Abstract
+
+Water and nitrogen management play vital roles in rice production.
+However, the mismanagement of these two management practices may trigger plant disease epidemics such as sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
+To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes and differing nitrogen treatments in the dry seasons of 2015 and 2016.
+Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
+While we were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season we suggest that further research on this subject is warranted.
+
+______
+
+#####
 
 # Materials and Methods
+## Experimental design
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14.14˚, longitude 121.27˚) in the 2015 and 2016 dry seasons.
+For the 2016 season changes were made to optimize the experiment  based on findings from the 2015 season.
+The changes are detailed following.
+
+### 2015 Dry Season
+Split plot design with irrigation as the main plot treatment and N rate as the split plot treatment.
+The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
+Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub plot for a whole experiment size of 1,152 sq m.
+
+### 2016 Dry Season
+The plot design again was a split plot design with irrigation as the main plot treatment and N rate as the split treatment.
+However, the plot size increased and due to these changes, the sizes of the replicates are not equal as necessitated by the use of a larger area for the experiment.
+The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
+The sub plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m).
+The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m).
+A buffer 0.5m per sub plot was used and the overall experiment size was 3471.6 sq m.
+
+## Data collection and analysis
+
+Data were analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
 
@@
 
-## Data analysis
-
-\pagebreak
-
 # Discussion
 
-# Acknowledgements
+# Acknowledgments
 
-<!--
 # Literature Cited
-\setlength{\parindent}{-0.2in}
-\setlength{\leftskip}{0.2in}
-\setlength{\parskip}{8pt}
-\vspace*{-0.2in}
-\noindent
--->

### 2017-04-05 reports/Effects_of_AWD_N_on_SB.rmd
Clarify wording in 2016 season methods
More edits for clarity to M&M

@@
 For the 2016 season changes were made to optimize the experiment based on findings from the 2015 season.
+Both seasons consisted of split plot design with four replicates where irrigation was the main plot and N rate was the split plot treatent.
 The changes are detailed following.
@@
 ### 2015 Dry Season
-Split plot design with irrigation as the main plot treatment and N rate as the split plot treatment.
 The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
 Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub plot for a whole experiment size of 1,152 sq m.
+The main plot treatments were alternate wetting and drying (AWD) and flooded or farmers' practice.
 
 ### 2016 Dry Season
-The plot design again was a split plot design with irrigation as the main plot treatment and N rate as the split treatment.
-However, the plot size increased and due to these changes, the sizes of the replicates are not equal as necessitated by the use of a larger area for the experiment.
+In 2016 dry season the plot size was increased and due to these changes, the sizes of the replicates are not equal as necessitated by the use of a larger area for the experiment.
 The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).

### 2017-04-07 reports/Effects_of_AWD_N_on_SB.rmd
Edit abstract for clarity; fix spelling in M&M

@@
 Water and nitrogen management play vital roles in rice production.
-However, the mismanagement of these two management practices may trigger plant disease epidemics such as sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
-To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes and differing nitrogen treatments in the dry seasons of 2015 and 2016.
-Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
-While we were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season we suggest that further research on this subject is warranted.
+However, the mismanagement of these two management practices may trigger sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
+To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water saving (alternate wetting and drying) regime and traditional flood irrigation regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
+Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
+We were unable to detect any differences in disease in either experiment due to irrigation regime, N rates or the interaction of the two treatments in either season.
+This suggests that farmers can adopt water saving technologies without risking increased sheath blight incidence.
+We suggest that further cross-cutting research in this area is warranted.
 
@@
 For the 2016 season changes were made to optimize the experiment based on findings from the 2015 season.
-Both seasons consisted of split plot design with four replicates where irrigation was the main plot and N rate was the split plot treatent.
-The changes are detailed following.
+Both seasons consisted of split plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split plot treatment.
+The changes between seasons and experiments are detailed following.
 

### 2017-04-07 reports/Effects_of_AWD_N_on_SB.rmd
Update ZES lat/lon

@@
 ## Experimental design
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14.14˚, longitude 121.27˚) in the 2015 and 2016 dry seasons.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14°11' N, , longitude 121°15' E) in the 2015 and 2016 dry seasons.
 For the 2016 season changes were made to optimize the experiment based on findings from the 2015 season.

### 2017-04-10 doc/APPS/README.Rmd
Knit Word document to share with Nancy and Ole

---
title: Do Alternate Wetting and Drying Irrigation Technologies and Nitrogen Rates
  Affect Rice Sheath Blight?
date: "10 April 2017"
output:
  word_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Adam H Sparks <sup>1</sup> , Nancy P Castilla <sup>2</sup> , Bjoern O Sander <sup>2</sup>

_1.	University of Southern Queensland, Toowoomba, QLD, Australia_  
_2.	Crop and Environmental Sciences Division, International Rice Research Institute, Los Baños, Laguna, Philippines_

Water and nitrogen management play vital roles in rice production. However, the mismanagement of these two management practices may trigger plant disease epidemics such as sheath blight of rice, caused by Rhizoctonia solani, which is favoured by wet conditions, high relative humidity, and high nitrogen fertiliser levels. In order to understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes in the dry seasons of 2015 and 2016. The main plot irrigation treatments in both experiments were: flooded, maintaining 10cm standing water through the season and alternate wetting and drying (AWD) a water saving technology described by the International Rice Research Institute (IRRI). In 2015 the split plots were nitrogen (N) applications applied as 0 kg ha-1, 120 kg ha–1, and 150 kg ha–1 total N. In 2016 changes were made between seasons to address issues that were previously discovered in 2015. In 2016 split plots were N applications at 60 kg ha-1 and 180 kg ha-1 total N. Nitrogen was applied in splits in both seasons. Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill. Five and four disease assessments were made in 2015 and 2016 respectively. Data were analysed using the area under the disease progress stairs (AUDPS) and multivariate generalised linear mixed models. We were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season. Our findings indicate that farmers can safely adopt AWD technology without risk of increasing sheath blight disease.

A/Prof Adam H Sparks leads the summer crop pathology research at USQ in the Centre for Crop Health, previously he worked with the International Rice Research Institute (IRRI) as a plant disease management specialist. Dr Nancy P Castilla works at the International Rice Research Institute (IRRI) as a researcher studying methods to control rice disease and offers training and support for capacity building for national partners. Dr Bjorn Ole Sander works at IRRI  as a scientist in IRRI’s climate change research group with a focus on greenhouse gas (GHG) mitigation technologies, which include alternate wetting and drying.

### 2017-04-10 reports/Effects_of_AWD_N_on_SB.rmd
Add Ole to authors on paper

@@
 ---
-title: "Effects of Alternate Wetting and Drying Irrigation and Nitrogen Fertilization on Sheath Blight of Rice"
+title: "Do Alternate Wetting and Drying Irrigation Technologies and Nitrogen Rates Affect Rice Sheath Blight?"
 thanks: "Replication files are available on the author's Github account (http://github.com/adamhsparks/AWD_N_SB).
@@
 author:
-  - A.H. Sparks and N.P. Castilla
+  - A.H. Sparks and N.P. Castilla and B.O. Sander
 keywords: "_Rhizoctonia solani_, Irrigation"
-abstract: "First author: University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350, Australia; and second author: International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna 4031, Philippines."
+abstract: "First author: University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350, Australia; and second and third authors: International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna 4031, Philippines."
 output:

### 2017-04-12 Analysis.Rmd
Update analysis file with links and instruction for interpretation

@@
 ## Notes on this analysis before starting
+
+#### How to interpret these analyses
+
+For a quick overview, see this thread on Stack Overflow that walks through the output of `summary.MCMCglmm`,
+which is used below. [R: Making sense of the output of a MCMCglmm](http://stackoverflow.com/questions/20993643/r-making-sense-of-the-output-of-a-mcmcglmm)
+
+The MCMCglmm documentation is more in-depth but should still be referenced.
+```{r, eval=FALSE}
+library(MCMCglmm)
+vignette("Overview")
+vignette("CourseNotes")
+```
 

### 2017-04-14 Analysis.Rmd
Add nested random effects analysis
Analyse the nested efffect of the main plot with replicate

Also name R chunks in both Rmd files

@@
 ## Notes on this analysis before starting
+
+These analyses DO NOT nest the main plot effect as a random effect with the replicate.
 
@@
 ### 2015 Leaf Sheath Blight Severity Model
-```{r}
+```{r 2015_LShB}
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE, ~REP, 
+LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
+                          random = ~REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 ### 2015 Tiller Sheath Blight Severity Model
-```{r}
+```{r 2015_TShB}
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
+TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
+                                   random = ~REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 ### 2015 Tiller Sheath Blight Incidence Model
-```{r}
+```{r 2015_TShB_incidence}
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, ~REP, 
+TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
+                                    random = ~REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 ### 2016 Leaf Sheath Blight Severity Model
-```{r}
+```{r 2016_LShB}
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE, ~REP, 
+LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
+                          random = ~REP, 
                           data = as.data.frame(AUDPS_2016),
@@
 ### 2016 Tiller Sheath Blight Severity Model
-```{r}
+```{r 2016_TShB}
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE, ~REP, 
+TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
+                                   random = ~REP, 
                           data = as.data.frame(AUDPS_2016),
@@
 ### 2016 Tiller Sheath Blight Incidence Model
-```{r}
+```{r 2016_TShB_incidence}
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, ~REP, 
+TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
+                                    random = ~REP, 
                           data = as.data.frame(AUDPS_2016),

### 2017-04-14 Analysis_nested_effects.Rmd
Add nested random effects analysis
Analyse the nested efffect of the main plot with replicate

Also name R chunks in both Rmd files

--- 2017-04-14 Analysis.Rmd
@@
 ---
-title: "Analysis"
+title: "Analysis with nested effects"
 output: github_document
@@
 
-These analyses DO NOT nest the main plot effect as a random effect with the replicate.
+These analyses nest the main plot effect as a random effect with the replicate.
 
@@
 The MCMCglmm documentation is more in-depth but should still be referenced.
-```{r, eval=FALSE}
+```{r MCMCglmm, eval=FALSE}
 library(MCMCglmm)
@@
 LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
-                          random = ~REP, 
+                          random = ~REP:WMGT, 
                           data = as.data.frame(AUDPS_2015),
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:14)])
 x <- 1:nrow(reps)
@@
 rdf <- data.frame(LShB_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
+plot_joint_random_error_dist_nested(d = rdf,
                              title = ("2015 Random Error Distribution for Leaf ShB Severity"))
@@
 TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP, 
+                                   random = ~REP:WMGT, 
                           data = as.data.frame(AUDPS_2015),
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:14)])
 reps <- melt(reps)
@@
 rdf <- data.frame(TShB_severity_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
+plot_joint_random_error_dist_nested(d = rdf,
                              title = ("2015 Random Error Distribution for Tiller ShB Severity"))
@@
 TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
-                                    random = ~REP, 
+                                    random = ~REP:WMGT, 
                           data = as.data.frame(AUDPS_2015),
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:14)])
 reps <- melt(reps)
@@
 rdf <- data.frame(TShB_incidence_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
+plot_joint_random_error_dist_nested(d = rdf,
                              title = ("2015 Random Error Distribution for Tiller ShB Incidence"))
@@
 LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
-                          random = ~REP, 
+                          random = ~REP:WMGT, 
                           data = as.data.frame(AUDPS_2016),
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:12)])
 reps <- melt(reps)
@@
 rdf <- data.frame(LShB_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
+plot_joint_random_error_dist_nested(d = rdf,
                              title = ("2016 Random Error Distribution for Leaf ShB Severity"))
@@
 TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP, 
+                                   random = ~REP:WMGT, 
                           data = as.data.frame(AUDPS_2016),
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:12)])
 reps <- melt(reps)
@@
 rdf <- data.frame(TShB_severity_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
+plot_joint_random_error_dist_nested(d = rdf,
                              title = ("2016 Random Error Distribution for Tiller ShB Severity"))
@@
 TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
-                                    random = ~REP, 
+                                    random = ~REP:WMGT, 
                           data = as.data.frame(AUDPS_2016),
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:12)])
 reps <- melt(reps)
@@
 rdf <- data.frame(TShB_incidence_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
+plot_joint_random_error_dist_nested(d = rdf,
                              title = ("2016 Random Error Distribution for Tiller ShB Incidence"))

### 2017-04-14 lib/helpers.R

@@ -46,6 +46,14 @@ plot_treatment_posteriors <- function(d, title) {
     ggtitle(paste(title))
 }
 
+plot_joint_random_error_dist_nested <- function(d, title) {
+  ggplot(d, aes(x = sqrt(REP.WMGT), y = sqrt(units))) +
+    geom_density2d() +
+    geom_abline(intercept = 0, slope = 1) +
+    ggtitle(paste(title)) +
+    theme_tufte()
+}
+
 plot_joint_random_error_dist <- function(d, title) {
   ggplot(d, aes(x = sqrt(REP), y = sqrt(units))) +
     geom_density2d() +

### 2017-04-21 Analysis.Rmd
Rearrange nested analysis
Nest REP within WMGT

Remove Analysis.Rmd and move Analysis_nested_effects.Rmd to Analysis.Rmd

Add R session info to analysis document

Rotate facet ribbon text, names no longer need to be changed/shortened

@@
 
+## Setup
+Use set seed for reproducibility.
+
+```{r set_seed}
+set.seed(27)
+```
+
 ## 2015
@@
 LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
-                          random = ~REP, 
+                          random = ~WMGT:REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
-names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
-names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
 trts <- melt(trts)
@@
 TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP, 
+                                   random = ~WMGT:REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
-names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
-names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
 trts <- melt(trts)
@@
 TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
-                                    random = ~REP, 
+                                    random = ~WMGT:REP, 
                           data = as.data.frame(AUDPS_2015),
@@
 trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
-names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
-names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
 trts <- melt(trts)
@@
 LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
-                          random = ~REP, 
+                          random = ~WMGT:REP, 
                           data = as.data.frame(AUDPS_2016),
@@
 trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
-names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
 trts <- melt(trts)
@@
 TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP, 
+                                   random = ~WMGT:REP, 
                           data = as.data.frame(AUDPS_2016),
@@
 trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
-names(trts)[names(trts) == "WMGTFLD.NRTE180"] <- "FLD.NRTE180"
 trts <- melt(trts)
@@
 TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
-                                    random = ~REP, 
+                                    random = ~WMGT:REP, 
                           data = as.data.frame(AUDPS_2016),
@@
 trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
-names(trts)[names(trts) == "WMGTFLD.NRTE100"] <- "FLD.NRTE100"
-names(trts)[names(trts) == "WMGTFLD.NRTE120"] <- "FLD.NRTE120"
 trts <- melt(trts)
@@
 
-The models all appear to be good fits after increasing the number of iterations.
+The models all appear to be good fits.
+
+None of the diagnostic plots show any signs of autocorrelation or any other obvious patterns.
+
 None of the treatments in either year, 2015 or 2016, were significant. The
@@
 in all of the posterior graphs.
+
+The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernable patterns.
+
+The random effects are all fairly equally distributed except for 2016 tiller sheath blight severity where water management:replicate has a larger effect.
+This is not surprising given that the plot and replicate sizes were different in 2016 due to the use of two fields in the IRRI experiment station, see the [2016 plot layout plan](https://github.com/adamhsparks/AWD_ShB_Interaction/blob/master/doc/Metadata/2016%20AWD%20ShB%20Metadata/ExptLayoutAWD2016.pdf).
+
+# R Session Info
+```{r session_info}
+sessionInfo()
+```

### 2017-04-21 lib/helpers.R

@@ -16,6 +16,7 @@ plot_diagnostic_lines <- function(d, x, title) {
     xlab("Iteration Number") +
     ylab(NULL) +
     facet_grid(variable ~ .) +
+    theme(strip.text.y = element_text(angle = 0)) +
     ggtitle(paste(title))
 }
 
@@ -47,7 +48,7 @@ plot_treatment_posteriors <- function(d, title) {
 }
 
 plot_joint_random_error_dist_nested <- function(d, title) {
-  ggplot(d, aes(x = sqrt(REP.WMGT), y = sqrt(units))) +
+  ggplot(d, aes(x = sqrt(WMGT.REP), y = sqrt(units))) +
     geom_density2d() +
     geom_abline(intercept = 0, slope = 1) +
     ggtitle(paste(title)) +

### 2017-04-24 Analysis.Rmd
Formatting in text
Update packages with packrat and revise analysis

--- 2017-04-14 Analysis.Rmd
@@
 ---
-title: "Analysis"
+title: "Analysis of split plot design using MCMCglmm"
 output: github_document
@@
 
-These analyses DO NOT nest the main plot effect as a random effect with the replicate.
-
 #### How to interpret these analyses
@@
 smaller errors for random effects and better models.
+
+## Setup
+Use `set.seed()` for reproducibility.
+
+```{r set_seed}
+set.seed(27)
+```
 

### 2017-04-24 lib/helpers.R

@@ -47,14 +47,6 @@ plot_treatment_posteriors <- function(d, title) {
     ggtitle(paste(title))
 }
 
-plot_joint_random_error_dist_nested <- function(d, title) {
-  ggplot(d, aes(x = sqrt(WMGT.REP), y = sqrt(units))) +
-    geom_density2d() +
-    geom_abline(intercept = 0, slope = 1) +
-    ggtitle(paste(title)) +
-    theme_tufte()
-}
-
 plot_joint_random_error_dist <- function(d, title) {
   ggplot(d, aes(x = sqrt(REP), y = sqrt(units))) +
     geom_density2d() +

### 2017-04-25 Probability_distribution_checks.Rmd
Revise analysis and data handling
**_THIS IS BEING REVISED_**

The original analysis is unlikely to be the correct approach. The data
are being examined again and a new analysis will be conducted that
accounts for the ordinal scale used for data collection for severity.

The data are now in a tidy data frame and are ready for checking

--- 2017-03-25 Probability_distribution_checks.Rmd
@@
 I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
-As you see in that guide, there are several distributions that can be checked, for my purposes normal or exponential are enough so I won't check the others.
+As you see in that guide, there are several distributions that can be checked.
 
-## 2015 Check probability distribution fit for leaf sheath blight
+## 2015 Check probability distribution fit for tiller sheath blight incidence
 
@@
 
-f1 <- fitdist(AUDPS_2015$LShB_AUDPS, "norm")
+f1 <- fitdist(DS2015$TShB_incidence, "norm")
 plot(f1)
-qqp(AUDPS_2015$LShB_AUDPS, "norm")
+car::qqp(DS2015$TShB_incidence, "norm")
 
-f2 <- fitdist(AUDPS_2015$LShB_AUDPS, "exp")
+f2 <- fitdist(DS2015$TShB_incidence, "exp")
 plot(f2)
-qqp(AUDPS_2015$LShB_AUDPS, "exp")
-
-```
-
-## 2015 Check probability distribution fit for tiller sheath blight
-
-```{r, results='hide', message=FALSE, warning=FALSE}
-
-f1 <- fitdist(AUDPS_2015$TShB_AUDPS, "norm")
-plot(f1)
-qqp(AUDPS_2015$TShB_AUDPS, "norm")
-
-f2 <- fitdist(AUDPS_2015$TShB_AUDPS, "exp")
-plot(f2)
-qqp(AUDPS_2015$TShB_AUDPS, "exp")
+car::qqp(DS2015$TShB_incidence, "exp")
 
@@
 
-## 2016 Check probability distribution fit for leaf sheath blight
+## 2016 Check probability distribution fit for tiller sheath blight incidence
 
@@
 
-f1 <- fitdist(AUDPS_2016$LShB_AUDPS, "norm")
+f1 <- fitdist(DS2016$TShB_incidence, "norm")
 plot(f1)
-qqp(AUDPS_2016$LShB_AUDPS, "norm")
+car::qqp(DS2016$TShB_incidence, "norm")
 
-f2 <- fitdist(AUDPS_2016$LShB_AUDPS, "exp")
+f2 <- fitdist(DS2016$TShB_incidence, "exp")
 plot(f2)
-qqp(AUDPS_2015$LShB_AUDPS, "exp")
-
-```
-
-## 2016 Check probability distribution fit for tiller sheath blight
-
-```{r, results='hide', message=FALSE, warning=FALSE}
-
-f1 <- fitdist(AUDPS_2016$TShB_AUDPS, "norm")
-plot(f1)
-qqp(AUDPS_2016$TShB_AUDPS, "norm")
-
-f2 <- fitdist(AUDPS_2016$TShB_AUDPS, "exp")
-plot(f2)
-qqp(AUDPS_2015$LShB_AUDPS, "exp")
+car::qqp(DS2016$TShB_incidence, "exp")
 

### 2017-04-25 munge/01_preprocess_2015_data.R

@@ -11,24 +11,244 @@ reformat <- function(files) {
   x <-
     x %>% mutate_each(funs(as.numeric), starts_with("SL"))
 
-  x <-
+  # Hill number tillers and number tillers with sheath blight ------------------
+  HILL <-
     x %>%
-    group_by(REP, WMGT, NRTE) %>%
-    mutate(TShB_incidence = NTShB/NTIL) %>%
-    gather(LShB, LShB_rating, starts_with("SL")) %>%
-    gather(TShB, TShB_rating, starts_with("SHB")) %>%
-    gather(GL, GL_value, starts_with("GL")) %>%
-    gather(DL, DL_value, starts_with("DL")) %>%
-    summarise_each(funs(mean, sd),
-                   NTIL,
-                   NTShB,
-                   LShB_rating,
-                   TShB_rating,
-                   TShB_incidence,
-                   GL_value,
-                   DL_value)
+    dplyr::select(TRT, REP, WMGT, SMPL, HILL, NRTE, NTIL, NTShB) %>%
+    mutate(TShB_incidence = NTShB / NTIL)
 
-  x[, 4:17] <- round(x[, 4:17], 2)
+  HILL$TShB_incidence <- round(HILL$TShB_incidence, 2)
+  # Tiller 1 -------------------------------------------------------------------
+  TIL1 <-
+    x %>%
+    dplyr::select(TRT,
+                  REP,
+                  WMGT,
+                  SMPL,
+                  NRTE,
+                  HILL,
+                  TIL1,
+                  GL1,
+                  DL1,
+                  SHB1,
+                  SLA1,
+                  SLB1,
+                  SLC1,
+                  SLD1,
+                  SLE1,
+                  SLF1) %>%
+    gather(
+      TIL_key,
+      TIL,
+      starts_with("TIL1"),
+      -TRT,
+      -REP,
+      -WMGT,
+      -SMPL,
+      -NRTE,
+      -HILL,
+      -GL1,
+      -DL1,
+      -SHB1,
+      -SLA1,
+      -SLB1,
+      -SLC1,
+      -SLD1,
+      -SLE1,
+      -SLF1
+    )
+
+  TIL1 <-
[…]

### 2017-04-25 munge/02-preprocess_2016_data.R

@@ -88,81 +88,76 @@ DS2016$NRTE[which(DS2016$NRTE == "N2")] = 180
 
 # Add treatment numbers --------------------------------------------------------
 DS2016$TRT <- NA
-DS2016$TRT[which(DS2016$WMGT == "FLD" & DS2016$NRTE == 60)] = "FLD_N60"
-DS2016$TRT[which(DS2016$WMGT == "FLD" & DS2016$NRTE == 180)] = "FLD_N180"
-DS2016$TRT[which(DS2016$WMGT == "AWD" & DS2016$NRTE == 60)] = "AWD_N60"
-DS2016$TRT[which(DS2016$WMGT == "AWD" & DS2016$NRTE == 180)] = "AWD_N180"
+DS2016$TRT[which(DS2016$WMGT == "FLD" &
+                   DS2016$NRTE == 60)] = "FLD_N60"
+DS2016$TRT[which(DS2016$WMGT == "FLD" &
+                   DS2016$NRTE == 180)] = "FLD_N180"
+DS2016$TRT[which(DS2016$WMGT == "AWD" &
+                   DS2016$NRTE == 60)] = "AWD_N60"
+DS2016$TRT[which(DS2016$WMGT == "AWD" &
+                   DS2016$NRTE == 180)] = "AWD_N180"
 
-# Rename columns for consistency with 2015 -------------------------------------
-DS2016 <- dplyr::rename(DS2016, TShB_rating = NSHShB)
-DS2016 <- dplyr::rename(DS2016, SLA = ShBL1)
-DS2016 <- dplyr::rename(DS2016, SLB = ShBL2)
-DS2016 <- dplyr::rename(DS2016, SLC = ShBL3)
-DS2016 <- dplyr::rename(DS2016, SLD = ShBL4)
-DS2016 <- dplyr::rename(DS2016, SLE = ShBL5)
-DS2016 <- dplyr::rename(DS2016, SLF = ShBL6)
+DS2016 <-
+  DS2016 %>%
+  gather(LEAF,
+         LEAF_SHB,
+         starts_with("ShBL"),
+         -DATE,
+         -ASMT,
+         -TRT,
+         -REP,
+         -WMGT,
+         -SMPL,
+         -NRTE,
+         -HILL,
+         -NTIL,
+         -GL,
+         -DL,
+         -NTShB,
+         -NSHShB,
+         -TIL
+  )
 
[…]

### 2017-04-25 munge/03_preprocess_data.R

@@ -1,76 +1,15 @@
+# Join the 2015 and 2016 Data into one Tibble ----------------------------------
 
-# Add plot numbers just to keep track of the data for calculations -------------
-DS2015$PLOT <- rep(1:24, 5)
-DS2016$PLOT <- rep(1:16, 4)
+RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
+                            as.data.frame(DS2016)))
 
-# Create new columns of dates to calcluate AUDPS -------------------------------
-#2015
-DATE_1_2015 <- DATE_2_2015 <- DS2015$DATE
-DATE_1_2015[which(DATE_1_2015 == min(DATE_1_2015))] = NA
-DATE_2_2015[which(DATE_2_2015 == max(DATE_2_2015))] = NA
-
-DATE_1 <- na.omit(DATE_1_2015)
-DATE_2 <- na.omit(DATE_2_2015)
-
-DAYS_2015 <- difftime(DATE_1, DATE_2)
-DS2015$DAYS <- c(rep(0, 24), DAYS_2015)
-
-# 2016
-DATE_1_2016 <- DATE_2_2016 <- DS2016$DATE
-DATE_1_2016[which(DATE_1_2016 == min(DATE_1_2016))] = NA
-DATE_2_2016[which(DATE_2_2016 == max(DATE_2_2016))] = NA
-
-DATE_1 <- na.omit(DATE_1_2016)
-DATE_2 <- na.omit(DATE_2_2016)
-
-DAYS_2016 <- difftime(DATE_1, DATE_2)
-DS2016$DAYS <- c(rep(0, 16), DAYS_2016)
-
-# Join 2015 and 2016 AUDPS data to make next few steps quicker -----------------
-
-RAW_data <- AUDPS <- as_tibble(rbind(as.data.frame(DS2015),
-                                     as.data.frame(DS2016)))
-
-# Calculate AUDPS (Simco and Piepho 2012, DOI: 10.1094/PHYTO-07-11-0216) -------
-
-mean_sd <-
-  AUDPS %>%
-  group_by(YEAR, REP, TRT, WMGT, NRTE, PLOT) %>%
-  summarise_each(funs(mean),
-                 LShB_rating_sd,
-                 TShB_rating_sd,
-                 TShB_incidence_sd)
-
-cols <- c(7:8)
[…]

### 2017-04-25 munge/04_visualise_data.R

@@ -1,32 +1,17 @@
-# density plot of LShB_rating_mean data ----------------------------------------
-ggplot(RAW_data, aes(x = LShB_rating_mean, linetype = as.factor(YEAR))) +
-  geom_density(aes(fill = as.factor(YEAR)),
-                   alpha = 0.5) +
-  viridis::scale_fill_viridis(discrete = TRUE,
-                              name = "Year") +
-  scale_linetype(name = "Year") +
-  facet_grid(WMGT ~ NRTE) +
-  ggtitle("Leaf Sheath Blight Severity Rating") +
-  theme_tufte()
-ggsave("graphs/LShB_rating_mean.png", width = 6, height = 4)
-
-# density plot of LShB_rating_sd data ------------------------------------------
-ggplot(RAW_data, aes(x = LShB_rating_sd, linetype = as.factor(YEAR))) +
+# density plot of LShB_rating data ----------------------------------------
+ggplot(RAW_data, aes(x = LEAF_SHB, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                alpha = 0.5) +
   viridis::scale_fill_viridis(discrete = TRUE,
                               name = "Year") +
   scale_linetype(name = "Year") +
   facet_grid(WMGT ~ NRTE) +
-  ggtitle("Leaf Sheath Blight Severity Rating Std Dev.") +
-  theme_tufte() +
-  theme(axis.text.x = element_text(size = 8,
-                                   angle = 45,
-                                   hjust = 1))
-ggsave("graphs/LShB_rating_sd.png", width = 6, height = 4)
+  ggtitle("Leaf Sheath Blight Severity Rating") +
+  theme_tufte()
+ggsave("graphs/LShB_rating.png", width = 6, height = 4)
 
-# density plot of TShB_rating_mean data ----------------------------------------
-ggplot(RAW_data, aes(x = TShB_rating_mean, linetype = as.factor(YEAR))) +
+# density plot of TShB_rating data ----------------------------------------
+ggplot(RAW_data, aes(x = TIL_SHB, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                alpha = 0.5) +
   viridis::scale_fill_viridis(discrete = TRUE,
@@ -35,22 +20,11 @@ ggplot(RAW_data, aes(x = TShB_rating_mean, linetype = as.factor(YEAR))) +
   facet_grid(WMGT ~ NRTE) +
[…]

### 2017-04-25 Analysis.Rmd
Revise analysis and data handling
**_THIS IS BEING REVISED_**

The original analysis is unlikely to be the correct approach. The data
are being examined again and a new analysis will be conducted that
accounts for the ordinal scale used for data collection for severity.

The data are now in a tidy data frame and are ready for checking
Calculate AUDPS for tiller sheath blight incidence
Double check tiller sheath blight incidence calculations, there is a
negative AUDPS value in 2015 data

@@
 ## Notes on this analysis before starting
+
+**_THIS IS BEING REVISED_**
+
+This analysis is unlikely to be the correct approach. The data are being examined
+again and a new analysis will be conducted that accounts for the ordinal scale
+used for data collection for severity.
+
+However, these analyses should be correct for the tiller sheath blight incidence.
 
@@
 ## 2015
-### 2015 Leaf Sheath Blight Severity Model
-```{r 2015_LShB}
-
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_lmm_2015 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
-                          random = ~REP, 
-                          data = as.data.frame(AUDPS_2015),
-                          verbose = FALSE,
-                          prior = eprior,
-                          nitt = 5e+05,
-                          burnin = 5000,
-                          thin = 100,
-                          pr = TRUE)
-
-summary(LShB_lmm_2015)
-
-# create data frames for generating diagnostic plots
-reps <- data.frame(LShB_lmm_2015$Sol[, c(1, 7:10)])
-x <- 1:nrow(reps)
-reps <- melt(reps)
-
-trts <-  data.frame(LShB_lmm_2015$Sol[, 2:6])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(LShB_lmm_2015$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Replicates, Leaf ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2015 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Treatments, Leaf ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2015 Posteriors for Treatments, Leaf ShB Severity")
-
-# check random effects
-plotTrace(LShB_lmm_2015$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(LShB_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Random Error Distribution for Leaf ShB Severity"))
-```
-
-### 2015 Tiller Sheath Blight Severity Model
-```{r 2015_TShB}
-
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2015 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP, 
-                          data = as.data.frame(AUDPS_2015),
-                          verbose = FALSE,
-                          prior = eprior,
-                          nitt = 5e+05,
-                          burnin = 5000,
-                          thin = 100,
-                          pr = TRUE)
-
-summary(TShB_severity_lmm_2015)
-
-# create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
-reps <- melt(reps)
-
-trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_severity_lmm_2015$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2015 Posteriors for Treatments, Tiller ShB Severity")
-
-# check random effects
-plotTrace(TShB_severity_lmm_2015$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(TShB_severity_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Random Error Distribution for Tiller ShB Severity"))
-```
 
@@
 ## 2016
-
-### 2016 Leaf Sheath Blight Severity Model
-```{r 2016_LShB}
-
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_lmm_2016 <- MCMCglmm(LShB_AUDPS ~ WMGT * NRTE,
-                          random = ~REP, 
-                          data = as.data.frame(AUDPS_2016),
-                          verbose = FALSE,
-                          nitt = 5e+05,
-                          burnin = 5000,
-                          thin = 100,
-                          prior = eprior,
-                          pr = TRUE)
-
-summary(LShB_lmm_2016)
-
-# create data frames for generating diagnostic plots
-reps <- data.frame(LShB_lmm_2016$Sol[, c(1, 5:8)])
-reps <- melt(reps)
-
-trts <-  data.frame(LShB_lmm_2016$Sol[, 2:4])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(LShB_lmm_2016$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Replicates, Leaf ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2016 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Treatments, Leaf ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2016 Posteriors for Treatments, Leaf ShB Severity")
-
-# check random effects
-plotTrace(LShB_lmm_2016$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(LShB_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Random Error Distribution for Leaf ShB Severity"))
-```
-
-### 2016 Tiller Sheath Blight Severity Model
-```{r 2016_TShB}
-
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2016 <- MCMCglmm(TShB_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP, 
-                          data = as.data.frame(AUDPS_2016),
-                          verbose = FALSE,
-                          nitt = 5e+05,
-                          burnin = 5000,
-                          thin = 100,
-                          prior = eprior,
-                          pr = TRUE)
-
-summary(TShB_severity_lmm_2016)
-
-# create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
-reps <- melt(reps)
-
-trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_severity_lmm_2016$Sol)
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2016 Posteriors for Treatments, Tiller ShB Severity")
-
-# check random effects
-plotTrace(TShB_severity_lmm_2016$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(TShB_severity_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Random Error Distribution for Tiller ShB Severity"))
-```
 

### 2017-04-25 Probability_distribution_checks.Rmd
Calculate AUDPS for tiller sheath blight incidence
Double check tiller sheath blight incidence calculations, there is a
negative AUDPS value in 2015 data

@@
 ```{r, results='hide', message=FALSE, warning=FALSE}
+AUDPS15 <- subset(AUDPS, YEAR == "2015")
+f1 <- fitdist(AUDPS15$TShB_incidence, "norm")
+plot(f1)
+car::qqp(AUDPS15$TShB_incidence, "norm")
 
-f1 <- fitdist(DS2015$TShB_incidence, "norm")
-plot(f1)
-car::qqp(DS2015$TShB_incidence, "norm")
-
-f2 <- fitdist(DS2015$TShB_incidence, "exp")
+f2 <- fitdist(AUDPS15$TShB_incidence, "exp")
 plot(f2)
-car::qqp(DS2015$TShB_incidence, "exp")
+car::qqp(AUDPS15$TShB_incidence, "exp")
 
@@
 ```{r, results='hide', message=FALSE, warning=FALSE}
+AUDPS156 <- subset(AUDPS, YEAR == "2016")
+f1 <- fitdist(AUDPS156$TShB_incidence, "norm")
+plot(f1)
+car::qqp(AUDPS156$TShB_incidence, "norm")
 
-f1 <- fitdist(DS2016$TShB_incidence, "norm")
-plot(f1)
-car::qqp(DS2016$TShB_incidence, "norm")
-
-f2 <- fitdist(DS2016$TShB_incidence, "exp")
+f2 <- fitdist(AUDPS156$TShB_incidence, "exp")
 plot(f2)
-car::qqp(DS2016$TShB_incidence, "exp")
+car::qqp(AUDPS156$TShB_incidence, "exp")
 

### 2017-04-25 munge/03_preprocess_data.R

@@ -1,7 +1,45 @@
+# Add plot numbers just to keep track of the data for calculations -------------
+DS2015$PLOT <- rep(1:24, 2160)
+DS2016$PLOT <- rep(1:16, 1728)
+
+# calculate tiller sheath blight incidence AUDPDS ------------------------------
+
+#2015
+DATE_1_2015 <- DATE_2_2015 <- DS2015$DATE
+DATE_1_2015[which(DATE_1_2015 == min(DATE_1_2015))] = NA
+DATE_2_2015[which(DATE_2_2015 == max(DATE_2_2015))] = NA
+
+DATE_1 <- na.omit(DATE_1_2015)
+DATE_2 <- na.omit(DATE_2_2015)
+
+# using lubridate::difftime calculate the time between observations
+DAYS_2015 <- difftime(DATE_1, DATE_2)
+
+# Add DAYS column to DS2015
+DS2015$DAYS <-
+  c(rep(0, nrow(DS2015) - length(DAYS_2015)), DAYS_2015)
+
+# 2016
+DATE_1_2016 <- DATE_2_2016 <- DS2016$DATE
+DATE_1_2016[which(DATE_1_2016 == min(DATE_1_2016))] = NA
+DATE_2_2016[which(DATE_2_2016 == max(DATE_2_2016))] = NA
+
+DATE_1 <- na.omit(DATE_1_2016)
+DATE_2 <- na.omit(DATE_2_2016)
+
+# using lubridate::difftime calculate the time between observations
+DAYS_2016 <- difftime(DATE_1, DATE_2)
+
+# Add DAYS column to DS2015
+DS2016$DAYS <-
+  c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)
+
 # Join the 2015 and 2016 Data into one Tibble ----------------------------------
 
 RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
                             as.data.frame(DS2016)))
+
+# convert columns to factor
 
 RAW_data$YEAR <- as.factor(RAW_data$YEAR)
 RAW_data$ASMT <- as.factor(RAW_data$ASMT)
@@ -13,3 +51,10 @@ RAW_data$SMPL <- as.factor(RAW_data$SMPL)
 RAW_data$HILL <- as.factor(RAW_data$HILL)
 RAW_data$TIL <- as.factor(RAW_data$TIL)
 RAW_data$LEAF <- as.factor(RAW_data$LEAF)
+
[…]

### 2017-04-26 Analysis.Rmd
Finalise data cleaning and run analysis on AUDPS only
Finalised data cleaning (again). Data are now in a tidy data frame for
ordinal analysis. AUDPS has been generated from the tiller incidence
data and analysed using MCMCglmm

All raw data graphs have been updated

@@
 
+# Separate the TRT column into the two treatments for analysis
+AUDPS <- separate(data = AUDPS, col = TRT, into = c("WMGT", "NRTE"))
+
 eprior <- list(R = list(V = 1, nu = 0.02),
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2015 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE,
+TShB_incidence_lmm_2015 <- MCMCglmm(AUDPS ~ WMGT * NRTE,
                                     random = ~REP, 
-                          data = as.data.frame(AUDPS_2015),
+                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2015, ]),
                           verbose = FALSE,
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2016 <- MCMCglmm(TShB_incidence_mean ~ WMGT * NRTE, 
+TShB_incidence_lmm_2016 <- MCMCglmm(AUDPS ~ WMGT * NRTE, 
                                     random = ~REP, 
-                          data = as.data.frame(AUDPS_2016),
+                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2016, ]),
                           verbose = FALSE,
@@
 
-The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernable patterns.
+The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernible patterns.
 

### 2017-04-26 Probability_distribution_checks.Rmd
Finalise data cleaning and run analysis on AUDPS only
Finalised data cleaning (again). Data are now in a tidy data frame for
ordinal analysis. AUDPS has been generated from the tiller incidence
data and analysed using MCMCglmm

All raw data graphs have been updated

--- 2017-04-25 Probability_distribution_checks.Rmd
@@
 I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
-As you see in that guide, there are several distributions that can be checked.
+As you see in that guide, there are several distributions that can be checked, however, the data both fit a normal distribution.
 
@@
 ```{r, results='hide', message=FALSE, warning=FALSE}
-
-f1 <- fitdist(DS2015$TShB_incidence, "norm")
+AUDPS15 <- subset(AUDPS, YEAR == "2015")
+f1 <- fitdist(AUDPS15$AUDPS, "norm")
 plot(f1)
-car::qqp(DS2015$TShB_incidence, "norm")
-
-f2 <- fitdist(DS2015$TShB_incidence, "exp")
-plot(f2)
-car::qqp(DS2015$TShB_incidence, "exp")
+car::qqp(AUDPS15$AUDPS, "norm")
 
@@
 ```{r, results='hide', message=FALSE, warning=FALSE}
-
-f1 <- fitdist(DS2016$TShB_incidence, "norm")
+AUDPS156 <- subset(AUDPS, YEAR == "2016")
+f1 <- fitdist(AUDPS156$AUDPS, "norm")
 plot(f1)
-car::qqp(DS2016$TShB_incidence, "norm")
-
-f2 <- fitdist(DS2016$TShB_incidence, "exp")
-plot(f2)
-car::qqp(DS2016$TShB_incidence, "exp")
+car::qqp(AUDPS156$AUDPS, "norm")
 
@@
 A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit.
-In this case, for the 2015 data, the leaf data fit a lognormal distribution best or exponential, for all others a normal distribution appears to be fine.
-Because of the non-normal residuals of the 2015 leaf sheath blight data we'll look at using something that can handle these data like `MCMCglmm`.
+Here both sets of data fit a normal distribution.

### 2017-04-26 munge/01_preprocess_2015_data.R

@@ -7,17 +7,29 @@ reformat <- function(files) {
   x <- read_csv(files)
   x[is.na(x)] <- 0
 
-  # ensure that all leaf sheath blight observations are numeric, not character
+  # ensure that all leaf sheath blight observations are numeric ----------------
   x <-
     x %>% mutate_each(funs(as.numeric), starts_with("SL"))
 
-  # Hill number tillers and number tillers with sheath blight ------------------
-  HILL <-
+  # calculate tiller sheath blight incidence -----------------------------------
+  x <-
     x %>%
-    dplyr::select(TRT, REP, WMGT, SMPL, HILL, NRTE, NTIL, NTShB) %>%
     mutate(TShB_incidence = NTShB / NTIL)
 
-  HILL$TShB_incidence <- round(HILL$TShB_incidence, 2)
+  x$TShB_incidence <- round(x$TShB_incidence, 2)
+
+  TShB_incidence <-
+    x %>% dplyr::select(REP,
+                        TRT,
+                        WMGT,
+                        NRTE,
+                        SMPL,
+                        HILL,
+                        HGHT,
+                        NTIL,
+                        NTShB,
+                        TShB_incidence)
+
   # Tiller 1 -------------------------------------------------------------------
   TIL1 <-
     x %>%
@@ -37,31 +49,9 @@ reformat <- function(files) {
                   SLD1,
                   SLE1,
                   SLF1) %>%
-    gather(
-      TIL_key,
-      TIL,
-      starts_with("TIL1"),
-      -TRT,
-      -REP,
-      -WMGT,
-      -SMPL,
-      -NRTE,
-      -HILL,
-      -GL1,
-      -DL1,
-      -SHB1,
-      -SLA1,
-      -SLB1,
-      -SLC1,
-      -SLD1,
-      -SLE1,
-      -SLF1
-    )
-
-  TIL1 <-
-    TIL1 %>%
[…]

### 2017-04-26 munge/02-preprocess_2016_data.R

@@ -100,7 +100,7 @@ DS2016$TRT[which(DS2016$WMGT == "AWD" &
 DS2016 <-
   DS2016 %>%
   gather(LEAF,
-         LEAF_SHB,
+         LEAF_ShB,
          starts_with("ShBL"),
          -DATE,
          -ASMT,
@@ -134,10 +134,10 @@ DS2016 <-
 
 DS2016$TShB_incidence <- round(DS2016$TShB_incidence, 2)
 
-DS2016 <- dplyr::rename(DS2016, TIL_SHB = NSHShB)
+DS2016 <- dplyr::rename(DS2016, TIL_ShB = NSHShB)
 
 DS2016$YEAR <- year(DS2016$DATE)
-DS2016$LEAF_SHB <- as.numeric(DS2016$LEAF_SHB)
+DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)
 
 DS2016 <-
   DS2016 %>% dplyr::select(
@@ -146,8 +146,6 @@ DS2016 <-
     ASMT,
     REP,
     TRT,
-    WMGT,
-    NRTE,
     SMPL,
     HILL,
     TIL,
@@ -155,9 +153,12 @@ DS2016 <-
     GL,
     DL,
     TShB_incidence,
-    TIL_SHB,
-    LEAF_SHB
+    TIL_ShB,
+    LEAF_ShB,
+    WMGT,
+    NRTE
   )
+
 
 # write CSV to cache -----------------------------------------------------------
 write_csv(DS2016, "./cache/AWD_2016_Data.csv")

### 2017-04-26 munge/03_preprocess_data.R

@@ -1,42 +1,4 @@
-# Add plot numbers just to keep track of the data for calculations -------------
-DS2015$PLOT <- rep(1:24, 2160)
-DS2016$PLOT <- rep(1:16, 1728)
 
-# calculate tiller sheath blight incidence AUDPDS ------------------------------
-
-#2015
-DATE_1_2015 <- DATE_2_2015 <- DS2015$DATE
-
-# set the first and last dates to NA
-DATE_1_2015[which(DATE_1_2015 == min(DATE_1_2015))] = NA
-DATE_2_2015[which(DATE_2_2015 == max(DATE_2_2015))] = NA
-
-# remove NA values
-DATE_1_2015 <- DATE_1_2015[!is.na(DATE_1_2015)]
-DATE_2_2015 <- DATE_2_2015[!is.na(DATE_2_2015)]
-
-# using lubridate::difftime calculate the time between observations
-DAYS_2015 <- difftime(DATE_1_2015, DATE_2_2015)
-
-# Add DAYS column to DS2015
-DS2015$DAYS <-
-  c(rep(0, nrow(DS2015) - length(DAYS_2015)), DAYS_2015)
-
-# 2016
-DATE_1_2016 <- DATE_2_2016 <- DS2016$DATE
-DATE_1_2016[which(DATE_1_2016 == min(DATE_1_2016))] = NA
-DATE_2_2016[which(DATE_2_2016 == max(DATE_2_2016))] = NA
-
-# remove NA values
-DATE_1_2016 <- DATE_1_2016[!is.na(DATE_1_2016)]
-DATE_2_2016 <- DATE_2_2016[!is.na(DATE_2_2016)]
-
-# using lubridate::difftime calculate the time between observations
-DAYS_2016 <- difftime(DATE_1_2016, DATE_2_2016)
-
-# Add DAYS column to DS2015
-DS2016$DAYS <-
-  c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)
 
 # Join the 2015 and 2016 Data into one Tibble ----------------------------------
 
@@ -56,9 +18,16 @@ RAW_data$HILL <- as.factor(RAW_data$HILL)
 RAW_data$TIL <- as.factor(RAW_data$TIL)
 RAW_data$LEAF <- as.factor(RAW_data$LEAF)
 
-# calculate AUDPS --------------------------------------------------------------
[…]

### 2017-04-26 munge/04_visualise_data.R

@@ -1,25 +1,23 @@
 # density plot of LShB_rating data ----------------------------------------
-ggplot(RAW_data, aes(x = LEAF_SHB, linetype = as.factor(YEAR))) +
+ggplot(RAW_data, aes(x = LEAF_ShB, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                alpha = 0.5) +
   viridis::scale_fill_viridis(discrete = TRUE,
                               name = "Year") +
   scale_linetype(name = "Year") +
   facet_grid(WMGT ~ NRTE) +
-  ggtitle("Leaf Sheath Blight Severity Rating") +
-  theme_tufte()
+  ggtitle("Leaf Sheath Blight Severity Rating")
 ggsave("graphs/LShB_rating.png", width = 6, height = 4)
 
 # density plot of TShB_rating data ----------------------------------------
-ggplot(RAW_data, aes(x = TIL_SHB, linetype = as.factor(YEAR))) +
+ggplot(RAW_data, aes(x = TIL_ShB, linetype = as.factor(YEAR))) +
   geom_density(aes(fill = as.factor(YEAR)),
                alpha = 0.5) +
   viridis::scale_fill_viridis(discrete = TRUE,
                               name = "Year") +
   scale_linetype(name = "Year") +
   facet_grid(WMGT ~ NRTE) +
-  ggtitle("Tiller Sheath Blight Severity Rating") +
-  theme_tufte()
+  ggtitle("Tiller Sheath Blight Severity Rating")
 ggsave("graphs/TShB_rating.png", width = 6, height = 4)
 
 
@@ -32,7 +30,6 @@ ggplot(RAW_data, aes(x = TShB_incidence, linetype = as.factor(YEAR))) +
   scale_linetype(name = "Year") +
   facet_grid(WMGT ~ NRTE) +
   ggtitle("Tiller Sheath Blight Incidence") +
-  theme_tufte() +
 theme(axis.text.x = element_text(size = 8,
                                  angle = 45,
                                  hjust = 1))
@@ -47,8 +44,7 @@ ggplot(RAW_data, aes(x = GL, linetype = as.factor(YEAR))) +
                               name = "Year") +
   scale_linetype(name = "Year") +
   xlab("Count") +
-  ggtitle("Green Leaf Count") +
-  theme_tufte()
+  ggtitle("Green Leaf (count)")
 ggsave("graphs/GL_value.png", width = 6, height = 4)
 
[…]

### 2017-04-28 Analysis.Rmd
Clean up Analysis.Rmd/md
Remove NTIL/NTShB in 2016 data
In some cases the number of infected tillers recorded is higher than
the number of tillers in the hill. I've recoded these two columns to be
NA where this happens

After doing this I've regenerated the data graphs for Tiller Sheath
Blight Severity Over Time and rerun the analysis for TSHB AUDPS

@@
 ## Notes on this analysis before starting
-
-**_THIS IS BEING REVISED_**
-
-This analysis is unlikely to be the correct approach. The data are being examined
-again and a new analysis will be conducted that accounts for the ordinal scale
-used for data collection for severity.
-
-However, these analyses should be correct for the tiller sheath blight incidence.
 
@@
 ```{r session_info}
-sessionInfo()
+devtools::session_info()
 ```

### 2017-04-28 munge/02-preprocess_2016_data.R

@@ -127,6 +127,13 @@ DS2016$LEAF[DS2016$LEAF == "ShBL4"] <- 4
 DS2016$LEAF[DS2016$LEAF == "ShBL5"] <- 5
 DS2016$LEAF[DS2016$LEAF == "ShBL6"] <- 6
 
+# before classifying incidence, set any values where there are more infected
+# tillers in the hill than there are tillers to NA for both columns
+
+DS2016$NTIL[DS2016$NTIL < DS2016$NTShB] <- NA
+DS2016$NTShB[is.na(DS2016$NTIL)] <- NA
+
+# calculate tiller sheath blight incidence
 DS2016 <-
   DS2016 %>%
   group_by(DATE, ASMT, REP, TRT, WMGT, NRTE, SMPL, HILL) %>%

### 2017-04-28 munge/04_visualise_data.R

@@ -66,14 +66,13 @@ ggsave("graphs/TShB_severity_over_time.png", width = 6, height = 4)
 # line plot of tiller sheath blight incidence data ---------------------------------
 ggplot(RAW_data, aes(x = ASMT, y = TShB_incidence,
                      group = TShB_incidence)) +
-  stat_summary(fun.y = "mean", geom = "line",
-               aes(group = TRT,
-                   colour = TRT,
-                   linetype = YEAR),
-               size = 1) +
-  viridis::scale_color_viridis(discrete = TRUE,
-                               name = "Treatment") +
-  scale_linetype(name = "Year") +
+  geom_point(position = position_jitter(width = 0.05),
+             aes(colour = YEAR), size = 0.75) +
+  xlab("Assessment") +
+  ylab("Incidence") +
+  facet_grid(. ~ TRT) +
+  ggtitle("Tiller Sheath Blight Severity Rating Over Time") +
+  theme(strip.text.x = element_text(angle = 90)) +
   xlab("Assessment") +
   ylab("Incidence") +
   ggtitle("Tiller Sheath Blight Incidence Over Time")

### 2017-04-28 munge/04_visualise_data.R
Update graphs
With the change to the tiller sheath blight incidence, regenerate all
affected graphs

Also change the AUDPS dot plot to include replicate so that it's
possible to see which replicate is missing

@@ -93,7 +93,7 @@ ggsave("graphs/TShB_Incidence_plot.png", width = 6, height = 4)
 
 # dotplots of tiller sheath blight AUDPS data ----------------------------------
 ggplot(AUDPS, aes(x = TRT, y = AUDPS)) +
-  geom_point(aes(colour = YEAR)) +
+  geom_point(aes(colour = YEAR, shape = REP), size = 2) +
   theme(axis.text.x = element_text(size = 8,
                                    angle = 45,
                                    hjust = 1)) +

### 2017-05-10 lib/helpers.R
Update analysis for tiller incidence

@@ -12,7 +12,6 @@ plot_diagnostic_lines <- function(d, x, title) {
     group = variable
   )) +
     geom_line() +
-    theme_tufte() +
     xlab("Iteration Number") +
     ylab(NULL) +
     facet_grid(variable ~ .) +
@@ -29,7 +28,6 @@ plot_replicate_posteriors <- function(d, title) {
                                 name = "Variable") +
     viridis::scale_color_viridis(discrete = TRUE,
                                 name = "Variable") +
-    theme_tufte() +
     ggtitle(paste(title))
 }
 
@@ -43,7 +41,6 @@ plot_treatment_posteriors <- function(d, title) {
                                 name = "Variable") +
     viridis::scale_color_viridis(discrete = TRUE,
                                   name = "Variable") +
-    theme_tufte() +
     ggtitle(paste(title))
 }
 
@@ -51,6 +48,5 @@ plot_joint_random_error_dist <- function(d, title) {
   ggplot(d, aes(x = sqrt(REP), y = sqrt(units))) +
     geom_density2d() +
     geom_abline(intercept = 0, slope = 1) +
-    ggtitle(paste(title)) +
-    theme_tufte()
+    ggtitle(paste(title))
 }

### 2017-05-10 Probability_distribution_checks.Rmd
Update probability distribution checks

@@
 
-```{r, results='hide', message=FALSE, warning=FALSE}
+### Normal
+```{r norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS15 <- subset(AUDPS, YEAR == "2015")
@@
 car::qqp(AUDPS15$AUDPS, "norm")
+```
 
+### Exponential
+
+```{r exp, results='hide', message=FALSE, warning=FALSE}
+AUDPS15 <- subset(AUDPS, YEAR == "2015")
+f1 <- fitdist(AUDPS15$AUDPS, "exp")
+plot(f1)
+car::qqp(AUDPS15$AUDPS, "exp")
 ```
@@
 
+Until the issue with more diseased tillers than tillers in a hill is addressed,
+this section will not work completely and properly.
+
 ```{r, results='hide', message=FALSE, warning=FALSE}
 AUDPS156 <- subset(AUDPS, YEAR == "2016")
-f1 <- fitdist(AUDPS156$AUDPS, "norm")
-plot(f1)
+# f1 <- fitdist(AUDPS156$AUDPS, "norm")
+#plot(f1)
 car::qqp(AUDPS156$AUDPS, "norm")

### 2017-06-01 Analysis.Rmd
Update analysis for tiller incidence
Add description to the Analysis describing how data load and where scripts are

@@
 ## Notes on this analysis before starting
+
+The analyses are semi-automated.
+When this file is knit, it automatically loads the _ProjectTemplate_ package and calls the `load.project()` function.
+This loads the data, cleans and munges it creating the `AUDPS` data frame used for the analysis below.
+The scripts used to clean and munge the data are located in the [munge](./munge) folder and numbered in the sequential order in which they are run.
 
@@
 # Separate the TRT column into the two treatments for analysis
-AUDPS <- separate(data = AUDPS, col = TRT, into = c("WMGT", "NRTE"))
+AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
 

### 2017-06-09 reports/Effects_of_AWD_N_on_SB.rmd
Update title per Ole's change

@@
 ---
-title: "Do Alternate Wetting and Drying Irrigation Technologies and Nitrogen Rates Affect Rice Sheath Blight?"
+title: "Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?"
 thanks: "Replication files are available on the author's Github account (http://github.com/adamhsparks/AWD_N_SB).

### 2017-06-09 reports/Effects_of_AWD_N_on_SB.rmd
add Buyung to list of authors, can sort order later

@@
 author:
-  - A.H. Sparks and N.P. Castilla and B.O. Sander
+  - A.H. Sparks and N.P. Castilla and B.O. Sander and B. Hadi
 keywords: "_Rhizoctonia solani_, Irrigation"

### 2017-06-09 reports/Effects_of_AWD_N_on_SB.rmd
Incorporate Ole's suggested changes, edits and references

@@
 
+# Introduction
+
+Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [-@Bouman2001; -@Feng2007].
+In AWD rice fields are exposed to several dry phases during the growth period without exposing the plants to water stress.
+In order to avoid yield decline under AWD “safe” thresholds have been developed.
+Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [-@Richards2014].
+Fields are furthermore kept flooded during the flowering period.
+Besides saving water AWD also reduces greenhouse gas (GHG) emissions of rice fields, which is a substantial factor in the GHG budget of rice producing countries, by around 50% [-@Yan2005; -@Sander2015].
+
+The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
+Various countries, e.g., Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [-@MOEF2015].
+However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
+
+We therefore established field experiments in order to…
+
 # Materials and Methods
@@
 Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub plot for a whole experiment size of 1,152 sq m.
-The main plot treatments were alternate wetting and drying (AWD) and flooded or farmers' practice.
+The main plot treatments were alternate wetting and drying (AWD) and ) and continuously flooded (CF) or farmers' practice.
+
+Irrigation in AWD plots was determined by the water level in plots, i.e., when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
+In CF plots a standing water layer of 3-5cm was maintained throughout the growing season.
+
+The sub plot treatments were different rates of nitrogen…
 

### 2017-06-15 Analysis.Rmd
Update probability distribution checks and analysis for tiller sheath blight incidence

@@
 #### Iterations
+
 Fitting the models with the default iterations resulted in some less than
@@
 ## Setup
+
 Use `set.seed()` for reproducibility.
@@
 ### 2015 Tiller Sheath Blight Incidence Model
+
 ```{r 2015_TShB_incidence}
@@
 AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
+AUDPS <- mutate_at(AUDPS, .funs = factor, .cols = c("NRTE", "WMGT"))
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2015 <- MCMCglmm(AUDPS ~ WMGT * NRTE,
+TShB_incidence_lmm_2015 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE,
                                     random = ~REP, 
@@
 ### 2016 Tiller Sheath Blight Incidence Model
+
 ```{r 2016_TShB_incidence}
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2016 <- MCMCglmm(AUDPS ~ WMGT * NRTE, 
+TShB_incidence_lmm_2016 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE, 
                                     random = ~REP, 
@@
 
-# Conclusions
+## Conclusions
+
+### Tiller Sheath Blight Incidence
+
+In 2015 the highest N treatment was significant, in 2016 both the flooded water management and the N rates were significant.
 
@@
 None of the diagnostic plots show any signs of autocorrelation or any other obvious patterns.
-
-None of the treatments in either year, 2015 or 2016, were significant. The
-see `pMCMC` values and also posterior graphs. There is a large amount of overlap
-in all of the posterior graphs.
 
@@
 
-# R Session Info
-```{r session_info}
+## R Session Info
+
+```{r session_info, echo=FALSE}
 devtools::session_info()

### 2017-06-15 Probability_distribution_checks.Rmd
Update probability distribution checks and analysis for tiller sheath blight incidence

--- 2017-04-26 Probability_distribution_checks.Rmd
@@
 I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
-As you see in that guide, there are several distributions that can be checked, however, the data both fit a normal distribution.
+As you see in that guide, there are several distributions that can be checked.
+However, in these data only normal and exponential
 
-## 2015 Check probability distribution fit for tiller sheath blight incidence
+## 2015
 
-```{r, results='hide', message=FALSE, warning=FALSE}
+### Check probability distribution fit for tiller sheath blight incidence
+
+#### Normal
+
+```{r 2015_inc_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS15 <- subset(AUDPS, YEAR == "2015")
-f1 <- fitdist(AUDPS15$AUDPS, "norm")
+f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "norm")
 plot(f1)
-car::qqp(AUDPS15$AUDPS, "norm")
+
+car::qqp(AUDPS15$TShB_inc_AUDPS, "norm")
+```
+
+#### Exponential
+
+```{r 2015_inc_exp, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
+plot(f1)
+car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
+car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")
 
@@
 
-## 2016 Check probability distribution fit for tiller sheath blight incidence
+## 2016
 
-```{r, results='hide', message=FALSE, warning=FALSE}
-AUDPS156 <- subset(AUDPS, YEAR == "2016")
-f1 <- fitdist(AUDPS156$AUDPS, "norm")
+### Check probability distribution fit for tiller sheath blight incidence
+
+#### Normal
+
+```{r, 2016_inc_norm, results='hide', message=FALSE, warning=FALSE}
+AUDPS16 <- subset(AUDPS, YEAR == "2016")
+ f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "norm")
 plot(f1)
-car::qqp(AUDPS156$AUDPS, "norm")
 
+car::qqp(AUDPS16$TShB_inc_AUDPS, "norm")
+```
+
+#### Exponential
+
+```{r 2016_inc_exp, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS16$TShB_inc_AUDPS, "exp")
+plot(f1)
+
+car::qqp(AUDPS16$TShB_inc_AUDPS, "exp")
 ```
@@
 A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit.
-Here both sets of data fit a normal distribution.
+
+### Tiller Incidence Distributions
+
+The 2015 data fit an exponential distribution while the 2016 data fit a normal distribution.

### 2017-06-15 Analysis.Rmd
Update tiller sheath blight incidence analysis

@@
 
+The `AUDPS` object is created when the project is loaded, in the file [munge/03_preprocess_data.R](munge/03_preprocess_data.R).
+However, because it is a `tibble` and the treatments exist in a single column for graphing the raw data, this object needs a few minor changes to be usable for the analysis.
+
+First, separate the TRT column into the two treatments for analysis
+
+```{r data_setup}
+AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
+AUDPS <- mutate_at(.tbl = AUDPS, .funs = factor, .cols = c("WMGT", "NRTE"))
+```
+
+Now create individual data frames for the analysis.
+
+```{r create_analysis_df}
+AUDPS_15 <- as.data.frame(AUDPS[AUDPS$YEAR == 2015, ])
+AUDPS_15 <- droplevels(AUDPS_15)
+
+AUDPS_16 <- as.data.frame(AUDPS[AUDPS$YEAR == 2016, ])
+AUDPS_16 <- droplevels(AUDPS_16)
+```
+
+Now that the `AUDPS_15` and `AUDPS_16` `data.frames` exist, we can start the analysis.
+
 ## 2015
@@
 ```{r 2015_TShB_incidence}
-
-# Separate the TRT column into the two treatments for analysis
-AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
-AUDPS <- mutate_at(AUDPS, .funs = factor, .cols = c("NRTE", "WMGT"))
-
 eprior <- list(R = list(V = 1, nu = 0.02),
@@
                                     random = ~REP, 
-                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2015, ]),
+                          data = AUDPS_15,
                           verbose = FALSE,
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+
 TShB_incidence_lmm_2016 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE, 
                                     random = ~REP, 
-                          data = as.data.frame(AUDPS[AUDPS$YEAR == 2016, ]),
+                          data = AUDPS_16,
                           verbose = FALSE,
@@
 
-In 2015 the highest N treatment was significant, in 2016 both the flooded water management and the N rates were significant.
+In 2015 the highest N treatment was significant, in 2016 the lowest N rates were significant.
 

### 2017-06-15 munge/03_preprocess_data.R

@@ -154,6 +154,5 @@ TShB_inc_16$PLOT <- as.character(TShB_inc_16$PLOT)
 
 ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))
 
-# Merge Tiller Incidence AUDPS data --------------------------------------------
-
+# Merge AUDPS data for graphing ------------------------------------------------
 AUDPS <- as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))

### 2017-06-15 Analysis.Rmd
Add severity analyses

@@
 
+### 2015 Tiller Sheath Blight Severity Model
+
+```{r 2015_TShB_severity}
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+TShB_severity_lmm_2015 <- MCMCglmm(TShB_sev_AUDPS ~ WMGT * NRTE,
+                                    random = ~REP, 
+                          data = AUDPS_15,
+                          verbose = FALSE,
+                          prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
+                          pr = TRUE)
+
+summary(TShB_severity_lmm_2015)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(TShB_severity_lmm_2015$Sol)
+
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Severity")
+
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
+
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Severity")
+
+# Posterior distributions for treatment
+plot_treatment_posteriors(d = trts,
+                          title = "2015 Posteriors for Treatments, Tiller ShB Severity")
+
+# check random effects
+plotTrace(TShB_severity_lmm_2015$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(TShB_severity_lmm_2015$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2015 Random Error Distribution for Tiller ShB Severity"))
+```
+
+```{r 2015_LShB_severity}
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+LShB_severity_lmm_2015 <- MCMCglmm(LShB_sev_AUDPS ~ WMGT * NRTE,
+                                    random = ~REP, 
+                          data = AUDPS_15,
+                          verbose = FALSE,
+                          prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
+                          pr = TRUE)
+
+summary(LShB_severity_lmm_2015)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(LShB_severity_lmm_2015$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(LShB_severity_lmm_2015$Sol[, 2:6])
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(LShB_severity_lmm_2015$Sol)
+
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Replicates, Leaf ShB Severity")
+
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2015 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
+
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2015 Diagnostic Plots for Treatments, Leaf ShB Severity")
+
+# Posterior distributions for treatment
+plot_treatment_posteriors(d = trts,
+                          title = "2015 Posteriors for Treatments, Leaf ShB Severity")
+
+# check random effects
+plotTrace(LShB_severity_lmm_2015$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(LShB_severity_lmm_2015$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2015 Random Error Distribution for Leaf ShB Severity"))
+```
+
 *******
@@
 
+### 2016 Tiller Sheath Blight Severity Model
+
+```{r 2016_TShB_severity}
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+TShB_severity_lmm_2016 <- MCMCglmm(TShB_sev_AUDPS ~ WMGT * NRTE,
+                                    random = ~REP, 
+                          data = AUDPS_15,
+                          verbose = FALSE,
+                          prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
+                          pr = TRUE)
+
+summary(TShB_severity_lmm_2016)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:6])
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(TShB_severity_lmm_2016$Sol)
+
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Severity")
+
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
+
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Severity")
+
+# Posterior distributions for treatment
+plot_treatment_posteriors(d = trts,
+                          title = "2016 Posteriors for Treatments, Tiller ShB Severity")
+
+# check random effects
+plotTrace(TShB_severity_lmm_2016$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(TShB_severity_lmm_2016$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2016 Random Error Distribution for Tiller ShB Severity"))
+```
+
+```{r 2016_LShB_severity}
+eprior <- list(R = list(V = 1, nu = 0.02),
+               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+LShB_severity_lmm_2016 <- MCMCglmm(LShB_sev_AUDPS ~ WMGT * NRTE,
+                                    random = ~REP, 
+                          data = AUDPS_15,
+                          verbose = FALSE,
+                          prior = eprior,
+                          nitt = 5e+05,
+                          burnin = 5000,
+                          thin = 100,
+                          pr = TRUE)
+
+summary(LShB_severity_lmm_2016)
+
+# create data frames for generating diagnostic plots
+reps <- data.frame(LShB_severity_lmm_2016$Sol[, c(1, 7:10)])
+reps <- melt(reps)
+
+trts <-  data.frame(LShB_severity_lmm_2016$Sol[, 2:6])
+trts <- melt(trts)
+
+# Create a dummy x-axis variable for plotting
+x <- 1:nrow(LShB_severity_lmm_2016$Sol)
+
+# diagnostic line plots for replicate
+plot_diagnostic_lines(d = reps,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Replicates, Leaf ShB Severity")
+
+# posterior distributions for replicate
+plot_replicate_posteriors(d = reps,
+                          title = "2016 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
+
+# diagnostic line plots for treatments
+plot_diagnostic_lines(d = trts,
+                      x = x,
+                      title = "2016 Diagnostic Plots for Treatments, Leaf ShB Severity")
+
+# Posterior distributions for treatment
+plot_treatment_posteriors(d = trts,
+                          title = "2016 Posteriors for Treatments, Leaf ShB Severity")
+
+# check random effects
+plotTrace(LShB_severity_lmm_2016$VCV, log = TRUE)
+
+# plot joint distibution of error
+rdf <- data.frame(LShB_severity_lmm_2016$VCV)
+plot_joint_random_error_dist(d = rdf,
+                             title = ("2016 Random Error Distribution for Leaf ShB Severity"))
+```
 ## Conclusions

### 2017-06-15 Probability_distribution_checks.Rmd
Add probability distribution checks for all data

@@
 
-## 2015
+## 2016
 
@@
 
-#### Normal
+#### Tiller Incidence Normal
 
-```{r 2015_inc_norm, results='hide', message=FALSE, warning=FALSE}
+```{r 2015_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS15 <- subset(AUDPS, YEAR == "2015")
@@
 
-#### Exponential
+#### Tiller Incidence Exponential
 
-```{r 2015_inc_exp, results='hide', message=FALSE, warning=FALSE}
+```{r 2015_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}
 
@@
 car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
-car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")
+```
 
+#### Tiller Severity Normal
+
+```{r 2015_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+AUDPS15 <- subset(AUDPS, YEAR == "2015")
+f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "norm")
+plot(f1)
+
+car::qqp(AUDPS15$TShB_sev_AUDPS, "norm")
 ```
+
+#### Tiller Severity Exponential
+
+```{r 2015_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "exp")
+plot(f1)
+car::qqp(AUDPS15$TShB_sev_AUDPS, "exp")
+```
+
+#### Leaf Severity Normal
+
+```{r 2015_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+AUDPS15 <- subset(AUDPS, YEAR == "2015")
+f1 <- fitdist(AUDPS15$LShB_sev_AUDPS, "norm")
+plot(f1)
+
+car::qqp(AUDPS15$LShB_sev_AUDPS, "norm")
+```
+
+#### Leaf Severity Exponential
+
+These data do not fit this distribution, all values must be positive.
 
@@
 
-#### Normal
+#### Tiller Incidence Normal
 
-```{r, 2016_inc_norm, results='hide', message=FALSE, warning=FALSE}
+```{r 2016_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS16 <- subset(AUDPS, YEAR == "2016")
@@
 
-#### Exponential
+#### Tiller Incidence Exponential
 
-```{r 2016_inc_exp, results='hide', message=FALSE, warning=FALSE}
+```{r 2016_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}
 
@@
 plot(f1)
+car::qqp(AUDPS16$TShB_inc_AUDPS, "exp")
+```
 
-car::qqp(AUDPS16$TShB_inc_AUDPS, "exp")
+#### Tiller Severity Normal
+
+```{r 2016_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+AUDPS16 <- subset(AUDPS, YEAR == "2016")
+f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "norm")
+plot(f1)
+
+car::qqp(AUDPS16$TShB_sev_AUDPS, "norm")
+```
+
+#### Tiller Severity Exponential
+
+```{r 2016_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "exp")
+plot(f1)
+car::qqp(AUDPS16$TShB_sev_AUDPS, "exp")
+```
+
+#### Leaf Severity Normal
+
+```{r 2016_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+AUDPS16 <- subset(AUDPS, YEAR == "2016")
+f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "norm")
+plot(f1)
+
+car::qqp(AUDPS16$LShB_sev_AUDPS, "norm")
+```
+
+#### Leaf Severity Exponential
+
+```{r 2016_LShB_sev_exp, results='hide', message=FALSE, warning=FALSE}
+
+f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "exp")
+plot(f1)
+car::qqp(AUDPS16$LShB_sev_AUDPS, "exp")
 ```
@@
 
-The 2015 data fit an exponential distribution while the 2016 data fit a normal distribution.
+The 2016 data fit an exponential distribution while the 2016 data fit a normal distribution.

### 2017-06-16 Analysis.Rmd
Add headers and flesh out the conclusions

@@
 
+### 2015 Leaf Sheath Blight Severity Model
+
 ```{r 2015_LShB_severity}
@@
 
+### 2016 Leaf Sheath Blight Severity Model
+
 ```{r 2016_LShB_severity}
@@
 
-### Tiller Sheath Blight Incidence
+### Tiller Sheath Blight Incidence and Severity
 
-In 2015 the highest N treatment was significant, in 2016 the lowest N rates were significant.
+In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity.
+
+### Leaf Sheath Blight Severity
+
+In neither experiment was the leaf sheath blight affected by nitrogen rates or irrigation regime.
+
+### Interactions of Nitrogen and Irrigation Regime
+
+In neither experiment was the interaction of nitrogen with irrigation regime significant.
+
+### Model Fit
 

### 2017-06-16 Analysis.Rmd
Fix errors in the analysis
- 2015 data was used where it should have been 2016 data in the analyses

- Downgrade to dplyr 0.5.0, I don't want to fix everything so that the
warning messages go away due to new functions

- Update conclusions based on the proper analysis

@@
 ```
+
 ## Notes on this analysis before starting
@@
 
-The `AUDPS` object is created when the project is loaded, in the file [munge/03_preprocess_data.R](munge/03_preprocess_data.R).
+The `AUDPS` object is created when the project is loaded, in the file [munge/03_preprocess_data.R](./munge/03_preprocess_data.R).
 However, because it is a `tibble` and the treatments exist in a single column for graphing the raw data, this object needs a few minor changes to be usable for the analysis.
@@
                                     random = ~REP, 
-                          data = AUDPS_15,
+                          data = AUDPS_16,
                           verbose = FALSE,
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 7:10)])
+reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:6])
+trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
 trts <- melt(trts)
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(LShB_severity_lmm_2016$Sol[, c(1, 7:10)])
+reps <- data.frame(LShB_severity_lmm_2016$Sol[, c(1, 5:8)])
 reps <- melt(reps)
 
-trts <-  data.frame(LShB_severity_lmm_2016$Sol[, 2:6])
+trts <-  data.frame(LShB_severity_lmm_2016$Sol[, 2:4])
 trts <- melt(trts)
@@
 ```
+
 ## Conclusions
@@
 
-In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity.
+In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity. In 2016 the flooding treatment was significant for tiller sheath blight severity.
 
@@
 
-In neither experiment was the interaction of nitrogen with irrigation regime significant.
+In 2015 no significant itneraction was observed. In 2016 a significant interaction between flooding and nitrogen rate is observed for both the tiller and leaf severity ratings.
 

### 2017-07-23 Analysis.Rmd
Update Analysis to use percentage values, not severity scale
- Add disease progress curves in "graphs" directory

- Change the colours in the diagnostic plots to use ColorBrewer rather
than viridis for discrete colours, not continuous

@@
 AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
-AUDPS <- mutate_at(.tbl = AUDPS, .funs = factor, .cols = c("WMGT", "NRTE"))
+AUDPS <- mutate_at(.tbl = AUDPS, .funs = factor, .vars = c("WMGT", "NRTE"))
 ```
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2015 <- MCMCglmm(TShB_sev_AUDPS ~ WMGT * NRTE,
+TShB_severity_lmm_2015 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
                                     random = ~REP, 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_severity_lmm_2015 <- MCMCglmm(LShB_sev_AUDPS ~ WMGT * NRTE,
+LShB_severity_lmm_2015 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
                                     random = ~REP, 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2016 <- MCMCglmm(TShB_sev_AUDPS ~ WMGT * NRTE,
+TShB_severity_lmm_2016 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
                                     random = ~REP, 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_severity_lmm_2016 <- MCMCglmm(LShB_sev_AUDPS ~ WMGT * NRTE,
+LShB_severity_lmm_2016 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
                                     random = ~REP, 

### 2017-07-23 Probability_distribution_checks.Rmd
Update Analysis to use percentage values, not severity scale
- Add disease progress curves in "graphs" directory

- Change the colours in the diagnostic plots to use ColorBrewer rather
than viridis for discrete colours, not continuous

@@
 
-```{r 2015_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+```{r 2015_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS15 <- subset(AUDPS, YEAR == "2015")
-f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "norm")
+f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "norm")
 plot(f1)
 
-car::qqp(AUDPS15$TShB_sev_AUDPS, "norm")
+car::qqp(AUDPS15$TShB_percent_AUDPS, "norm")
 ```
@@
 
-```{r 2015_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}
-
-f1 <- fitdist(AUDPS15$TShB_sev_AUDPS, "exp")
-plot(f1)
-car::qqp(AUDPS15$TShB_sev_AUDPS, "exp")
-```
+2015 Tiller AUDPS is negative, so an exponential model will not fit
 
@@
 
-```{r 2015_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+```{r 2015_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS15 <- subset(AUDPS, YEAR == "2015")
-f1 <- fitdist(AUDPS15$LShB_sev_AUDPS, "norm")
+f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "norm")
 plot(f1)
 
-car::qqp(AUDPS15$LShB_sev_AUDPS, "norm")
+car::qqp(AUDPS15$LShB_percent_AUDPS, "norm")
 ```
@@
 
-```{r 2016_TShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+```{r 2016_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS16 <- subset(AUDPS, YEAR == "2016")
-f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "norm")
+f1 <- fitdist(AUDPS16$TShB_percent_AUDPS, "norm")
 plot(f1)
 
-car::qqp(AUDPS16$TShB_sev_AUDPS, "norm")
+car::qqp(AUDPS16$TShB_percent_AUDPS, "norm")
 ```
@@
 
-```{r 2016_TShB_sev_exp, results='hide', message=FALSE, warning=FALSE}
+```{r 2016_TShB_percent_exp, results='hide', message=FALSE, warning=FALSE}
 
-f1 <- fitdist(AUDPS16$TShB_sev_AUDPS, "exp")
+f1 <- fitdist(AUDPS16$TShB_percent_AUDPS, "exp")
 plot(f1)
-car::qqp(AUDPS16$TShB_sev_AUDPS, "exp")
+car::qqp(AUDPS16$TShB_percent_AUDPS, "exp")
 ```
@@
 
-```{r 2016_LShB_sev_norm, results='hide', message=FALSE, warning=FALSE}
+```{r 2016_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
 AUDPS16 <- subset(AUDPS, YEAR == "2016")
-f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "norm")
+f1 <- fitdist(AUDPS16$LShB_percent_AUDPS, "norm")
 plot(f1)
 
-car::qqp(AUDPS16$LShB_sev_AUDPS, "norm")
+car::qqp(AUDPS16$LShB_percent_AUDPS, "norm")
 ```
@@
 
-```{r 2016_LShB_sev_exp, results='hide', message=FALSE, warning=FALSE}
+```{r 2016_LShB_percent_exp, results='hide', message=FALSE, warning=FALSE}
 
-f1 <- fitdist(AUDPS16$LShB_sev_AUDPS, "exp")
+f1 <- fitdist(AUDPS16$LShB_percent_AUDPS, "exp")
 plot(f1)
-car::qqp(AUDPS16$LShB_sev_AUDPS, "exp")
+car::qqp(AUDPS16$LShB_percent_AUDPS, "exp")
 ```

### 2017-07-23 lib/helpers.R

@@ -24,9 +24,9 @@ plot_replicate_posteriors <- function(d, title) {
                                                color = variable,
                                                fill = variable)) +
     geom_density(alpha = 0.25) +
-    viridis::scale_fill_viridis(discrete = TRUE,
+    scale_fill_brewer(type = "qual", palette = "Set1",
                                 name = "Variable") +
-    viridis::scale_color_viridis(discrete = TRUE,
+    scale_colour_brewer(type = "qual", palette = "Set1",
                                 name = "Variable") +
     ggtitle(paste(title))
 }
@@ -37,9 +37,9 @@ plot_treatment_posteriors <- function(d, title) {
                        color = variable,
                        fill = variable)) +
     geom_density(alpha = 0.25) +
-    viridis::scale_fill_viridis(discrete = TRUE,
+    scale_fill_brewer(type = "qual", palette = "Set1",
                                 name = "Variable") +
-    viridis::scale_color_viridis(discrete = TRUE,
+    scale_colour_brewer(type = "qual", palette = "Set1",
                                   name = "Variable") +
     ggtitle(paste(title))
 }

### 2017-07-23 munge/04_visualise_data.R

@@ -103,7 +103,7 @@ ggplot(AUDPS, aes(x = as.factor(TRT), y = TShB_inc_AUDPS)) +
 ggsave("graphs/TShB_inc_AUDPS_dotplot.png", width = 6, height = 4)
 
 # dotplots of tiller sheath blight severity AUDPS data ------------------------
-ggplot(AUDPS, aes(x = as.factor(TRT), y = TShB_sev_AUDPS)) +
+ggplot(AUDPS, aes(x = as.factor(TRT), y = TShB_percent_AUDPS)) +
   geom_point(aes(colour = YEAR, shape = REP), size = 2) +
   theme(axis.text.x = element_text(size = 8,
                                    angle = 45,
@@ -111,10 +111,10 @@ ggplot(AUDPS, aes(x = as.factor(TRT), y = TShB_sev_AUDPS)) +
   xlab("Treatment") +
   ylab("AUDPS") +
   ggtitle("Tiller Sheath Blight Severity")
-ggsave("graphs/TShB_sev_AUDPS_dotplot.png", width = 6, height = 4)
+ggsave("graphs/TShB_percent_AUDPS_dotplot.png", width = 6, height = 4)
 
-# dotplots of leav sheath blight severity AUDPS data ------------------------
-ggplot(AUDPS, aes(x = as.factor(TRT), y = LShB_sev_AUDPS)) +
+# dotplots of leaf sheath blight severity AUDPS data ------------------------
+ggplot(AUDPS, aes(x = as.factor(TRT), y = LShB_percent_AUDPS)) +
   geom_point(aes(colour = YEAR, shape = REP), size = 2) +
   theme(axis.text.x = element_text(size = 8,
                                    angle = 45,
@@ -122,4 +122,43 @@ ggplot(AUDPS, aes(x = as.factor(TRT), y = LShB_sev_AUDPS)) +
   xlab("Treatment") +
   ylab("AUDPS") +
   ggtitle("Leaf Sheath Blight Severity")
-ggsave("graphs/LShB_sev_AUDPS_dotplot.png", width = 6, height = 4)
+ggsave("graphs/LShB_percent_AUDPS_dotplot.png", width = 6, height = 4)
+
+RAW_data %>% group_by(YEAR, TRT, ASMT) %>%
+  summarize(value = mean(LEAF_ShB)) %>%
+  ggplot(aes(x = ASMT,
+             y = value,
+             color = TRT,
+             group = TRT)) +
+  geom_line() +
[…]

### 2017-07-23 Probability_distribution_checks.Rmd
Update Probability_distribution_checks.Rmd/md

@@
 
-Here we check the probability distribution that best fits these data.
-I'm following a method from http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
+Here we check the probability distribution that best fits these data. I'm
+following a method from
+http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html.
 As you see in that guide, there are several distributions that can be checked.
-However, in these data only normal and exponential
+However, in these data only normal and exponential are necessary.
 
@@
 
-To read the graphs, we want to select a distribution where most of the points fall between the dotted red lines.
-On the y-axis are the observations and on the x-axis the quantiles modelled by the distribution.
-A perfect distribution fit is represented by the solid red line and the dashed red lines are the confidence intervals of the perfect distribution fit.
+To read the graphs, we want to select a distribution where most of the points
+fall between the dotted red lines. On the y-axis are the observations and on the
+x-axis the quantiles modelled by the distribution. A perfect distribution fit is
+represented by the solid red line and the dashed red lines are the confidence
+intervals of the perfect distribution fit.
 
@@
 
-The 2016 data fit an exponential distribution while the 2016 data fit a normal distribution.
+The 2015 data fit an exponential distribution while the 2016 data fit a normal
+distribution.
+
+### Leaf Sheath Blight Severity Distributions
+
+The 2015 data contain negative values, so an exponential distribution will not
+fit. The 2016 data fit a normal distribution better than exponential.
+
+### Tiller Sheath Blight Severity Distributions
+
+The 2015 data contain negative values, so an exponential distribution will not
+fit. The 2016 data fit a normal distribution better than exponential.

### 2017-07-27 munge/01_preprocess_2015_data.R
Correct errors in munging 2015 data

@@ -12,10 +12,6 @@ reformat <- function(files) {
   # add plot numbers
   x$PLOT <- rep(1:24, each = 18)
 
-  # ensure that all leaf sheath blight observations are numeric ----------------
-  x <-
-    x %>% mutate_each(funs(as.numeric), starts_with("SL"))
-
   # calculate tiller sheath blight incidence -----------------------------------
   x <-
     x %>%
@@ -81,30 +77,30 @@ reformat <- function(files) {
                   NRTE,
                   HILL,
                   TIL2,
-                  GL1,
-                  DL1,
-                  SHB1,
-                  SLA1,
-                  SLB1,
-                  SLC1,
-                  SLD1,
-                  SLE1,
-                  SLF1) %>%
+                  GL2,
+                  DL2,
+                  SHB2,
+                  SLA2,
+                  SLB2,
+                  SLC2,
+                  SLD2,
+                  SLE2,
+                  SLF2) %>%
     gather(LEAF,
            LEAF_ShB,
-           SLA1:SLF1)
+           SLA2:SLF2)
 
-  TIL2$LEAF[TIL2$LEAF == "SLA1"] <- 1
-  TIL2$LEAF[TIL2$LEAF == "SLB1"] <- 2
-  TIL2$LEAF[TIL2$LEAF == "SLC1"] <- 3
-  TIL2$LEAF[TIL2$LEAF == "SLD1"] <- 4
-  TIL2$LEAF[TIL2$LEAF == "SLE1"] <- 5
-  TIL2$LEAF[TIL2$LEAF == "SLF1"] <- 6
+  TIL2$LEAF[TIL2$LEAF == "SLA2"] <- 1
+  TIL2$LEAF[TIL2$LEAF == "SLB2"] <- 2
+  TIL2$LEAF[TIL2$LEAF == "SLC2"] <- 3
+  TIL2$LEAF[TIL2$LEAF == "SLD2"] <- 4
+  TIL2$LEAF[TIL2$LEAF == "SLE2"] <- 5
+  TIL2$LEAF[TIL2$LEAF == "SLF2"] <- 6
 
-  TIL2 <- rename(TIL2, GL = GL1)
-  TIL2 <- rename(TIL2, DL = DL1)
+  TIL2 <- rename(TIL2, GL = GL2)
+  TIL2 <- rename(TIL2, DL = DL2)
[…]

### 2017-07-27 munge/04_visualise_data.R

@@ -6,6 +6,7 @@ ggplot(RAW_data, aes(x = LEAF_ShB)) +
   ggtitle("Leaf Sheath Blight Severity Rating")
 ggsave("graphs/LShB_rating.png", width = 6, height = 4)
 
+
 # histogram plot of TShB_rating data ----------------------------------------
 ggplot(RAW_data, aes(x = TIL_ShB)) +
   geom_histogram(aes(fill = YEAR), stat = "count") +
@@ -27,21 +28,23 @@ theme(axis.text.x = element_text(size = 8,
 ggsave("graphs/TShB_incidence.png", width = 6, height = 4)
 
 
-# histogram plot of green leaf data ----------------------------------------------
+# histogram plot of green leaf data -------------------------------------------
 ggplot(RAW_data, aes(x = GL, linetype = YEAR)) +
   geom_histogram(aes(fill = YEAR), position = "dodge") +
   xlab("Count") +
   ggtitle("Green Leaves per Tiller")
 ggsave("graphs/GL_value.png", width = 6, height = 4)
 
-# histogram plot plot of dead leaf data -----------------------------------------------
+
+# histogram plot plot of dead leaf data ---------------------------------------
 ggplot(RAW_data, aes(x = DL, linetype = YEAR)) +
   geom_histogram(aes(fill = YEAR), position = "dodge") +
   xlab("Count") +
   ggtitle("Dry Leaves per Tiller")
 ggsave("graphs/DL_value.png", width = 6, height = 4)
 
-# dot plot of leaf sheath blight severity data ---------------------------------
+
+# dot plot of leaf sheath blight severity data --------------------------------
 ggplot(RAW_data, aes(x = ASMT, y = LEAF_ShB)) +
   geom_point(position = position_jitter(width = 0.05),
              aes(colour = YEAR), size = 0.75) +
@@ -51,6 +54,7 @@ ggplot(RAW_data, aes(x = ASMT, y = LEAF_ShB)) +
   facet_grid(. ~ TRT) +
   theme(strip.text.x = element_text(angle = 90))
 ggsave("graphs/LShB_severity_over_time.png", width = 6, height = 4)
+
 
 # dot plot of tiller sheath blight severity data ------------------------------
 ggplot(RAW_data, aes(x = ASMT, y = TIL_ShB)) +
[…]

### 2017-07-31 Analysis.Rmd
Update for dplyr 0.7; fix munging issues in DS2015 data; generate new graphs

@@
 
-In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity. In 2016 the flooding treatment was significant for tiller sheath blight severity.
+In 2015 and 2016 the highest N treatments (note that they were different amounts
+in these two years) were significant in both the tiller
+sheath blight incidence and severity. In 2016 the flooding treatment was
+significant for tiller sheath blight severity.
 
@@
 
-In 2015 no significant itneraction was observed. In 2016 a significant interaction between flooding and nitrogen rate is observed for both the tiller and leaf severity ratings.
+In 2015 no significant interaction was observed. In 2016 a significant interaction between flooding and nitrogen rate is observed for both the tiller and leaf severity ratings.
 

### 2017-07-31 munge/01_preprocess_2015_data.R

@@ -1,10 +1,64 @@
-# Preprocess 2015 data for all assessments
+# Preprocess 2015 data for all assessment dates
 
 files <-
   list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)
 
 reformat <- function(files) {
-  x <- read_csv(files)
+  x <- read_csv(
+    files,
+    cols(
+      col_character(),
+      col_character(),
+      col_character(),
+      col_character(),
+      col_character(),
+      col_character(),
+      col_double(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer(),
+      col_integer()
+    ),
+    col_names = TRUE
+  )
   x[is.na(x)] <- 0
 
   x <- arrange(x, REP, TRT)
@@ -20,25 +74,24 @@ reformat <- function(files) {
   x$TShB_incidence <- round(x$TShB_incidence, 2)
 
   TShB_incidence <-
-    x %>% select(REP,
-                 TRT,
-                 WMGT,
-                 NRTE,
-                 SMPL,
-                 HILL,
-                 HGHT,
-                 NTIL,
-                 NTShB,
-                 TShB_incidence)
+    x %>% dplyr::select(REP,
+                        TRT,
+                        WMGT,
+                        NRTE,
+                        SMPL,
+                        HILL,
+                        HGHT,
+                        NTIL,
[…]

### 2017-07-31 munge/02-preprocess_2016_data.R

@@ -92,24 +92,25 @@ DS2016$TRT[which(DS2016$WMGT == "AWD" &
 
 DS2016 <-
   DS2016 %>%
-  gather(LEAF,
-         LEAF_ShB,
-         starts_with("ShBL"),
-         -DATE,
-         -ASMT,
-         -PLOT,
-         -TRT,
-         -REP,
-         -WMGT,
-         -SMPL,
-         -NRTE,
-         -HILL,
-         -NTIL,
-         -GL,
-         -DL,
-         -NTShB,
-         -NSHShB,
-         -TIL
+  gather(
+    LEAF,
+    LEAF_ShB,
+    starts_with("ShBL"),
+    -DATE,
+    -ASMT,
+    -PLOT,
+    -TRT,
+    -REP,
+    -WMGT,
+    -SMPL,
+    -NRTE,
+    -HILL,
+    -NTIL,
+    -GL,
+    -DL,
+    -NTShB,
+    -NSHShB,
+    -TIL
   )
 
 # reclassify LEAF column to leaf numbers 1...6
@@ -141,7 +142,7 @@ DS2016$YEAR <- year(DS2016$DATE)
 DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)
 
 DS2016 <-
-  DS2016 %>% select(
+  DS2016 %>% dplyr::select(
     YEAR,
     DATE,
     ASMT,
@@ -175,7 +176,39 @@ DAYS_2016 <- time_length(DATE_1 - DATE_2, unit = "day")
 DS2016$DAYS <-
   c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)
 
-rm(DS2016_A1, DS2016_A2, DS2016_A3, DS2016_A4, DATE_1, DATE_1_2016, DATE_2, DATE_2_2016, DAYS_2016)
+rm(
+  DS2016_A1,
+  DS2016_A2,
+  DS2016_A3,
+  DS2016_A4,
+  DATE_1,
+  DATE_1_2016,
+  DATE_2,
+  DATE_2_2016,
+  DAYS_2016
+)
+
+DS2016 <-
+  DS2016 %>% dplyr::select(
+    YEAR,
+    DATE,
+    ASMT,
+    REP,
+    PLOT,
+    TRT,
+    SMPL,
+    HILL,
+    TIL,
+    LEAF,
+    GL,
+    DL,
+    TShB_incidence,
+    TIL_ShB,
+    LEAF_ShB,
+    WMGT,
[…]

### 2017-07-31 munge/03_preprocess_data.R

@@ -69,8 +69,8 @@ DS2016 <- subset(RAW_data, YEAR == "2016")
 TShB_inc_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_each(funs(round(mean(., na.rm = TRUE), 2)),
-                 PLOT_TShB_incidence = TShB_incidence) %>%
+  summarise_at(.funs = funs(round(mean(., na.rm = TRUE), 2)),
+               .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
   arrange(PLOT)
 
 TShB_inc_wide <-
@@ -79,8 +79,8 @@ TShB_inc_wide <-
 TShB_sev_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_each(funs(round(mean(., na.rm = TRUE), 2)),
-                 PLOT_TShB_severity = TIL_ShB) %>%
+  summarise_at(.funs = funs(round(mean(., na.rm = TRUE), 2)),
+               .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
   arrange(PLOT)
 
 TShB_sev_wide <-
@@ -89,8 +89,8 @@ TShB_sev_wide <-
 TShB_perc_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_each(funs(round(mean(., na.rm = TRUE), 2)),
-                 PLOT_TShB_PERCENT = PERC_TIL_ShB) %>%
+  summarise_at(.funs = funs(round(mean(., na.rm = TRUE), 2)),
+               .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
   arrange(PLOT)
 
 TShB_perc_wide <-
@@ -99,8 +99,8 @@ TShB_perc_wide <-
 LShB_sev_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_each(funs(round(mean(., na.rm = TRUE), 2)),
-                 PLOT_LShB_severity = LEAF_ShB) %>%
+  summarise_at(.funs = funs(round(mean(., na.rm = TRUE), 2)),
[…]

### 2017-07-31 munge/04_visualise_data.R
follow same naming convention for all graphs
Also fixes README.md not displaying all graphs

@@ -95,7 +95,7 @@ ggplot(RAW_data, aes(x = TRT, y = TShB_incidence)) +
   xlab("Treatment") +
   ylab("Incidence per Hill") +
   ggtitle("Tiller Sheath Blight Incidence")
-ggsave("graphs/TShB_Incidence_plot.png", width = 6, height = 4)
+ggsave("graphs/TShB_incidence_plot.png", width = 6, height = 4)
 
 
 # dotplots of tiller sheath blight incidence AUDPS data ------------------------
@@ -176,4 +176,4 @@ RAW_data %>% group_by(YEAR, WMGT, TRT, ASMT) %>%
   ylab("Mean Tiller Sheath Blight Incidence") +
   facet_grid(. ~ YEAR) +
   ggtitle("Tiller Sheath Blight Incidence Disease Progress Curves")
-ggsave("graphs/TShB_Incidence_progress_curves.png", width = 6, height = 4)
+ggsave("graphs/TShB_incidence_progress_curves.png", width = 6, height = 4)

### 2017-07-31 Probability_distribution_checks.Rmd
Correct errors in munging 2015 data
Correct days for AUDPS calculation in 2015

@@
 
-## 2016
+## 2015
 
@@
 car::qqp(AUDPS15$TShB_inc_AUDPS, "norm")
+
 ```
 
-#### Tiller Incidence Exponential
+#### Tiller Incidence Log Normal
 
-```{r 2015_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}
+```{r 2015_TShB_inc_norm, results='hide', message=FALSE, warning=FALSE}
+AUDPS15 <- subset(AUDPS, YEAR == "2015")
+f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "lnorm")
+plot(f1)
 
-f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
-plot(f1)
-car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
+car::qqp(AUDPS15$TShB_inc_AUDPS, "lnorm")
 ```
@@
 
-These data do not fit this distribution, all values must be positive.
+These data do not fit this distribution, all values must be positive. There are
+negative AUDPS values present.
 

### 2017-07-31 munge/01_preprocess_2015_data.R

@@ -225,7 +225,7 @@ DS2015 <- as_tibble(arrange(DS2015, ASMT, PLOT))
 
 DAYS <- as.numeric(substr(files, 17, 18))
 
-DS2015$DAYS <- c(rep(0, 432), rep(diff(DAYS), each = 432))
+DS2015$DAYS <- c(rep(0, 10368), rep(diff(DAYS), each = 10368))
 
 rm(files, reformat)
 

### 2017-07-31 munge/03_preprocess_data.R

@@ -38,6 +38,7 @@ RAW_data$TRT <-
   )
 
 # add column with midpoint % tiller ShB severity
+
 RAW_data <- mutate(RAW_data, PERC_TIL_ShB = ifelse(TIL_ShB == 0, 0,
                                                    ifelse(
                                                      TIL_ShB == 1, 1,
@@ -66,6 +67,7 @@ DS2016 <- subset(RAW_data, YEAR == "2016")
 # calculate AUDPS values -------------------------------------------------------
 
 # 2015 AUDPS -------------------------------------------------------------------
+# 2015 Tiller Incidence AUDPS --------------------------------------------------
 TShB_inc_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
@@ -76,6 +78,7 @@ TShB_inc_15 <-
 TShB_inc_wide <-
   dcast(TShB_inc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_incidence")
 
+# 2015 Tiller Severity AUDPS ---------------------------------------------------
 TShB_sev_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
@@ -96,6 +99,7 @@ TShB_perc_15 <-
 TShB_perc_wide <-
   dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")
 
+# 2015 Leaf Severity AUDPS -----------------------------------------------------
 LShB_sev_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
@@ -149,7 +153,7 @@ TShB_inc_15$PLOT <- as.character(TShB_inc_15$PLOT)
 ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")
 
 # 2016 AUDPS -------------------------------------------------------------------
-
+# 2015 Tiller Incidence AUDPS --------------------------------------------------
 TShB_inc_16 <-
   DS2016 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
@@ -169,6 +173,8 @@ TShB_sev_16 <-
 
 TShB_sev_wide <-
   dcast(TShB_sev_16, PLOT ~ ASMT, value.var = "PLOT_TShB_severity")
+
[…]

### 2017-07-31 munge/04_visualise_data.R

@@ -118,7 +118,7 @@ ggplot(AUDPS, aes(x = as.factor(TRT), y = TShB_percent_AUDPS)) +
                                    hjust = 1)) +
   xlab("Treatment") +
   ylab("AUDPS") +
-  ggtitle("Tiller Sheath Blight Severity")
+  ggtitle("Tiller Sheath Blight")
 ggsave("graphs/TShB_percent_AUDPS_dotplot.png", width = 6, height = 4)
 
 
@@ -130,20 +130,20 @@ ggplot(AUDPS, aes(x = as.factor(TRT), y = LShB_percent_AUDPS)) +
                                    hjust = 1)) +
   xlab("Treatment") +
   ylab("AUDPS") +
-  ggtitle("Leaf Sheath Blight Severity")
+  ggtitle("Leaf Sheath Blight")
 ggsave("graphs/LShB_percent_AUDPS_dotplot.png", width = 6, height = 4)
 
 
-# line graph of leaf sheath blight severity AUDPS data ------------------------
+# line graph of leaf sheath blight severity data -------------------------------
 RAW_data %>% group_by(YEAR, WMGT, TRT, ASMT) %>%
-  summarize(value = mean(LEAF_ShB)) %>%
+  summarize(value = mean(PERC_LEAF_ShB)) %>%
   ggplot(aes(x = ASMT,
              y = value,
              color = TRT,
              group = TRT)) +
   geom_line(aes(linetype = WMGT)) +
   xlab("Assessment") +
-  ylab("Mean Sheath Blight Severity Rating") +
+  ylab("Severity (%)") +
   facet_grid(. ~ YEAR) +
   ggtitle("Leaf Sheath Blight Severity Disease Progress Curves")
 ggsave("graphs/LShB_progress_curves.png", width = 6, height = 4)
@@ -151,16 +151,16 @@ ggsave("graphs/LShB_progress_curves.png", width = 6, height = 4)
 
 # line graph of tiller sheath blight severity AUDPS data ----------------------
 RAW_data %>% group_by(YEAR, WMGT, TRT, ASMT) %>%
-  summarize(value = mean(TIL_ShB)) %>%
+  summarize(value = mean(PERC_TIL_ShB)) %>%
   ggplot(aes(x = ASMT,
              y = value,
              color = TRT,
              group = TRT)) +
   geom_line(aes(linetype = WMGT)) +
[…]

### 2017-07-31 munge/testing_models.R
Update probability distribution checks

@@ -1,3 +1,0 @@
-# library(ordinal)
-# Res.clmm <- clmm(TIL_ShB  ~ WMGT * NRTE + (1 | REP/TRT/SMPL/HILL/TIL/LEAF), data = DS2015)
-# summary(Res.clmm)

### 2017-07-31 01-Probability_distribution_checks.Rmd
Rename Probability check file to "01-..." to suggest order in which to run

--- 2017-07-23 Probability_distribution_checks.Rmd
@@
 car::qqp(AUDPS15$TShB_inc_AUDPS, "norm")
+
 ```
@@
 
-```{r 2015_TShB_inc_exp, results='hide', message=FALSE, warning=FALSE}
-
+```{r 2015_TShB_incidence_exp, results='hide', message=FALSE, warning=FALSE}
 f1 <- fitdist(AUDPS15$TShB_inc_AUDPS, "exp")
 plot(f1)
+
 car::qqp(AUDPS15$TShB_inc_AUDPS, "exp")
@@
 ```{r 2015_TShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
-AUDPS15 <- subset(AUDPS, YEAR == "2015")
 f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "norm")
@@
 
-2015 Tiller AUDPS is negative, so an exponential model will not fit
+```{r 2015_TShB_percent_exp, results='hide', message=FALSE, warning=FALSE}
+f1 <- fitdist(AUDPS15$TShB_percent_AUDPS, "exp")
+plot(f1)
+
+car::qqp(AUDPS15$TShB_percent_AUDPS, "exp")
+```
 
@@
 ```{r 2015_LShB_percent_norm, results='hide', message=FALSE, warning=FALSE}
-AUDPS15 <- subset(AUDPS, YEAR == "2015")
 f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "norm")
@@
 
-These data do not fit this distribution, all values must be positive.
+```{r 2015_LShB_percent_exp, results='hide', message=FALSE, warning=FALSE}
+f1 <- fitdist(AUDPS15$LShB_percent_AUDPS, "exp")
+plot(f1)
+
+car::qqp(AUDPS15$LShB_percent_AUDPS, "exp")
+```
 

### 2017-07-31 02-Analysis.Rmd
Update analysis posterior graphs

--- 2017-07-31 Analysis.Rmd
@@
 ```{r create_analysis_df}
-AUDPS_15 <- as.data.frame(AUDPS[AUDPS$YEAR == 2015, ])
-AUDPS_15 <- droplevels(AUDPS_15)
+AUDPS_2015 <- as.data.frame(AUDPS[AUDPS$YEAR == 2015, ])
+AUDPS_2015 <- droplevels(AUDPS_2015)
 
@@
                                     random = ~REP, 
-                          data = AUDPS_15,
+                          data = AUDPS_2015,
                           verbose = FALSE,

### 2017-07-31 lib/helpers.R

@@ -4,7 +4,6 @@ helper.function <- function()
 }
 
 plot_diagnostic_lines <- function(d, x, title) {
-
   # Diagnostic line plots for replicate
   ggplot(data = d, aes(
     x = rep(x, length(unique(d$variable))),
@@ -20,28 +19,22 @@ plot_diagnostic_lines <- function(d, x, title) {
 }
 
 plot_replicate_posteriors <- function(d, title) {
-  ggplot(d[d$variable != "X.Intercept.",], aes(x = value,
-                                               color = variable,
-                                               fill = variable)) +
-    geom_density(alpha = 0.25) +
-    scale_fill_brewer(type = "qual", palette = "Set1",
-                                name = "Variable") +
-    scale_colour_brewer(type = "qual", palette = "Set1",
-                                name = "Variable") +
-    ggtitle(paste(title))
+  ggplot(data = d[d$variable != "X.Intercept.", ], aes(x = variable,
+                                                       y = value)) +
+    geom_violin() +
+    geom_abline(slope = 0, intercept = 0) +
+    ggtitle(paste(title)) +
+    theme(axis.text.x = element_text(angle = 35, hjust = 1))
 }
 
 
 plot_treatment_posteriors <- function(d, title) {
-  ggplot(data = d, aes(x = value,
-                       color = variable,
-                       fill = variable)) +
-    geom_density(alpha = 0.25) +
-    scale_fill_brewer(type = "qual", palette = "Set1",
-                                name = "Variable") +
-    scale_colour_brewer(type = "qual", palette = "Set1",
-                                  name = "Variable") +
-    ggtitle(paste(title))
+  ggplot(data = d, aes(x = variable,
+                       y = value)) +
+    geom_violin() +
+    geom_abline(slope = 0, intercept = 0) +
+    ggtitle(paste(title)) +
+    theme(axis.text.x = element_text(angle = 35, hjust = 1))
 }
 
 plot_joint_random_error_dist <- function(d, title) {

### 2017-07-31 02-Analysis.Rmd
Update analysis

@@
 
-AUDPS_16 <- as.data.frame(AUDPS[AUDPS$YEAR == 2016, ])
-AUDPS_16 <- droplevels(AUDPS_16)
+AUDPS_2016 <- as.data.frame(AUDPS[AUDPS$YEAR == 2016, ])
+AUDPS_2016 <- droplevels(AUDPS_2016)
 ```
@@
                                     random = ~REP, 
-                          data = AUDPS_16,
+                          data = AUDPS_2016,
                           verbose = FALSE,
@@
 In 2015 and 2016 the highest N treatments (note that they were different amounts
-in these two years) were significant in both the tiller
-sheath blight incidence and severity. In 2016 the flooding treatment was
-significant for tiller sheath blight severity.
+in these two years) were significant in both the tiller sheath blight incidence
+and severity. In 2016 the flooding treatment was significant for tiller sheath
+blight severity.
 

### 2017-08-01 Analysis.Rmd
Clarify analysis further
# Main changes

- Reorder base factors for analysis to make interpretation easier

- Add more detail on how the MCMCglmm models are set up and should be
interpreted

- Add more detail interpreting the model outputs

# Minor changes

- Remove probability distribution checks

- Update README.md

- Add links to more resources

--- 2017-07-23 Analysis.Rmd
@@
 
-## Notes on this analysis before starting
+## Notes on This Analysis Before Starting
+
+If you have not already looked at the
+[01-Probability_distribution_checks](01-Probability_distribution_checks.md),
+please see that first to understand why MCMCglmm was chosen for this analysis
+due to the nature of the data.
 
@@
 
-#### How to interpret these analyses
+#### Interpreting these analyses
 
@@
 
+I found this CrossValidated topic to be useful in interpreting the outputs from
+MCMCglmm as it explains the interpretation of the effects. While it is about
+output from a `lmer`, the output is read in the same way, [How to interpret 2-way and 3-way interaction in lmer?](https://stats.stackexchange.com/questions/87412/how-to-interpret-2-way-and-3-way-interaction-in-lmer#87415).
+
+The base levels for this analysis are:
+
+- 2015 `NRTE:0`
+
+- 2015 `WMGT:FLD`
+
+- 2016 `NRTE:60`
+
+- 2016 `WMGT:FLD`
+
 #### Changes between 2015 and 2016
@@
 be combined due to changes in inoculation methods; there are other changes too,
-but the main one is this. Therefore, the analyses will be conducted separately for
-leaf severity and Leaf severity for 2015 dry season and 2016 dry season.
-Comparisons will only be observational and cannot be statistically compared.
+but the main one is this. Therefore, the analyses will be conducted separately
+such that comparisons will only be observational and cannot be statistically
+compared.
 
-#### Iterations
+#### MCMCglmm model fitting notes
 
@@
 
-First, separate the TRT column into the two treatments for analysis
+First, separate the TRT column into the two treatments for analysis.
 
@@
 ```{r create_analysis_df}
-AUDPS_15 <- as.data.frame(AUDPS[AUDPS$YEAR == 2015, ])
-AUDPS_15 <- droplevels(AUDPS_15)
+AUDPS_2015 <- as.data.frame(AUDPS[AUDPS$YEAR == 2015, ])
+AUDPS_2015 <- droplevels(AUDPS_2015)
 
-AUDPS_16 <- as.data.frame(AUDPS[AUDPS$YEAR == 2016, ])
-AUDPS_16 <- droplevels(AUDPS_16)
+# relevel factors for easier interpretation of  analysis
+AUDPS_2015 <- within(AUDPS_2015, NRTE <- relevel(NRTE, ref = "N0"))
+AUDPS_2015 <- within(AUDPS_2015, WMGT <- relevel(WMGT, ref = "FLD"))
+
+AUDPS_2016 <- as.data.frame(AUDPS[AUDPS$YEAR == 2016, ])
+AUDPS_2016 <- droplevels(AUDPS_2016)
+
+# relevel factors for easier interpretation of  analysis
+AUDPS_2016 <- within(AUDPS_2016, NRTE <- relevel(NRTE, ref = "N60"))
+AUDPS_2016 <- within(AUDPS_2016, WMGT <- relevel(WMGT, ref = "FLD"))
 ```
 
-Now that the `AUDPS_15` and `AUDPS_16` `data.frames` exist, we can start the analysis.
+Now that the `AUDPS_2015` and `AUDPS_2016` `data.frames` exist, we can start the analysis.
 
@@
 
-## Conclusions
-
-### Tiller Sheath Blight Incidence and Severity
-
-In 2015 and 2016 the highest N treatment was significant in both the tiller sheath blight incidence and severity. In 2016 the flooding treatment was significant for tiller sheath blight severity.
-
-### Leaf Sheath Blight Severity
-
-In neither experiment was the leaf sheath blight affected by nitrogen rates or irrigation regime.
-
-### Interactions of Nitrogen and Irrigation Regime
-
-In 2015 no significant itneraction was observed. In 2016 a significant interaction between flooding and nitrogen rate is observed for both the tiller and leaf severity ratings.
-
 ### Model Fit
@@
 
-None of the diagnostic plots show any signs of autocorrelation or any other obvious patterns.
+None of the diagnostic plots show any signs of auto-correlation or any other obvious patterns.
 
@@
 
-The random effects are all fairly equally distributed except for 2016 tiller sheath blight severity where water management:replicate has a larger effect.
-This is not surprising given that the plot and replicate sizes were different in 2016 due to the use of two fields in the IRRI experiment station, see the [2016 plot layout plan](https://github.com/adamhsparks/AWD_ShB_Interaction/blob/master/doc/Metadata/2016%20AWD%20ShB%20Metadata/ExptLayoutAWD2016.pdf).
+## Conclusions
+
+### Tiller Sheath Blight Incidence
+
+In 2015 the highest N rate, N120, was significantly different from the base, N0 rate.
+
+In 2016 both the AWD and highest N rate, N180, were significantly different from the FLD and N60 treatments.
+
+No interactions were found to be significant in the tiller sheath blight incidence.
+
+## Tiller Sheath Blight Severity
+
+In 2015 both the N100 and N120 rates were significantly different from the N0 treatment. The interaction of the N100 rate with AWD was also significantly different than N0 and FLD treatments.
+
+In 2016 the N180 was significantly different from the N60 rate and the interaction of the N180 and AWD was significantly different than the N60 and FLD interaction.
+
+### Leaf Sheath Blight Severity
+
+In 2015 the N120 was significantly different than the N0 treatment. The interactions of both the N100 and N120 with AWD were significantly different than the N0 FLD interaction.
+
+In 2016 the N180 was significantly different from the N60 treatment.
+The AWD was significantly different from the FLD and the interaction of N180:AWD was significantly different from the N60:FLD treatments interaction.
 

### 2017-08-01 test_analysis.Rmd
Add test analysis with lme4; clean up Analysis.Rmd file

--- 2017-08-01 Analysis.Rmd
@@
 ---
-title: "Analysis of split plot design using MCMCglmm"
+  title: "Analysis of split plot design using lme4"
 output: github_document
@@
 ## Notes on This Analysis Before Starting
-
-If you have not already looked at the
-[01-Probability_distribution_checks](01-Probability_distribution_checks.md),
-please see that first to understand why MCMCglmm was chosen for this analysis
-due to the nature of the data.
-
-The analyses are semi-automated.
-When this file is knit, it automatically loads the _ProjectTemplate_ package and calls the `load.project()` function.
-This loads the data, cleans and munges it creating the `AUDPS` data frame used for the analysis below.
-The scripts used to clean and munge the data are located in the [munge](./munge) folder and numbered in the sequential order in which they are run.
-
-#### Interpreting these analyses
-
-For a quick overview, see this thread on Stack Overflow that walks through the output of `summary.MCMCglmm`,
-which is used below. [R: Making sense of the output of a MCMCglmm](http://stackoverflow.com/questions/20993643/r-making-sense-of-the-output-of-a-mcmcglmm)
-
-The MCMCglmm documentation is more in-depth but should still be referenced.
-```{r MCMCglmm, eval=FALSE}
-library(MCMCglmm)
-vignette("Overview")
-vignette("CourseNotes")
-```
-
-I found this CrossValidated topic to be useful in interpreting the outputs from
-MCMCglmm as it explains the interpretation of the effects. While it is about
-output from a `lmer`, the output is read in the same way, [How to interpret 2-way and 3-way interaction in lmer?](https://stats.stackexchange.com/questions/87412/how-to-interpret-2-way-and-3-way-interaction-in-lmer#87415).
 
@@
 
-#### MCMCglmm model fitting notes
-
-Fitting the models with the default iterations resulted in some less than
-acceptable models. Because of this, the number of iterations has been increased,
-`nitt = 5e+05` and `burnin = 5000` and `thin = 100`. This results in much
-smaller errors for random effects and better models.
-
 ## Setup
-
-Use `set.seed()` for reproducibility.
-
-```{r set_seed}
-set.seed(27)
-```
 
@@
 ```{r 2015_TShB_incidence}
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2015 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE,
-                                    random = ~REP, 
-                          data = AUDPS_2015,
-                          verbose = FALSE,
-                          prior = eprior,
-                          nitt = 5e+05,
-                          burnin = 5000,
-                          thin = 100,
-                          pr = TRUE)
+library(pbkrtest)
+lmodr <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
+lmoda <- lmer(TShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
 
-summary(TShB_incidence_lmm_2015)
+KRmodcomp(lmodr, lmoda)
 
-# create data frames for generating diagnostic plots
-reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
-reps <- melt(reps)
+lmodi <- lmer(yield ~ irrigation + (1|field),data=irrigation)
+KRmodcomp(lmoda, lmodi)
 
-trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_incidence_lmm_2015$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Incidence")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Incidence")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2015 Posteriors for Treatments, Tiller ShB Incidence")
-
-# check random effects
-plotTrace(TShB_incidence_lmm_2015$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(TShB_incidence_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Random Error Distribution for Tiller ShB Incidence"))
+lmodv <- lmer(yield ~  variety + (1|field),data=irrigation)
+KRmodcomp(lmoda, lmodv)
 ```

### 2017-08-01 lme4_analysis.Rmd
Add analysis using lme4
The models don’t appear to be a good fit though, mainly for comment
from Nancy

--- 2017-08-01 test_analysis.Rmd
@@
 ```{r 2015_TShB_incidence}
-library(pbkrtest)
-lmodr <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
-lmoda <- lmer(TShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
+library(lme4)
+library(lsmeans)
+TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
+summary(TShB_inc_AUDPS)
 
-KRmodcomp(lmodr, lmoda)
+plot(TShB_inc_AUDPS)
+qqnorm(resid(TShB_inc_AUDPS))
+qqline(resid(TShB_inc_AUDPS))
 
-lmodi <- lmer(yield ~ irrigation + (1|field),data=irrigation)
-KRmodcomp(lmoda, lmodi)
-
-lmodv <- lmer(yield ~  variety + (1|field),data=irrigation)
-KRmodcomp(lmoda, lmodv)
+print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
+print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
+print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2015_TShB_severity}
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2015 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP,
-                                   data = AUDPS_2015,
-                                   verbose = FALSE,
-                                   prior = eprior,
-                                   nitt = 5e+05,
-                                   burnin = 5000,
-                                   thin = 100,
-                                   pr = TRUE)
+TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
+summary(TShB_sev_AUDPS)
 
-summary(TShB_severity_lmm_2015)
+plot(TShB_sev_AUDPS)
+qqnorm(resid(TShB_sev_AUDPS))
+qqline(resid(TShB_sev_AUDPS))
 
-# create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
-reps <- melt(reps)
-
-trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_severity_lmm_2015$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Replicates, Tiller ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2015 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Treatments, Tiller ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2015 Posteriors for Treatments, Tiller ShB Severity")
-
-# check random effects
-plotTrace(TShB_severity_lmm_2015$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(TShB_severity_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Random Error Distribution for Tiller ShB Severity"))
+print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
+print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
+print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2015_LShB_severity}
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_severity_lmm_2015 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP,
-                                   data = AUDPS_2015,
-                                   verbose = FALSE,
-                                   prior = eprior,
-                                   nitt = 5e+05,
-                                   burnin = 5000,
-                                   thin = 100,
-                                   pr = TRUE)
+LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
+summary(LShB_sev_AUDPS)
 
-summary(LShB_severity_lmm_2015)
+plot(LShB_sev_AUDPS)
+qqnorm(resid(LShB_sev_AUDPS))
+qqline(resid(LShB_sev_AUDPS))
 
-# create data frames for generating diagnostic plots
-reps <- data.frame(LShB_severity_lmm_2015$Sol[, c(1, 7:10)])
-reps <- melt(reps)
-
-trts <-  data.frame(LShB_severity_lmm_2015$Sol[, 2:6])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(LShB_severity_lmm_2015$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Replicates, Leaf ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2015 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2015 Diagnostic Plots for Treatments, Leaf ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2015 Posteriors for Treatments, Leaf ShB Severity")
-
-# check random effects
-plotTrace(LShB_severity_lmm_2015$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(LShB_severity_lmm_2015$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2015 Random Error Distribution for Leaf ShB Severity"))
+print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
+print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
+print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2016_TShB_incidence}
+TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
+summary(TShB_inc_AUDPS)
 
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
+plot(TShB_inc_AUDPS)
+qqnorm(resid(TShB_inc_AUDPS))
+qqline(resid(TShB_inc_AUDPS))
 
-TShB_incidence_lmm_2016 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE,
-                                    random = ~REP,
-                                    data = AUDPS_2016,
-                                    verbose = FALSE,
-                                    prior = eprior,
-                                    nitt = 5e+05,
-                                    burnin = 5000,
-                                    thin = 100,
-                                    pr = TRUE)
-
-summary(TShB_incidence_lmm_2016)
-
-# create data frames for generating diagnostic plots
-reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:8)])
-reps <- melt(reps)
-
-trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_incidence_lmm_2016$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Incidence")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Incidence")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Incidence")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2016 Posteriors for Treatments, Tiller ShB Incidence")
-
-# check random effects
-plotTrace(TShB_incidence_lmm_2016$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(TShB_incidence_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Random Error Distribution for Tiller ShB Incidence"))
+print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
+print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
+print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2016_TShB_severity}
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2016 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP,
-                                   data = AUDPS_2016,
-                                   verbose = FALSE,
-                                   prior = eprior,
-                                   nitt = 5e+05,
-                                   burnin = 5000,
-                                   thin = 100,
-                                   pr = TRUE)
+TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
+summary(TShB_sev_AUDPS)
 
-summary(TShB_severity_lmm_2016)
+plot(TShB_sev_AUDPS)
+qqnorm(resid(TShB_sev_AUDPS))
+qqline(resid(TShB_sev_AUDPS))
 
-# create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
-reps <- melt(reps)
-
-trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(TShB_severity_lmm_2016$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Replicates, Tiller ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2016 Reps Replicate Posteriors for Replicates, Tiller ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Treatments, Tiller ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2016 Posteriors for Treatments, Tiller ShB Severity")
-
-# check random effects
-plotTrace(TShB_severity_lmm_2016$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(TShB_severity_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Random Error Distribution for Tiller ShB Severity"))
+print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
+print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
+print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2016_LShB_severity}
-eprior <- list(R = list(V = 1, nu = 0.02),
-               G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_severity_lmm_2016 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
-                                   random = ~REP,
-                                   data = AUDPS_2016,
-                                   verbose = FALSE,
-                                   prior = eprior,
-                                   nitt = 5e+05,
-                                   burnin = 5000,
-                                   thin = 100,
-                                   pr = TRUE)
+LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
+summary(LShB_sev_AUDPS)
 
-summary(LShB_severity_lmm_2016)
+plot(LShB_sev_AUDPS)
+qqnorm(resid(LShB_sev_AUDPS))
+qqline(resid(LShB_sev_AUDPS))
 
-# create data frames for generating diagnostic plots
-reps <- data.frame(LShB_severity_lmm_2016$Sol[, c(1, 5:8)])
-reps <- melt(reps)
-
-trts <-  data.frame(LShB_severity_lmm_2016$Sol[, 2:4])
-trts <- melt(trts)
-
-# Create a dummy x-axis variable for plotting
-x <- 1:nrow(LShB_severity_lmm_2016$Sol)
-
-# diagnostic line plots for replicate
-plot_diagnostic_lines(d = reps,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Replicates, Leaf ShB Severity")
-
-# posterior distributions for replicate
-plot_replicate_posteriors(d = reps,
-                          title = "2016 Reps Replicate Posteriors for Replicates, Leaf ShB Severity")
-
-# diagnostic line plots for treatments
-plot_diagnostic_lines(d = trts,
-                      x = x,
-                      title = "2016 Diagnostic Plots for Treatments, Leaf ShB Severity")
-
-# Posterior distributions for treatment
-plot_treatment_posteriors(d = trts,
-                          title = "2016 Posteriors for Treatments, Leaf ShB Severity")
-
-# check random effects
-plotTrace(LShB_severity_lmm_2016$VCV, log = TRUE)
-
-# plot joint distibution of error
-rdf <- data.frame(LShB_severity_lmm_2016$VCV)
-plot_joint_random_error_dist(d = rdf,
-                             title = ("2016 Random Error Distribution for Leaf ShB Severity"))
+print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ NRTE)), adjust = c("tukey"))
+print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
+print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
-
-### Model Fit
-
-The models all appear to be good fits.
-
-None of the diagnostic plots show any signs of auto-correlation or any other obvious patterns.
-
-The random effects all appear to be acceptable, the dotted line stays near to the solid line with no discernible patterns.
 
@@
 
-### Tiller Sheath Blight Incidence
-
-In 2015 the highest N rate, N120, was significantly different from the base, N0 rate.
-
-In 2016 both the AWD and highest N rate, N180, were significantly different from the FLD and N60 treatments.
-
-No interactions were found to be significant in the tiller sheath blight incidence.
-
-## Tiller Sheath Blight Severity
-
-In 2015 both the N100 and N120 rates were significantly different from the N0 treatment. The interaction of the N100 rate with AWD was also significantly different than N0 and FLD treatments.
-
-In 2016 the N180 was significantly different from the N60 rate and the interaction of the N180 and AWD was significantly different than the N60 and FLD interaction.
-
-### Leaf Sheath Blight Severity
-
-In 2015 the N120 was significantly different than the N0 treatment. The interactions of both the N100 and N120 with AWD were significantly different than the N0 FLD interaction.
-
-In 2016 the N180 was significantly different from the N60 treatment.
-The AWD was significantly different from the FLD and the interaction of N180:AWD was significantly different from the N60:FLD treatments interaction.
+The `lme4` `lmer` models do not appear to be a good fit based on the qqplots.
+However, they do seem to agree with the `MCMCglmm` analysis results. But I'm
+dubious about using these models based on the diagnostics that I see above.
 

### 2017-08-02 lme4_analysis.Rmd
TShSB Incidence didn't run interactions
Fix that issue. Now runs WMGT * NRTE not WMGT + NRTE

@@
 library(lsmeans)
-TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
+TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
 summary(TShB_inc_AUDPS)
@@
 ```{r 2016_TShB_incidence}
-TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
+TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
 summary(TShB_inc_AUDPS)

### 2017-08-03 lme4_analysis.Rmd
Clean up summary output of lmer

@@
 TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
-summary(TShB_inc_AUDPS)
+print(summary(TShB_inc_AUDPS), correlation = FALSE)
 
@@
 TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
-summary(TShB_sev_AUDPS)
+print(summary(TShB_sev_AUDPS), correlation = FALSE)
 
@@
 LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
-summary(LShB_sev_AUDPS)
+print(summary(LShB_sev_AUDPS), correlation = FALSE)
 
@@
 TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
-summary(TShB_inc_AUDPS)
+print(summary(TShB_inc_AUDPS), correlation = FALSE)
 
@@
 TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
-summary(TShB_sev_AUDPS)
+print(summary(TShB_sev_AUDPS), correlation = FALSE)
 
@@
 LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
-summary(LShB_sev_AUDPS)
+print(summary(LShB_sev_AUDPS), correlation = FALSE)
 
@@
 
-The `lme4` `lmer` models do not appear to be a good fit based on the qqplots.
-However, they do seem to agree with the `MCMCglmm` analysis results. But I'm
-dubious about using these models based on the diagnostics that I see above.
-
 ## R Session Info

### 2017-08-03 munge/03_preprocess_data.R
Clean up comments in 03_preprocess_data.R

@@ -37,7 +37,7 @@ RAW_data$TRT <-
     "FLD_N180"
   )
 
-# add column with midpoint % tiller ShB severity
+# add column with midpoint % tiller ShB severity -------------------------------
 
 RAW_data <- mutate(RAW_data, PERC_TIL_ShB = ifelse(TIL_ShB == 0, 0,
                                                    ifelse(
@@ -49,7 +49,7 @@ RAW_data <- mutate(RAW_data, PERC_TIL_ShB = ifelse(TIL_ShB == 0, 0,
                                                             ))
                                                    )))
 
-# add column with midpoint % leaf ShB severity
+# add column with midpoint % leaf ShB severity ---------------------------------
 RAW_data <-
   mutate(RAW_data, PERC_LEAF_ShB = ifelse(LEAF_ShB == 0, 0,
                                           ifelse(
@@ -66,8 +66,7 @@ DS2016 <- subset(RAW_data, YEAR == "2016")
 
 # calculate AUDPS values -------------------------------------------------------
 
-# 2015 AUDPS -------------------------------------------------------------------
-# 2015 Tiller Incidence AUDPS --------------------------------------------------
+# 2015 Tiller Incidence setup --------------------------------------------------
 TShB_inc_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
@@ -99,7 +98,7 @@ TShB_perc_15 <-
 TShB_perc_wide <-
   dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")
 
-# 2015 Leaf Severity AUDPS -----------------------------------------------------
+# 2015 Leaf Severity setup -----------------------------------------------------
 LShB_sev_15 <-
   DS2015 %>%
   group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
@@ -119,6 +118,8 @@ LShB_perc_15 <-
 
 LShB_perc_wide <-
   dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")
+
+# 2015 AUDPS -------------------------------------------------------------------
 
 TShB_inc_AUDPS <-
[…]

### 2017-08-04 lme4_analysis.Rmd
Clean up comments in 03_preprocess_data.R
Simplify lmer analysis

@@
 library(lsmeans)
-TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
+TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
 print(summary(TShB_inc_AUDPS), correlation = FALSE)
@@
 plot(TShB_inc_AUDPS)
-qqnorm(resid(TShB_inc_AUDPS))
-qqline(resid(TShB_inc_AUDPS))
+qqnorm(residuals(TShB_inc_AUDPS))
+qqline(residuals(TShB_inc_AUDPS))
 
@@
 print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
-print(lsmeans(TShB_inc_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
-print(lsmeans(TShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2015_LShB_severity}
-LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2015)
+LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2015)
 print(summary(LShB_sev_AUDPS), correlation = FALSE)
@@
 print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT)), adjust = c("tukey"))
-print(lsmeans(LShB_sev_AUDPS, list(pairwise ~ WMGT | NRTE)), adjust = c("tukey"))
 ```
@@
 ```{r 2016_TShB_incidence}
-TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
+TShB_inc_AUDPS <- lmer(TShB_inc_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
 print(summary(TShB_inc_AUDPS), correlation = FALSE)
@@
 ```{r 2016_TShB_severity}
-TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
+TShB_sev_AUDPS <- lmer(TShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
 print(summary(TShB_sev_AUDPS), correlation = FALSE)
@@
 ```{r 2016_LShB_severity}
-LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT * NRTE + (1|REP), data = AUDPS_2016)
+LShB_sev_AUDPS <- lmer(LShB_percent_AUDPS ~ WMGT + NRTE + (1|REP), data = AUDPS_2016)
 print(summary(LShB_sev_AUDPS), correlation = FALSE)

### 2017-08-06 Test Residuals for Model Fits.Rmd
add tests for residuals prior to model fitting
See “Test Residuals for Model Fits.Rmd/md”

---
title: "Test Residuals for Model Fits"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ProjectTemplate)
load.project()
```

```{r}
require(car)
require(MASS)

# This is so that distributions that must be non-zero can make sense of my
# data
AUDPS_15 <- subset(AUDPS, YEAR == 2015)
AUDPS_16 <- subset(AUDPS, YEAR == 2016)

qqp(AUDPS_15$LShB_percent_AUDPS, "norm")
qqp(AUDPS_15$LShB_percent_AUDPS, "lnorm")
qqp(AUDPS_15$LShB_percent_AUDPS, "exp")
qqp(AUDPS_15$LShB_percent_AUDPS, "chisq", df = 2)

qqp(AUDPS_16$LShB_percent_AUDPS, "norm")
qqp(AUDPS_16$LShB_percent_AUDPS, "lnorm")
qqp(AUDPS_16$LShB_percent_AUDPS, "exp")
qqp(AUDPS_16$LShB_percent_AUDPS, "chisq", df = 2)

qqp(AUDPS_15$TShB_percent_AUDPS, "norm")
qqp(AUDPS_15$TShB_percent_AUDPS, "lnorm")
qqp(AUDPS_15$TShB_percent_AUDPS, "exp")
qqp(AUDPS_15$TShB_percent_AUDPS, "chisq", df = 2)

qqp(AUDPS_16$TShB_percent_AUDPS, "norm")
qqp(AUDPS_16$TShB_percent_AUDPS, "lnorm")
qqp(AUDPS_16$TShB_percent_AUDPS, "exp")
qqp(AUDPS_16$TShB_percent_AUDPS, "chisq", df = 2)

qqp(AUDPS_15$TShB_inc_AUDPS, "norm")
qqp(AUDPS_15$TShB_inc_AUDPS, "lnorm")
qqp(AUDPS_15$TShB_inc_AUDPS, "exp")
qqp(AUDPS_15$TShB_inc_AUDPS, "chisq", df = 2)

qqp(AUDPS_16$TShB_inc_AUDPS, "norm")
qqp(AUDPS_16$TShB_inc_AUDPS, "lnorm")
qqp(AUDPS_16$TShB_inc_AUDPS, "exp")
qqp(AUDPS_16$TShB_inc_AUDPS, "chisq", df = 2)
```

### 2017-08-06 graphs/imgDetails.sh

@@ -12,7 +12,6 @@
 declare -i COUNT=0
 declare -i SUCCESS=0
 declare -r OUT=./imgDetails.html
-declare -r CMD="sips -g pixelWidth -g pixelHeight"
 declare -ar ALLOWED=(*.jpg *.JPG *.jpeg *.GIF *.gif *.png *.PNG)
 
 rm imgDetails.html

### 2017-08-24 Analysis.Rmd
Fix headers in Analysis.Rmd/md
Migrate to ProjectTemplate 0.8 and update MCMCglmm analysis
- Update the project for use with ProjectTemplate 0.8

- _lme4_ analysis does not include interactions based on AIC values,
dropped the interactions for the _MCMCglmm_ analysis in this commit

@@
 ## Notes on This Analysis Before Starting
-
-If you have not already looked at the
-[01-Probability_distribution_checks](01-Probability_distribution_checks.md),
-please see that first to understand why MCMCglmm was chosen for this analysis
-due to the nature of the data.
 
@@
 
-First, separate the TRT column into the two treatments for analysis.
-
-```{r data_setup}
-AUDPS <- separate(data = AUDPS, col = TRT, sep = "_", into = c("WMGT", "NRTE"))
-AUDPS <- mutate_at(.tbl = AUDPS, .funs = factor, .vars = c("WMGT", "NRTE"))
-```
-
-Now create individual data frames for the analysis.
+Create individual data frames for the analysis.
 
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_incidence_lmm_2015 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE,
+TShB_incidence_lmm_2015 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT + NRTE,
                                     random = ~REP, 
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(TShB_incidence_lmm_2015$Sol[, c(1, 5:8)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:6])
+trts <-  data.frame(TShB_incidence_lmm_2015$Sol[, 2:4])
 trts <- melt(trts)
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2015 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
+TShB_severity_lmm_2015 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT + NRTE,
                                     random = ~REP, 
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(TShB_severity_lmm_2015$Sol[, c(1, 5:8)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:6])
+trts <-  data.frame(TShB_severity_lmm_2015$Sol[, 2:4])
 trts <- melt(trts)
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_severity_lmm_2015 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
+LShB_severity_lmm_2015 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT + NRTE,
                                     random = ~REP, 
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(LShB_severity_lmm_2015$Sol[, c(1, 7:10)])
+reps <- data.frame(LShB_severity_lmm_2015$Sol[, c(1, 5:8)])
 reps <- melt(reps)
 
-trts <-  data.frame(LShB_severity_lmm_2015$Sol[, 2:6])
+trts <-  data.frame(LShB_severity_lmm_2015$Sol[, 2:4])
 trts <- melt(trts)
@@
 
-TShB_incidence_lmm_2016 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT * NRTE, 
+TShB_incidence_lmm_2016 <- MCMCglmm(TShB_inc_AUDPS ~ WMGT + NRTE, 
                                     random = ~REP, 
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(TShB_incidence_lmm_2016$Sol[, c(1, 4:7)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:4])
+trts <-  data.frame(TShB_incidence_lmm_2016$Sol[, 2:3])
 trts <- melt(trts)
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-TShB_severity_lmm_2016 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT * NRTE,
+TShB_severity_lmm_2016 <- MCMCglmm(TShB_percent_AUDPS ~ WMGT + NRTE,
                                     random = ~REP, 
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(TShB_severity_lmm_2016$Sol[, c(1, 4:7)])
 reps <- melt(reps)
 
-trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:4])
+trts <-  data.frame(TShB_severity_lmm_2016$Sol[, 2:3])
 trts <- melt(trts)
@@
                G = list(G1 = list(V = 1, nu = 0.02, alpha.V = 1000)))
-LShB_severity_lmm_2016 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT * NRTE,
+LShB_severity_lmm_2016 <- MCMCglmm(LShB_percent_AUDPS ~ WMGT + NRTE,
                                     random = ~REP, 
@@
 # create data frames for generating diagnostic plots
-reps <- data.frame(LShB_severity_lmm_2016$Sol[, c(1, 5:8)])
+reps <- data.frame(LShB_severity_lmm_2016$Sol[, c(1, 4:7)])
 reps <- melt(reps)
 
-trts <-  data.frame(LShB_severity_lmm_2016$Sol[, 2:4])
+trts <-  data.frame(LShB_severity_lmm_2016$Sol[, 2:3])
 trts <- melt(trts)
@@
 
-## Tiller Sheath Blight Severity
+### Tiller Sheath Blight Severity
 

### 2017-08-24 munge/01_preprocess_2015_data.R

@@ -189,7 +189,7 @@ DS2015$TRT[which(DS2015$WMGT == "AWD" &
 DS2015$TRT[which(DS2015$WMGT == "AWD" &
                    DS2015$NRTE == 120)] = "AWD_N120"
 
-DS2015$YEAR <- year(DS2015$DATE)
+DS2015$YEAR <- lubridate::year(DS2015$DATE)
 
 DS2015$PLOT <- rep(1:24, each = 432)
 

### 2017-08-24 lme4_analysis.Rmd
Update lme4 analysis to use updated data frames
- Rerun lme4 analysis with corrected data frames

@@
 
+## Conclusions
+
+### Tiller Sheath Blight Incidence
+
+In 2015 both the nitrogen rates, N100 and N120, were significant when compared with the base N0 rate, water management was not significant.
+
+In 2016 the nitrogen rate N180, was significantly different than the base N60 rate, water management was not significant.
+
+### Tiller Sheath Blight Severity
+
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
+
+In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the base flooding treatment.
+
+### Leaf Sheath Blight Severity
+
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
+
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the base treatment for leaf sheath blight severity.
+
 ## R Session Info

### 2017-08-24 02_MCMCglmm_analysis.Rmd
Add conclusion to tests for model fits; rename files
Prepend 01, 02, etc. for order in which they are run

--- 2017-08-24 Analysis.Rmd
@@
 
-In 2015 the highest N rate, N120, was significantly different from the base, N0 rate.
+In 2015 both the nitrogen rates, N100 and N120, were significant when compared with the base N0 rate, water management was not significant.
 
-In 2016 both the AWD and highest N rate, N180, were significantly different from the FLD and N60 treatments.
-
-No interactions were found to be significant in the tiller sheath blight incidence.
+In 2016 the nitrogen rate N180, was significantly different than the base N60 rate, water management was not significant.
 
@@
 
-In 2015 both the N100 and N120 rates were significantly different from the N0 treatment. The interaction of the N100 rate with AWD was also significantly different than N0 and FLD treatments.
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
 
-In 2016 the N180 was significantly different from the N60 rate and the interaction of the N180 and AWD was significantly different than the N60 and FLD interaction.
+In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the base flooding treatment.
 
@@
 
-In 2015 the N120 was significantly different than the N0 treatment. The interactions of both the N100 and N120 with AWD were significantly different than the N0 FLD interaction.
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
 
-In 2016 the N180 was significantly different from the N60 treatment.
-The AWD was significantly different from the FLD and the interaction of N180:AWD was significantly different from the N60:FLD treatments interaction.
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the base treatment for leaf sheath blight severity.
 

### 2017-08-24 01_Test_Residuals_for_Model_Fits.Rmd
Cleanup README.md
Relink to analysis and residual test files

---
title: "Test Residuals for Model Fits"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ProjectTemplate)
load.project()
library(car)
library(MASS)

AUDPS_15 <- subset(AUDPS, YEAR == 2015)
AUDPS_16 <- subset(AUDPS, YEAR == 2016)
```

Using the R packages, _car_ and _MASS_, it is possible to check the residuals prior to fitting a model to help instruct in model selection.

Below are several tests for each of the different sets of data using four different data distributions:

- Normal,

- Log normal,

- Exponential, and

- Chi-squared.

## 2015 Tiller Incidence

```{r 2015_Tiller_Inc}
qqp(AUDPS_15$TShB_inc_AUDPS, "norm")
qqp(AUDPS_15$TShB_inc_AUDPS, "lnorm")
qqp(AUDPS_15$TShB_inc_AUDPS, "exp")
qqp(AUDPS_15$TShB_inc_AUDPS, "chisq", df = 2)
```

## 2015 Tiller Severity

```{r 2015_Tiller_Sev}
qqp(AUDPS_15$TShB_percent_AUDPS, "norm")
qqp(AUDPS_15$TShB_percent_AUDPS, "lnorm")
qqp(AUDPS_15$TShB_percent_AUDPS, "exp")
qqp(AUDPS_15$TShB_percent_AUDPS, "chisq", df = 2)
```

## 2015 Leaf Severity

```{r 2015_Leaf_Sev}
qqp(AUDPS_15$LShB_percent_AUDPS, "norm")
qqp(AUDPS_15$LShB_percent_AUDPS, "lnorm")
qqp(AUDPS_15$LShB_percent_AUDPS, "exp")
qqp(AUDPS_15$LShB_percent_AUDPS, "chisq", df = 2)
```

## 2016 Tiller Incidence

```{r 2016_Tiller_Inc}
qqp(AUDPS_16$TShB_inc_AUDPS, "norm")
qqp(AUDPS_16$TShB_inc_AUDPS, "lnorm")
qqp(AUDPS_16$TShB_inc_AUDPS, "exp")
qqp(AUDPS_16$TShB_inc_AUDPS, "chisq", df = 2)
```

## 2016 Tiller Severity

```{r 2016_Tiller_Sev}
qqp(AUDPS_16$TShB_percent_AUDPS, "norm")
qqp(AUDPS_16$TShB_percent_AUDPS, "lnorm")
qqp(AUDPS_16$TShB_percent_AUDPS, "exp")
qqp(AUDPS_16$TShB_percent_AUDPS, "chisq", df = 2)
```

## 2016 Leaf Severity

```{r 2016_Leaf_Sev}
qqp(AUDPS_16$LShB_percent_AUDPS, "norm")
qqp(AUDPS_16$LShB_percent_AUDPS, "lnorm")
qqp(AUDPS_16$LShB_percent_AUDPS, "exp")
qqp(AUDPS_16$LShB_percent_AUDPS, "chisq", df = 2)
```

Based on these graphs, few of the data are a good fit for a normal distribution, which suggests that using an analysis that does need these assumptions to be met, _e.g._ a Bayesian analysis method. The _MCMCglmm_ package provides an easy way to implement this type of analysis.

These analyses can be found in the [02_MCMC_glmm_analysis.md](02_MCMC_glmm_analysis.md) file.

## R Session Info

```{r session_info, echo=FALSE}
devtools::session_info()
```

### 2017-08-24 01_Test_Residuals_for_Model_Fits.Rmd
Fix residuals test files
- Rerun with renamed files to generate proper filenames for graphs to
display in resulting MarkDown file

- Add _MASS_ to global.dcf file to be sure it’s installed when this
project is loaded

@@
 
-Based on these graphs, few of the data are a good fit for a normal distribution, which suggests that using an analysis that does need these assumptions to be met, _e.g._ a Bayesian analysis method.
+Based on these graphs, few of the data are a good fit for a normal distribution.
+Ideally, we want to see the residuals close to the solid line and between the dotted lines.
+Several of the data do not exhibit this behaviour, which suggests that using an analysis that does need these assumptions to be met, _e.g._ a Bayesian analysis method should be used.
 The _MCMCglmm_ package provides an easy way to implement this type of analysis.
-
-These analyses can be found in the [02_MCMC_glmm_analysis.md](02_MCMC_glmm_analysis.md) file.
+The analyses can be found in the [02_MCMC_glmm_analysis.md](02_MCMC_glmm_analysis.md) file.
 

### 2017-08-24 02_MCMCglmm_analysis.Rmd
Clean up and detail the analysis document

@@
 
-For a quick overview, see this thread on Stack Overflow that walks through the output of `summary.MCMCglmm`,
-which is used below. [R: Making sense of the output of a MCMCglmm](http://stackoverflow.com/questions/20993643/r-making-sense-of-the-output-of-a-mcmcglmm)
+The _MCMCglmm_ documentation provides an excellent resource for interpreting the outputs for each of the models below.
 
-The MCMCglmm documentation is more in-depth but should still be referenced.
 ```{r MCMCglmm, eval=FALSE}
@@
 
-I found this CrossValidated topic to be useful in interpreting the outputs from
-MCMCglmm as it explains the interpretation of the effects. While it is about
-output from a `lmer`, the output is read in the same way, [How to interpret 2-way and 3-way interaction in lmer?](https://stats.stackexchange.com/questions/87412/how-to-interpret-2-way-and-3-way-interaction-in-lmer#87415).
+When comparing the treatments in the analysis, the model compares each treatment to the base (control) treatement.
 
@@
 
-- 2015 `NRTE:0`
+- 2015
 
-- 2015 `WMGT:FLD`
+    - `NRTE:0`
 
-- 2016 `NRTE:60`
+    - `WMGT:FLD`
 
-- 2016 `WMGT:FLD`
+- 2016
+
+    - `NRTE:60`
+
+    - `WMGT:FLD`
 
@@
 
-#### MCMCglmm model fitting notes
+#### _MCMCglmm_ model fitting notes
 
@@
 The `AUDPS` object is created when the project is loaded, in the file [munge/03_preprocess_data.R](./munge/03_preprocess_data.R).
-However, because it is a `tibble` and the treatments exist in a single column for graphing the raw data, this object needs a few minor changes to be usable for the analysis.
+However, because it is a `tibble()` and the treatments exist in a single column for graphing the raw data, this object needs a few minor changes to be usable for the analysis.
 
@@
 
-Now that the `AUDPS_2015` and `AUDPS_2016` `data.frames` exist, we can start the analysis.
+Now that the `AUDPS_2015` and `AUDPS_2016` `data.frames()` exist, we can start the analysis.
 

### 2017-08-24 README.Rmd
Convert analysis to R package
- Uses PLOS template for document output in “/analysis/paper/paper.Rmd”

- Vignettes detail checking and analysis done

- Data munging is to be shown in “/data-raw” Rmd files

- Raw data is in “/inst/extdata”

---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rice.awd.shb

The goal of rice.awd.shb is to ...

### Citation

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### Licenses

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2017-08-24 analysis/paper/paper.Rmd
Convert analysis to R package
- Uses PLOS template for document output in “/analysis/paper/paper.Rmd”

- Vignettes detail checking and analysis done

- Data munging is to be shown in “/data-raw” Rmd files

- Raw data is in “/inst/extdata”

--- 2017-06-09 reports/Effects_of_AWD_N_on_SB.rmd
@@
 ---
-title: "Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?"
-thanks: "Replication files are available on the author's Github account (http://github.com/adamhsparks/AWD_N_SB).
-**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Adam.Sparks@usq.edu.au"
+title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Pests and Diseases?
 author:
-  - A.H. Sparks and N.P. Castilla and B.O. Sander and B. Hadi
-keywords: "_Rhizoctonia solani_, Irrigation"
-abstract: "First author: University of Southern Queensland, Centre for Crop Health, West St., Toowoomba, Queensland 4350, Australia; and second and third authors: International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna 4031, Philippines."
-output:
-  word_document:
-    keep_md: yes
-    reference_docx: Phytopathology_Style_Reference.docx
-  html_document: default
-csl: phytopathology.csl
-bibliography: AWD_N_ShB.bib
----
-
-Corresponding author: Adam H. Sparks; E-mail address: Adam.Sparks@usq.edu.au
-
-______
-
-# Abstract
-
+  - name: A.H. Sparks
+    email: adam.sparks@usq.edu.au
+    affiliation: University of Southern Queensland
+    corresponding: adam.sparks@usq.edu.au
+  - name: N.P. Castilla
+    email: n.castilla@irri.org
+    affiliation: International Rice Research Institute
+  - name: B.A.R. Hadi
+    email: b.hadi@irri.org
+    affiliation: International Rice Research Institute
+  - name: B.O. Sander
+    email: b.sander@irri.org
+    affiliation: International Rice Research Institute
+address:
+  - code: University of Southern Queensland
+    address: Centre for Crop Health, West Street, Toowoomba, Queensland, Australia, 4350
+  - code: International Rice Research Institute
+    address: Los Baños, Laguna, Philippines, 4031
+abstract: |
   Water and nitrogen management play vital roles in rice production.
@@
 
-______
+author_summary: |
+  Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
-#####
+bibliography: references.bib
+output: rticles::plos_article
+csl: plos.csl
+---
+
+_Text based on plos sample manuscript, see [http://journals.plos.org/ploscompbiol/s/latex](http://journals.plos.org/ploscompbiol/s/latex)_
 
@@
 
-Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [-@Bouman2001; -@Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
 In AWD rice fields are exposed to several dry phases during the growth period without exposing the plants to water stress.
 In order to avoid yield decline under AWD “safe” thresholds have been developed.
-Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [-@Richards2014].
+Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [@Richards2014].
 Fields are furthermore kept flooded during the flowering period.
-Besides saving water AWD also reduces greenhouse gas (GHG) emissions of rice fields, which is a substantial factor in the GHG budget of rice producing countries, by around 50% [-@Yan2005; -@Sander2015].
+Besides saving water AWD also reduces greenhouse gas (GHG) emissions of rice fields, which is a substantial factor in the GHG budget of rice producing countries, by around 50% [@Yan2005; @Sander2015].
 
 The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, e.g., Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [-@MOEF2015].
+Various countries, e.g., Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015].
 However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
@@
 # Materials and Methods
+
 ## Experimental design
+
 Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14°11' N, , longitude 121°15' E) in the 2015 and 2016 dry seasons.
@@
 ### 2015 Dry Season
+
 The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
@@
 ### 2016 Dry Season
+
 In 2016 dry season the plot size was increased and due to these changes, the sizes of the replicates are not equal as necessitated by the use of a larger area for the experiment.
@@
 
+# Conclusions (optional)
+
 # Acknowledgments
 
-# Literature Cited
+# References {#references .unnumbered}
+
+Supporting information captions (if applicable)

### 2017-08-24 analysis/paper/paper.tex
Convert analysis to R package
- Uses PLOS template for document output in “/analysis/paper/paper.Rmd”

- Vignettes detail checking and analysis done

- Data munging is to be shown in “/data-raw” Rmd files

- Raw data is in “/inst/extdata”

% Template for PLoS
% Version 3.4 January 2017
\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
% \usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
% \bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below
\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

\usepackage{forarray}
\usepackage{xstring}
\newcommand{\getIndex}[2]{
  \ForEach{,}{\IfEq{#1}{\thislevelitem}{\number\thislevelcount\ExitForEach}{}}{#2}
}

\setcounter{secnumdepth}{0}

\newcommand{\getAff}[1]{
  \getIndex{#1}{University of Southern Queensland,International Rice Research Institute}
}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates
Affect Rice Pests and Diseases?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
\\
A.H. Sparks\textsuperscript{\getAff{University of Southern Queensland}}\textsuperscript{*},
N.P. Castilla\textsuperscript{\getAff{International Rice Research Institute}},
B.A.R. Hadi\textsuperscript{\getAff{International Rice Research Institute}},
B.O. Sander\textsuperscript{\getAff{International Rice Research Institute}}\\
\bigskip
\textbf{\getAff{University of Southern Queensland}}Centre for Crop Health, West Street, Toowoomba, Queensland, Australia,
4350\\
\textbf{\getAff{International Rice Research Institute}}Los Baños, Laguna, Philippines, 4031\\
\bigskip
* Corresponding author: adam.sparks@usq.edu.au\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Water and nitrogen management play vital roles in rice production.
However, the mismanagement of these two management practices may trigger
sheath blight of rice, caused by \emph{Rhizoctonia solani}, which is
favored by wet conditions, high relative humidity, and high nitrogen
fertilizer levels. To understand how different combinations of water and
nitrogen management affect sheath blight epidemics, we conducted two
separate split-plot experiments with a water saving (alternate wetting
and drying) regime and traditional flood irrigation regime combined with
differing nitrogen treatments in the dry seasons of 2015 and 2016.
Disease was scored in the same way in both experiments using a sheath
blight assessment scale for field evaluation developed at the
International Rice Research Institute to assess the severity on infected
sheaths and leaves while sheath blight incidence on tillers were counted
per hill. We were unable to detect any differences in disease in either
experiment due to irrigation regime, N rates or the interaction of the
two treatments in either season. This suggests that farmers can adopt
water saving technologies without risking increased sheath blight
incidence. We suggest that further cross-cutting research in this area
is warranted.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget
porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut
dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id
velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium
diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\emph{Text based on plos sample manuscript, see
\url{http://journals.plos.org/ploscompbiol/s/latex}}

\section{Introduction}\label{introduction}

Alternate wetting and drying (AWD) is an irrigation technique for
irrigated rice developed by the International Rice Research Institute
(IRRI) and its partners that saves about 15-40\% of irrigation water
{[}1,2{]}. In AWD rice fields are exposed to several dry phases during
the growth period without exposing the plants to water stress. In order
to avoid yield decline under AWD ``safe'' thresholds have been
developed. Under safe AWD irrigation water is applied when the field
water level reaches 15cm below the soil surface {[}3{]}. Fields are
furthermore kept flooded during the flowering period. Besides saving
water AWD also reduces greenhouse gas (GHG) emissions of rice fields,
which is a substantial factor in the GHG budget of rice producing
countries, by around 50\% {[}4,5{]}.

The AWD technology has been identified as promising climate smart
practice for different rice growing regions that can stabilize rice
production in water scarce areas as well as help reduce the carbon
footprint of rice production. Various countries, e.g., Bangladesh,
Vietnam, Thailand and the Philippines, plan to widely apply AWD to local
rice production {[}6{]}. However, a change in water regime in rice
fields on large scale might encompass different other effects, for
example related to plant health.

We therefore established field experiments in order to\ldots{}

\section{Materials and Methods}\label{materials-and-methods}

\subsection{Experimental design}\label{experimental-design}

Two experiments were conducted at the International Rice Research
Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon,
Philippines (latitude 14°11' N, , longitude 121°15' E) in the 2015 and
2016 dry seasons. For the 2016 season changes were made to optimize the
experiment based on findings from the 2015 season. Both seasons
consisted of split plot design with four replicates where irrigation was
the main plot and nitrogen (N) rate was the split plot treatment. The
changes between seasons and experiments are detailed following.

\subsubsection{2015 Dry Season}\label{dry-season}

The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m
x 5m (25 sq m). Replication size was 12m x 24m (288 sq m) with a buffer
of 1m per sub plot for a whole experiment size of 1,152 sq m. The main
plot treatments were alternate wetting and drying (AWD) and ) and
continuously flooded (CF) or farmers' practice.

Irrigation in AWD plots was determined by the water level in plots,
i.e., when the water level reached 15cm below the soil surface
irrigation water was applied to a level of 5cm. In CF plots a standing
water layer of 3-5cm was maintained throughout the growing season.

The sub plot treatments were different rates of nitrogen\ldots{}

\subsubsection{2016 Dry Season}\label{dry-season-1}

In 2016 dry season the plot size was increased and due to these changes,
the sizes of the replicates are not equal as necessitated by the use of
a larger area for the experiment. The main plot sizes were: Block 1 (B1)
21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
The sub plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m
(218.7 sq m). The replication sizes were B1 - 42m x 20.5m (861 sq m) and
B2 - 40.5m x 21.6m (874.8 sq m). A buffer 0.5m per sub plot was used and
the overall experiment size was 3471.6 sq m.

\subsection{Data collection and
analysis}\label{data-collection-and-analysis}

Data were analysed using multivariate generalised linear mixed models
implemented in the MCMCglmm package {[}7{]} in R {[}8{]}.

\section{Results}\label{results}

\section{Discussion}\label{discussion}

\section{Conclusions (optional)}\label{conclusions-optional}

\section{Acknowledgments}\label{acknowledgments}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

Supporting information captions (if applicable)

\hypertarget{refs}{}
\hypertarget{ref-Bouman2001}{}
1. Bouman B, Tuong T. Field water management to save water and increase
its productivity in irrigated lowland rice. Agricultural Water
Management. 2001;49: 11--30.
doi:\href{https://doi.org/https://doi.org/10.1016/S0378-3774(00)00128-1}{https://doi.org/10.1016/S0378-3774(00)00128-1}

\hypertarget{ref-Feng2007}{}
2. Feng L, Bouman B, Tuong T, Cabangon R, Li Y, Lu G, et al. Exploring
options to grow rice using less water in northern china using a
modelling approach: I. field experiments and model evaluation.
Agricultural Water Management. 2007;88: 1--13.
doi:\href{https://doi.org/https://doi.org/10.1016/j.agwat.2006.10.006}{https://doi.org/10.1016/j.agwat.2006.10.006}

\hypertarget{ref-Richards2014}{}
3. Richards M, Sander BO. Alternate wetting and drying in irrigated
rice. Copenhagen, Denmark: CGIAR Research Program on Climate Change,
Agriculture; Food Security (CCAFS); 2014 Apr.

\hypertarget{ref-Yan2005}{}
4. Yan X, Yagi K, Akiyama H, Akimoto H. Statistical analysis of the
major variables controlling methane emission from rice fields. Global
Change Biology. Blackwell Science Ltd; 2005;11: 1131--1141.
doi:\href{https://doi.org/10.1111/j.1365-2486.2005.00976.x}{10.1111/j.1365-2486.2005.00976.x}

\hypertarget{ref-Sander2015}{}
5. Sander BO, Wassmann R, Siopongco JDLC. Mitigating greenhouse gas
emissions from rice production through water-saving techniques:
Potential, adoption and empirical evidence. In: Hoanh CT, Johnston R,
Smakhtin V, editors. Centre for Agriculture; Biosciences International;
2016. p. 193.

\hypertarget{ref-MOEF2015}{}
6. Environment M of, Government of the People's Republic of Bangladesh F
(MOEF). Intended nationally determined contributions (indc).

\hypertarget{ref-MCMCglmm2017}{}
7. Hadfield JD. MCMC methods for multi-response generalized linear mixed
models: The MCMCglmm R package. Journal of Statistical Software.
2010;33: 1--22. Available: \url{http://www.jstatsoft.org/v33/i02/}

\hypertarget{ref-R2017}{}
8. R Core Team. R: A language and environment for statistical computing
{[}Internet{]}. Vienna, Austria: R Foundation for Statistical Computing;
2017. Available: \url{https://www.R-project.org/}

\nolinenumbers

\end{document}

### 2017-08-24 R/02-preprocess_2016_data.R

@@ -1,0 +1,218 @@
+# Preprocess 2016 data for all assessments
+#
+# 1. Cleanup date format and fill empty dates
+# 2. Fill empty NTIL (for same hill, not missing values)
+# 3. Fill empty NTShB (for same hill, not missing values)
+
+# First assessment -------------------------------------------------------------
+DS2016_A1 <- read_csv("data/DS2016_Raw_1.csv")
+# Fill missing values in NTIL and NTShB
+DS2016_A1 <-
+  DS2016_A1 %>% fill(NTIL)
+DS2016_A1 <-
+  DS2016_A1 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A1[, 1] <- as.Date("2016-03-15", origin = "1970-01-01")
+DS2016_A1$ASMT <- rep(1, nrow(DS2016_A1))
+DS2016_A1$PLOT <- rep(1:16, each = 72)
+
+
+# Second assessement -----------------------------------------------------------
+DS2016_A2 <- read_csv("data/DS2016_Raw_2.csv")
+DS2016_A2 <-
+  DS2016_A2 %>% fill(NTIL)
+DS2016_A2 <-
+  DS2016_A2 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A2[, 1] <- as.Date("2016-03-29", origin = "1970-01-01")
+DS2016_A2$ASMT <- rep(2, nrow(DS2016_A2))
+DS2016_A2$PLOT <- rep(1:16, each = 72)
+
+
+# Third assessement ------------------------------------------------------------
+DS2016_A3 <- read_csv("data/DS2016_Raw_3.csv")
+DS2016_A3 <-
+  DS2016_A3 %>% fill(NTIL)
+DS2016_A3 <-
+  DS2016_A3 %>% fill(NTShB)
+
+# Fill dates
+DS2016_A3[, 1] <- as.Date("2016-04-12", origin = "1970-01-01")
+DS2016_A3$ASMT <- rep(3, nrow(DS2016_A3))
+DS2016_A3$PLOT <- rep(1:16, each = 72)
+
+# Fourth assessment ------------------------------------------------------------
+DS2016_A4 <- read_csv("data/DS2016_Raw_4.csv")
+DS2016_A4 <-
+  DS2016_A4 %>% fill(NTIL)
+DS2016_A4 <-
+  DS2016_A4 %>% fill(NTShB)
+
+# Fill dates
[…]

### 2017-08-24 graphs/imgDetails.sh

@@ -1,44 +1,0 @@
-#!/bin/bash
-#
-###########################################################
-# Usage: imgDetails.sh
-#
-# Script will save to ./imgDetails_(PID).html
-# with the details of images it came across in the current
-# directory which the script was run.
-# Taken from: http://hints.macworld.com/article.php?story=20041220171133228
-############################################################
-#
-declare -i COUNT=0
-declare -i SUCCESS=0
-declare -r OUT=./imgDetails.html
-declare -ar ALLOWED=(*.jpg *.JPG *.jpeg *.GIF *.gif *.png *.PNG)
-
-rm imgDetails.html
-
-for ITEM in ${ALLOWED[@]}; do
-  if [ -f $ITEM ]; then
-    declare -i POS=0
-    declare -a PROPS=()
-    for PROP in $($CMD "$ITEM"|tail -2|sed 's/ //g'|awk -F':' '{print $2}')
-    do
-      echo $PROP | egrep '[0-9]+'>/dev/null 2>&1
-      if [ $? == 0 ]; then
-        PROPS[$POS]=$PROP
-        POS=POS+1
-      fi
-    done
-    if [ -n ${PROPS[0]} -a -n ${PROPS[1]} ]; then
-      echo "<img src=\"${ITEM}\" alt=\"${ITEM}\" />" | tee -a $OUT
-      [ $? == 0 ] && SUCCESS=SUCCESS+1
-    fi
-    COUNT=COUNT+1
-  fi
-done
-
-echo -e "\nAttempted to process (${COUNT}) files."
-echo -e "Successfully processed (${SUCCESS}) files."
-
-[ -f $OUT ]
-
-exit 0

### 2017-08-24 lib/helpers.R

@@ -1,45 +1,0 @@
-helper.function <- function()
-{
-  return(1)
-}
-
-plot_diagnostic_lines <- function(d, x, title) {
-  # Diagnostic line plots for replicate
-  ggplot(data = d, aes(
-    x = rep(x, length(unique(d$variable))),
-    y = value,
-    group = variable
-  )) +
-    geom_line() +
-    xlab("Iteration Number") +
-    ylab(NULL) +
-    facet_grid(variable ~ .) +
-    theme(strip.text.y = element_text(angle = 0)) +
-    ggtitle(paste(title))
-}
-
-plot_replicate_posteriors <- function(d, title) {
-  ggplot(data = d[d$variable != "X.Intercept.", ], aes(x = variable,
-                                                       y = value)) +
-    geom_violin() +
-    geom_abline(slope = 0, intercept = 0) +
-    ggtitle(paste(title)) +
-    theme(axis.text.x = element_text(angle = 35, hjust = 1))
-}
-
-
-plot_treatment_posteriors <- function(d, title) {
-  ggplot(data = d, aes(x = variable,
-                       y = value)) +
-    geom_violin() +
-    geom_abline(slope = 0, intercept = 0) +
-    ggtitle(paste(title)) +
-    theme(axis.text.x = element_text(angle = 35, hjust = 1))
-}
-
-plot_joint_random_error_dist <- function(d, title) {
-  ggplot(d, aes(x = sqrt(REP), y = sqrt(units))) +
-    geom_density2d() +
-    geom_abline(intercept = 0, slope = 1) +
-    ggtitle(paste(title))
-}

### 2017-08-24 munge/02-preprocess_2016_data.R

@@ -1,218 +1,0 @@
-# Preprocess 2016 data for all assessments
-#
-# 1. Cleanup date format and fill empty dates
-# 2. Fill empty NTIL (for same hill, not missing values)
-# 3. Fill empty NTShB (for same hill, not missing values)
-
-# First assessment -------------------------------------------------------------
-DS2016_A1 <- read_csv("data/DS2016_1.csv")
-# Fill missing values in NTIL and NTShB
-DS2016_A1 <-
-  DS2016_A1 %>% fill(NTIL)
-DS2016_A1 <-
-  DS2016_A1 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A1[, 1] <- as.Date("2016-03-15", origin = "1970-01-01")
-DS2016_A1$ASMT <- rep(1, nrow(DS2016_A1))
-DS2016_A1$PLOT <- rep(1:16, each = 72)
-
-
-# Second assessement -----------------------------------------------------------
-DS2016_A2 <- read_csv("data/DS2016_2.csv")
-DS2016_A2 <-
-  DS2016_A2 %>% fill(NTIL)
-DS2016_A2 <-
-  DS2016_A2 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A2[, 1] <- as.Date("2016-03-29", origin = "1970-01-01")
-DS2016_A2$ASMT <- rep(2, nrow(DS2016_A2))
-DS2016_A2$PLOT <- rep(1:16, each = 72)
-
-
-# Third assessement ------------------------------------------------------------
-DS2016_A3 <- read_csv("data/DS2016_3.csv")
-DS2016_A3 <-
-  DS2016_A3 %>% fill(NTIL)
-DS2016_A3 <-
-  DS2016_A3 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A3[, 1] <- as.Date("2016-04-12", origin = "1970-01-01")
-DS2016_A3$ASMT <- rep(3, nrow(DS2016_A3))
-DS2016_A3$PLOT <- rep(1:16, each = 72)
-
-# Fourth assessment ------------------------------------------------------------
-DS2016_A4 <- read_csv("data/DS2016_4.csv")
-DS2016_A4 <-
-  DS2016_A4 %>% fill(NTIL)
-DS2016_A4 <-
-  DS2016_A4 %>% fill(NTShB)
-
-# Fill dates
[…]

### 2017-08-24 data-raw/01-Clean_2015_Raw_Data.Rmd
Add data-raw files

---
title: "Clean 2015 Raw Data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:

```{r, eval=FALSE}
load(system.file("extdata", "DS2015_Raw_22DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_35DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_49DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_62DAI.csv", package = "rice.awd.pests"))
load(system.file("extdata", "DS2015_Raw_83DAI.csv", package = "rice.awd.pests"))
```

```{r}

library(readr)
library(magrittr)

# Preprocess 2015 data for all assessment dates

files <-
  list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)

reformat <- function(files) {
  x <- read_csv(
    files,
    cols(
      col_character(),
      col_character(),
      col_character(),
      col_character(),
      col_character(),
      col_character(),
      col_double(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer(),
      col_integer()
    ),
    col_names = TRUE
  )
  x[is.na(x)] <- 0

  x <- dplyr::arrange(x, REP, TRT)

  # add plot numbers
  x$PLOT <- rep(1:24, each = 18)

  # Calculate tiller sheath blight incidence -----------------------------------
  x <-
    x %>%
    dplyr::mutate(TShB_incidence = NTShB / NTIL)

  TShB_incidence <-
    x %>% dplyr::select(REP,
                        TRT,
                        WMGT,
                        NRTE,
                        SMPL,
                        HILL,
                        HGHT,
                        NTIL,
                        NTShB,
                        TShB_incidence)

  # Gather tillers--------------------------------------------------------------
  TIL <- vector(mode = "list", length = 4)

  for (i in 1:4) {
    y <-
      x %>%
      dplyr::select(
        TRT,
        REP,
        WMGT,
        SMPL,
        NRTE,
        HILL,
        paste0("TIL", i),
        paste0("GL", i),
        paste0("DL", i),
        paste0("SHB", i),
        paste0("SLA", i),
        paste0("SLB", i),
        paste0("SLC", i),
        paste0("SLD", i),
        paste0("SLE", i),
        paste0("SLF", i)
      ) %>%
      tidyr::gather(LEAF,
                    LEAF_ShB,
                    dplyr::starts_with("SL"))

    names(y)[7] <- "TIL"
    names(y)[8] <- "GL"
    names(y)[9] <- "DL"
    names(y)[10] <- "TIL_ShB"

    y$LEAF[y$LEAF == paste0("SLA", i)] <- 1
    y$LEAF[y$LEAF == paste0("SLB", i)] <- 2
    y$LEAF[y$LEAF == paste0("SLC", i)] <- 3
    y$LEAF[y$LEAF == paste0("SLD", i)] <- 4
    y$LEAF[y$LEAF == paste0("SLE", i)] <- 5
    y$LEAF[y$LEAF == paste0("SLF", i)] <- 6

    TIL[[i]] <- y
  }

  z <- dplyr::bind_rows(TIL)
  x <- dplyr::left_join(TShB_incidence, z)

  # Add dates ------------------------------------------------------------------

  switch(
    files,
    "data/DS2015_Raw_22DAI.csv" = {
      DATE <- rep(as.Date("2015-02-12", origin = "1970-01-01"),
                  times = nrow(x))
      ASMT <- rep(1, times = nrow(x))
      visit <- data.frame(DATE, ASMT, x)
    },
    "data/DS2015_Raw_35DAI.csv" = {
      DATE <- rep(as.Date("2015-02-20", origin = "1970-01-01"),
                  times = nrow(x))
      ASMT <- rep(2, times = nrow(x))
      visit <- data.frame(DATE, ASMT, x)
    },
    "data/DS2015_Raw_49DAI.csv" = {
      DATE <- rep(as.Date("2015-03-05", origin = "1970-01-01"),
                  times = nrow(x))
      ASMT <- rep(3, times = nrow(x))
      visit <- data.frame(DATE, ASMT, x)
    },
    "data/DS2015_Raw_62DAI.csv" = {
      DATE <- rep(as.Date("2015-03-19", origin = "1970-01-01"),
                  times = nrow(x))
      ASMT <- rep(4, times = nrow(x))
      visit <- data.frame(DATE, ASMT, x)
    },
    "data/DS2015_Raw_83DAI.csv" = {
      DATE <- rep(as.Date("2015-04-01", origin = "1970-01-01"),
                  times = nrow(x))
      ASMT <- rep(5, times = nrow(x))
      visit <- data.frame(DATE, ASMT, x)
    }
  )
}

# Run reformat function for all 2015 files -------------------------------------
DS2015 <- purrr::map_df(files, reformat)

# Replace "N*" with a number for NRTE ------------------------------------------
DS2015$NRTE[which(DS2015$NRTE == "N0")] <- 0
DS2015$NRTE[which(DS2015$NRTE == "N1")] <- 100
DS2015$NRTE[which(DS2015$NRTE == "N2")] <- 120

# Add treatment numbers --------------------------------------------------------
DS2015$TRT <- NA
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 0)] = "FLD_N0"
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 100)] = "FLD_N100"
DS2015$TRT[which(DS2015$WMGT == "FLD" &
                   DS2015$NRTE == 120)] = "FLD_N120"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 0)] = "AWD_N0"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 100)] = "AWD_N100"
DS2015$TRT[which(DS2015$WMGT == "AWD" &
                   DS2015$NRTE == 120)] = "AWD_N120"

DS2015$YEAR <- lubridate::year(DS2015$DATE)

DS2015$PLOT <- rep(1:24, each = 432)

# Arrange columns --------------------------------------------------------------
DS2015 <-
  DS2015 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

DS2015$LEAF_ShB <- as.numeric(DS2015$LEAF_ShB)

DS2015 <- tibble::as_tibble(dplyr::arrange(DS2015, ASMT, PLOT))

# Create new columns of days to calcluate AUDPS -------------------------------

DAYS <- as.numeric(substr(files, 17, 18))

DS2015$DAYS <- c(rep(0, 10368), rep(diff(DAYS), each = 10368))

rm(files, reformat)

# Save data for inclusion in the package ---------------------------------------

if (!dir.exists("../data")) {
  dir.create("../data", recursive = TRUE)
}

save(DS2015, file = "../data/DS2015", compress = "bzip2")

```

The raw data are located in the `extdata` folder of the installed
_rice.awd.pests_ and can be accessed using:

`load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))`
`load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))`
`load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))`
`load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))`

```{r}
# Preprocess 2016 data for all assessments
#
# 1. Cleanup date format and fill empty dates
# 2. Fill empty NTIL (for same hill, not missing values)
# 3. Fill empty NTShB (for same hill, not missing values)

# First assessment -------------------------------------------------------------
DS2016_A1 <- readr::read_csv("data/DS2016_Raw_1.csv")
# Fill missing values in NTIL and NTShB
DS2016_A1 <-
  DS2016_A1 %>% tidyr::fill(NTIL)
DS2016_A1 <-
  DS2016_A1 %>% tidyr::fill(NTShB)

# Fill dates
DS2016_A1[, 1] <- as.Date("2016-03-15", origin = "1970-01-01")
DS2016_A1$ASMT <- rep(1, nrow(DS2016_A1))
DS2016_A1$PLOT <- rep(1:16, each = 72)

# Second assessement -----------------------------------------------------------
DS2016_A2 <- readr::read_csv("data/DS2016_Raw_2.csv")
DS2016_A2 <-
  DS2016_A2 %>% tidyr::fill(NTIL)
DS2016_A2 <-
  DS2016_A2 %>% tidyr::fill(NTShB)

# Fill dates
DS2016_A2[, 1] <- as.Date("2016-03-29", origin = "1970-01-01")
DS2016_A2$ASMT <- rep(2, nrow(DS2016_A2))
DS2016_A2$PLOT <- rep(1:16, each = 72)

# Third assessement ------------------------------------------------------------
DS2016_A3 <- readr::read_csv("data/DS2016_Raw_3.csv")
DS2016_A3 <-
  DS2016_A3 %>% tidyr::fill(NTIL)
DS2016_A3 <-
  DS2016_A3 %>% tidyr::fill(NTShB)

# Fill dates
DS2016_A3[, 1] <- as.Date("2016-04-12", origin = "1970-01-01")
DS2016_A3$ASMT <- rep(3, nrow(DS2016_A3))
DS2016_A3$PLOT <- rep(1:16, each = 72)

# Fourth assessment ------------------------------------------------------------
DS2016_A4 <- readr::read_csv("data/DS2016_Raw_4.csv")
DS2016_A4 <-
  DS2016_A4 %>% tidyr::fill(NTIL)
DS2016_A4 <-
  DS2016_A4 %>% tidyr::fill(NTShB)

# Fill dates
DS2016_A4[, 1] <- as.Date("2016-04-26", origin = "1970-01-01")
DS2016_A4$ASMT <- rep(4, nrow(DS2016_A4))
DS2016_A4$PLOT <- rep(1:16, each = 72)

# Combine all assessments ------------------------------------------------------
DS2016 <- rbind(
  as.data.frame(DS2016_A1),
  as.data.frame(DS2016_A2),
  as.data.frame(DS2016_A3),
  as.data.frame(DS2016_A4)
)

# Set any NA values to 0, per Dr. Castilla on 060317 ---------------------------
# "We used to put zeroes on the data sheets, but Dr. Savary later suggested that
# we leave the cells blank because it has caused difficulties in proof reading
# the data. We also found more mistakes in data encoding when there are a lot
# of zeroes."
# Set any NA values to 0, per Dr. Castilla on 060317 ---------------------------

DS2016[is.na(DS2016)] <- 0

# Replace "Flooded" with "FLD" -------------------------------------------------
DS2016$WMGT[which(DS2016$WMGT == "Flooded")] = "FLD"

# Replace "N*" with a number for NRTE ------------------------------------------
DS2016$NRTE[which(DS2016$NRTE == "N1")] = 60
DS2016$NRTE[which(DS2016$NRTE == "N2")] = 180

# Add treatment numbers --------------------------------------------------------
DS2016$TRT <- NA
DS2016$TRT[which(DS2016$WMGT == "FLD" &
                   DS2016$NRTE == 60)] = "FLD_N60"
DS2016$TRT[which(DS2016$WMGT == "FLD" &
                   DS2016$NRTE == 180)] = "FLD_N180"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 60)] = "AWD_N60"
DS2016$TRT[which(DS2016$WMGT == "AWD" &
                   DS2016$NRTE == 180)] = "AWD_N180"

DS2016 <-
  DS2016 %>%
  tidyr::gather(
    LEAF,
    LEAF_ShB,
    dplyr::starts_with("ShBL"),
    -DATE,
    -ASMT,
    -PLOT,
    -TRT,
    -REP,
    -WMGT,
    -SMPL,
    -NRTE,
    -HILL,
    -NTIL,
    -GL,
    -DL,
    -NTShB,
    -NSHShB,
    -TIL
  )

# reclassify LEAF column to leaf numbers 1...6

DS2016$LEAF[DS2016$LEAF == "ShBL1"] <- 1
DS2016$LEAF[DS2016$LEAF == "ShBL2"] <- 2
DS2016$LEAF[DS2016$LEAF == "ShBL3"] <- 3
DS2016$LEAF[DS2016$LEAF == "ShBL4"] <- 4
DS2016$LEAF[DS2016$LEAF == "ShBL5"] <- 5
DS2016$LEAF[DS2016$LEAF == "ShBL6"] <- 6

# before classifying incidence, set any values where there are more infected
# tillers in the hill than there are tillers to NA for both columns

DS2016$NTIL[DS2016$NTIL < DS2016$NTShB] <- NA
DS2016$NTShB[is.na(DS2016$NTIL)] <- NA

# calculate tiller sheath blight incidence
DS2016 <-
  DS2016 %>%
  dplyr::group_by(DATE, ASMT, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
  dplyr::mutate(TShB_incidence = NTShB / NTIL)

DS2016 <- dplyr::rename(DS2016, TIL_ShB = NSHShB)

DS2016$YEAR <- lubridate::year(DS2016$DATE)
DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)

DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE
  )

DS2016 <- tibble::as_tibble(dplyr::arrange(DS2016, ASMT, PLOT))

# Create new columns of days to calcluate AUDPS -------------------------------

DATE_1_2016 <- DATE_2_2016 <- DS2016$DATE
DATE_1_2016[which(DATE_1_2016 == min(DATE_1_2016))] <- NA
DATE_2_2016[which(DATE_2_2016 == max(DATE_2_2016))] <- NA

DATE_1 <- na.omit(DATE_1_2016)
DATE_2 <- na.omit(DATE_2_2016)

DAYS_2016 <- lubridate::time_length(DATE_1 - DATE_2, unit = "day")
DS2016$DAYS <-
  c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)

# cleanup workspace ------------------------------------------------------------

rm(
  DS2016_A1,
  DS2016_A2,
  DS2016_A3,
  DS2016_A4,
  DATE_1,
  DATE_1_2016,
  DATE_2,
  DATE_2_2016,
  DAYS_2016
)

# Arrange columns --------------------------------------------------------------
DS2016 <-
  DS2016 %>% dplyr::select(
    YEAR,
    DATE,
    ASMT,
    REP,
    PLOT,
    TRT,
    SMPL,
    HILL,
    TIL,
    LEAF,
    GL,
    DL,
    TShB_incidence,
    TIL_ShB,
    LEAF_ShB,
    WMGT,
    NRTE,
    DAYS
  )
```

```{r}
# Join the 2015 and 2016 Data into one Tibble ----------------------------------

RAW_data <- tibble::as_tibble(rbind(as.data.frame(DS2015),
                                    as.data.frame(DS2016)))

# convert columns to factor ----------------------------------------------------
RAW_data$YEAR <- factor(RAW_data$YEAR)
RAW_data$ASMT <- factor(RAW_data$ASMT)
RAW_data$PLOT <- factor(RAW_data$PLOT)
RAW_data$REP <- factor(RAW_data$REP)
RAW_data$TRT <- factor(RAW_data$TRT)
RAW_data$WMGT <- factor(RAW_data$WMGT)
RAW_data$NRTE <- factor(RAW_data$NRTE)
RAW_data$SMPL <- factor(RAW_data$SMPL)
RAW_data$HILL <- factor(RAW_data$HILL)
RAW_data$TIL <- factor(RAW_data$TIL)
RAW_data$LEAF <- factor(RAW_data$LEAF)

# reorder the treatments by level/year - low to high, 2015-2016 for graphs -----
RAW_data$NRTE <-
  forcats::fct_relevel(RAW_data$NRTE,
                       "0",
                       "100",
                       "120",
                       "60",
                       "180")

RAW_data$TRT <-
  forcats::fct_relevel(
    RAW_data$TRT,
    "AWD_N0",
    "AWD_N100",
    "AWD_N120",
    "AWD_N60",
    "AWD_N180",
    "FLD_N0",
    "FLD_N100",
    "FLD_N120",
    "FLD_N60",
    "FLD_N180"
  )

# add column with midpoint % tiller ShB severity -------------------------------

RAW_data <-
  dplyr::mutate(
    RAW_data,
    PERC_TIL_ShB = dplyr::case_when(
      TIL_ShB == 0 ~ 0,
      TIL_ShB == 1 ~ 1,
      TIL_ShB == 2 ~ 2.5,
      TIL_ShB == 3 ~ 10,
      TIL_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

# add column with midpoint % leaf ShB severity ---------------------------------
RAW_data <-
  dplyr::mutate(
    RAW_data,
    PERC_LEAF_ShB = dplyr::case_when(
      LEAF_ShB == 0 ~ 0,
      LEAF_ShB == 1 ~ 1,
      LEAF_ShB == 2 ~ 2.5,
      LEAF_ShB == 3 ~ 10,
      LEAF_ShB == 4 ~ 32.5,
      TRUE ~ 75
    )
  )

DS2015 <- subset(RAW_data, YEAR == "2015")
DS2016 <- subset(RAW_data, YEAR == "2016")

# calculate AUDPS values -------------------------------------------------------

# 2015 AUDPS -------------------------------------------------------------------

# 2015 Tiller incidence setup --------------------------------------------------
TShB_inc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

TShB_inc_wide <-
  reshape2::dcast(TShB_inc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_incidence")

# 2015 Tiller Severity AUDPS ---------------------------------------------------
TShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

TShB_sev_wide <-
  reshape2::dcast(TShB_sev_15, PLOT ~ ASMT, value.var = "PLOT_TShB_severity")

TShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  dplyr::arrange(PLOT)

TShB_perc_wide <-
  reshape2::dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")

# 2015 Leaf Severity setup -----------------------------------------------------
LShB_sev_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

LShB_sev_wide <-
  reshape2::dcast(LShB_sev_15, PLOT ~ ASMT, value.var = "PLOT_LShB_severity")

LShB_perc_15 <-
  DS2015 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

LShB_perc_wide <-
  reshape2::dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")

# Calculate 2015 AUDPS ---------------------------------------------------------

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
                   dates = as.vector(TShB_inc_15[1:5, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
                   dates = as.vector(TShB_sev_15[1:5, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
                   dates = as.vector(LShB_sev_15[1:5, 6]))

TShB_percent_AUDPS <-
  audps(evaluation = TShB_perc_wide[, 2:6],
        dates = as.vector(TShB_perc_15[1:5, 6]))

LShB_percent_AUDPS <-
  audps(evaluation = LShB_perc_wide[, 2:6],
        dates = as.vector(LShB_perc_15[1:5, 6]))

AUDPS_15 <-
  tibble::as_tibble(
    cbind(
      PLOT = 1:24,
      TShB_inc_AUDPS,
      TShB_sev_AUDPS,
      TShB_percent_AUDPS,
      LShB_sev_AUDPS,
      LShB_percent_AUDPS
    )
  )

AUDPS_15$PLOT <- as.character(AUDPS_15$PLOT)
TShB_inc_15$PLOT <- as.character(TShB_inc_15$PLOT)

ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")

# 2015 AUDPS -------------------------------------------------------------------

# 2016 Tiller Incidence setup --------------------------------------------------
TShB_inc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
  dplyr::arrange(PLOT)

TShB_inc_wide <-
  reshape2::dcast(TShB_inc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_incidence")

TShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
  dplyr::arrange(PLOT)

TShB_sev_wide <-
  reshape2::dcast(TShB_sev_16, PLOT ~ ASMT, value.var = "PLOT_TShB_severity")

# 2016 Tiller Severity setup ---------------------------------------------------

TShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
  varrange(PLOT)

TShB_perc_wide <-
  reshape2::dcast(TShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")

# 2016 Leaf Severity setup -----------------------------------------------------

LShB_sev_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

LShB_sev_wide <-
  reshape2::dcast(LShB_sev_16, PLOT ~ ASMT, value.var = "PLOT_LShB_severity")

LShB_perc_16 <-
  DS2016 %>%
  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
  dplyr::arrange(PLOT)

LShB_perc_wide <-
  reshape2::dcast(LShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")

# 2016 AUDPS -------------------------------------------------------------------

TShB_inc_AUDPS <-
  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
                   dates = as.vector(TShB_inc_16[1:4, 6]))

TShB_sev_AUDPS <-
  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
                   dates = as.vector(TShB_sev_16[1:4, 6]))

LShB_sev_AUDPS <-
  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
                   dates = as.vector(LShB_sev_16[1:4, 6]))

TShB_percent_AUDPS <-
  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
                   dates = as.vector(TShB_perc_16[1:4, 6]))

LShB_percent_AUDPS <-
  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
                   dates = as.vector(LShB_perc_16[1:4, 6]))

AUDPS_16 <-
  tibble::as_tibble(
    cbind(
      PLOT = 1:16,
      TShB_inc_AUDPS,
      TShB_sev_AUDPS,
      TShB_percent_AUDPS,
      LShB_sev_AUDPS,
      LShB_percent_AUDPS
    )
  )

# add plot numbers to merge with the remaing treatment data
AUDPS_16$PLOT <- as.character(AUDPS_16$PLOT)
TShB_inc_16$PLOT <- as.character(TShB_inc_16$PLOT)

ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))

# Merge AUDPS data for graphing ------------------------------------------------
AUDPS <- tibble::as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
                         sep = "_",
                         into = c("WMGT", "NRTE"))
AUDPS <- agricolae::mutate_at(.tbl = AUDPS,
                              .funs = factor,
                              .vars = c("WMGT", "NRTE"))

# Save data for inclusion in the package ---------------------------------------

if (!dir.exists("../data")) {
  dir.create("../data", recursive = TRUE)
}

save(AUDPS, file = "../data/AWD_AUDPS", compress = "bzip2")
```

### 2017-08-24 data-raw/01-Clean_Raw_Data.Rmd
Add data-raw files

--- 2017-08-24 data-raw/01-Clean_2015_Raw_Data.Rmd
@@
 ```
+
+## 2015 raw data
 
@@
 
-# Save data for inclusion in the package ---------------------------------------
+```
 
-if (!dir.exists("../data")) {
-  dir.create("../data", recursive = TRUE)
-}
-
-save(DS2015, file = "../data/DS2015", compress = "bzip2")
-
-```
+## 2016 raw data
 
@@
 
+## Calculate AUDPS and create final data for analysis
+
 ```{r}
@@
   agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
-                   dates = as.vector(TShB_inc_15[1:5, 6]))
+                   dates = dplyr::pull(TShB_inc_15[1:5, 6]))
 
@@
   agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
-                   dates = as.vector(TShB_sev_15[1:5, 6]))
+                   dates = dplyr::pull(TShB_sev_15[1:5, 6]))
 
@@
   agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
-                   dates = as.vector(LShB_sev_15[1:5, 6]))
+                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))
 
 TShB_percent_AUDPS <-
-  audps(evaluation = TShB_perc_wide[, 2:6],
-        dates = as.vector(TShB_perc_15[1:5, 6]))
+  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
+        dates = dplyr::pull(TShB_perc_15[1:5, 6]))
 
 LShB_percent_AUDPS <-
-  audps(evaluation = LShB_perc_wide[, 2:6],
-        dates = as.vector(LShB_perc_15[1:5, 6]))
+  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
+        dates = dplyr::pull(LShB_perc_15[1:5, 6]))
 
@@
 
-ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")
+ShB_15 <- dplyr::left_join(TShB_inc_15, AUDPS_15, by = "PLOT")
 
@@
                       .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
-  varrange(PLOT)
+  dplyr::arrange(PLOT)
 
@@
   agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
-                   dates = as.vector(TShB_inc_16[1:4, 6]))
+                   dates = dplyr::pull(TShB_inc_16[1:4, 6]))
 
@@
   agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
-                   dates = as.vector(TShB_sev_16[1:4, 6]))
+                   dates = dplyr::pull(TShB_sev_16[1:4, 6]))
 
@@
   agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
-                   dates = as.vector(LShB_sev_16[1:4, 6]))
+                   dates = dplyr::pull(LShB_sev_16[1:4, 6]))
 
@@
   agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
-                   dates = as.vector(TShB_perc_16[1:4, 6]))
+                   dates = dplyr::pull(TShB_perc_16[1:4, 6]))
 
@@
   agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
-                   dates = as.vector(LShB_perc_16[1:4, 6]))
+                   dates = dplyr::pull(LShB_perc_16[1:4, 6]))
 
@@
 
-ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))
+ShB_16 <- dplyr::left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))
 
 # Merge AUDPS data for graphing ------------------------------------------------
-AUDPS <- tibble::as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
+AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))
 AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
@@
                          into = c("WMGT", "NRTE"))
-AUDPS <- agricolae::mutate_at(.tbl = AUDPS,
+AUDPS <- dplyr::mutate_at(.tbl = AUDPS,
                               .funs = factor,
@@
 
-save(AUDPS, file = "../data/AWD_AUDPS", compress = "bzip2")
+save(AUDPS, file = "../data/AWD_AUDPS.rda", compress = "bzip2")
 ```

### 2017-08-24 data-raw/02-Visualise_data.Rmd
Add data-raw files

---
title: "04 Visualise data"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("rice.awd.pests")
load(system.file("data", "AWD_AUDPS.rda", package = "rice.awd.pests"))
```

```{r}
# Histogram plot of LShB_rating data ----------------------------------------
ggplot(RAW_data, aes(x = LEAF_ShB)) +
  geom_histogram(aes(fill = YEAR), stat = "count") +
  scale_linetype(name = "Year") +
  facet_grid(WMGT ~ NRTE) +
  ggtitle("Leaf Sheath Blight Severity Rating")
ggsave("graphs/01_LShB_rating.png", width = 6, height = 4)
```

```{r}
# Histogram plot of TShB_rating data ----------------------------------------
ggplot(RAW_data, aes(x = TIL_ShB)) +
  geom_histogram(aes(fill = YEAR), stat = "count") +
  scale_linetype(name = "Year") +
  facet_grid(WMGT ~ NRTE) +
  ggtitle("Tiller Sheath Blight Severity Rating")
ggsave("graphs/02_TShB_rating.png", width = 6, height = 4)
```

```{r}
# Density plot of TShB_incidence data ----------------------------------------
ggplot(RAW_data, aes(x = TShB_incidence)) +
  geom_density(aes(fill = YEAR, colour = YEAR)) +
  geom_rug() +
  scale_linetype(name = "Year") +
  facet_grid(WMGT ~ NRTE) +
  ggtitle("Tiller Sheath Blight Incidence") +
theme(axis.text.x = element_text(size = 8,
                                 angle = 45,
                                 hjust = 1))
ggsave("graphs/03_TShB_incidence.png", width = 6, height = 4)
```

```{r}
# Histogram plot of green leaf data -------------------------------------------
ggplot(RAW_data, aes(x = GL, linetype = YEAR)) +
  geom_histogram(aes(fill = YEAR), position = "dodge") +
  xlab("Count") +
  ggtitle("Green Leaves per Tiller")
ggsave("graphs/04_GL_value.png", width = 6, height = 4)
```

```{r}
# Histogram plot plot of dead leaf data ---------------------------------------
ggplot(RAW_data, aes(x = DL, linetype = YEAR)) +
  geom_histogram(aes(fill = YEAR), position = "dodge") +
  xlab("Count") +
  ggtitle("Dry Leaves per Tiller")
ggsave("graphs/05_DL_value.png", width = 6, height = 4)
```

```{r}
# Dot plot of leaf sheath blight severity data --------------------------------
ggplot(RAW_data, aes(x = ASMT, y = LEAF_ShB)) +
  geom_point(position = position_jitter(width = 0.05),
             aes(colour = YEAR), size = 0.75) +
  xlab("Assessment") +
  ylab("Rating") +
  ggtitle("Leaf Sheath Blight Severity at Each Assessment") +
  facet_grid(. ~ TRT) +
  theme(strip.text.x = element_text(angle = 90))
ggsave("graphs/06_LShB_severity_over_time.png", width = 6, height = 4)
```

```{r}
# Dot plot of tiller sheath blight severity data ------------------------------
ggplot(RAW_data, aes(x = ASMT, y = TIL_ShB)) +
  geom_point(position = position_jitter(width = 0.05),
             aes(colour = YEAR), size = 0.75) +
  xlab("Assessment") +
  ylab("Rating") +
  facet_grid(. ~ TRT) +
  ggtitle("Tiller Sheath Blight Severity at Each Assessment") +
  theme(strip.text.x = element_text(angle = 90))
ggsave("graphs/07_TShB_severity_over_time.png", width = 6, height = 4)
```

```{r}
# Line graph of tiller sheath blight incidence data ---------------------------
ggplot(RAW_data, aes(x = ASMT, y = TShB_incidence,
                     group = TShB_incidence)) +
  geom_point(position = position_jitter(width = 0.05),
             aes(colour = YEAR), size = 0.75) +
  xlab("Assessment") +
  ylab("Incidence") +
  facet_grid(. ~ TRT) +
  ggtitle("Tiller Sheath Blight Severity Rating Over Time") +
  theme(strip.text.x = element_text(angle = 90)) +
  xlab("Assessment") +
  ylab("Incidence") +
  ggtitle("Tiller Sheath Blight at Each Assessment")
ggsave("graphs/08_TShB_incidence_over_time.png", width = 6, height = 4)
```

```{r}
# Violin/dot plots of tiller sheath blight incidence data ----------------------
ggplot(RAW_data, aes(x = TRT, y = TShB_incidence)) +
  geom_point(position = position_jitter(width = 0.2),
             aes(colour = YEAR), size = 0.1) +
  geom_violin(fill = NA) +
  theme(axis.text.x = element_text(size = 8,
                                   angle = 45,
                                   hjust = 1)) +
  xlab("Treatment") +
  ylab("Incidence per Hill") +
  ggtitle("Tiller Sheath Blight Incidence")
ggsave("graphs/09_TShB_incidence_violin_plot.png", width = 6, height = 4)
```

```{r}
# Reorder factors for easier interpretation of plots
AUDPS$NRTE <-
  forcats::fct_relevel(AUDPS$NRTE,
                       "N0",
                       "N100",
                       "N120",
                       "N60",
                       "N180")

# Box/dotplots of leaf sheath blight severity AUDPS ----------------------------
ggplot(AUDPS, aes(x = NRTE, y = LShB_percent_AUDPS)) +
  geom_boxplot(aes(fill = YEAR)) +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  ggtitle("Leaf Sheath Blight Severity")
ggsave("graphs/10_LShB_severity_NRTE_AUDPS_boxplot.png", width = 6, height = 4)
```

```{r}
ggplot(AUDPS, aes(WMGT, y = LShB_percent_AUDPS)) +
  geom_boxplot(aes(fill = YEAR)) +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  facet_grid(. ~ YEAR) +
  ggtitle("Leaf Sheath Blight Severity")
ggsave("graphs/11_LShB_severity_WMGT_AUDPS_boxplot.png", width = 6, height = 4)
```

```{r}
# Box/dotplots of tiller sheath blight incidence AUDPS data --------------------
ggplot(AUDPS, aes(x = NRTE, y = TShB_inc_AUDPS)) +
  geom_boxplot(aes(fill = YEAR)) +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  ggtitle("Tiller Sheath Blight Incidence")
ggsave("graphs/12_TShB_inc_AUDPS_NRTE_boxplot.png", width = 6, height = 4)
```

```{r}
ggplot(AUDPS, aes(x = WMGT, y = TShB_inc_AUDPS)) +
  geom_boxplot(aes(fill = YEAR)) +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  facet_grid(. ~ YEAR) +
  ggtitle("Tiller Sheath Blight Incidence")
ggsave("graphs/13_TShB_inc_AUDPS_WMGT_boxplot.png", width = 6, height = 4)
```

```{r}
# Box/dotplots of leaf sheath blight severity AUDPS data -----------------------
ggplot(AUDPS, aes(x = NRTE, y = TShB_percent_AUDPS)) +
  geom_boxplot(aes(fill = YEAR)) +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  ggtitle("Tiller Sheath Blight Severity")
ggsave("graphs/14_TShB_severity_NRTE_AUDPS_boxplot.png", width = 6, height = 4)
```

```{r}
ggplot(AUDPS, aes(x = WMGT, y = TShB_inc_AUDPS)) +
  geom_boxplot(aes(fill = YEAR)) +
  geom_point() +
  xlab("Treatment") +
  ylab("AUDPS") +
  facet_grid(. ~ YEAR) +
  ggtitle("Tiller Sheath Blight Severity")
ggsave("graphs/15_TShB_severity_WMGT_AUDPS_boxplot.png", width = 6, height = 4)
```

```{r}
# Line graph of leaf sheath blight severity data -------------------------------
RAW_data %>% group_by(YEAR, WMGT, NRTE, ASMT) %>%
  summarize(value = mean(PERC_LEAF_ShB)) %>%
  ggplot(aes(x = ASMT,
             y = value,
             color = NRTE,
             group = NRTE)) +
  geom_line() +
  xlab("Assessment") +
  ylab("Severity (%)") +
  facet_grid(WMGT ~ YEAR) +
  ggtitle("Leaf Sheath Blight")
ggsave("graphs/16_LShB_progress_curves.png", width = 6, height = 4)
```

```{r}
# Line graph of tiller sheath blight severity AUDPS data ----------------------
RAW_data %>% group_by(YEAR, WMGT, NRTE, ASMT) %>%
  summarize(value = mean(PERC_TIL_ShB)) %>%
  ggplot(aes(x = ASMT,
             y = value,
             color = NRTE,
             group = NRTE)) +
  geom_line() +
  xlab("Assessment") +
  ylab("Severity (%)") +
  facet_grid(WMGT ~ YEAR) +
  ggtitle("Tiller Sheath Blight")
ggsave("graphs/17_TShB_progress_curves.png", width = 6, height = 4)
```

```{r}
# Line graph of tiller sheath blight incidence AUDPS data ---------------------
RAW_data %>% group_by(YEAR, WMGT, NRTE, ASMT) %>%
  summarize(value = mean(TShB_incidence)) %>%
  ggplot(aes(x = ASMT,
             y = value,
             color = NRTE,
             group = NRTE)) +
  geom_line() +
  xlab("Assessment") +
  ylab("Incidence (%)") +
  facet_grid(WMGT ~ YEAR) +
  ggtitle("Tiller Sheath Blight")
ggsave("graphs/18_TShB_incidence_progress_curves.png", width = 6, height = 4)
```

### 2017-08-24 R/02-preprocess_2016_data.R

@@ -1,218 +1,0 @@
-# Preprocess 2016 data for all assessments
-#
-# 1. Cleanup date format and fill empty dates
-# 2. Fill empty NTIL (for same hill, not missing values)
-# 3. Fill empty NTShB (for same hill, not missing values)
-
-# First assessment -------------------------------------------------------------
-DS2016_A1 <- read_csv("data/DS2016_Raw_1.csv")
-# Fill missing values in NTIL and NTShB
-DS2016_A1 <-
-  DS2016_A1 %>% fill(NTIL)
-DS2016_A1 <-
-  DS2016_A1 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A1[, 1] <- as.Date("2016-03-15", origin = "1970-01-01")
-DS2016_A1$ASMT <- rep(1, nrow(DS2016_A1))
-DS2016_A1$PLOT <- rep(1:16, each = 72)
-
-
-# Second assessement -----------------------------------------------------------
-DS2016_A2 <- read_csv("data/DS2016_Raw_2.csv")
-DS2016_A2 <-
-  DS2016_A2 %>% fill(NTIL)
-DS2016_A2 <-
-  DS2016_A2 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A2[, 1] <- as.Date("2016-03-29", origin = "1970-01-01")
-DS2016_A2$ASMT <- rep(2, nrow(DS2016_A2))
-DS2016_A2$PLOT <- rep(1:16, each = 72)
-
-
-# Third assessement ------------------------------------------------------------
-DS2016_A3 <- read_csv("data/DS2016_Raw_3.csv")
-DS2016_A3 <-
-  DS2016_A3 %>% fill(NTIL)
-DS2016_A3 <-
-  DS2016_A3 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A3[, 1] <- as.Date("2016-04-12", origin = "1970-01-01")
-DS2016_A3$ASMT <- rep(3, nrow(DS2016_A3))
-DS2016_A3$PLOT <- rep(1:16, each = 72)
-
-# Fourth assessment ------------------------------------------------------------
-DS2016_A4 <- read_csv("data/DS2016_Raw_4.csv")
-DS2016_A4 <-
-  DS2016_A4 %>% fill(NTIL)
-DS2016_A4 <-
-  DS2016_A4 %>% fill(NTShB)
-
-# Fill dates
[…]

### 2017-08-24 R/03_preprocess_data.R

@@ -1,264 +1,0 @@
-
-# Join the 2015 and 2016 Data into one Tibble ----------------------------------
-
-RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
-                            as.data.frame(DS2016)))
-
-# convert columns to factor ----------------------------------------------------
-RAW_data$YEAR <- factor(RAW_data$YEAR)
-RAW_data$ASMT <- factor(RAW_data$ASMT)
-RAW_data$PLOT <- factor(RAW_data$PLOT)
-RAW_data$REP <- factor(RAW_data$REP)
-RAW_data$TRT <- factor(RAW_data$TRT)
-RAW_data$WMGT <- factor(RAW_data$WMGT)
-RAW_data$NRTE <- factor(RAW_data$NRTE)
-RAW_data$SMPL <- factor(RAW_data$SMPL)
-RAW_data$HILL <- factor(RAW_data$HILL)
-RAW_data$TIL <- factor(RAW_data$TIL)
-RAW_data$LEAF <- factor(RAW_data$LEAF)
-
-
-# reorder the treatments by level/year - low to high, 2015-2016 for graphs -----
-RAW_data$NRTE <-
-  forcats::fct_relevel(RAW_data$NRTE,
-                       "0",
-                       "100",
-                       "120",
-                       "60",
-                       "180")
-
-RAW_data$TRT <-
-  forcats::fct_relevel(
-    RAW_data$TRT,
-    "AWD_N0",
-    "AWD_N100",
-    "AWD_N120",
-    "AWD_N60",
-    "AWD_N180",
-    "FLD_N0",
-    "FLD_N100",
-    "FLD_N120",
-    "FLD_N60",
-    "FLD_N180"
-  )
-
-# add column with midpoint % tiller ShB severity -------------------------------
-
-RAW_data <-
-  mutate(
-    RAW_data,
-    PERC_TIL_ShB = case_when(
-      TIL_ShB == 0 ~ 0,
-      TIL_ShB == 1 ~ 1,
-      TIL_ShB == 2 ~ 2.5,
-      TIL_ShB == 3 ~ 10,
-      TIL_ShB == 4 ~ 32.5,
-      TRUE ~ 75
-    )
-  )
-
-
[…]

### 2017-08-25 README.Rmd
Clean up R package
Package is now fully functional and passes R CMD checks

_pkgdown_ site is now included as well.

@@
 ---
-output:
-  md_document:
-    variant: markdown_github
+output: github_document
 ---
@@
 
-The goal of rice.awd.shb is to ...
+The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect pests and sheath blight disease in rice paddies.
+
+## Study
+
+**Objective:** Study the effects of different water and nitrogen managements on sheath blight of rice
+
+**Project PI:** Dr. Adam H Sparks  and Dr. Buyung AR Hadi
+
+**Staff:**
+
+  * Dr. Nancy P. Castilla (2016)
+
+  * Mr. Michael Noel (2015)
+
+******
+
+### 1. SCHEDULE
+
+IRRI Dry Season (2)
+
+ * 2015 (December 2014 – April 2015)
+
+ * 2016 (January 2016 - May 2016)
+
+### 2. METHODOLOGY
+
+**Experimental Design: Split-plot**
+
+  * Main plot : Water management (2)
+
+    * W1 – Alternate Wetting and Drying (AWD)
+
+    * W2 – Flooded/Farmer’s Practice
+
+  * Sub-plot : Nitrogen management (5)
+
+    * 2015
+
+      * N0 – 0 kg/ha
+
+      * N1 – 100 kg/ha (farmer’s practice – based from J. Bigornia research)
+
+      * N2 – 120 kg/ha (IRRI practice – based from L. Willocquet research)
+
+    * 2016
+
+      * N3 – 60 kg/ha
+
+      * N4 - 180 kg/ha
+
+  * Replication: Four (4)
+
+  * Plot Sizes (2015)
+
+    * Main plot size: 12m x 12m (144 sq m)
+
+    * Sub-plot size: 5m x 5m (25 sq m)
+
+    * Replication size: 12m x 24m (288 sq m)
+
+    * Buffer: 1m per sub plot
+
+    * Experiment size: 1,152 sq m
+
+  * Plot Sizes (2016)
+
+    * Main plot size
+
+      * Block 2007: 21m x 20.5m (412.5 sq m)
+
+      * Block 2008: 20.25m x 21.6m (437.4 sq m)
+
+    * Sub-plot size
+
+      * Block 2007: 21m x 10.25m (215.25 sq m)
+
+      * Block 2008: 20.25m x 10.8m (218.7 sq m)
+
+    * Replication size:
+
+      * Block 2007: 42m x 20.5m (861 sq m)
+
+      * Block 2008: 40.5m x 21.6m (874.8 sq m)
+
+    * Buffer: 0.5m per sub plot
+
+    * Experiment size: 3471.6 sq m
+
+******
+
+**Disease Rating Scale**
+
+Disease was rated using an ordinal scale for field evaluation of sheath blight (S Savary & N Castilla).
+
+* **Rating Scale - Severity (%)**
+
+    * 0 - 0,
+
+    * 1 - 1%,
+
+    * 2 - 5%,
+
+    * 3 - 15%,
+
+    * 4 - 50%,
+
+    * 5 - >50%
+
+******
+
+**Nitrogen Management Rates**
+
+<table width = "500">
+<tr>
+  <th rowspan = "2">Nitrogen<br>treatment</th>
+  <th rowspan = "2">Year</th>
+  <th rowspan = "2">Total N<br>(kg/ha)</th>
+  <th colspan = "4">Application Amount (kg/ha)</th>
+</tr>
+<tr>
+  <th>Basal</th>
+  <th>Tillering</th>
+  <th>Panicle<br>Intitiation</th>
+</tr>
+<tr>
+  <td>N0</td>
+  <td>2015</td>
+  <td>0</td>
+  <td>0</td>
+  <td>0</td>
+  <td>0</td>
+</tr>
+<tr>
+  <td>N100</td>
+  <td>2015</td>
+  <td>100</td>
+  <td>60</td>
+  <td>20</td>
+  <td>20</td>
+</tr>
+<tr>
+  <td>N120</td>
+  <td>2015</td>
+  <td>120</td>
+  <td>60</td>
+  <td>30</td>
+  <td>30</td>
+</tr>
+<tr>
+  <td>N60</td>
+  <td>2016</td>
+  <td>60</td>
+  <td>30</td>
+  <td>30</td>
+  <td>0</td>
+</tr>
+<tr>
+  <td>N180</td>
+  <td>2016</td>
+  <td>180</td>
+  <td>60</td>
+  <td>60</td>
+  <td>60</td>
+</tr>
+</table>
+
+## Resources
+
+### glmm split plot analysis
+
+http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html
+
+http://www.stat.wisc.edu/courses/st572-larget/Spring2007/handouts16-4.pdf
+
+http://www.maths.bath.ac.uk/~jjf23/mixchange/split.html
+
+### Using MCMCglmm
+
+http://www.maths.bath.ac.uk/~jjf23/mixchange/onewayanova.html
+
+http://www.maths.bath.ac.uk/~jjf23/mixchange/split.html#mcmcglmm
+
+https://github.com/tmalsburg/MCMCglmm-intro
+
+### General GLMM in R
+
+http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html
 
@@
 
-$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+**Data:** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
 

### 2017-08-25 R/data.R

@@ -1,0 +1,15 @@
+
+#' A Tidy Data Frame of Area Under the Disease Progress Stairs for Sheath Blight Observations
+#'
+#' A dataset containing the alternate wetting and drying study data observations
+#' and calculated Area Under the Disease Progress Stairs (AUDPS)
+#'
+"AUDPS"
+
+#' A Tidy Data frame of Raw Data for Sheath Blight Observations
+#'
+#' A dataset containing the alternate wetting and drying study data observations
+#' organised into a tidy data frame.
+#'
+"RAW_data"
+

### 2017-08-25 R/diagnostic_plots.R

@@ -1,0 +1,90 @@
+
+#' @title MCMCglmm diagnostic plots
+#'
+#' @description Plot diagnostic graphs from MCMCglmm outputs
+#'
+#' @export
+#' @name plot_mcmc_glmm
+#' @param d A melted data.frame of MCMCglmm diagnostic outputs
+#' @param x Dummy x-axis for diagnostic lines plot
+#' @param title Title to be used in resulting graph output
+#'
+#'
+#' @section Functions:
+#' \itemize{
+#'  \item \code{plot_diagnostic_lines()} plots diagnostic lines from MCMCglmm
+#'  output
+#'  \item \code{plot_replicate_posteriors()} plots a violin plot of posteriors
+#'  for experimental plot replicates
+#'  \item \code{plot_treatment_posteriors()} plots a violin plot of posteriors
+#'  for experimental plot treatments
+#'  \item \code{plot_joint_random_error_dist()} plots joint distribution
+#' }
+#'
+#' @examples \dontrun{
+#' # Plot diagnostic lines
+#' plot_diagnostic_lines(d = reps, x = x, title = "Diagnostic Lines Plot")
+#'
+#' # Plot replicate posteriors
+#' plot_replicate_posteriors(d = reps, title = "Replicate Posteriors")
+#'
+#' # Plot treatment posteriors
+#' plot_treatment_posteriors(d =  trts, title = "Treatment Posteriors")
+#'
+#' # Plot joint random error
+#' plot_joint_random_error_dist(d = rdf, title = ("Random Error Distribution"))
+#' }
+#'
+#' @author Adam H Sparks, \email{adamhsparks@gmail.com}
+#'
+#'
+#' @export
+#' @rdname plot_mcmc_glmm
+plot_diagnostic_lines <- function(d, x, title) {
+  ggplot2::ggplot(data = d, ggplot2::aes(
+    x = rep(x, length(unique(d$variable))),
+    y = d$value,
+    group = d$variable
+  )) +
+    ggplot2::geom_line() +
+    ggplot2::xlab("Iteration Number") +
+    ggplot2::ylab(NULL) +
+    ggplot2::facet_grid(variable ~ .) +
+    ggplot2::theme(strip.text.y = ggplot2::element_text(angle = 0)) +
+    ggplot2::ggtitle(paste(title))
+}
+
+#' @export
+#' @rdname plot_mcmc_glmm
+plot_replicate_posteriors <- function(d, title) {
[…]

### 2017-08-25 README.Rmd
Update README.md
Remove link in "Data"

@@
 
-**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+Text and figures:  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
 
-**Code:** See the [DESCRIPTION](DESCRIPTION) file
+Code: See the [DESCRIPTION](DESCRIPTION) file
 
-**Data:** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
 

### 2017-08-25 data-raw/01-Clean_2015_Raw_Data.Rmd
Update 01-Clean_2015_Raw_Data.Rmd

@@
 _rice.awd.pests_ and can be accessed using:
-
-`load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))`
+```r
+load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
+```
 

### 2017-08-25 data-raw/01-Clean_2015_Raw_Data.Rmd
Update 01-Clean_2015_Raw_Data.Rmd

--- 2017-08-24 data-raw/01-Clean_2015_Raw_Data.Rmd
@@
 _rice.awd.pests_ and can be accessed using:
-
-`load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))`
+```{r, eval=FALSE}
+load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
+```
 

### 2017-08-25 data-raw/Clean_Data_and_Calculate_AUDPS.Rmd
Cleanup in RAW_data
Remove extra files and add documentation to file about the cleaning

--- 2017-08-24 data-raw/01-Clean_2015_Raw_Data.Rmd
@@
 The raw data are located in the `extdata` folder of the installed
-_rice.awd.pests_ and can be accessed using:
+_rice.awd.pests_
+
+# Dry season 2015 importing and cleaning
+
+DS2015 data can be accessed using:
 
@@
 }
-
-save(DS2015, file = "../data/DS2015", compress = "bzip2")
-
 ```
 
-The raw data are located in the `extdata` folder of the installed
+# Dry season 2016 importing and cleaning
+
+The 2016 season raw data are located in the `extdata` folder of the installed
 _rice.awd.pests_ and can be accessed using:
 
-`load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))`
-`load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))`
+```{r, eval=FALSE}
+load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
+load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
+```
 
@@
 
+# Calculating Area Under the Disease Progress Stairs (AUDPS)
+
+Because the data were collected on an ordinal scale, but not evenly spaced,
+the data are converted to the midpoint value of the percent range for severity
+and then the AUDPS is calculated from that. See lines 544 and 559 for this.
+
+After that the AUDPS is calculated using functionality from the _agricolae_
+package.
+
+Last, the data are saved in the package for use analysis, which is detailed
+in the package [vingettes](../vignettes).
+
 ```{r}
@@
 # add column with midpoint % tiller ShB severity -------------------------------
-
 RAW_data <-
@@
 TShB_percent_AUDPS <-
-  audps(evaluation = TShB_perc_wide[, 2:6],
+  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
         dates = as.vector(TShB_perc_15[1:5, 6]))
@@
 LShB_percent_AUDPS <-
-  audps(evaluation = LShB_perc_wide[, 2:6],
+  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
         dates = as.vector(LShB_perc_15[1:5, 6]))
@@
 
-save(AUDPS, file = "../data/AWD_AUDPS", compress = "bzip2")
+devtools::use_data(AUDPS,
+                   compress = "bzip2",
+                   overwrite = TRUE)
 ```

### 2017-08-25 data-raw/Clean_Data_and_Calculate_AUDPS.Rmd
Fix bug related to creation of AUDPS data frame for analysis
Package now passes R CMD checks

@@
   agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
-                   dates = as.vector(LShB_sev_15[1:5, 6]))
+                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))
 
@@
   agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
-        dates = as.vector(TShB_perc_15[1:5, 6]))
+        dates = dplyr::pull(TShB_perc_15[1:5, 6]))
 
@@
   agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
-        dates = as.vector(LShB_perc_15[1:5, 6]))
+        dates = dplyr::pull(LShB_perc_15[1:5, 6]))
 
@@
 
-# 2015 AUDPS -------------------------------------------------------------------
+# 2016 AUDPS -------------------------------------------------------------------
 
@@
 
-# add plot numbers to merge with the remaing treatment data
+# add plot numbers to merge with the remaining treatment data
 AUDPS_16$PLOT <- as.character(AUDPS_16$PLOT)

### 2017-08-25 README.Rmd
Add travis and appveyor CI and badges
Maybe we don’t need no steenking badges?

They’re nice anyway. I think we’ll keep ‘em.

@@
 ```
+[![Travis-CI Build Status](https://travis-ci.org/phytopathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/phytopathology/rice_awd_pests)
+[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/rice_awd_pests?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/rice_awd_pests)
 

### 2017-08-25 R/data.R
Lint files and check package spelling

@@ -12,4 +12,3 @@
 #' organised into a tidy data frame.
 #'
 "RAW_data"
-

### 2017-08-25 README.Rmd
Clarify a few points in README

@@
 
-The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect pests and sheath blight disease in rice paddies.
+The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.
 
@@
 
-**Objective:** Study the effects of different water and nitrogen managements on sheath blight of rice
+**Objective 1:** Study the effects of different water and nitrogen managements on sheath blight of rice
 

### 2017-08-25 README.Rmd
Update README
Correct repository references

@@
 
-# rice.awd.shb
+# rice.awd.pests
 
-The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.
+The goal of _rice.awd.pests_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.
 
@@
 
-**Project PI:** Dr. Adam H Sparks  and Dr. Buyung AR Hadi
+**Project PI:** Dr. Adam H Sparks
 

### 2017-08-25 analysis/paper/paper.tex
Add eps file and edit title of paper

@@
 \textbf\newline{Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates
-Affect Rice Pests and Diseases?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+Affect Rice Insect Populations and Diseases?} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }

### 2017-09-20 analysis/paper/paper.Rmd
Add eps file and edit title of paper
Add metadata and apps abstract to analysis directory

@@
 ---
-title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Pests and Diseases?
+title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Insect Populations and Diseases?
 author:
@@
 
-The sub plot treatments were different rates of nitrogen…
+The subplot treatments were different rates of nitrogen…
+
+The plots were inoculated using...
 
@@
 A buffer 0.5m per sub plot was used and the overall experiment size was 3471.6 sq m.
+
+The plots were inoculated using...
 

### 2017-09-21 R/rice.awd.pests.R
Update authors and cleanup file structure
- Delete "doc" directory

- Add Nancy and Kyle as contributors to the package

- Add rice.awd.pests-package documentation

@@ -1,0 +1,25 @@
+
+#' Reproducible Research Compendium for Analysing Effects of Water Management and Nitrogen on Rice Sheath Blight and Insect Populations
+#'
+#' @description
+#' Provides a research compendium of analysis associated with experiments
+#' conducted at the International Rice Research Institute (IRRI), Los Baños,
+#' Calabarzon, Philippines in the dry seasons of 2015 and 2016. The experiments
+#' were designed to test the effects of alternate wetting and drying irrigation
+#' management on rice sheath blight disease. The plots were split plot with an
+#' irrigation main plot and nitrogen sub-plot treatments.
+#'
+#' @name rice.awd.pests-package
+#' @author Adam H Sparks and Nancy P Castilla and Michael Noel
+#' @docType package
+#'
+#' @seealso
+#'\strong{Useful links:}
+#' \itemize{
+#' \item{\url{https://github.com/phytopathology/rice_awd_pests}}
+#' \item{Report bugs at
+#'  \url{https://github.com/phytopathology/rice_awd_pests/issues}}
+#' \item{Research compendium website
+#'  \url{https://phytopathology.github.io/rice_awd_pests/}}
+#' }
+NULL

### 2018-03-15 analysis/paper/paper.Rmd
Update paper template
Won't submit to PLOS. Use generic template for time-being for eventual pre-print submission.

@@
 ---
-title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Insect Populations and Diseases?
-author:
-  - name: A.H. Sparks
-    email: adam.sparks@usq.edu.au
-    affiliation: University of Southern Queensland
-    corresponding: adam.sparks@usq.edu.au
-  - name: N.P. Castilla
-    email: n.castilla@irri.org
-    affiliation: International Rice Research Institute
-  - name: B.A.R. Hadi
-    email: b.hadi@irri.org
-    affiliation: International Rice Research Institute
-  - name: B.O. Sander
-    email: b.sander@irri.org
-    affiliation: International Rice Research Institute
-address:
-  - code: University of Southern Queensland
-    address: Centre for Crop Health, West Street, Toowoomba, Queensland, Australia, 4350
-  - code: International Rice Research Institute
-    address: Los Baños, Laguna, Philippines, 4031
+title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?
+author: |
+  | Adam H. Sparks 1^[Corresponding author: Adam.Sparks@usq.edu.au] $^1, *$, Nancy P. Castilla $^1$, Bjorn Ole Sander $^1$
+  | $^1$International Rice Research Institute, Los Baños, Laguna, Philippines, 4031 $*$Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
 abstract: |
@@
 
-author_summary: |
-  Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+bibliography: references.bib
+output:
+  bookdown::pdf_document2:
+  toc: no
+fig_caption: yes
 
-bibliography: references.bib
-output: rticles::plos_article
-csl: plos.csl
+always_allow_html: yes
+
+# These are LaTex settings to take care of floating figures/tables, line spacing, etc
+header-includes:
+  - \usepackage{endfloat}    
+  - \usepackage{setspace}\doublespacing
+  - \usepackage{lineno}
+  - \linenumbers
 ---
 
-_Text based on plos sample manuscript, see [http://journals.plos.org/ploscompbiol/s/latex](http://journals.plos.org/ploscompbiol/s/latex)_
+```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
+knitr::opts_chunk$set(fig.pos = "p") # Places figures on their own pages
+knitr::opts_chunk$set(out.width = "100%", dpi = 300)
+
+# I usually load my libraries up front to keep things organized
+library(bookdown)
+library(knitr)
+library(kableExtra)
+library(ggplot2)
+library(ggthemes)
+library(ggExtra)
+library(dplyr)
+library(stringr)
+```
 
@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14°11' N, , longitude 121°15' E) in the 2015 and 2016 dry seasons.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons.
 For the 2016 season changes were made to optimize the experiment based on findings from the 2015 season.

### 2018-03-15 analysis/paper/paper.Rmd
Fix author affiliations and addresses

@@
 author: |
-  | Adam H. Sparks 1^[Corresponding author: Adam.Sparks@usq.edu.au] $^1, *$, Nancy P. Castilla $^1$, Bjorn Ole Sander $^1$
-  | $^1$International Rice Research Institute, Los Baños, Laguna, Philippines, 4031 $*$Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
+  | Adam H. Sparks 1^[Corresponding author: Adam.Sparks@usq.edu.au]  \textsuperscript{1, \dag}, Nancy P. Castilla \textsuperscript{1}, Bjorn Ole Sander \textsuperscript{1}
+  | \textsuperscript{1}International Rice Research Institute, Crop and Environmental Sciences Divsion, Los Baños, Laguna, Philippines, 4031 \newline \textsuperscript{\dag} Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
 abstract: |

### 2018-03-15 analysis/paper/paper.Rmd
Remove TOC from PDF
Clean up extra spaces in code
Remove code comment

@@
 
-# I usually load my libraries up front to keep things organized
 library(bookdown)

### 2018-03-15 analysis/paper/paper.Rmd
Add more description to data analysis

@@
 The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, e.g., Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015].
+Various countries, \textit{e.g.}, Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015].
 However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
@@
 
-Data were analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
+Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
+Five and four disease assessments were made in 2015 and 2016, respectively.
+Data were analysed using the area under the disease progress stairs (AUDPS) and multivariate generalised linear mixed models.
+We were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season.
+Our findings indicate that farmers can safely adopt the AWD technology without risk of increasing sheath blight disease.
+
+Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area] and analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
 
@@
 # Discussion
-
-# Conclusions (optional)
 

### 2018-03-15 analysis/paper/paper.Rmd
Clean up data collection and analysis section

@@
 Five and four disease assessments were made in 2015 and 2016, respectively.
-Data were analysed using the area under the disease progress stairs (AUDPS) and multivariate generalised linear mixed models.
-We were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season.
-Our findings indicate that farmers can safely adopt the AWD technology without risk of increasing sheath blight disease.
 

### 2018-03-15 analysis/paper/paper.Rmd
Remove extra R libraries
Correct spelling of "Division" and fix new line in affiliations

@@
   | Adam H. Sparks 1^[Corresponding author: Adam.Sparks@usq.edu.au]  \textsuperscript{1, \dag}, Nancy P. Castilla \textsuperscript{1}, Bjorn Ole Sander \textsuperscript{1}
-  | \textsuperscript{1}International Rice Research Institute, Crop and Environmental Sciences Divsion, Los Baños, Laguna, Philippines, 4031 \newline \textsuperscript{\dag} Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
+  | \textsuperscript{1}International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna, Philippines, 4031
+  | \textsuperscript{\dag} Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
 abstract: |
@@
 library(kableExtra)
-library(ggplot2)
-library(ggthemes)
-library(ggExtra)
-library(dplyr)
-library(stringr)
 ```

### 2018-03-15 analysis/paper/paper.Rmd
Remove "," from my affiliation superscript notation
Remove extra "1" from my name in author list
Clean up comments

@@
 author: |
-  | Adam H. Sparks 1^[Corresponding author: Adam.Sparks@usq.edu.au]  \textsuperscript{1, \dag}, Nancy P. Castilla \textsuperscript{1}, Bjorn Ole Sander \textsuperscript{1}
+  | Adam H. Sparks^[Corresponding author: Adam.Sparks@usq.edu.au]  \textsuperscript{1\dag}, Nancy P. Castilla \textsuperscript{1}, Bjorn Ole Sander \textsuperscript{1}
   | \textsuperscript{1}International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna, Philippines, 4031
@@
 
-# These are LaTex settings to take care of floating figures/tables, line spacing, etc
 header-includes:
@@
 ```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(fig.pos = "p") # Places figures on their own pages
+knitr::opts_chunk$set(fig.pos = "p")
 knitr::opts_chunk$set(out.width = "100%", dpi = 300)

### 2018-03-15 analysis/paper/paper.Rmd
Capitalise all headings in the same fashion
Update m&m section

@@
 
-## Experimental design
+## Experimental Design
 
@@
 
-Irrigation in AWD plots was determined by the water level in plots, i.e., when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
+Irrigation in AWD plots was determined by the water level in plots, \emph{i.e.}, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
 In CF plots a standing water layer of 3-5cm was maintained throughout the growing season.
 
-The subplot treatments were different rates of nitrogen…
+The subplot treatments were different rates of nitrogen, 0 kg/ha (control), 100 kg/ha in three splits, and 120 kg/ha in three splits.
 
-The plots were inoculated using...
+The plots were inoculated 20 days after transplanting using 151g of inoculum per plot (4m x 11m).
 
@@
 
-The plots were inoculated using...
+Subplot N rates were changed from the 2015 rates to use 60 kg/ha split into two applications (control) and 180 kg/ha in three splits.
 
-## Data collection and analysis
+Based on the 2015 results, the inoculation methods were modified in 2016 to increase the amount of inoculum applied to a smaller area.
+Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1m x 1m) per plot, where one bottle contained 151g inoculum.
+A total amount of 1,510g of inoculum was applied to a 1m x 1m area.
 
-Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
+## Data Collection and Analysis
+
+Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI.
+Two sample areas per plot (1m x 1m) were assessed.
+for 9 hills per sample, the number of tillers per hill and number of tillers with sheath blight (incidence) were measured.
+Tiller sheath blight severity was measured for four tillers per hill and six leaves tiller.
 Five and four disease assessments were made in 2015 and 2016, respectively.

### 2018-03-15 analysis/paper/paper.Rmd
Add severity rating figure
Will need to be adapted for publication, but will work for now for drafting article

@@
 
-Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI.
+Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI \ref{figure1}.
 Two sample areas per plot (1m x 1m) were assessed.
@@
 Five and four disease assessments were made in 2015 and 2016, respectively.
+
+![IRRI sheath blight field severity rating scale where, 0 - 0%, 1 - 1%, 2 - 5%,
+3 - 15%, 4 - 50%, 5 - >50%. \label{figure1}](./Figures/Figure 1 IRRI Sheath Blight Severity Assessment.png)
 

### 2018-03-17 analysis/paper/paper.Rmd
Edits to m&m section
Clean up N rate description for 2016 and clarify analysis statement

@@
 
-Subplot N rates were changed from the 2015 rates to use 60 kg/ha split into two applications (control) and 180 kg/ha in three splits.
+Subplot N rates differed from the 2015 rates. The control was applied as 60 kg/ha split into two applications and a second treatment of 180 kg/ha in three splits was applied.
 
@@
 
-Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area] and analysed using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
+Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area].
+As most of the data did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
 

### 2018-03-17 analysis/paper/paper.Rmd
Add results to write from

@@
 
+### Tiller Sheath Blight Incidence
+
+In 2015 both the nitrogen rates, N100 and N120, were significant when compared with the base N0 rate, water management was not significant.
+
+In 2016 the nitrogen rate N180, was significantly different than the base N60 rate, water management was not significant.
+
+### Tiller Sheath Blight Severity
+
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
+
+In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the base flooding treatment.
+
+### Leaf Sheath Blight Severity
+
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
+
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the base treatment for leaf sheath blight severity.
+
 # Discussion

### 2018-04-06 analysis/paper/paper.Rmd
Add scientific names to introduction text

@@
 
-Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
-In AWD rice fields are exposed to several dry phases during the growth period without exposing the plants to water stress.
+Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice (\emph{Oryza sativa L.}) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
+In AWD rice, fields are exposed to several dry phases during the growth period without exposing the plants to water stress.
 In order to avoid yield decline under AWD “safe” thresholds have been developed.
@@
 Fields are furthermore kept flooded during the flowering period.
-Besides saving water AWD also reduces greenhouse gas (GHG) emissions of rice fields, which is a substantial factor in the GHG budget of rice producing countries, by around 50% [@Yan2005; @Sander2015].
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50% [@Yan2005; @Sander2015].
 
@@
 
-We therefore established field experiments in order to…
+We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (\emph{Rhizoctonia solani} Kühn) [(teleomorph: \emph{Thanatephorus cucumeris} (A.B.
+Frank) Donk.] of rice.
 

### 2018-04-06 README.Rmd
Update Travis badge link

@@
 ```
-[![Travis-CI Build Status](https://travis-ci.org/phytopathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/phytopathology/rice_awd_pests)
+[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
 [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/rice_awd_pests?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/rice_awd_pests)

### 2018-04-09 README.Rmd
Clean up linebreaks and whatnot in README.Rmd

--- 2017-08-25 README.Rmd
@@
 ```
-[![Travis-CI Build Status](https://travis-ci.org/phytopathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/phytopathology/rice_awd_pests)
+
+[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
 [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/rice_awd_pests?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/rice_awd_pests)
@@
 
-The goal of _rice.awd.pests_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.
+The goal of _rice.awd.pests_ is to examine the effects of using alternate
+wetting and drying irrigation techniques on insect populations and sheath blight
+disease in rice paddies.
 
@@
 
-**Objective 1:** Study the effects of different water and nitrogen managements on sheath blight of rice
+**Objective 1:** Study the effects of different water and nitrogen managements
+on sheath blight of rice
 
@@
 
-Disease was rated using an ordinal scale for field evaluation of sheath blight (S Savary & N Castilla).
+Disease was rated using an ordinal scale for field evaluation of sheath blight
+(S Savary & N Castilla).
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Title of compendium_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Authors, (`r format(Sys.Date(), "%Y")`).
+_Reproducible Research Compendium for Analysing Effects of Water Management and Nitrogen on Rice Sheath Blight_.
+Accessed `r format(Sys.Date(), "%d %b %Y")`.
+Online at <https://doi.org/xxx/xxx>
 
@@
 
-Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse
+Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
+requested in reuse
 
@@
 
-We welcome contributions from everyone.
-Before you get started, please see our [contributor guidelines](CONTRIBUTING.md).
-Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
-By participating in this project you agree to abide by its terms.
+We welcome contributions from everyone. Before you get started, please see our
+[contributor guidelines](CONTRIBUTING.md). Please note that this project is
+released with a [Contributor Code of Conduct](CONDUCT.md). By participating in
+this project you agree to abide by its terms.

### 2018-04-09 README.Rmd
Update study description in README.Rmd

@@
 The goal of _rice.awd.pests_ is to examine the effects of using alternate
-wetting and drying irrigation techniques on insect populations and sheath blight
-disease in rice paddies.
+wetting and drying irrigation techniques on sheath blight disease in rice
+paddies.
 

### 2018-04-09 README.Rmd
Update README.Rmd
Add badges and restructure to fit research compendium structure

@@
 ```
-
+[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/openplantpathology/rice.awd.pests/commits/master)
+[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
+[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
 [![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
@@
 
-# rice.awd.pests
+## Research compendium for a report on the effects of using alternate wetting and drying irrigation techniques on sheath blight disease in rice paddies.
 
-The goal of _rice.awd.pests_ is to examine the effects of using alternate
-wetting and drying irrigation techniques on sheath blight disease in rice
-paddies.
+### Compendium DOI:
 
-## Study
+http://dx.doi.org/xxxxxxx
 
-**Objective 1:** Study the effects of different water and nitrogen managements
-on sheath blight of rice
+The files at the URL above will generate the results as found in the
+publication. The files hosted at github.com/openplantpathology/rice.awd.pests
+are the development versions and may have changed since the report was
+published.
 
-**Project PI:** Dr. Adam H Sparks
+### Authors of this repository:
 
-**Staff:**
+Adam H. Sparks (adam.sparks@usq.edu.au)
 
-  * Dr. Nancy P. Castilla (2016)
+Nancy P. Castilla (n.castilla@irri.org)
 
-  * Mr. Michael Noel (2015)
+B. Ole Sander (b.sander@irri.org)
 
-******
+M. Noel
 
-### 1. SCHEDULE
+### Published in:
 
-IRRI Dry Season (2)
+Sparks, A,  xxxxx
 
- * 2015 (December 2014 – April 2015)
+### Overview of contents
 
- * 2016 (January 2016 - May 2016)
+This repository is our research compendium for our analysis of the effects of
+alternate wetting and drying irrigation technology on rice sheath blight
+disease. The compendium contains all data, code, and text associated with the
+publication. The `Rmd` files in the `analysis/paper/` directory contain details
+of how all the analyses reported in the paper were conducted, as well as
+instructions on how to rerun the analysis to reproduce the results. The
+`data/` directory in the `analysis/` directory contains all the raw data.
 
-### 2. METHODOLOGY
+### The supplementary files
 
-**Experimental Design: Split-plot**
+The `analysis/` directory contains:
 
-  * Main plot : Water management (2)
+- the manuscript as submitted (in PDF format) and it's Rmd source file
+- all the data files (in CSV file format, in the `data/` directory)
+- supplementary information source files (in R markdown format) and executed versions
+- all the figures that are included in the paper (in the `figures/` directory)
 
-    * W1 – Alternate Wetting and Drying (AWD)
+### The R package
 
-    * W2 – Flooded/Farmer’s Practice
+This repository is organized as an R package. There are no actual R functions in
+this package - all the R code is in the Rmd file. I simply used the R package
+structure to help manage dependencies, to take advantage of continuous
+integration for automated code testing, and so I didn't have to think too much
+about how to organise the files.
 
-  * Sub-plot : Nitrogen management (5)
+To download the package source as you see it on GitHub, for offline browsing,
+use this line at the shell prompt (assuming you have Git installed on your
+computer):
 
-    * 2015
+```
+git clone https://github.com/openplantpathology/rice_awd_pests.git
+```
 
-      * N0 – 0 kg/ha
+Once the download is complete, open the `rice.awd.pests.Rproj` in RStudio to
+begin working with the package and compendium files.
 
-      * N1 – 100 kg/ha (farmer’s practice – based from J. Bigornia research)
+The package has a number of dependencies on other R packages, and programs
+outside of R. These are listed at the bottom of this README. Installing these
+can be time-consuming and complicated, so we've done two things to simpify
+access to the compendium. First is the packrat directory, which contains the
+source code for all the packages we depend on. If all works well, these will be
+installed on your computer when you open `rice_awd_.pests.Rproj` in RStudio.
+Second is our Docker image that includes all the necessary software, code and
+data to run our analysis. The Docker image may give a quicker entry point to the
+project, and is more self-contained, so might save some fiddling with installing
+things.
 
-      * N2 – 120 kg/ha (IRRI practice – based from L. Willocquet research)
+### The Docker image
 
-    * 2016
+A Docker image is a lightweight GNU/Linux virtual computer that can be run as a
+piece of software on Windows and OSX (and other Linux systems). To capture the
+complete computational environment used for this project we have a Dockerfile
+that specifies how to make the Docker image that we developed this project in.
+The Docker image includes all of the software dependencies needed to run the
+code in this project, as well as the R package and other compendium files. To
+launch the Docker image for this project, first, 
+[install Docker](https://docs.docker.com/installation/) on your computer. At the
+Docker prompt, enter:
 
-      * N3 – 60 kg/ha
+    docker run -dp 8787:8787 adamhsparks/rice.awd.pests
 
-      * N4 - 180 kg/ha
+This will start a server instance of RStudio. Then open your web browser at
+localhost:8787 or or run `docker-machine ip default` in the shell to find the
+correct IP address, and log in with rstudio/rstudio.
 
-  * Replication: Four (4)
+Once logged in, use the Files pane (bottom right) to navigate to `/` (the root
+directory), then open the folder for this project, and open the `.Rproj` file
+for this project. Once that's open, you'll see the `analysis/paper` directory in
+the Files pane where you can find the R markdown document, and knit them to
+produce the results in the paper. More information about using RStudio in Docker
+is avaiable at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
 
-  * Plot Sizes (2015)
+We developed and tested the package on this Docker container, so this is the
+only platform that We're confident it works on, and so recommend to anyone
+wanting to use this package to generate the vignette, etc.
 
-    * Main plot size: 12m x 12m (144 sq m)
-
-    * Sub-plot size: 5m x 5m (25 sq m)
-
-    * Replication size: 12m x 24m (288 sq m)
-
-    * Buffer: 1m per sub plot
-
-    * Experiment size: 1,152 sq m
-
-  * Plot Sizes (2016)
-
-    * Main plot size
-
-      * Block 2007: 21m x 20.5m (412.5 sq m)
-
-      * Block 2008: 20.25m x 21.6m (437.4 sq m)
-
-    * Sub-plot size
-
-      * Block 2007: 21m x 10.25m (215.25 sq m)
-
-      * Block 2008: 20.25m x 10.8m (218.7 sq m)
-
-    * Replication size:
-
-      * Block 2007: 42m x 20.5m (861 sq m)
-
-      * Block 2008: 40.5m x 21.6m (874.8 sq m)
-
-    * Buffer: 0.5m per sub plot
-
-    * Experiment size: 3471.6 sq m
-
-******
-
-**Disease Rating Scale**
-
-Disease was rated using an ordinal scale for field evaluation of sheath blight
-(S Savary & N Castilla).
-
-* **Rating Scale - Severity (%)**
-
-    * 0 - 0,
-
-    * 1 - 1%,
-
-    * 2 - 5%,
-
-    * 3 - 15%,
-
-    * 4 - 50%,
-
-    * 5 - >50%
-
-******
-
-**Nitrogen Management Rates**
-
-<table width = "500">
-<tr>
-  <th rowspan = "2">Nitrogen<br>treatment</th>
-  <th rowspan = "2">Year</th>
-  <th rowspan = "2">Total N<br>(kg/ha)</th>
-  <th colspan = "4">Application Amount (kg/ha)</th>
-</tr>
-<tr>
-  <th>Basal</th>
-  <th>Tillering</th>
-  <th>Panicle<br>Intitiation</th>
-</tr>
-<tr>
-  <td>N0</td>
-  <td>2015</td>
-  <td>0</td>
-  <td>0</td>
-  <td>0</td>
-  <td>0</td>
-</tr>
-<tr>
-  <td>N100</td>
-  <td>2015</td>
-  <td>100</td>
-  <td>60</td>
-  <td>20</td>
-  <td>20</td>
-</tr>
-<tr>
-  <td>N120</td>
-  <td>2015</td>
-  <td>120</td>
-  <td>60</td>
-  <td>30</td>
-  <td>30</td>
-</tr>
-<tr>
-  <td>N60</td>
-  <td>2016</td>
-  <td>60</td>
-  <td>30</td>
-  <td>30</td>
-  <td>0</td>
-</tr>
-<tr>
-  <td>N180</td>
-  <td>2016</td>
-  <td>180</td>
-  <td>60</td>
-  <td>60</td>
-  <td>60</td>
-</tr>
-</table>
-
-## Resources
-
-### glmm split plot analysis
-
-http://ase.tufts.edu/gsc/gradresources/guidetomixedmodelsinr/mixed%20model%20guide.html
-
-http://www.stat.wisc.edu/courses/st572-larget/Spring2007/handouts16-4.pdf
-
-http://www.maths.bath.ac.uk/~jjf23/mixchange/split.html
-
-### Using MCMCglmm
-
-http://www.maths.bath.ac.uk/~jjf23/mixchange/onewayanova.html
-
-http://www.maths.bath.ac.uk/~jjf23/mixchange/split.html#mcmcglmm
-
-https://github.com/tmalsburg/MCMCglmm-intro
-
-### General GLMM in R
-
-http://bbolker.github.io/mixedmodels-misc/glmmFAQ.html
-
-### Citation
+## Citation
 
@@
 
-### Licenses
+## Licenses
 
-Text and figures: [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
+Manuscript: [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)
 
-Code: See the [DESCRIPTION](DESCRIPTION) file
+Code: [MIT](http://opensource.org/licenses/MIT) year: 
+`r format(Sys.Date(), "%Y")`, copyright holder: Adam Sparks
 
@@
 
-### Contributions
+## Dependencies
 
-We welcome contributions from everyone. Before you get started, please see our
-[contributor guidelines](CONTRIBUTING.md). Please note that this project is
-released with a [Contributor Code of Conduct](CONDUCT.md). By participating in
-this project you agree to abide by its terms.
+I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu
+17.10. See the colophon section of the docx file in `analysis/paper` for a
+full list of the packages that this project depends on.
+
+## Contact
+
+Adam Sparks, Associate Professor, Centre for Crop Health  
+University of Southern Queensland, West St.  
+Toowoomba, Qld 4350 Australia
+
+(+61) 7.4631.1948   adam.sparks@usq.edu.au  
+https://staffprofile.usq.edu.au/Profile/Adam-Sparks

### 2018-04-12 analysis/paper/paper.Rmd
add Sri's paper as a reference
Update paper and add Word output
Edits to introduction, M&M, analysis and results

Spell check

@@
 output:
-  bookdown::pdf_document2:
+  bookdown::word_document2:
     toc: no
@@
 The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, \textit{e.g.}, Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015].
+Various countries, \textit{e.g.}, Bangladesh, Vietnam, Thailand and the Philip pines, plan to widely apply AWD to local rice production [@MOEF2015].
 However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
 
-We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (\emph{Rhizoctonia solani} Kühn) [(teleomorph: \emph{Thanatephorus cucumeris} (A.B.
+We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (\emph{Rhizoctonia solani} Kühn), anastamosis group 1 [(teleomorph: \emph{Thanatephorus cucumeris} (A.B.
 Frank) Donk.] of rice.
+
+Sheath blight is economically important worldwide and it is difficult to find resistance to the disease [@Srinivasachary2011].
+Therefore management is usually a combination of cultural practices, which include nitrogen and water management.
+High nitrogen levels
 
@@
 
-## Experimental Design
+## Crop establishment
 
@@
 For the 2016 season changes were made to optimize the experiment based on findings from the 2015 season.
-Both seasons consisted of split plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split plot treatment.
+
+Nurseries of NSIC Rc222, a short-season in-bred irrigated lowland rice variety with 114 day maturity when transplanted were established on 27 December 2014 and 7 January 2015 for the 2015 and 2016 experiments, respectively.
+Seedlings were transplanted on 9 January 2015 and 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+
+## Inoculum
+
+An isolate of *Rhizoctonia solani* AG1-1a from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
+The isolate was transferred to 90mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C).
+Glass bottles of autoclaved rice grain and hull substrate were prepared and plugs of the culture were transferred from Petri dishes to the autoclaved substrate and incubated at room temperature for two weeks.
+
+## Experimental Design
+
+Both experiments consisted of split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split plot treatment.
+The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (CF) or farmers' practice, the control treatment.
 The changes between seasons and experiments are detailed following.
 
-### 2015 Dry Season
-
-The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
-Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub plot for a whole experiment size of 1,152 sq m.
-The main plot treatments were alternate wetting and drying (AWD) and ) and continuously flooded (CF) or farmers' practice.
+**2015 Dry Season Experiment** The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
+Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub-plot for a whole experiment size of 1,152 sq m.
 
@@
 
-The subplot treatments were different rates of nitrogen, 0 kg/ha (control), 100 kg/ha in three splits, and 120 kg/ha in three splits.
+The sub-plot treatments were different rates of nitrogen, N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
 
@@
 
-### 2016 Dry Season
+**2016 Dry Season Experiment** In 2016 dry season the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
+The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
+The sub-plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m).
+The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m).
+A buffer 0.5m per sub-plot was used and the overall experiment size was 3471.6 sq m.
 
-In 2016 dry season the plot size was increased and due to these changes, the sizes of the replicates are not equal as necessitated by the use of a larger area for the experiment.
-The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
-The sub plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m).
-The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m).
-A buffer 0.5m per sub plot was used and the overall experiment size was 3471.6 sq m.
-
-Subplot N rates differed from the 2015 rates. The control was applied as 60 kg/ha split into two applications and a second treatment of 180 kg/ha in three splits was applied.
+Sub-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) was applied.
 
@@
 
-Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI \ref{figure1}.
+Disease scoring was the same in both experiments using the same sheath blight assessment scale for field evaluation developed at IRRI \ref{figure1}.
 Two sample areas per plot (1m x 1m) were assessed.
-for 9 hills per sample, the number of tillers per hill and number of tillers with sheath blight (incidence) were measured.
-Tiller sheath blight severity was measured for four tillers per hill and six leaves tiller.
-Five and four disease assessments were made in 2015 and 2016, respectively.
+For nine hills per sample, the number of tillers per hill and number of tillers with sheath blight (incidence) were measured.
+Tiller sheath blight severity was measured for four tillers per hill and six leaves tiller using the rating scale.
+Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
 
-![IRRI sheath blight field severity rating scale where, 0 - 0%, 1 - 1%, 2 - 5%,
-3 - 15%, 4 - 50%, 5 - >50%. \label{figure1}](./Figures/Figure 1 IRRI Sheath Blight Severity Assessment.png)
+![IRRI sheath blight field severity rating scale for rice leaf tissue where, 0 - 0%, 1 - 1%, 2 - 5%,
+3 - 15%, 4 - 50%, 5 - >50% severity. \label{figure1}](./Figures/Figure 1 IRRI Sheath Blight Severity Assessment.png)
 
 Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area].
-As most of the data did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2017].
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2018].
 
@@
 
-In 2015 both the nitrogen rates, N100 and N120, were significant when compared with the base N0 rate, water management was not significant.
+In 2015 both of the nitrogen rates, N100 and N120, were significantly different when compared with the control N0 rate. However, water management was not significantly different.
 
-In 2016 the nitrogen rate N180, was significantly different than the base N60 rate, water management was not significant.
+In 2016 the nitrogen rate N180, was significantly different than the control N60 rate. As in the 2015 study, water management did not significantly differ.
 
@@
 
-In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
+In 2015 both the N100 and N120 rates were significantly different than the control N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
 
-In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the base flooding treatment.
+In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the control flooding treatment.
 
@@
 
-In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the base flooding treatment.
+In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
 
-In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the base treatment for leaf sheath blight severity.
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf sheath blight severity.
 
@@
 
-# References {#references .unnumbered}
+The authors wish to thank Rachel King University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper, Dale Amozola for technical support in the field.
+Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in 2015.
 
-Supporting information captions (if applicable)
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+# References 
+<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
+<div id="refs"></div>
+
+##### pagebreak
+
+### Colophon
+
+This report was generated on `r Sys.time()` using the following computational environment and dependencies:
+
+```{r colophon, cache = FALSE}
+# which R packages and versions?
+devtools::session_info()
+```
+
+The current Git commit details are:
+
+```{r}
+# what commit is this file at? You may need to change the path value
+# if your Rmd is not in analysis/paper/
+git2r::repository("../..")
+```

### 2018-04-12 analysis/paper/paper.Rmd
flip coordinates of posterior plots

@@
 Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
-We were unable to detect any differences in disease in either experiment due to irrigation regime, N rates or the interaction of the two treatments in either season.
-This suggests that farmers can adopt water saving technologies without risking increased sheath blight incidence.
+We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did differ significantly by irrigation treament but leaf sheath blight severity did not.
+Our findings suggests that farmers can adopt water saving technologies without risking increased sheath blight incidence.
 We suggest that further cross-cutting research in this area is warranted.

### 2018-04-12 R/diagnostic_plots.R

@@ -64,6 +64,7 @@ plot_replicate_posteriors <- function(d, title) {
     ggplot2::geom_violin() +
     ggplot2::geom_abline(slope = 0, intercept = 0) +
     ggplot2::ggtitle(paste(title)) +
+    ggplot2::coord_flip() +
     ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 35, hjust = 1))
 }
 
@@ -76,6 +77,7 @@ plot_treatment_posteriors <- function(d, title) {
     ggplot2::geom_violin() +
     ggplot2::geom_abline(slope = 0, intercept = 0) +
     ggplot2::ggtitle(paste(title)) +
+    ggplot2::coord_flip() +
     ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 35, hjust = 1))
 }
 

### 2018-04-12 R/diagnostic_plots.R
generate plots with flipped axis

@@ -64,8 +64,7 @@ plot_replicate_posteriors <- function(d, title) {
     ggplot2::geom_violin() +
     ggplot2::geom_abline(slope = 0, intercept = 0) +
     ggplot2::ggtitle(paste(title)) +
-    ggplot2::coord_flip() +
-    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 35, hjust = 1))
+    ggplot2::coord_flip()
 }
 
 #' @export
@@ -77,8 +76,7 @@ plot_treatment_posteriors <- function(d, title) {
     ggplot2::geom_violin() +
     ggplot2::geom_abline(slope = 0, intercept = 0) +
     ggplot2::ggtitle(paste(title)) +
-    ggplot2::coord_flip() +
-    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 35, hjust = 1))
+    ggplot2::coord_flip()
 }
 
 #' @export

### 2018-04-12 analysis/paper/paper.Rmd
Minor edits to analysis section

@@
 
-Disease severity was converted to area under the disease progress stairs (AUDPS) [@simko2012area].
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2017] in R [@R2018].
+Disease incidence and severity were converted to area under the disease progress stairs (AUDPS) [@simko2012area].
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2010] in the R programming environment [@R2018].
 

### 2018-04-12 analysis/paper/paper.Rmd
Clarify terminology
replate "N* rate" with "N* treatment".

@@
 
-In 2015 both of the nitrogen rates, N100 and N120, were significantly different when compared with the control N0 rate. However, water management was not significantly different.
+In 2015 both of the nitrogen treatements, N100 and N120, were significantly different when compared with the control N0 treatement. However, water management was not significantly different.
 
-In 2016 the nitrogen rate N180, was significantly different than the control N60 rate. As in the 2015 study, water management did not significantly differ.
+In 2016 the nitrogen treatment N180, was significantly different than the control N60 treatment. As in the 2015 study, water management did not significantly differ.
 
@@
 
-In 2015 both the N100 and N120 rates were significantly different than the control N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
 
-In 2016 the N180 was significantly different from the N60 rate. The AWD water management was also significantly different from the control flooding treatment.
+In 2016 the N180 treatement was significantly different from the N60 treatment. The AWD water management was also significantly different from the control flooding treatment.
 
@@
 
-In 2015 both the N100 and N120 rates were significantly different than the N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
 

### 2018-04-12 README.Rmd
Correct link for docker image installation in README
Update README

@@
 
-## Research compendium for a report on the effects of using alternate wetting and drying irrigation techniques on sheath blight disease in rice paddies.
+## Research compendium for a report on the effects of using alternate wetting and drying irrigation techniques and nitrogen rates on sheath blight disease in rice paddies.
 
@@
 
-    docker run -dp 8787:8787 adamhsparks/rice.awd.pests
+    docker run -dp 8787:8787 adamhsparks/rice_awd_pests
 

### 2018-04-14 analysis/paper/paper.Rmd
Major edits to text and output
- Add figures 1-3 of disease progress over time

- Add more text to experimental design and results

- Add new reference for Nancy's 1996 paper

- Add csl for EJPP

- Add Word template for knitting Word, but waiting on PR to be accepted in `rrtools` with new Springer template that we can use

@@
   | \textsuperscript{\dag} Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
+csl: "../templates/european-journal-of-plant-pathology.csl" # Insert path for the bib-style
 abstract: |
@@
 We suggest that further cross-cutting research in this area is warranted.
-
 bibliography: references.bib
@@
     fig_caption: yes
-
+    reference_docx: "../templates/template.docx"
 always_allow_html: yes
-
 header-includes:
-  - \usepackage{endfloat}
-  - \usepackage{setspace}\doublespacing
-  - \usepackage{lineno}
-  - \linenumbers
+   \usepackage{endfloat}
+   \usepackage{setspace}\doublespacing
+   \usepackage{lineno}
+   \linenumbers
 ---
@@
 knitr::opts_chunk$set(out.width = "100%", dpi = 300)
+knitr::opts_chunk$set(eval = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(message = FALSE)
 
@@
 library(kableExtra)
+library(rice.awd.pests)
+library(ggpubr)
 ```
 
-# Introduction
+# Introduction {-}
 
-Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice (\emph{Oryza sativa L.}) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growth period without exposing the plants to water stress.
@@
 The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, \textit{e.g.}, Bangladesh, Vietnam, Thailand and the Philip pines, plan to widely apply AWD to local rice production [@MOEF2015].
+Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and the Philip pines, plan to widely apply AWD to local rice production [@MOEF2015].
 However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
 
-We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (\emph{Rhizoctonia solani} Kühn), anastamosis group 1 [(teleomorph: \emph{Thanatephorus cucumeris} (A.B.
+Nitrogen is known to affect sheath blight [@Castilla1996]...
+
+We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
 Frank) Donk.] of rice.
@@
 
-# Materials and Methods
+# Materials and Methods {-}
 
-## Crop establishment
+## Crop establishment {-}
 
@@
 
-## Inoculum
+## Inoculum {-}
 
@@
 
-## Experimental Design
+## Experimental Design {-}
 
@@
 
-**2015 Dry Season Experiment** The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
+### 2015 Dry Season Experiment {-}
+
+The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
 Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub-plot for a whole experiment size of 1,152 sq m.
 
-Irrigation in AWD plots was determined by the water level in plots, \emph{i.e.}, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
+Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
 In CF plots a standing water layer of 3-5cm was maintained throughout the growing season.
@@
 
-**2016 Dry Season Experiment** In 2016 dry season the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
+### 2016 Dry Season Experiment {-}
+
+In 2016 dry season the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
 The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
@@
 
-## Data Collection and Analysis
+## Data Collection and Analysis {-}
 
-Disease scoring was the same in both experiments using the same sheath blight assessment scale for field evaluation developed at IRRI \ref{figure1}.
+Disease scoring was the same in both experiments using the same sheath blight disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
+Where severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
 Two sample areas per plot (1m x 1m) were assessed.
@@
 
-![IRRI sheath blight field severity rating scale for rice leaf tissue where, 0 - 0%, 1 - 1%, 2 - 5%,
-3 - 15%, 4 - 50%, 5 - >50% severity. \label{figure1}](./Figures/Figure 1 IRRI Sheath Blight Severity Assessment.png)
+Disease severity values were converted to the midpoint percentage value of the disease assessment scale.
+Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].
 
-Disease incidence and severity were converted to area under the disease progress stairs (AUDPS) [@simko2012area].
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the MCMCglmm package [@MCMCglmm2010] in the R programming environment [@R2018].
+# Results {-}
 
-# Results
+## Tiller Sheath Blight Incidence {-}
 
-### Tiller Sheath Blight Incidence
+In 2015 the incidence of tiller sheath blight remained low throughout the growing season only reaching 15% in 2015 in the N120/flooded treatment (Figure \@ref(fig:figure-1)).
+The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment.
+However, water management was not significantly different.
 
-In 2015 both of the nitrogen treatements, N100 and N120, were significantly different when compared with the control N0 treatement. However, water management was not significantly different.
+```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}
 
-In 2016 the nitrogen treatment N180, was significantly different than the control N60 treatment. As in the 2015 study, water management did not significantly differ.
+ggplot(RAW_data,
+       aes(x = ASMT,
+           y = TShB_incidence,
+           linetype = NRTE,
+           shape = NRTE)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = TRT)) +
+  stat_summary(fun.y = "mean",
+               geom = "point",
+               aes(group = TRT)) +
+  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
+  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  ylab("Tiller Sheath Blight Incidence (%)") +
+  xlab("Assessment") +
+  facet_grid(WMGT ~ YEAR) +
+  labs(linetype = "Nitrogen treatment",
+       shape = "Nitrogen treatment") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  theme(legend.position = "bottom")
+```
 
-### Tiller Sheath Blight Severity
+The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N180/flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
+The nitrogen treatment N180, was significantly different than the control N60 treatment.
+As in the 2015 study, water management did not significantly differ.
+
+## Tiller Sheath Blight Severity {-}
 
@@
 
-In 2016 the N180 treatement was significantly different from the N60 treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2016 the N180 treatment was significantly different from the N60 treatment. The AWD water management was also significantly different from the control flooding treatment.
 
-### Leaf Sheath Blight Severity
+```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}
+
+ggplot(RAW_data,
+       aes(x = ASMT,
+           y = PERC_TIL_ShB,
+           linetype = NRTE,
+           shape = NRTE)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = TRT)) +
+  stat_summary(fun.y = "mean",
+               geom = "point",
+               aes(group = TRT)) +
+  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  ylab("Tiller Sheath Blight Severity (%)") +
+  xlab("Assessment") +
+  facet_grid(WMGT ~ YEAR) +
+  labs(linetype = "Nitrogen treatment",
+       shape = "Nitrogen treatment") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  theme(legend.position = "bottom")
+```
+
+## Leaf Sheath Blight Severity {-}
 
@@
 
-# Discussion
+```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years.
+Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}
 
-# Acknowledgments
+ggplot(RAW_data,
+       aes(x = ASMT,
+           y = PERC_LEAF_ShB,
+           linetype = NRTE,
+           shape = NRTE)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = TRT)) +
+  stat_summary(fun.y = "mean",
+               geom = "point",
+               aes(group = TRT)) +
+  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  ylab("Leaf Sheath Blight Severity (%)") +
+  xlab("Assessment") +
+  facet_grid(WMGT ~ YEAR) +
+  labs(linetype = "Nitrogen treatment",
+       shape = "Nitrogen treatment") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  theme(legend.position = "bottom")
+```
+
+# Discussion {-}
+
+# Notes {-}
+
+## Acknowledgments {-}
 
@@
 
-# References 
+# References {-}
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
@@
 
-### Colophon
+### Colophon {-}
 

### 2018-04-14 analysis/paper/paper.Rmd
Figure formatting
- Move figures to end of manuscript

- Format legend to have two rows

- Generate eps files at 84mm x 84 mm and save in "./analysis/paper/figures"

@@
 knitr::opts_chunk$set(out.width = "100%", dpi = 300)
+knitr::opts_chunk$set(fig.width = 3.31)
+knitr::opts_chunk$set(fig.height = 3.31)
 knitr::opts_chunk$set(eval = TRUE)
@@
 
+The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N180/flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
+The nitrogen treatment N180, was significantly different than the control N60 treatment.
+As in the 2015 study, water management did not significantly differ.
+
+## Tiller Sheath Blight Severity {-}
+
+In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
+
+In 2016 the N180 treatment was significantly different from the N60 treatment. The AWD water management was also significantly different from the control flooding treatment.
+
+## Leaf Sheath Blight Severity {-}
+
+In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
+
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf sheath blight severity.
+
+# Discussion {-}
+
+# Notes {-}
+
+## Acknowledgments {-}
+
+The authors wish to thank Rachel King University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper, Dale Amozola for technical support in the field.
+Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in 2015.
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
+##### pagebreak
+
+# References {-}
+<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
+<div id="refs"></div>
+
+##### pagebreak
+
+# Figures {-}
+
 ```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
 Five different nitrogen treatments were applied depending on the experiment.
@@
   facet_grid(WMGT ~ YEAR) +
-  labs(linetype = "Nitrogen treatment",
-       shape = "Nitrogen treatment") +
+  labs(linetype = "N Treatment",
+       shape = "N Treatment") +
   theme_bw() +
@@
         axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  guides(linetype = guide_legend(nrow = 2),
+         shape = guide_legend(nrow = 2))
+
+ggsave("./Figures/Sparks_Figure_1.eps", width = 84, height = 84, units = "mm")
+
 ```
 
-The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N180/flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
-The nitrogen treatment N180, was significantly different than the control N60 treatment.
-As in the 2015 study, water management did not significantly differ.
-
-## Tiller Sheath Blight Severity {-}
-
-In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
-
-In 2016 the N180 treatment was significantly different from the N60 treatment. The AWD water management was also significantly different from the control flooding treatment.
-
 ```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
 Five different nitrogen treatments were applied depending on the experiment.
@@
         axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  guides(linetype = guide_legend(nrow = 2),
+         shape = guide_legend(nrow = 2))
+
+ggsave("./Figures/Sparks_Figure_2.eps", width = 84, height = 84, units = "mm")
 ```
 
-## Leaf Sheath Blight Severity {-}
-
-In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
-
-In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf sheath blight severity.
-
 ```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years.
-Main plot irrigation treaments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
 Five different nitrogen treatments were applied depending on the experiment.
@@
         axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") +
+  guides(linetype = guide_legend(nrow = 2),
+         shape = guide_legend(nrow = 2))
+
+ggsave("./Figures/Sparks_Figure_3.eps", width = 84, height = 84, units = "mm")
 ```
-
-# Discussion {-}
-
-# Notes {-}
-
-## Acknowledgments {-}
-
-The authors wish to thank Rachel King University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper, Dale Amozola for technical support in the field.
-Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in 2015.
-
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
-
-# References {-}
-<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
-<div id="refs"></div>
 

### 2018-04-14 analysis/paper/paper.Rmd
Automatically export figures as .eps when knitting to Word

@@
 ```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(fig.pos = "p")
-knitr::opts_chunk$set(out.width = "100%", dpi = 300)
-knitr::opts_chunk$set(fig.width = 3.31)
-knitr::opts_chunk$set(fig.height = 3.31)
-knitr::opts_chunk$set(eval = TRUE)
-knitr::opts_chunk$set(echo = FALSE)
-knitr::opts_chunk$set(message = FALSE)
+
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  warning = FALSE,
+  message = FALSE,
+  echo = FALSE,
+  comment = "#>",
+  fig.path = "../figures/",
+  dev = c("postscript"),
+  fig.width = 3.31,
+  fig.height = 3.31,
+  out.width = "100%",
+  dpi = 300
+)
 
@@
 
-ggsave("./Figures/Sparks_Figure_1.eps", width = 84, height = 84, units = "mm")
-
 ```
@@
 
-ggsave("./Figures/Sparks_Figure_2.eps", width = 84, height = 84, units = "mm")
 ```
@@
 
-ggsave("./Figures/Sparks_Figure_3.eps", width = 84, height = 84, units = "mm")
 ```

### 2018-04-14 analysis/paper/paper.Rmd
Edits to paper.Rmd
- Spelling corrections

- Change nitrogen treatment designations to N0 - N4.

- Use subscripts for N designations

- Replace "CF" with "FLD" for flooded treatment

@@
 
-## Crop establishment {-}
+## Crop Establishment {-}
 
 Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons.
-For the 2016 season changes were made to optimize the experiment based on findings from the 2015 season.
+For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment.
 
-Nurseries of NSIC Rc222, a short-season in-bred irrigated lowland rice variety with 114 day maturity when transplanted were established on 27 December 2014 and 7 January 2015 for the 2015 and 2016 experiments, respectively.
+### 2015 Crop Establishment
+
+In 2015 trays of NSIC Rc222, a short-season in-bred irrigated lowland rice variety with 114 day maturity when transplanted were established on 27 December 2014.
+Trays were randomised and transplanted using a mechanical transplanter.
+
+### 2016 Crop Establishment
+
+Nurseries of NSIC Rc222 were established on 7 January 2015 for the 2015 and 2016 experiments, respectively.
 Seedlings were transplanted on 9 January 2015 and 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
@@
 Both experiments consisted of split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split plot treatment.
-The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (CF) or farmers' practice, the control treatment.
+The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice, the control treatment.
 The changes between seasons and experiments are detailed following.
@@
 Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
-In CF plots a standing water layer of 3-5cm was maintained throughout the growing season.
+In FLD plots a standing water layer of 3-5cm was maintained throughout the growing season.
 
-The sub-plot treatments were different rates of nitrogen, N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
+The sub-plot treatments were different rates of nitrogen, N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
 
@@
 
-Sub-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) was applied.
+Sub-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.
 
@@
 
-In 2015 the incidence of tiller sheath blight remained low throughout the growing season only reaching 15% in 2015 in the N120/flooded treatment (Figure \@ref(fig:figure-1)).
-The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment.
+In 2015 the incidence of tiller sheath blight remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)).
+The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment.
 However, water management was not significantly different.
 
-The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N180/flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
-The nitrogen treatment N180, was significantly different than the control N60 treatment.
+The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N~4~, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
+The nitrogen treatment N~4~, was significantly different than the control N~3~ treatment.
 As in the 2015 study, water management did not significantly differ.
@@
 
-In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
 
-In 2016 the N180 treatment was significantly different from the N60 treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2016 the N~4~ treatment was significantly different from the N~3~ treatment. The AWD water management was also significantly different from the control flooding treatment.
 
@@
 
-In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
 
@@
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatements were applied: no N (N0), 100 units of N (N100) and 180 units of N (N180).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 units of N (N60) and 180 units of N (N180)."}
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~).
+Points represent the mean of four replications."}
 
@@
   scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
-  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
-  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  scale_shape_discrete(labels = c(expression(N[0]),
+                                  expression(N[1]),
+                                  expression(N[2]),
+                                  expression(N[3]),
+                                  expression(N[4]))) +
+  scale_linetype_discrete(labels = c(expression(N[0]),
+                                     expression(N[1]),
+                                     expression(N[2]),
+                                     expression(N[3]),
+                                     expression(N[4]))) +
   ylab("Tiller Sheath Blight Incidence (%)") +
@@
          shape = guide_legend(nrow = 2))
+```
 
-```
+##### pagebreak
 
@@
                aes(group = TRT)) +
-  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
-  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  scale_shape_discrete(labels = c(expression(N[0]),
+                                  expression(N[1]),
+                                  expression(N[2]),
+                                  expression(N[3]),
+                                  expression(N[4]))) +
+  scale_linetype_discrete(labels = c(expression(N[0]),
+                                     expression(N[1]),
+                                     expression(N[2]),
+                                     expression(N[3]),
+                                     expression(N[4]))) +
   ylab("Tiller Sheath Blight Severity (%)") +
@@
                aes(group = TRT)) +
-  scale_shape_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
-  scale_linetype_discrete(labels = c("N0", "N100", "N120", "N60", "N180")) +
+  scale_shape_discrete(labels = c(expression(N[0]),
+                                  expression(N[1]),
+                                  expression(N[2]),
+                                  expression(N[3]),
+                                  expression(N[4]))) +
+  scale_linetype_discrete(labels = c(expression(N[0]),
+                                     expression(N[1]),
+                                     expression(N[2]),
+                                     expression(N[3]),
+                                     expression(N[4]))) +
   ylab("Leaf Sheath Blight Severity (%)") +
@@
          shape = guide_legend(nrow = 2))
-
 ```

### 2018-04-14 analysis/paper/paper.Rmd
Split experiments in M&M and Results
It's more clear if one experiment is discussed at a time

Split up discussion

Add placeholder and reminder for a table for N treatements

@@
 
-## Crop Establishment {-}
-
 Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons.
 For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment.
+Details were as follows.
 
-### 2015 Crop Establishment
+## 2015 Experiment {-}
 
-In 2015 trays of NSIC Rc222, a short-season in-bred irrigated lowland rice variety with 114 day maturity when transplanted were established on 27 December 2014.
-Trays were randomised and transplanted using a mechanical transplanter.
+### Experimental Design {-}
 
-### 2016 Crop Establishment
+The plot design was a split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split-plot treatment.
+The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice, the control treatment.
 
-Nurseries of NSIC Rc222 were established on 7 January 2015 for the 2015 and 2016 experiments, respectively.
-Seedlings were transplanted on 9 January 2015 and 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+The main plot size was 12m x 12m (144 sq m), with a split-plot size of 5m x 5m (25 sq m).
+Replication size was 12m x 24m (288 sq m) with a buffer of 1m per split-plot for a whole experiment size of 1,152 sq m.
 
-## Inoculum {-}
+Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
+In FLD plots a standing water layer of 3-5cm was maintained throughout the growing season.
+
+The split-plot treatments were different rates of nitrogen, N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
+
+### Crop Establishment {-}
+
+Trays of NSIC Rc222, a short-season inbred irrigated lowland rice variety with 114 day maturity when transplanted were established on 19 December 2014.
+Trays were randomised and transplanted using a mechanical transplanter on 9 January 2015.
+
+### Inoculum Preparation and Application {-}
 
@@
 
-## Experimental Design {-}
-
-Both experiments consisted of split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split plot treatment.
-The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice, the control treatment.
-The changes between seasons and experiments are detailed following.
-
-### 2015 Dry Season Experiment {-}
-
-The main plot size was 12m x 12m (144 sq m), with a sub-plot size of 5m x 5m (25 sq m).
-Replication size was 12m x 24m (288 sq m) with a buffer of 1m per sub-plot for a whole experiment size of 1,152 sq m.
-
-Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
-In FLD plots a standing water layer of 3-5cm was maintained throughout the growing season.
-
-The sub-plot treatments were different rates of nitrogen, N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
-
 The plots were inoculated 20 days after transplanting using 151g of inoculum per plot (4m x 11m).
 
-### 2016 Dry Season Experiment {-}
+## 2016 Experiment {-}
 
-In 2016 dry season the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
+### Experimental Design {-}
+
+The experiment followed the same split-plot design as described for the 2015 experiment.
+However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
 The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
-The sub-plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m).
+The split-plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m).
 The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m).
-A buffer 0.5m per sub-plot was used and the overall experiment size was 3471.6 sq m.
+A buffer 0.5m per split-plot was used and the overall experiment size was 3471.6 sq m.
 
-Sub-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.
+split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.
+
+### Crop Establishment {-}
+
+Nurseries of NSIC Rc222 were established on 7 January 2015 for the 2015 and 2016 experiments, respectively.
+Seedlings were transplanted on 9 January 2015 and 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+
+### Inoculum Preparation and Application {-}
 
@@
 
-## Tiller Sheath Blight Incidence {-}
+## 2015 Experiment
+
+### Tiller Sheath Blight Incidence {-}
 
@@
 
+### Tiller Sheath Blight Severity {-}
+
+In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+
+### Leaf Sheath Blight Severity {-}
+
+In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+
+## 2016 Experiment {-}
+
+### Tiller Sheath Blight Incidence {-}
+
 The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N~4~, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
@@
 
-## Tiller Sheath Blight Severity {-}
-
-In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+### Tiller Sheath Blight Severity {-}
 
@@
 
-## Leaf Sheath Blight Severity {-}
-
-In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+### Leaf Sheath Blight Severity {-}
 
@@
 <div id="refs"></div>
+
+##### pagebreak
+
+# Tables {-}
+
+Table of N application timings and dates here...
 

### 2018-04-14 data-raw/README.Rmd
Update data-raw
Add days after inoculation (DAI) column to RAW_data for use in plots

--- 2017-08-25 data-raw/Clean_Data_and_Calculate_AUDPS.Rmd
@@
 
-The raw data are located in the `extdata` folder of the installed
+The raw data are located in the `data` folder of the installed
 _rice.awd.pests_
@@
 library(readr)
-library(magrittr)
+library(dplyr)
 
@@
 
+# Add days after inoculation column
+DS2015 <- 
+  DS2015 %>%
+  mutate(
+    DAI = case_when(
+      ASMT == 1 ~ 14,
+      ASMT == 2 ~ 22,
+      ASMT == 3 ~ 35,
+      ASMT == 4 ~ 49,
+      ASMT == 5 ~ 62,
+    )
+  )
+
 # Replace "N*" with a number for NRTE ------------------------------------------
@@
     ASMT,
+    DAI,
     REP,
@@
 
+# Fill days after inoculation
+DS2016_A1$DAI <- rep(14, nrow(DS2016_A1))
+
 # Second assessement -----------------------------------------------------------
@@
 DS2016_A2$PLOT <- rep(1:16, each = 72)
+
+# Fill days after inoculation
+DS2016_A2$DAI <- rep(28, nrow(DS2016_A2))
 
@@
 
+# Fill days after inoculation
+DS2016_A3$DAI <- rep(43, nrow(DS2016_A3))
+
 # Fourth assessment ------------------------------------------------------------
@@
 DS2016_A4$PLOT <- rep(1:16, each = 72)
+
+# Fill days after inoculation
+DS2016_A4$DAI <- rep(59, nrow(DS2016_A4))
 
@@
     -ASMT,
+    -DAI,
     -PLOT,
@@
   DS2016 %>%
-  dplyr::group_by(DATE, ASMT, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
+  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
   dplyr::mutate(TShB_incidence = NTShB / NTIL)
@@
 RAW_data$ASMT <- factor(RAW_data$ASMT)
+RAW_data$DAI <- factor(RAW_data$DAI)
 RAW_data$PLOT <- factor(RAW_data$PLOT)
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
   dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
@@
 
+devtools::use_data(RAW_data,
+                   compress = "bzip2",
+                   overwrite = TRUE)
+
 devtools::use_data(AUDPS,

### 2018-04-14 analysis/paper/paper.Rmd
Update graphs using DAI for x-axis

@@
 
-Disease severity values were converted to the midpoint percentage value of the disease assessment scale.
+Because the data were collected on an ordinal scale, but not evenly spaced, the data are converted to the midpoint value of the percent range for severity.
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
@@
 ggplot(RAW_data,
-       aes(x = ASMT,
+       aes(x = DAI,
            y = TShB_incidence,
@@
   ylab("Tiller Sheath Blight Incidence (%)") +
-  xlab("Assessment") +
-  facet_grid(WMGT ~ YEAR) +
+  xlab("Days After Inoculation") +
+  facet_grid(WMGT ~ YEAR,
+             scales = "free_x") +
   labs(linetype = "N Treatment",
@@
 ggplot(RAW_data,
-       aes(x = ASMT,
+       aes(x = DAI,
            y = PERC_TIL_ShB,
@@
   ylab("Tiller Sheath Blight Severity (%)") +
-  xlab("Assessment") +
-  facet_grid(WMGT ~ YEAR) +
+  xlab("Days After Inoculation") +
+  facet_grid(WMGT ~ YEAR,
+             scales = "free_x") +
   labs(linetype = "N Treatment",
@@
 ggplot(RAW_data,
-       aes(x = ASMT,
+       aes(x = DAI,
            y = PERC_LEAF_ShB,
@@
   ylab("Leaf Sheath Blight Severity (%)") +
-  xlab("Assessment") +
-  facet_grid(WMGT ~ YEAR) +
+  xlab("Days After Inoculation") +
+  facet_grid(WMGT ~ YEAR,
+             scales = "free_x") +
   labs(linetype = "N Treatment",

### 2018-04-14 data-raw/README.Rmd
Don't convert DAI as a factor

@@
 RAW_data$ASMT <- factor(RAW_data$ASMT)
-RAW_data$DAI <- factor(RAW_data$DAI)
 RAW_data$PLOT <- factor(RAW_data$PLOT)

### 2018-04-14 analysis/paper/paper.Rmd
Update y-axis code for figure 1
Cleaner code

@@
                aes(group = TRT)) +
-  scale_y_continuous(labels = function(x) paste0(x*100), limits = c(0, 1)) +
+  scale_y_continuous(labels = function(x) paste0(x*100),
+                     limits = c(0, 1),
+                     name = "Tiller Sheath Blight Incidence (%)") +
   scale_shape_discrete(labels = c(expression(N[0]),
@@
                                      expression(N[4]))) +
-  ylab("Tiller Sheath Blight Incidence (%)") +
   xlab("Days After Inoculation") +

### 2018-04-14 README.Rmd
Update README

@@
 The files at the URL above will generate the results as found in the
-publication. The files hosted at github.com/openplantpathology/rice.awd.pests
-are the development versions and may have changed since the report was
-published.
+publication. The files hosted at
+<https://github.com/openplantpathology/rice_awd_pests> are the development
+versions and may have changed since the report was published.
 
@@
 
+The `data-raw` directory contains:
+
+- a Rmd file and Markdown file detailing how the raw data was handled and
+Area Under the Disease Progress Stairs (AUDPS) was calculated for analysis and
+the .Rda files used in the analysis were generated
+
 The `analysis/` directory contains:
 
-- the manuscript as submitted (in PDF format) and it's Rmd source file
+- the manuscript as submitted (in MS Word format) and it's Rmd source file
+
 - all the data files (in CSV file format, in the `data/` directory)
-- supplementary information source files (in R markdown format) and executed versions
+
+- supplementary information source files (in R markdown format) and executed
+versions
+
 - all the figures that are included in the paper (in the `figures/` directory)
@@
 
-This repository is organized as an R package. There are no actual R functions in
-this package - all the R code is in the Rmd file. I simply used the R package
+This repository is organized as an R package. There are a few R functions in
+this package that were used to generate some of the diagnostic plots related to
+the analysis. However, for the most part I simply used the R package
 structure to help manage dependencies, to take advantage of continuous
@@
 outside of R. These are listed at the bottom of this README. Installing these
-can be time-consuming and complicated, so we've done two things to simpify
-access to the compendium. First is the packrat directory, which contains the
-source code for all the packages we depend on. If all works well, these will be
-installed on your computer when you open `rice_awd_.pests.Rproj` in RStudio.
-Second is our Docker image that includes all the necessary software, code and
-data to run our analysis. The Docker image may give a quicker entry point to the
-project, and is more self-contained, so might save some fiddling with installing
-things.
+can be time-consuming and complicated, so we've used a Docker image. The Docker
+image includes all the necessary software, code and data to run our analysis.
+The Docker image may give a quicker entry point to the project, and is more
+self-contained, so might save some fiddling with installing things.
 
@@
 
-Once logged in, use the Files pane (bottom right) to navigate to `/` (the root
-directory), then open the folder for this project, and open the `.Rproj` file
-for this project. Once that's open, you'll see the `analysis/paper` directory in
-the Files pane where you can find the R markdown document, and knit them to
-produce the results in the paper. More information about using RStudio in Docker
-is avaiable at the [Rocker](https://github.com/rocker-org) [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
+Once logged in, use the Files pane (bottom right) open the folder for this
+project, and open the `.Rproj` file for this project. Once that's open, you'll
+see the `analysis/paper` directory in the Files pane where you can find the R
+markdown document, and knit them to produce the results in the paper. More
+information about using RStudio in Docker is avaiable at the
+[Rocker](https://github.com/rocker-org)
+[wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
 
 We developed and tested the package on this Docker container, so this is the
-only platform that We're confident it works on, and so recommend to anyone
-wanting to use this package to generate the vignette, etc.
+only platform that we're confident it works on, and so recommend to anyone
+wanting to use this package to generate the vignettes, etc.
 
@@
 https://staffprofile.usq.edu.au/Profile/Adam-Sparks
+
+## Required packages
+ - agricolae
+ - bookdown
+ - car
+ - carData
+ - dplyr (>= 0.7.0)
+ - fitdistrplus
+ - forcats
+ - ggplot2
+ - ggpubr
+ - kableExtra
+ - knitr
+ - lattice
+ - lubridate
+ - MASS
+ - MCMCglmm
+ - reshape2
+ - rmarkdown
+ - plotMCMC
+ - purrr (>= 0.2.3)
+ - tibble
+ - tidyr (>= 0.7.0)

### 2018-04-14 data-raw/README.Rmd
Cleanup data-raw README

@@
 
-# Dry season 2015 importing and cleaning
-
-DS2015 data can be accessed using:
-
-```{r, eval=FALSE}
-load(system.file("extdata", "DS2015_Raw_22DAI.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2015_Raw_35DAI.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2015_Raw_49DAI.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2015_Raw_62DAI.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2015_Raw_83DAI.csv", package = "rice.awd.pests"))
-```
+# 2015 experiment
 
@@
 
-# Dry season 2016 importing and cleaning
-
-The 2016 season raw data are located in the `extdata` folder of the installed
-_rice.awd.pests_ and can be accessed using:
-
-```{r, eval=FALSE}
-load(system.file("extdata", "DS2016_Raw_1.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2016_Raw_2.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2016_Raw_3.csv", package = "rice.awd.pests"))
-load(system.file("extdata", "DS2016_Raw_4.csv", package = "rice.awd.pests"))
-```
+# 2016 experiment
 

### 2018-04-15 analysis/paper/paper.Rmd
Update conclusions in paper
Fix misspelled "Philippines"

@@
 The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and the Philip pines, plan to widely apply AWD to local rice production [@MOEF2015].
+Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015].
 However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
@@
 
-In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.
 
@@
 
-In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.
 

### 2018-04-19 analysis/paper/paper.Rmd
Edits to main text

@@
 
+Sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
+Frank) Donk.] of rice is economically important worldwide and difficult to find resistance to the disease [@Srinivasachary2011].
+Therefore management is usually a combination of cultural practices, which include nitrogen and water management (citation).
+
 Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
@@
 
-We therefore established field experiments in order to determine what effects AWD could have on sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
-Frank) Donk.] of rice.
-
-Sheath blight is economically important worldwide and it is difficult to find resistance to the disease [@Srinivasachary2011].
-Therefore management is usually a combination of cultural practices, which include nitrogen and water management.
-High nitrogen levels
+We therefore established field experiments in order to determine what effects AWD could have on sheath blight.
 

### 2018-04-22 analysis/paper/paper.Rmd
Add new references

@@
 Sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
-Frank) Donk.] of rice is economically important worldwide and difficult to find resistance to the disease [@Srinivasachary2011].
-Therefore management is usually a combination of cultural practices, which include nitrogen and water management (citation).
+Frank) Donk.] of rice is an economically important disease worldwide causing up to 25% yield losses [@Kumar2009].
+The disease is best managed through an integrated disease management approach which includes fungicide applications [@Groth2008], nitrogen management [@Castilla1996, @Slaton2003, @Tang2007] and water management [@Castilla1996].
 

### 2018-04-22 analysis/paper/paper.Rmd
Rearrange instroduction and add citation for yield loss

--- 2018-04-19 analysis/paper/paper.Rmd
@@
 
-Sheath blight disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
-Frank) Donk.] of rice is economically important worldwide and difficult to find resistance to the disease [@Srinivasachary2011].
-Therefore management is usually a combination of cultural practices, which include nitrogen and water management (citation).
+Sheath blight (SB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
+Frank) Donk.] of rice is an economically important disease worldwide, which can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.
 
@@
 
-Nitrogen is known to affect sheath blight [@Castilla1996]...
-
-We therefore established field experiments in order to determine what effects AWD could have on sheath blight.
+Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996].
+We therefore established field experiments in order to determine what effects AWD and N had upon SB incidence and severity.
 
@@
 
-Disease scoring was the same in both experiments using the same sheath blight disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
-Where severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
+Disease scoring was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
+Where severity was considered to be the amount of leaf or sheath tissue covered by SB lesions.
 Two sample areas per plot (1m x 1m) were assessed.
-For nine hills per sample, the number of tillers per hill and number of tillers with sheath blight (incidence) were measured.
-Tiller sheath blight severity was measured for four tillers per hill and six leaves tiller using the rating scale.
+For nine hills per sample, the number of tillers per hill and number of tillers with SB (incidence) were measured.
+Tiller SB severity was measured for four tillers per hill and six leaves tiller using the rating scale.
 Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
@@
 
-In 2015 the incidence of tiller sheath blight remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)).
+In 2015 the incidence of tiller SB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)).
 The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment.
@@
 
-In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf sheath blight severity.
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf SB severity.
 

### 2018-04-23 analysis/paper/paper.Rmd
Clean up yaml header

@@
   bookdown::word_document2:
+    #keep_tex: yes
     toc: no

### 2018-04-23 analysis/paper/paper.Rmd
Edits to paper

--- 2018-04-22 analysis/paper/paper.Rmd
@@
 
-Sheath blight (SB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
-Frank) Donk.] of rice is an economically important disease worldwide, which can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.
+Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
+Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
+The disease can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.
+
+Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996].
 
@@
 
-Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996].
-We therefore established field experiments in order to determine what effects AWD and N had upon SB incidence and severity.
+Because of the interactions between irrigation and N, we established field experiments in order to determine what effects AWD and N had upon ShB incidence and severity.
 
@@
 Disease scoring was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
-Where severity was considered to be the amount of leaf or sheath tissue covered by SB lesions.
+Where severity was considered to be the amount of leaf or sheath tissue covered by ShB lesions.
 Two sample areas per plot (1m x 1m) were assessed.
-For nine hills per sample, the number of tillers per hill and number of tillers with SB (incidence) were measured.
-Tiller SB severity was measured for four tillers per hill and six leaves tiller using the rating scale.
+For nine hills per sample, the number of tillers per hill and number of tillers with ShB (incidence) were measured.
+Tiller ShB severity was measured for four tillers per hill and six leaves tiller using the rating scale.
 Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
@@
 
-In 2015 the incidence of tiller SB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)).
+In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)).
 The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment.
@@
 
-In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf SB severity.
+In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf ShB severity.
 

### 2018-04-23 analysis/paper/paper.Rmd
Fix some reference issues and add new

@@
 Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-The disease can cause up to 44% yield losses [@Marchetti1991] under conducive conditions.
-
-Sheath blight is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Castilla1996; @Slaton2003; @Tang2007] and water management [@Castilla1996].
+The disease can cause up to 50\% yield losses [@Marchetti1991] under conducive conditions.
+Studies by Savary et al.
+[-@Savary2000] estimated yield losses in tropical irrigated lowland rice in Asia at 5-10\%.
+As resistance is difficult to breed for [@Srinivasachary2011], the disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
@@
 
-Because of the interactions between irrigation and N, we established field experiments in order to determine what effects AWD and N had upon ShB incidence and severity.
+Because of the well documented interactions between irrigation and N, we established field experiments to determine what effects AWD and N could have upon ShB incidence and severity in tropical rice.
 
@@
 
-split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.
+Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.
 
@@
 
-The authors wish to thank Rachel King University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper, Dale Amozola for technical support in the field.
-Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in 2015.
+The authors wish to thank Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
+We would also like to thank Dale Amozola, Paul Escandor and P.
+Lapis for their technical support in the field.
+Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in September 2016.
 

### 2018-04-24 analysis/paper/paper.Rmd
Fix an errant "," and objective statement

@@
 
-Because of the well documented interactions between irrigation and N, we established field experiments to determine what effects AWD and N could have upon ShB incidence and severity in tropical rice.
+Because of the well documented effects of irrigation and N on ShB, we established field experiments to study what effects AWD irrigation technologies and N could have upon ShB incidence and severity in tropical rice.
 
@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, , longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons.
 For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment.

### 2018-04-25 data-raw/README.Rmd
Cleanup data-raw README file
Update data.raw to include session_info
Add N treatment tibble
Create tibble for distribution with package and inclusion in paper as a table

@@
 
-# Save data for inclusion in the package ---------------------------------------
-
-if (!dir.exists("../data")) {
-  dir.create("../data", recursive = TRUE)
-}
 ```
@@
 # 3. Fill empty NTShB (for same hill, not missing values)
+# 4. Add column with number of days after inoculation (DAI)
 
@@
 ```
+
+# Nitrogen management data
+
+Create a `tibble` object of the N treatments for use in the paper as a table.
+
+```{r}
+
+N_management <- tibble::tibble(
+  `Nitrogen treatment` = character(),
+  Year = integer(),
+  `Total N (kg/ha)` = integer(),
+  `Basal Application` = integer(),
+  `Tillering Application` = integer(),
+  `Panicle Initiation` = integer()
+)
+
+N_management <- tibble::add_row(N_management, `Nitrogen treatment` = c("N0",
+  "N100",
+  "N120",
+  "N60",
+  "N180"
+))
+
+N_management$Year <- c(
+  2015,
+  2015,
+  2015,
+  2016,
+  2016
+)
+
+N_management$`Total N (kg/ha)` <- c(
+  0,
+  100,
+  120,
+  60,
+  180
+)
+
+N_management$`Basal Application` <- c(
+  0,
+  60,
+  60,
+  30,
+  60
+)
+
+N_management$`Tillering Application` <- c(
+  0,
+  20,
+  30,
+  30,
+  60
+)
+
+N_management$`Panicle Initiation` <- c(
+  0,
+  20,
+  30,
+  0,
+  60
+)
+
+N_management
+
+devtools::use_data(N_management,
+                   compress = "bzip2",
+                   overwrite = TRUE)
+```
+
+# Colophon
+
+```{r}
+sessioninfo::session_info()
+```

### 2018-04-25 data-raw/README.Rmd
Change field names in N_management tibble

--- 2018-04-14 data-raw/README.Rmd
@@
 ```
+
+# Nitrogen management data
+
+Create a `tibble` object of the N treatments for use in the paper as a table.
+
+```{r}
+
+N_management <- tibble::tibble(
+  `Nitrogen treatment` = character(),
+  Year = integer(),
+  `Total N (kg/ha)` = integer(),
+  `Basal` = integer(),
+  `Tillering` = integer(),
+  `Panicle Initiation` = integer()
+  )
+
+  N_management <-
+  tibble::add_row(N_management,
+  `Nitrogen treatment` = c("N0",
+  "N100",
+  "N120",
+  "N60",
+  "N180"))
+
+  N_management$Year <- c(2015,
+  2015,
+  2015,
+  2016,
+  2016)
+
+  N_management$`Total N (kg/ha)` <- c(0,
+  100,
+  120,
+  60,
+  180)
+
+  N_management$Basal <- c(0,
+  60,
+  60,
+  30,
+  60)
+
+  N_management$Tillering <- c(0,
+  20,
+  30,
+  30,
+  60)
+
+  N_management$`Panicle Initiation` <- c(0,
+  20,
+  30,
+  0,
+  60)
+
+  N_management
+
+devtools::use_data(N_management,
+                   compress = "bzip2",
+                   overwrite = TRUE)
+```
+
+# Colophon
+
+```{r}
+sessioninfo::session_info()
+```

### 2018-04-25 data-raw/README.Rmd
Fix issue with numbers in N_management
Set to integer on creation

@@
 
-N_management <- tibble::tibble(
-  `Nitrogen treatment` = character(),
-  Year = integer(),
-  `Total N (kg/ha)` = integer(),
-  `Basal` = integer(),
-  `Tillering` = integer(),
-  `Panicle Initiation` = integer()
-  )
+N_management <- tibble::tibble(`Nitrogen treatment` = character())
 
@@
 
-  N_management$Year <- c(2015,
+N_management$Year <- as.integer(c(2015,
                                   2015,
@@
                                   2016,
-  2016)
+                                  2016))
 
-  N_management$`Total N (kg/ha)` <- c(0,
+N_management$`Total N (kg/ha)` <- as.integer(c(0,
                                                100,
@@
                                                60,
-  180)
+                                               180))
 
-  N_management$Basal <- c(0,
+N_management$Basal <- as.integer(c(0,
                                    60,
@@
                                    30,
-  60)
+                                   60))
 
-  N_management$Tillering <- c(0,
+N_management$Tillering <- as.integer(c(0,
                                        20,
@@
                                        30,
-  60)
+                                       60))
 
-  N_management$`Panicle Initiation` <- c(0,
+N_management$`Panicle Initiation` <- as.integer(c(0,
                                                   20,
@@
                                                   0,
-  60)
+                                                  60))
 

### 2018-04-25 analysis/paper/paper.Rmd
Fix typos, add table

@@
 library(knitr)
-library(kableExtra)
+library(flextable)
 library(rice.awd.pests)
@@
 Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-The disease can cause up to 50\% yield losses [@Marchetti1991] under conducive conditions.
+Under conducive conditions he disease can cause up to 50\% yield losses [@Marchetti1991].
 Studies by Savary et al.
-[-@Savary2000] estimated yield losses in tropical irrigated lowland rice in Asia at 5-10\%.
-As resistance is difficult to breed for [@Srinivasachary2011], the disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
+[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10\%.
+The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009, @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
@@
 
-The plot design was a split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split-plot treatment.
-The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice, the control treatment.
+The plot design was a split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split-plot.
+The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice as the control treatment.
 
@@
 
-The split-plot treatments were different rates of nitrogen, N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
+The split-plot treatment rates of nitrogen were N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
 
@@
 
-The plots were inoculated 20 days after transplanting using 151g of inoculum per plot (4m x 11m).
+The plots were inoculated 20 days after transplanting by spreading 151g of inoculum over the split-plot area with a 1m buffer on either end (4m x 11m).
 
@@
 
-Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) was applied.
+Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) being applied.
 
@@
 
-Nurseries of NSIC Rc222 were established on 7 January 2015 for the 2015 and 2016 experiments, respectively.
-Seedlings were transplanted on 9 January 2015 and 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+Nurseries of NSIC Rc222 were established on 7 January 2016 experiments.
+Seedlings were transplanted by hand 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
 
@@
 
-Because the data were collected on an ordinal scale, but not evenly spaced, the data are converted to the midpoint value of the percent range for severity.
+Because the data were collected on an ordinal scale, but not evenly spaced, the data were converted to the midpoint value of the percent range for severity.
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
@@
 
-In 2016 the N~4~ treatment was significantly different from the N~3~ treatment. The AWD water management was also significantly different from the control flooding treatment.
+In 2016 the N~4~ treatment was significantly different from the N~3~ treatment, with N~4~ severity being higher. The AWD water management, which was lower than FLD, was also significantly different.
 
@@
 
-In 2016 the none of the treatments, nitrogen rate or water management, were significantly different from the control treatment for leaf ShB severity.
+In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity.
 
 # Discussion {-}
+
+In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology.
+In 2016 one measurement, tiller sheath blight severity, was significantly lower for AWD than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on leaf ShB severity.
 
@@
 
-Table of N application timings and dates here...
+```{r N-management, }
+regulartable(N_management, col_keys = c("Nitrogen treatment",
+                                        "Year", 
+                                        "Total N (kg/ha)",
+                                        "Basal",
+                                        "Tillering",
+                                        "Panicle Initiation")
+             )
+```
 

### 2018-04-25 data-raw/README.Rmd
Remove N table from raw-data
This reverts commit 4a044efbbc24cef0132051b2d82c58b30015642a.

@@
 
-# Nitrogen management data
-
-Create a `tibble` object of the N treatments for use in the paper as a table.
-
-```{r}
-
-N_management <- tibble::tibble(`Nitrogen treatment` = character())
-
-N_management <-
-  tibble::add_row(N_management,
-                  `Nitrogen treatment` = c("N0",
-                                           "N100",
-                                           "N120",
-                                           "N60",
-                                           "N180"))
-
-N_management$Year <- as.integer(c(2015,
-                                  2015,
-                                  2015,
-                                  2016,
-                                  2016))
-
-N_management$`Total N (kg/ha)` <- as.integer(c(0,
-                                               100,
-                                               120,
-                                               60,
-                                               180))
-
-N_management$Basal <- as.integer(c(0,
-                                   60,
-                                   60,
-                                   30,
-                                   60))
-
-N_management$Tillering <- as.integer(c(0,
-                                       20,
-                                       30,
-                                       30,
-                                       60))
-
-N_management$`Panicle Initiation` <- as.integer(c(0,
-                                                  20,
-                                                  30,
-                                                  0,
-                                                  60))
-
-N_management
-
-devtools::use_data(N_management,
-                   compress = "bzip2",
-                   overwrite = TRUE)
-```
-
 # Colophon

### 2018-04-25 analysis/paper/paper.Rmd
Add Table 1

@@
 
+# table captions
+tn <- local({
+  i = 0
+  function(x) {
+    i <<- i + 1
+    paste('\n\nTable ', i, ': ', x, sep = '')
+    # The : before Table tells pandoc to wrap your caption in <caption></caption>
+  }
+})
+knitr::knit_hooks$set(tab.cap = function(before, options, envir) {
+  if (!before)
+    tn(options$tab.cap)
+})
+default_output_hook = knitr::knit_hooks$get("output")
+knitr::knit_hooks$set(output = function(x, options) {
+  if (is.null(options$tab.cap) == F)  
+    x
+  else
+    default_output_hook(x,options)
+})
+
 library(bookdown)
@@
 library(flextable)
+library(ggpubr)
+library(officer)
 library(rice.awd.pests)
-library(ggpubr)
+library(xtable)
 ```
@@
 
-```{r N-management, }
-regulartable(N_management, col_keys = c("Nitrogen treatment",
-                                        "Year", 
-                                        "Total N (kg/ha)",
-                                        "Basal",
-                                        "Tillering",
-                                        "Panicle Initiation")
+```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016.
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~).
+Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}
+
+N_management <- tibble::tibble(Year = integer())
+
+N_management <-
+  tibble::add_row(N_management,
+                  Year = as.integer(c(2015,
+                                      2015,
+                                      2015,
+                                      2016,
+                                      2016)))
+
+N_management$`Total N` <- as.integer(c(0,
+                                                100,
+                                                120,
+                                                60,
+                                                180))
+
+N_management$Basal <- as.integer(c(0,
+                                   60,
+                                   60,
+                                   30,
+                                   60))
+
+N_management$Tillering <- as.integer(c(0,
+                                       20,
+                                       30,
+                                       30,
+                                       60))
+
+N_management$`Panicle\nInitiation` <- as.integer(c(0,
+                                                   20,
+                                                   30,
+                                                   0,
+                                                   60))
+
+N_management <- xtable(N_management)
+N_management <- xtable_to_flextable(x = N_management, NA.string = "-")
+
+N_management <- flextable::display(
+  N_management,
+  i = 1,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
 )
+
+N_management <- flextable::display(
+  N_management,
+  i = 2,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_management <- flextable::display(
+  N_management,
+  i = 3,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_management <- flextable::display(
+  N_management,
+  i = 4,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_management <- flextable::display(
+  N_management,
+  i = 5,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_management <- add_header(N_management,
+                           Year = "Year",
+                           Tillering = "Application Rate (kg/ha)")
+
+N_management <- merge_v(N_management, part = "header")
+
+N_management <- autofit(N_management)
+N_management
+
 ```

### 2018-04-25 README.Rmd
add statement about data-raw to README
Update static docs

@@
 instructions on how to rerun the analysis to reproduce the results. The
-`data/` directory in the `analysis/` directory contains all the raw data.
+`data/` directory in the `analysis/` directory contains all the raw data. The
+`data-raw` directory contains a README.Rmd, which when knit generates the data
+used in the analysis of the paper and places `.rda` files in `data/` for the
+analysis.
 
@@
 https://staffprofile.usq.edu.au/Profile/Adam-Sparks
-
-## Required packages
- - agricolae
- - bookdown
- - car
- - carData
- - dplyr (>= 0.7.0)
- - fitdistrplus
- - forcats
- - ggplot2
- - ggpubr
- - kableExtra
- - knitr
- - lattice
- - lubridate
- - MASS
- - MCMCglmm
- - reshape2
- - rmarkdown
- - plotMCMC
- - purrr (>= 0.2.3)
- - tibble
- - tidyr (>= 0.7.0)

### 2018-04-25 analysis/paper/paper.Rmd
Split N_rates into own data
Generate `tibble` object of N rates ad timing in "/data-raw"

Include `N_rates` as a `tibble` object

Document `N_rates`

Update static docs

--- 2018-04-25 analysis/paper/paper.Rmd
@@
 
-```{r N-management, }
-regulartable(N_management, col_keys = c("Nitrogen treatment",
-                                        "Year", 
-                                        "Total N (kg/ha)",
-                                        "Basal",
-                                        "Tillering",
-                                        "Panicle Initiation")
+```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016.
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~).
+Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}
+
+N_rate <- xtable(N_rate) # the N_rate object is a tibble of data distributed with rice.awd.pests
+N_rate <- xtable_to_flextable(x = N_rate, NA.string = "-")
+
+N_rate <- flextable::display(
+  N_rate,
+  i = 1,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
 )
+
+N_rate <- flextable::display(
+  N_rate,
+  i = 2,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rate <- flextable::display(
+  N_rate,
+  i = 3,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rate <- flextable::display(
+  N_rate,
+  i = 4,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rate <- flextable::display(
+  N_rate,
+  i = 5,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rate <- add_header(N_rate,
+                           Year = "Year",
+                           Tillering = "Application Rate (kg/ha)")
+
+N_rate <- merge_v(N_rate, part = "header")
+
+N_rate <- autofit(N_rate)
+N_rate
+
 ```

### 2018-04-25 R/data.R

@@ -12,3 +12,10 @@
 #' organised into a tidy data frame.
 #'
 "RAW_data"
+
+#' A Tibble of Nitrogen Rates and Split Application Timings
+#'
+#' A dataset containing the N rates and time of application split organised
+#' into a tidy data frame.
+#'
+"N_rates"

### 2018-04-25 analysis/paper/paper.Rmd
Fix N_rate/N_rates in paper.Rmd

--- 2018-04-25 analysis/paper/paper.Rmd
@@
 
-```{r N-management, }
-regulartable(N_management, col_keys = c("Nitrogen treatment",
-                                        "Year", 
-                                        "Total N (kg/ha)",
-                                        "Basal",
-                                        "Tillering",
-                                        "Panicle Initiation")
+```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016.
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~).
+Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}
+
+N_rates <- xtable(N_rates) # the N_rates object is a tibble of data distributed with rice.awd.pests
+N_rates <- xtable_to_flextable(x = N_rates, NA.string = "-")
+
+N_rates <- flextable::display(
+  N_rates,
+  i = 1,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
 )
+
+N_rates <- flextable::display(
+  N_rates,
+  i = 2,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rates <- flextable::display(
+  N_rates,
+  i = 3,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rates <- flextable::display(
+  N_rates,
+  i = 4,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rates <- flextable::display(
+  N_rates,
+  i = 5,
+  col_key = "rowname",
+  pattern = "{{val}}{{pow}}",
+  part = "body",
+  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
+  fprops = list(pow = fp_text(
+    vertical.align = "subscript", font.size = 8
+  ))
+)
+
+N_rates <- add_header(N_rates,
+                           Year = "Year",
+                           Tillering = "Application Rate (kg/ha)")
+
+N_rates <- merge_v(N_rates, part = "header")
+
+N_rates <- autofit(N_rates)
+N_rates
+
 ```

### 2018-04-25 analysis/paper/paper.Rmd
Update figure sizes

@@
   dev = c("postscript"),
-  fig.width = 3.31,
-  fig.height = 3.31,
+  fig.width = 6.85,
+  fig.height = 6.85,
   out.width = "100%",
@@
 
-## Data Collection and Analysis {-}
+### Data Collection {-}
 
@@
 
-Because the data were collected on an ordinal scale, but not evenly spaced, the data were converted to the midpoint value of the percent range for severity.
+### Statistical Analysis {-}
+
+Because the severity data were collected on an unevenly spaced ordinal scale, they were converted to the midpoint value of the percent range for severity.
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
+
 As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].
+
+For each measurement, e.g.
+2015 tiller incidence, 2016 tiller incidence, a  single  MCMC chain was run for 50,000 steps, with the first 5000 discarded as burn in.
+The remaining samples were thinned by taking every one-hundredth sample, yielding 5000 independent draws from the posterior distribution of the  parameters of the model.
+Convergence of the chains was assessed using the coda package in R.
+The priors of the variances and covariances of the random effects in the  model are locally non-informative priors [74].
 

### 2018-04-25 R/diagnostic_plots.R
Use density plots for diagnostics

@@ -59,24 +59,28 @@ plot_diagnostic_lines <- function(d, x, title) {
 plot_replicate_posteriors <- function(d, title) {
   d <- d[d$variable != "X.Intercept.", ]
   ggplot2::ggplot(data = d,
-                  ggplot2::aes(x = d$variable,
-                               y = d$value)) +
-    ggplot2::geom_violin() +
-    ggplot2::geom_abline(slope = 0, intercept = 0) +
+                  ggplot2::aes(x = d$value,
+                               colour = d$variable)) +
+    ggplot2::geom_density() +
     ggplot2::ggtitle(paste(title)) +
-    ggplot2::coord_flip()
+    ggplot2::scale_color_brewer(type = "qual") +
+    ggplot2::guides(colour = ggplot2::guide_legend(title = "Treatment")) +
+    ggplot2::xlab("Sheath Blight Rating")
 }
 
 #' @export
 #' @rdname plot_mcmc_glmm
 plot_treatment_posteriors <- function(d, title) {
   ggplot2::ggplot(data = d,
-                  ggplot2::aes(x = d$variable,
-                               y = d$value)) +
-    ggplot2::geom_violin() +
-    ggplot2::geom_abline(slope = 0, intercept = 0) +
+                  ggplot2::aes(colour = d$variable,
+                               linetype = d$variable,
+                               x = d$value)) +
+    ggplot2::geom_density() +
     ggplot2::ggtitle(paste(title)) +
-    ggplot2::coord_flip()
+    ggplot2::scale_color_brewer(type = "qual") +
+    ggplot2::scale_linetype(name = "Treatment") +
+    ggplot2::guides(colour = ggplot2::guide_legend(title = "Treatment")) +
+    ggplot2::xlab("Sheath Blight Rating")
 }
 
 #' @export

### 2018-04-26 data-raw/README.Rmd
Add Table 1
Split N_rates into own data
Generate `tibble` object of N rates ad timing in "/data-raw"

Include `N_rates` as a `tibble` object

Document `N_rates`

Update static docs
Update N_rates data frame

@@
 
+# N rates
+
+Create a `tibble` of N rates and time of application used in this study.
+
+```{r N_rates}
+
+Year <- as.integer(c(2015,
+                     2015,
+                     2015,
+                     2016,
+                     2016))
+
+`Total N (kg/ha)` <- as.integer(c(0,
+                                  100,
+                                  120,
+                                  60,
+                                  180))
+
+`Basal N (kg/ha)` <- as.integer(c(0,
+                                  60,
+                                  60,
+                                  30,
+                                  60))
+
+`Tillering N (kg/ha)` <- as.integer(c(0,
+                                      20,
+                                      30,
+                                      30,
+                                      60))
+
+`Panicle Initiation N (kg/ha)` <- as.integer(c(0,
+                                               20,
+                                               30,
+                                               0,
+                                               60))
+
+N_rates <- cbind(Year,
+                 `Total N (kg/ha)`,
+                 `Basal N (kg/ha)`,
+                 `Tillering N (kg/ha)`,
+                 `Panicle Initiation N (kg/ha)`)
+
+row.names(N_rates) <- c("N0", "N100", "N120", "N60", "N180")
+
+devtools::use_data(N_rates,
+                   compress = "bzip2",
+                   overwrite = TRUE)
+```
+
 # Colophon

### 2018-04-26 R/data.R

@@ -13,7 +13,7 @@
 #'
 "RAW_data"
 
-#' A Tibble of Nitrogen Rates and Split Application Timings
+#' A data.frame of Nitrogen Rates and Split Application Timings
 #'
 #' A dataset containing the N rates and time of application split organised
 #' into a tidy data frame.

### 2018-04-26 analysis/paper/paper.Rmd
Replace Nsub with N0...N180
This just makes it easier to follow the treatments and create the document

Use `kable` to generate the table because Pandoc > 2.0 is not in rocker/verse

@@
 library(bookdown)
+library(kableExtra)
 library(knitr)
-library(flextable)
 library(ggpubr)
-library(officer)
 library(rice.awd.pests)
-library(xtable)
 ```
@@
 
-The split-plot treatment rates of nitrogen were N~0~ (no nitrogen supply), N~1~ (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N~2~ (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
+The split-plot treatment rates of nitrogen were N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
 
@@
 
-Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N~3~ (60 kg per ha as urea split into two applications) and N~4~ (180 kg per ha in three splits) being applied.
+Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied.
 
@@
 
-In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N~2~, flooded treatment (Figure \@ref(fig:figure-1)).
-The nitrogen treatments, N~1~ and N~2~, were both significantly different when compared with the control N~0~ treatment.
+In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N120, flooded treatment (Figure \@ref(fig:figure-1)).
+The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment.
 However, water management was not significantly different.
@@
 
-In 2015 both the N~1~ and N~2~ treatments were significantly different than the control N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.
+In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. However, the AWD water management was not significantly different from the FLD treatment.
 
@@
 
-In 2015 both the N~1~ and N~2~ treatments were significantly different than the N~0~ treatment. However, the AWD water management was not significantly different from the FLD treatment.
+In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. However, the AWD water management was not significantly different from the FLD treatment.
 
@@
 
-The changes to the inoculation methodology resulted in a much higher rate of infection in 2016, with the N~4~, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
-The nitrogen treatment N~4~, was significantly different than the control N~3~ treatment.
+The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
+The nitrogen treatment N180, was significantly different than the control N60 treatment.
 As in the 2015 study, water management did not significantly differ.
@@
 
-In 2016 the N~4~ treatment was significantly different from the N~3~ treatment, with N~4~ severity being higher. The AWD water management, which was lower than FLD, was also significantly different.
+In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher. The AWD water management, which was lower than FLD, was also significantly different.
 
@@
 
-```{r N-management, tab.cap="Nitrogen application rates for 2015 and 2016.
+```{r table-1, tab.cap="Nitrogen application rates for 2015 and 2016.
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
 Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}
-
-N_rates <- xtable(N_rates) # the N_rates object is a tibble of data distributed with rice.awd.pests
-N_rates <- xtable_to_flextable(x = N_rates, NA.string = "-")
-
-N_rates <- flextable::display(
-  N_rates,
-  i = 1,
-  col_key = "rowname",
-  pattern = "{{val}}{{pow}}",
-  part = "body",
-  formatters = list(val ~ as.character("N"), pow ~ as.character("0")),
-  fprops = list(pow = fp_text(
-    vertical.align = "subscript", font.size = 8
-  ))
-)
-
-N_rates <- flextable::display(
-  N_rates,
-  i = 2,
-  col_key = "rowname",
-  pattern = "{{val}}{{pow}}",
-  part = "body",
-  formatters = list(val ~ as.character("N"), pow ~ as.character("1")),
-  fprops = list(pow = fp_text(
-    vertical.align = "subscript", font.size = 8
-  ))
-)
-
-N_rates <- flextable::display(
-  N_rates,
-  i = 3,
-  col_key = "rowname",
-  pattern = "{{val}}{{pow}}",
-  part = "body",
-  formatters = list(val ~ as.character("N"), pow ~ as.character("2")),
-  fprops = list(pow = fp_text(
-    vertical.align = "subscript", font.size = 8
-  ))
-)
-
-N_rates <- flextable::display(
-  N_rates,
-  i = 4,
-  col_key = "rowname",
-  pattern = "{{val}}{{pow}}",
-  part = "body",
-  formatters = list(val ~ as.character("N"), pow ~ as.character("3")),
-  fprops = list(pow = fp_text(
-    vertical.align = "subscript", font.size = 8
-  ))
-)
-
-N_rates <- flextable::display(
-  N_rates,
-  i = 5,
-  col_key = "rowname",
-  pattern = "{{val}}{{pow}}",
-  part = "body",
-  formatters = list(val ~ as.character("N"), pow ~ as.character("4")),
-  fprops = list(pow = fp_text(
-    vertical.align = "subscript", font.size = 8
-  ))
-)
-
-N_rates <- add_header(N_rates,
-                           Year = "Year",
-                           Tillering = "Application Rate (kg/ha)")
-
-N_rates <- merge_v(N_rates, part = "header")
-
-N_rates <- autofit(N_rates)
-N_rates
+kable(N_rates)
 
@@
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N~0~), 100 kg per ha N (N~1~) and 180 kg per ha N (N~2~).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N~3~) and 180 kg per ha N (N~4~).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
 Points represent the mean of four replications."}

### 2018-04-26 analysis/paper/paper.Rmd
Not using kableExtra
Remove from libraries in paper.Rmd
Update figures
Update with new N rate designators

@@
 library(bookdown)
-library(kableExtra)
 library(knitr)
@@
                      name = "Tiller Sheath Blight Incidence (%)") +
-  scale_shape_discrete(labels = c(expression(N[0]),
-                                  expression(N[1]),
-                                  expression(N[2]),
-                                  expression(N[3]),
-                                  expression(N[4]))) +
-  scale_linetype_discrete(labels = c(expression(N[0]),
-                                     expression(N[1]),
-                                     expression(N[2]),
-                                     expression(N[3]),
-                                     expression(N[4]))) +
+  scale_shape_discrete(labels = c("N0",
+                                  "N100",
+                                  "N120",
+                                  "N60",
+                                  "N180")) +
+  scale_linetype_discrete(labels = c("N0",
+                                     "N100",
+                                     "N120",
+                                     "N60",
+                                     "N180")) +
   xlab("Days After Inoculation") +
@@
         axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom") +
-  guides(linetype = guide_legend(nrow = 2),
-         shape = guide_legend(nrow = 2))
+  theme(legend.position = "bottom")
 ```
@@
                aes(group = TRT)) +
-  scale_shape_discrete(labels = c(expression(N[0]),
-                                  expression(N[1]),
-                                  expression(N[2]),
-                                  expression(N[3]),
-                                  expression(N[4]))) +
-  scale_linetype_discrete(labels = c(expression(N[0]),
-                                     expression(N[1]),
-                                     expression(N[2]),
-                                     expression(N[3]),
-                                     expression(N[4]))) +
+  scale_shape_discrete(labels = c("N0",
+                                  "N100",
+                                  "N120",
+                                  "N60",
+                                  "N180")) +
+  scale_linetype_discrete(labels = c("N0",
+                                     "N100",
+                                     "N120",
+                                     "N60",
+                                     "N180")) +
   ylab("Tiller Sheath Blight Severity (%)") +
@@
                aes(group = TRT)) +
-  scale_shape_discrete(labels = c(expression(N[0]),
-                                  expression(N[1]),
-                                  expression(N[2]),
-                                  expression(N[3]),
-                                  expression(N[4]))) +
-  scale_linetype_discrete(labels = c(expression(N[0]),
-                                     expression(N[1]),
-                                     expression(N[2]),
-                                     expression(N[3]),
-                                     expression(N[4]))) +
+  scale_shape_discrete(labels = c("N0",
+                                  "N100",
+                                  "N120",
+                                  "N60",
+                                  "N180")) +
+  scale_linetype_discrete(labels = c("N0",
+                                     "N100",
+                                     "N120",
+                                     "N60",
+                                     "N180")) +
   ylab("Leaf Sheath Blight Severity (%)") +

### 2018-04-26 analysis/paper/paper.Rmd
Add better descriptor of statistical analysis and Data and code availability statement

@@
 For each measurement, e.g.
-2015 tiller incidence, 2016 tiller incidence, a  single  MCMC chain was run for 50,000 steps, with the first 5000 discarded as burn in.
-The remaining samples were thinned by taking every one-hundredth sample, yielding 5000 independent draws from the posterior distribution of the  parameters of the model.
-Convergence of the chains was assessed using the coda package in R.
-The priors of the variances and covariances of the random effects in the  model are locally non-informative priors [74].
+2015 tiller incidence, 2016 tiller incidence, a single MCMC chain was run for 55,000 steps, with the first 5000 discarded as burn in.
+The remaining 50,000 samples were thinned by taking every tenth sample, resulting in 5000 independent draws from the posterior distribution of the parameters of the model.
 
@@
 # Notes {-}
+
+## Data and Code Availability
+
+All data generated from this project and code used for analysis are available as a research compendium from <https://github.com/openplantpathology/rice_awd_pests> with instructions on how to cite the compendium and use the Docker file to recreate the full analysis and this manuscript [@Sparks2018].
 

### 2018-04-26 analysis/paper/paper.Rmd
Update static docs

@@
 The remaining 50,000 samples were thinned by taking every tenth sample, resulting in 5000 independent draws from the posterior distribution of the parameters of the model.
+The model
 
@@
 
-In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher. The AWD water management, which was lower than FLD, was also significantly different.
+In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher.
+The AWD water management, which was lower than the FLD treatment, was also significantly different.
 
@@
 
-All data generated from this project and code used for analysis are available as a research compendium from <https://github.com/openplantpathology/rice_awd_pests> with instructions on how to cite the compendium and use the Docker file to recreate the full analysis and this manuscript [@Sparks2018].
+All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
 

### 2018-04-26 analysis/paper/paper.Rmd
Add figure 4

@@
 
+The changes made for the 2016 experiment appear to have worked, increasing the incidence and decreased variability of sheath blight in the plots.
+
 # Notes {-}
@@
 
+```{r figure-4, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
+  geom_boxplot(fill = NA) +
+  theme(axis.text.x = element_text(size = 8,
+                                   angle = 45,
+                                   hjust = 1)) +
+  xlab("Treatment") +
+  ylab("Incidence per Hill") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  facet_grid(. ~ YEAR) +
+  theme(legend.position = "bottom")
+```
+
+##### pagebreak
+
 ### Colophon {-}

### 2018-04-26 analysis/paper/paper.Rmd
Update figures
Add figure for 2016 tiller sheath blight severity where lower in AWD

@@
 In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology.
-In 2016 one measurement, tiller sheath blight severity, was significantly lower for AWD than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on leaf ShB severity.
+In 2016 one measurement, tiller sheath blight severity, was significantly lower for AWD (FIGURE XXX) than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on leaf ShB severity.
 
@@
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+ggplot(subset(AUDPS, YEAR == 2016),
+       aes(x = WMGT, y = TShB_percent_AUDPS)) +
+  geom_boxplot() +
+  geom_point() +
+  xlab("Treatment") +
+  ylab("AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"))
+```
+
+##### pagebreak
+
+```{r figure-5, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
 ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
@@
         axis.line = element_line(colour = "black")) +
-  facet_grid(. ~ YEAR) +
-  theme(legend.position = "bottom")
+  facet_grid(. ~ YEAR)
 ```

### 2018-04-26 analysis/paper/paper.Rmd
Flesh out figure captions

@@
 
-```{r figure-4, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
+```{r figure-4, fig.cap="Tiller sheath blight severity progress was measured in the 2016 experiment at four assessment points.
+Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
@@
 ```{r figure-5, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Sheath blight incidence was calculated as the number of tillers per hill that were infected with sheath blight divided by the whole number of tillers in the hill.
+Differing inoculation techniques were used in the 2015 and 2016 experiments, leading to a higher rate of incidence in 2016."}
 ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +

### 2018-04-26 analysis/paper/paper.Rmd
Add a bit more to the discussion and cross references to figures and table 1

@@
 The plot design was a split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split-plot.
+
 The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice as the control treatment.
-
 The main plot size was 12m x 12m (144 sq m), with a split-plot size of 5m x 5m (25 sq m).
@@
 
-The split-plot treatment rates of nitrogen were N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation).
+The split-plot treatment rates of nitrogen were N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Table \@ref(tab:N-rates)).
 
@@
 
-Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied.
+Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Table \@ref(tab:N-rates)).
 
@@
 
-In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology.
-In 2016 one measurement, tiller sheath blight severity, was significantly lower for AWD (FIGURE XXX) than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on leaf ShB severity.
+In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology.
+In only one instance were we able to detect any effect of AWD on ShB (Figure \@ref(fig:TShB-sev)).
+In the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on tiller ShB severity.
 
-The changes made for the 2016 experiment appear to have worked, increasing the incidence and decreased variability of sheath blight in the plots.
+The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Figure \@ref(fig:TShB-inc)).
 
@@
 
-```{r table-1, tab.cap="Nitrogen application rates for 2015 and 2016.
+```{r N-rates}
+
+kable(N_rates,
+      caption = "Nitrogen application rates for 2015 and 2016.
 Five different nitrogen treatments were applied depending on the experiment.
@@
 In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Treatments were applied in splits, basal, tillering and panicle initiation growth stages."}
-kable(N_rates)
+Treatments were applied in splits, basal, tillering and panicle initiation growth stages.")
 
@@
 
-```{r figure-4, fig.cap="Tiller sheath blight severity progress was measured in the 2016 experiment at four assessment points.
+```{r TShB-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2016 experiment at four assessment points.
 Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
@@
 
-```{r figure-5, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
+```{r TShB-inc, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).

### 2018-04-26 analysis/paper/paper.Rmd
Add new figures
Add figures for all statistical analyses performed

@@
 
-In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher.
-The AWD water management, which was lower than the FLD treatment, was also significantly different.
+In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:TShB-N-sev)).
+The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:TShB-W-sev)).
 
@@
 
-In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity.
+In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:LShB-W-sev), \@ref(fig:LShB-N-sev)).
 
@@
 
-##### pagebreak
+##### Tiller ShB progress
 
@@
 
-##### pagebreak
+##### Leaf ShB progress
 
@@
 
-##### pagebreak
+##### Tiller ShB incidence - WMGT
 
-```{r TShB-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2016 experiment at four assessment points.
-Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
+```{r TShB-W-inc, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
-ggplot(subset(AUDPS, YEAR == 2016),
-       aes(x = WMGT, y = TShB_percent_AUDPS)) +
+ggplot(AUDPS,
+       aes(x = WMGT, y = TShB_inc_AUDPS)) +
   geom_boxplot() +
@@
         panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black"))
+        axis.line = element_line(colour = "black")) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
 ```
 
-##### pagebreak
+##### Tiller ShB incidence - NRTE
 
-```{r TShB-inc, fig.cap="Tiller sheath blight incidence per hill in the 2015 and 2016 experiments.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Sheath blight incidence was calculated as the number of tillers per hill that were infected with sheath blight divided by the whole number of tillers in the hill.
-Differing inoculation techniques were used in the 2015 and 2016 experiments, leading to a higher rate of incidence in 2016."}
-ggplot(RAW_data, aes(x = WMGT, y = TShB_incidence)) +
-  geom_boxplot(fill = NA) +
-  theme(axis.text.x = element_text(size = 8,
-                                   angle = 45,
-                                   hjust = 1)) +
+```{r TShB-N-inc, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+ggplot(AUDPS,
+       aes(x = NRTE, y = TShB_inc_AUDPS)) +
+  geom_boxplot() +
+  geom_point() +
   xlab("Treatment") +
-  ylab("Incidence per Hill") +
+  ylab("AUDPS") +
   theme_bw() +
@@
         axis.line = element_line(colour = "black")) +
-  facet_grid(. ~ YEAR)
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+```
+
+##### Tiller ShB severity - WMGT
+
+```{r TShB-W-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+ggplot(AUDPS,
+       aes(x = WMGT, y = TShB_sev_AUDPS)) +
+  geom_boxplot() +
+  geom_point() +
+  xlab("Treatment") +
+  ylab("AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+```
+
+##### Tiller ShB severity - NRTE
+
+```{r TShB-N-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+ggplot(AUDPS,
+       aes(x = NRTE, y = TShB_sev_AUDPS)) +
+  geom_boxplot() +
+  geom_point() +
+  xlab("Treatment") +
+  ylab("AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+```
+
+##### Leaf ShB severity - WMGT
+
+```{r LShB-W-sev, fig.cap="Leaf sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+ggplot(AUDPS,
+       aes(x = WMGT, y = LShB_percent_AUDPS)) +
+  geom_boxplot() +
+  geom_point() +
+  xlab("Treatment") +
+  ylab("AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+```
+
+##### Leaf ShB severity - NRTE
+
+```{r LShB-N-sev, fig.cap="Leaf sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+ggplot(AUDPS,
+       aes(x = NRTE, y = LShB_percent_AUDPS)) +
+  geom_boxplot() +
+  geom_point() +
+  xlab("Treatment") +
+  ylab("AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
 ```

### 2018-04-26 analysis/paper/paper.Rmd
Rejig figures

@@
 In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N120, flooded treatment (Figure \@ref(fig:figure-1)).
-The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment.
-However, water management was not significantly different.
+The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Figure \@ref(fig:TShB-N-inc)).
+However, water management was not significantly different (Figure \@ref(fig:TShB-W-inc)).
 
@@
 
-In 2015 both the N100 and N120 treatments were significantly different than the control N0 treatment. However, the AWD water management was not significantly different from the FLD treatment.
+Tiller ShB severity remained below 2% (Figure \@ref(fig:figure-2)).
+Both the N100 and N120 treatments were significantly different than the control N0 treatment (Figure \@ref(fig:TShB-N-sev)).
+However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:TShB-w-sev)).
 
@@
 
-In 2015 both the N100 and N120 treatments were significantly different than the N0 treatment. However, the AWD water management was not significantly different from the FLD treatment.
+Severity of leaf ShB remained low, less than 0.4% across all treatments (Figure \@ref(fig:figure-3))).
+Both the N100 and N120 treatments were significantly different than the N0 treatment (Figure \@ref(fig:LShB-N-sev)).
+However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:LShB-W-sev)).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
-The nitrogen treatment N180, was significantly different than the control N60 treatment.
-As in the 2015 study, water management did not significantly differ.
+The nitrogen treatment N180, was significantly different than the control N60 treatment (Figure \@ref(fig:TShB-N-inc)).
+As in the 2015 study, water management did not significantly differ \@ref(fig:TShB-W-inc)).
 
@@
 
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded
 In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:TShB-N-sev)).
@@
 
-```{r figure-1, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+```{r tiller-ShB-w-progress, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
 Points represent the mean of four replications."}
@@
            y = TShB_incidence,
-           linetype = NRTE,
-           shape = NRTE)) +
+           group = WMGT,
+           shape = WMGT,
+           linetype = WMGT)) +
   stat_summary(fun.y = "mean",
-               geom = "line",
-               aes(group = TRT)) +
+               geom = "line") +
   stat_summary(fun.y = "mean",
-               geom = "point",
-               aes(group = TRT)) +
+               geom = "point") +
   scale_y_continuous(labels = function(x) paste0(x*100),
@@
                      name = "Tiller Sheath Blight Incidence (%)") +
-  scale_shape_discrete(labels = c("N0",
-                                  "N100",
-                                  "N120",
-                                  "N60",
-                                  "N180")) +
-  scale_linetype_discrete(labels = c("N0",
-                                     "N100",
-                                     "N120",
-                                     "N60",
-                                     "N180")) +
   xlab("Days After Inoculation") +
-  facet_grid(WMGT ~ YEAR,
+  facet_grid(. ~ YEAR,
+             scales = "free_x") +
+  labs(linetype = "N Treatment",
+       shape = "N Treatment") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black")) +
+  theme(legend.position = "bottom")
+```
+
+##### Tiller ShB severity - NRTE
+
+```{r tiller-ShB-w-progress, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Points represent the mean of four replications."}
+
+ggplot(RAW_data,
+       aes(x = DAI,
+           y = TShB_incidence,
+           group = NRTE,
+           shape = NRTE,
+           linetype = NRTE)) +
+  stat_summary(fun.y = "mean",
+               geom = "line") +
+  stat_summary(fun.y = "mean",
+               geom = "point") +
+  scale_y_continuous(labels = function(x) paste0(x*100),
+                     limits = c(0, 1),
+                     name = "Tiller Sheath Blight Incidence (%)") +
+  xlab("Days After Inoculation") +
+  facet_grid(. ~ YEAR,
              scales = "free_x") +

### 2018-04-27 R/mcmc_table.R
add mcmc_table function

@@ -1,0 +1,33 @@
+
+#' @title MCMCglmm results table
+#'
+#' @description Generate a table of MCMCglmm results
+#'
+#' @export
+#' @name mcmc_table
+#' @param x An MCMCglmm model
+#'
+#' @examples \dontrun{
+#' mcmc_table(MCMC_model)
+#' }
+#'
+#' @author Adam H Sparks, \email{adamhsparks@gmail.com}
+
+mcmc_table <- function(x) {
+  sols <- summary(x)$solutions[-1, -4]
+
+  DV <- c(deparse(substitute(x)), rep(" ", nrow(sols) - 1))
+  Predictors <- row.names(sols)
+  DIC <- c(round(x$DIC, 2), rep(" ", nrow(sols) - 1))
+
+  y <- data.frame(DV, Predictors, sols, DIC)
+  names(y) <- c("Dependent Variable",
+                "Predictors",
+                "Post Mean",
+                "Lower 95% CI",
+                "Upper 95% CI",
+                "P MCMC",
+                "DIC")
+  row.names(y) <- NULL
+  return(y)
+}

### 2018-04-27 analysis/paper/paper.Rmd
Clean up figures
Group figures into four total figures with sub panels

@@
 library(knitr)
+library(ggplot2)
 library(ggpubr)
+library(grid)
+library(gridExtra)
 library(rice.awd.pests)
@@
 
-Disease scoring was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
+Two sample areas per plot (1m x 1m) were assessed.
+For nine hills per sample, the total number of tillers per hill and number of tillers with ShB (incidence) were measured.
+Tiller ShB severity was measured for four tillers per hill and six leaves tiller using the rating scale.
+Leaves were rated as green (living) having at least XXX% living tissue or dead, defined as having less than XXX% living tissue.
+Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
+
+Disease rating was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
 Where severity was considered to be the amount of leaf or sheath tissue covered by ShB lesions.
-Two sample areas per plot (1m x 1m) were assessed.
-For nine hills per sample, the number of tillers per hill and number of tillers with ShB (incidence) were measured.
-Tiller ShB severity was measured for four tillers per hill and six leaves tiller using the rating scale.
-Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
 
@@
 
-Because the severity data were collected on an unevenly spaced ordinal scale, they were converted to the midpoint value of the percent range for severity.
+Because the severity data were collected on an unevenly spaced categorical scale, they were converted to the midpoint value of the percent range for severity.
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
@@
 
-```{r tiller-ShB-w-progress, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+```{r tiller-ShB-w-progress, fig.cap="Tiller sheath blight progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
@@
 
-ggplot(RAW_data,
+p1 <- ggplot(RAW_data,
        aes(x = DAI,
@@
                      limits = c(0, 1),
-                     name = "Tiller Sheath Blight Incidence (%)") +
+                     name = "Tiller Incidence (%)") +
   xlab("Days After Inoculation") +
@@
              scales = "free_x") +
-  labs(linetype = "N Treatment",
-       shape = "N Treatment") +
+  labs(linetype = "Irrigation",
+       shape = "Irrigation") +
   theme_bw() +
@@
         axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        legend.position = c(x = 0.065, y = 0.76),
+        legend.background = element_rect(color = "black", 
+                                         size = 0.5,
+                                         linetype = "solid"),
+        axis.title.x = element_blank())
+
+p2 <- ggplot(RAW_data,
+             aes(x = DAI,
+                 y = PERC_TIL_ShB,
+                 group = WMGT,
+                 shape = WMGT,
+                 linetype = WMGT)) +
+  stat_summary(fun.y = "mean",
+               geom = "line") +
+  stat_summary(fun.y = "mean",
+               geom = "point") +
+  scale_y_continuous(labels = function(x) paste0(x*100),
+                     limits = c(0, 1),
+                     name = "Tiller Severity (%)") +
+  xlab("Days After Inoculation") +
+  facet_grid(. ~ YEAR,
+             scales = "free_x") +
+  labs(linetype = "Irrigation",
+       shape = "Irrigation") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        legend.position = "none",
+        axis.title.x = element_blank(),)
+
+p3 <- ggplot(RAW_data,
+             aes(x = DAI,
+                 y = PERC_LEAF_ShB,
+                 group = WMGT,
+                 shape = WMGT,
+                 linetype = WMGT)) +
+  stat_summary(fun.y = "mean",
+               geom = "line") +
+  stat_summary(fun.y = "mean",
+               geom = "point") +
+  scale_y_continuous(labels = function(x) paste0(x*100),
+                     limits = c(0, 1),
+                     name = "Leaf Severity (%)") +
+  xlab("Days After Inoculation") +
+  facet_grid(. ~ YEAR,
+             scales = "free_x") +
+  labs(linetype = "Irrigation",
+       shape = "Irrigation") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        legend.position = "none")
+
+grid.arrange(p1, p2, p3, ncol = 1, nrow = 3)
 ```
 
-##### Tiller ShB severity - NRTE
+##### Tiller ShB N progress
 
-```{r tiller-ShB-w-progress, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+```{r tiller-ShB-N-progress, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+Five different nitrogen treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
 Points represent the mean of four replications."}
 
-ggplot(RAW_data,
+p4 <- ggplot(RAW_data,
              aes(x = DAI,
@@
                      limits = c(0, 1),
-                     name = "Tiller Sheath Blight Incidence (%)") +
-  xlab("Days After Inoculation") +
+                     name = "Tiller Incidence (%)") +
   facet_grid(. ~ YEAR,
              scales = "free_x") +
-  labs(linetype = "N Treatment",
-       shape = "N Treatment") +
+  labs(linetype = "N Rate",
+       shape = "N Rate") +
   theme_bw() +
@@
         axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
-```
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        legend.position = c(x = 0.095, y = 0.69),
+        legend.background = element_rect(color = "black", 
+                                         size = 0.5,
+                                         linetype = "solid"),
+        axis.title.x = element_blank()) +
+  guides(linetype = guide_legend(ncol = 2),
+         shape = guide_legend(ncol = 2))
 
-##### Tiller ShB progress
-
-```{r figure-2, fig.cap="Tiller sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Points represent the mean of four replications."}
-
-ggplot(RAW_data,
+p5 <- ggplot(RAW_data,
              aes(x = DAI,
                  y = PERC_TIL_ShB,
-           linetype = NRTE,
-           shape = NRTE)) +
+                 group = NRTE,
+                 shape = NRTE,
+                 linetype = NRTE)) +
   stat_summary(fun.y = "mean",
-               geom = "line",
-               aes(group = TRT)) +
+               geom = "line") +
   stat_summary(fun.y = "mean",
-               geom = "point",
-               aes(group = TRT)) +
-  scale_shape_discrete(labels = c("N0",
-                                  "N100",
-                                  "N120",
-                                  "N60",
-                                  "N180")) +
-  scale_linetype_discrete(labels = c("N0",
-                                     "N100",
-                                     "N120",
-                                     "N60",
-                                     "N180")) +
-  ylab("Tiller Sheath Blight Severity (%)") +
-  xlab("Days After Inoculation") +
-  facet_grid(WMGT ~ YEAR,
+               geom = "point") +
+  scale_y_continuous(labels = function(x) paste0(x*100),
+                     limits = c(0, 1),
+                     name = "Tiller Severity (%)") +
+  facet_grid(. ~ YEAR,
              scales = "free_x") +
-  labs(linetype = "N Treatment",
-       shape = "N Treatment") +
+  labs(linetype = "N Rate",
+       shape = "N Rate") +
   theme_bw() +
@@
         panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
-```
+        axis.line = element_line(colour = "black"),
+        legend.position = "none",
+        axis.title.x = element_blank(),)
 
-##### Leaf ShB progress
-
-```{r figure-3, fig.cap="Leaf sheath blight severity progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season in both years.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Points represent the mean of four replications."}
-
-ggplot(RAW_data,
+p6 <- ggplot(RAW_data,
              aes(x = DAI,
                  y = PERC_LEAF_ShB,
-           linetype = NRTE,
-           shape = NRTE)) +
+                 group = NRTE,
+                 shape = NRTE,
+                 linetype = NRTE)) +
   stat_summary(fun.y = "mean",
-               geom = "line",
-               aes(group = TRT)) +
+               geom = "line") +
   stat_summary(fun.y = "mean",
-               geom = "point",
-               aes(group = TRT)) +
-  scale_shape_discrete(labels = c("N0",
-                                  "N100",
-                                  "N120",
-                                  "N60",
-                                  "N180")) +
-  scale_linetype_discrete(labels = c("N0",
-                                     "N100",
-                                     "N120",
-                                     "N60",
-                                     "N180")) +
-  ylab("Leaf Sheath Blight Severity (%)") +
+               geom = "point") +
+  scale_y_continuous(labels = function(x) paste0(x*100),
+                     limits = c(0, 1),
+                     name = "Leaf Severity (%)") +
   xlab("Days After Inoculation") +
-  facet_grid(WMGT ~ YEAR,
+  facet_grid(. ~ YEAR,
              scales = "free_x") +
-  labs(linetype = "N Treatment",
-       shape = "N Treatment") +
+  labs(linetype = "N Rate",
+       shape = "N Rate") +
   theme_bw() +
@@
         panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  theme(legend.position = "bottom")
+        axis.line = element_line(colour = "black"),
+        legend.position = "none")
+
+grid.arrange(p4, p5, p6, ncol = 1, nrow = 3)
 ```
 
-##### Tiller ShB incidence - WMGT
+##### ShB boxplot - WMGT
 
-```{r TShB-W-inc, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+```{r TShB-W-inc, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
-ggplot(AUDPS,
+p7 <- ggplot(AUDPS,
              aes(x = WMGT, y = TShB_inc_AUDPS)) +
   geom_boxplot() +
-  geom_point() +
+  ylab("Tiller Incidence AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        axis.title.x = element_blank()) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+
+p8 <- ggplot(AUDPS,
+       aes(x = WMGT, y = TShB_sev_AUDPS)) +
+  geom_boxplot() +
+  ylab("Tiller Severity AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        axis.title.x = element_blank()) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+
+p9 <- ggplot(AUDPS,
+       aes(x = WMGT, y = LShB_sev_AUDPS)) +
+  geom_boxplot() +
   xlab("Treatment") +
-  ylab("AUDPS") +
+  ylab("Leaf Severity AUDPS") +
   theme_bw() +
@@
              scales = "free_x")
+
+grid.arrange(p7, p8, p9, ncol = 1, nrow = 3)
 ```
 
-##### Tiller ShB incidence - NRTE
+##### ShB boxplot - NRTE
 
-```{r TShB-N-inc, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+```{r TShB-N-sev, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Five different nitrogen treatments were applied depending on the experiment.
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Five different nitrogen treatments were applied to split plots depending on the experiment.
 In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
 In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
-ggplot(AUDPS,
+p10 <- ggplot(AUDPS,
               aes(x = NRTE, y = TShB_inc_AUDPS)) +
   geom_boxplot() +
-  geom_point() +
   xlab("Treatment") +
-  ylab("AUDPS") +
+  ylab("Tiller Incidence AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        axis.title.x = element_blank()) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+
+p11 <- ggplot(AUDPS,
+              aes(x = NRTE, y = TShB_percent_AUDPS)) +
+  geom_boxplot() +
+  ylab("Tiller Severity AUDPS") +
+  theme_bw() +
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        axis.line = element_line(colour = "black"),
+        axis.title.x = element_blank()) +
+  facet_grid(. ~ YEAR,
+             scales = "free_x")
+
+p12 <- ggplot(AUDPS,
+              aes(x = NRTE, y = LShB_percent_AUDPS)) +
+  geom_boxplot() +
+  xlab("Treatment") +
+  ylab("Leaf Severity AUDPS") +
   theme_bw() +
@@
              scales = "free_x")
-```
 
-##### Tiller ShB severity - WMGT
-
-```{r TShB-W-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
-ggplot(AUDPS,
-       aes(x = WMGT, y = TShB_sev_AUDPS)) +
-  geom_boxplot() +
-  geom_point() +
-  xlab("Treatment") +
-  ylab("AUDPS") +
-  theme_bw() +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  facet_grid(. ~ YEAR,
-             scales = "free_x")
-```
-
-##### Tiller ShB severity - NRTE
-
-```{r TShB-N-sev, fig.cap="Tiller sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
-Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
-ggplot(AUDPS,
-       aes(x = NRTE, y = TShB_sev_AUDPS)) +
-  geom_boxplot() +
-  geom_point() +
-  xlab("Treatment") +
-  ylab("AUDPS") +
-  theme_bw() +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  facet_grid(. ~ YEAR,
-             scales = "free_x")
-```
-
-##### Leaf ShB severity - WMGT
-
-```{r LShB-W-sev, fig.cap="Leaf sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
-ggplot(AUDPS,
-       aes(x = WMGT, y = LShB_percent_AUDPS)) +
-  geom_boxplot() +
-  geom_point() +
-  xlab("Treatment") +
-  ylab("AUDPS") +
-  theme_bw() +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  facet_grid(. ~ YEAR,
-             scales = "free_x")
-```
-
-##### Leaf ShB severity - NRTE
-
-```{r LShB-N-sev, fig.cap="Leaf sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight severity was rated on an unevenly spaced ordinal scale and converted to the mid-point percentage value to calculate the area under the disease progress stairs (AUDPS).
-Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
-ggplot(AUDPS,
-       aes(x = NRTE, y = LShB_percent_AUDPS)) +
-  geom_boxplot() +
-  geom_point() +
-  xlab("Treatment") +
-  ylab("AUDPS") +
-  theme_bw() +
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  facet_grid(. ~ YEAR,
-             scales = "free_x")
+grid.arrange(p10, p11, p12, ncol = 1, nrow = 3)
 ```

### 2018-04-27 R/mcmc_table.R
Add table for MCMC results

@@ -15,14 +15,13 @@
 
 mcmc_table <- function(x) {
   sols <- summary(x)$solutions[-1, -4]
+  sols[, c(1:3)] <- round(sols[, c(1:3)], 3)
 
-  DV <- c(deparse(substitute(x)), rep(" ", nrow(sols) - 1))
   Predictors <- row.names(sols)
   DIC <- c(round(x$DIC, 2), rep(" ", nrow(sols) - 1))
 
-  y <- data.frame(DV, Predictors, sols, DIC)
-  names(y) <- c("Dependent Variable",
-                "Predictors",
+  y <- data.frame(Predictors, sols, DIC)
+  names(y) <- c("Predictors",
                 "Post Mean",
                 "Lower 95% CI",
                 "Upper 95% CI",

### 2018-04-27 analysis/paper/paper.Rmd
Add new MCMC table to paper
Update static docs

@@
 ```{r N-rates}
-
 kable(N_rates,
@@
 
+```{r MCMC-table}
+MCMC_table <- readRDS("../data/derived_data/MCMC_table.Rds")
+kable(MCMC_table,
+      caption = "MCMC fit")
+```
+
+##### pagebreak
+
 # Figures {-}
 
-```{r tiller-ShB-w-progress, fig.cap="Tiller sheath blight progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+```{r ShB-W-progress, fig.cap="Sheath blight progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
@@
 
-```{r tiller-ShB-N-progress, fig.cap="Tiller sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+```{r ShB-N-progress, fig.cap="Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Five different nitrogen treatments were applied to split plots depending on the experiment.
@@
 
-```{r TShB-W-inc, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+```{r ShB-W-inc, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
@@
 
-```{r TShB-N-sev, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+```{r ShB-N-sev, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).

### 2018-04-29 R/plot_estimates.R
Add plot_estimates()

@@ -1,0 +1,36 @@
+
+#' @title Plot MCMCglmm estimates
+#'
+#' @description Plot estimates of posterior distributions and credible
+#'  intervales of MCMCglmm outputs
+#'
+#' @name plot_estimates
+#' @param x An\code{\link[coda]{mcmc.list}} object
+#'
+#' @examples \dontrun{
+#' # Plot posterior means and credible intervals
+#' plot_estimates(m1)
+#'}
+#'
+#' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
+#'
+#' @export
+plot_estimates <- function(x) {
+  par(mfrow = c(1, 1))
+  if (class(x) != "summary.mcmc")
+    x <- summary(x)
+  n <- dim(x$statistics)[1]
+  par(mar = c(2, 7, 4, 1))
+  plot(
+    x$statistics[, 1],
+    n:1,
+    yaxt = "n",
+    ylab = "",
+    xlim = range(x$quantiles) * 1.2,
+    pch = 19,
+    main = "Posterior means and 95% credible intervals"
+  )
+  axis(2, at = n:1, rownames(x$statistics), las = 2)
+  arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
+  abline(v = 0, lty = 2)
+}

### 2018-04-29 R/diagnostic_plots.R
Remove diagnostic_plots()

@@ -1,94 +1,0 @@
-
-#' @title MCMCglmm diagnostic plots
-#'
-#' @description Plot diagnostic graphs from MCMCglmm outputs
-#'
-#' @export
-#' @name plot_mcmc_glmm
-#' @param d A melted data.frame of MCMCglmm diagnostic outputs
-#' @param x Dummy x-axis for diagnostic lines plot
-#' @param title Title to be used in resulting graph output
-#'
-#'
-#' @section Functions:
-#' \itemize{
-#'  \item \code{plot_diagnostic_lines()} plots diagnostic lines from MCMCglmm
-#'  output
-#'  \item \code{plot_replicate_posteriors()} plots a violin plot of posteriors
-#'  for experimental plot replicates
-#'  \item \code{plot_treatment_posteriors()} plots a violin plot of posteriors
-#'  for experimental plot treatments
-#'  \item \code{plot_joint_random_error_dist()} plots joint distribution
-#' }
-#'
-#' @examples \dontrun{
-#' # Plot diagnostic lines
-#' plot_diagnostic_lines(d = reps, x = x, title = "Diagnostic Lines Plot")
-#'
-#' # Plot replicate posteriors
-#' plot_replicate_posteriors(d = reps, title = "Replicate Posteriors")
-#'
-#' # Plot treatment posteriors
-#' plot_treatment_posteriors(d =  trts, title = "Treatment Posteriors")
-#'
-#' # Plot joint random error
-#' plot_joint_random_error_dist(d = rdf, title = ("Random Error Distribution"))
-#' }
-#'
-#' @author Adam H Sparks, \email{adamhsparks@gmail.com}
-#'
-#'
-#' @export
-#' @rdname plot_mcmc_glmm
-plot_diagnostic_lines <- function(d, x, title) {
-  ggplot2::ggplot(data = d, ggplot2::aes(
-    x = rep(x, length(unique(d$variable))),
-    y = d$value,
-    group = d$variable
-  )) +
-    ggplot2::geom_line() +
-    ggplot2::xlab("Iteration Number") +
-    ggplot2::ylab(NULL) +
-    ggplot2::facet_grid(variable ~ .) +
-    ggplot2::theme(strip.text.y = ggplot2::element_text(angle = 0)) +
-    ggplot2::ggtitle(paste(title))
-}
-
-#' @export
-#' @rdname plot_mcmc_glmm
-plot_replicate_posteriors <- function(d, title) {
[…]

### 2018-04-29 analysis/paper/paper.Rmd
Update paper
Detail statisitcal analysis

@@
 
-Because the severity data were collected on an unevenly spaced categorical scale, they were converted to the midpoint value of the percent range for severity.
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
+Because the severity data were collected on an unevenly spaced categorical scale, they were converted to the midpoint value of the percent range.
 
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using multivariate generalised linear mixed models implemented in the `MCMCglmm` package [@MCMCglmm2010] in the R programming environment [@R2018].
-
-For each measurement, e.g.
-2015 tiller incidence, 2016 tiller incidence, a single MCMC chain was run for 55,000 steps, with the first 5000 discarded as burn in.
-The remaining 50,000 samples were thinned by taking every tenth sample, resulting in 5000 independent draws from the posterior distribution of the parameters of the model.
-The model
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@R2018; @MCMCglmm2010].
+Six models were created where the the dependent variables were 2015 tiller ShB incidence, 2015 tiller ShB severity, 2015 leaf ShB severity; 2016 tiller ShB incidence, 2016 tiller ShB severity; 2016 leaf ShB severity, respectively.
+The independent variables were the irrigation management and nitrogen rate and replicate was treated as a random variable.
+The base levels (control treatments) for the analyses for 2015 were: N rate, 0 kg/ha; irrigation management, FLD and for 2016 were: N rate, 60 kg/ha; irrigation management, FLD.
+Four MCMC chains were run for 55,000 steps, with the first 5000 discarded as burn in.
+The remaining 50,000 samples were thinned by taking every tenth sample resulting in 5,000 independent draws from the posterior distribution of the parameters of the model.
+The `coda` [@coda2006] package was used to provide utilities to check convergence using visual inspection of graphs and the Gelman-Rubin test.
+All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
 
@@
 
-## Data and Code Availability
-
-All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
-
 ## Acknowledgments {-}
@@
 
-```
-
-##### pagebreak
-
-```{r MCMC-table}
-MCMC_table <- readRDS("../data/derived_data/MCMC_table.Rds")
-kable(MCMC_table,
-      caption = "MCMC fit")
 ```

### 2018-04-29 R/mcmc_table.R
Remove mcmc_table

@@ -1,32 +1,0 @@
-
-#' @title MCMCglmm results table
-#'
-#' @description Generate a table of MCMCglmm results
-#'
-#' @export
-#' @name mcmc_table
-#' @param x An MCMCglmm model
-#'
-#' @examples \dontrun{
-#' mcmc_table(MCMC_model)
-#' }
-#'
-#' @author Adam H Sparks, \email{adamhsparks@gmail.com}
-
-mcmc_table <- function(x) {
-  sols <- summary(x)$solutions[-1, -4]
-  sols[, c(1:3)] <- round(sols[, c(1:3)], 3)
-
-  Predictors <- row.names(sols)
-  DIC <- c(round(x$DIC, 2), rep(" ", nrow(sols) - 1))
-
-  y <- data.frame(Predictors, sols, DIC)
-  names(y) <- c("Predictors",
-                "Post Mean",
-                "Lower 95% CI",
-                "Upper 95% CI",
-                "P MCMC",
-                "DIC")
-  row.names(y) <- NULL
-  return(y)
-}

### 2018-04-29 analysis/paper/paper.Rmd
Use ggplot2 theme_classic()

@@
        shape = "Irrigation") +
-  theme_bw() +
+  theme_classic() +
   theme(panel.grid.major = element_blank(),
@@
        shape = "N Rate") +
-  theme_bw() +
+  theme_classic() +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Tiller Incidence AUDPS") +
-  theme_bw() +
+  theme_classic() +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Tiller Severity AUDPS") +
-  theme_bw() +
+  theme_classic() +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Leaf Severity AUDPS") +
-  theme_bw() +
+  theme_classic() +
   theme(panel.grid.major = element_blank(),

### 2018-04-29 R/plot_estimates.R
Correct spelling in documentation

@@ -2,7 +2,7 @@
 #' @title Plot MCMCglmm estimates
 #'
 #' @description Plot estimates of posterior distributions and credible
-#'  intervales of MCMCglmm outputs
+#'  intervals of MCMCglmm outputs
 #'
 #' @name plot_estimates
 #' @param x An\code{\link[coda]{mcmc.list}} object

### 2018-04-29 data-raw/README.Rmd
Remove TRT from data
The interaction of irrigation and N management are not analysed. remove from data

@@
 
-  x <- dplyr::arrange(x, REP, TRT)
+  x <- dplyr::arrange(x, REP, WMGT, NRTE)
 
@@
     x %>% dplyr::select(REP,
-                        TRT,
                         WMGT,
@@
       dplyr::select(
-        TRT,
         REP,
@@
 
-    names(y)[7] <- "TIL"
-    names(y)[8] <- "GL"
-    names(y)[9] <- "DL"
-    names(y)[10] <- "TIL_ShB"
+    names(y)[6] <- "TIL"
+    names(y)[7] <- "GL"
+    names(y)[8] <- "DL"
+    names(y)[9] <- "TIL_ShB"
 
@@
 
-# Add treatment numbers --------------------------------------------------------
-DS2015$TRT <- NA
-DS2015$TRT[which(DS2015$WMGT == "FLD" &
-                   DS2015$NRTE == 0)] = "FLD_N0"
-DS2015$TRT[which(DS2015$WMGT == "FLD" &
-                   DS2015$NRTE == 100)] = "FLD_N100"
-DS2015$TRT[which(DS2015$WMGT == "FLD" &
-                   DS2015$NRTE == 120)] = "FLD_N120"
-DS2015$TRT[which(DS2015$WMGT == "AWD" &
-                   DS2015$NRTE == 0)] = "AWD_N0"
-DS2015$TRT[which(DS2015$WMGT == "AWD" &
-                   DS2015$NRTE == 100)] = "AWD_N100"
-DS2015$TRT[which(DS2015$WMGT == "AWD" &
-                   DS2015$NRTE == 120)] = "AWD_N120"
-
 DS2015$YEAR <- lubridate::year(DS2015$DATE)
@@
     PLOT,
-    TRT,
     SMPL,
@@
 ```{r}
+
 # Preprocess 2016 data for all assessments
@@
 
-# Add treatment numbers --------------------------------------------------------
-DS2016$TRT <- NA
-DS2016$TRT[which(DS2016$WMGT == "FLD" &
-                   DS2016$NRTE == 60)] = "FLD_N60"
-DS2016$TRT[which(DS2016$WMGT == "FLD" &
-                   DS2016$NRTE == 180)] = "FLD_N180"
-DS2016$TRT[which(DS2016$WMGT == "AWD" &
-                   DS2016$NRTE == 60)] = "AWD_N60"
-DS2016$TRT[which(DS2016$WMGT == "AWD" &
-                   DS2016$NRTE == 180)] = "AWD_N180"
-
 DS2016 <-
@@
     -PLOT,
-    -TRT,
     -REP,
@@
   DS2016 %>%
-  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
+  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, WMGT, NRTE, SMPL, HILL) %>%
   dplyr::mutate(TShB_incidence = NTShB / NTIL)
@@
 RAW_data$REP <- factor(RAW_data$REP)
-RAW_data$TRT <- factor(RAW_data$TRT)
 RAW_data$WMGT <- factor(RAW_data$WMGT)
@@
 
-RAW_data$TRT <-
+RAW_data$WMGT <-
   forcats::fct_relevel(
-    RAW_data$TRT,
-    "AWD_N0",
-    "AWD_N100",
-    "AWD_N120",
-    "AWD_N60",
-    "AWD_N180",
-    "FLD_N0",
-    "FLD_N100",
-    "FLD_N120",
-    "FLD_N60",
-    "FLD_N180"
+    RAW_data$WMGT,
+    "AWD",
+    "FLD"
   )
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAYS) %>%
   dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
+  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
   dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
@@
   agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
-                   dates = dplyr::pull(TShB_inc_15[1:5, 6]))
+                   dates = dplyr::pull(TShB_inc_15[1:5, 8]))
 
@@
   agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
-                   dates = dplyr::pull(TShB_sev_15[1:5, 6]))
+                   dates = dplyr::pull(TShB_sev_15[1:5, 8]))
 
@@
   agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
-                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))
+                   dates = dplyr::pull(LShB_sev_15[1:5, 8]))
 
@@
   agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
-        dates = dplyr::pull(TShB_perc_15[1:5, 6]))
+        dates = dplyr::pull(TShB_perc_15[1:5, 8]))
 
@@
   agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
-        dates = dplyr::pull(LShB_perc_15[1:5, 6]))
+        dates = dplyr::pull(LShB_perc_15[1:5, 8]))
 
@@
   DS2016 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  dplyr::group_by(YEAR, REP, WMGT, NRTE, PLOT, ASMT, DAI, DAYS) %>%
   dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
@@
   agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
-                   dates = dplyr::pull(TShB_inc_16[1:4, 6]))
+                   dates = dplyr::pull(TShB_inc_16[1:4, 8]))
 
@@
   agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
-                   dates = dplyr::pull(TShB_sev_16[1:4, 6]))
+                   dates = dplyr::pull(TShB_sev_16[1:4, 8]))
 
@@
   agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
-                   dates = dplyr::pull(LShB_sev_16[1:4, 6]))
+                   dates = dplyr::pull(LShB_sev_16[1:4, 8]))
 
@@
   agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
-                   dates = dplyr::pull(TShB_perc_16[1:4, 6]))
+                   dates = dplyr::pull(TShB_perc_16[1:4, 8]))
 
@@
   agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
-                   dates = dplyr::pull(LShB_perc_16[1:4, 6]))
+                   dates = dplyr::pull(LShB_perc_16[1:4, 8]))
 
@@
 AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))
-AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
-                         sep = "_",
-                         into = c("WMGT", "NRTE"))
-AUDPS <- dplyr::mutate_at(.tbl = AUDPS,
-                              .funs = factor,
-                              .vars = c("WMGT", "NRTE"))
+
+# Arrange NRTE values
+AUDPS$NRTE <-
+  forcats::fct_relevel(AUDPS$NRTE,
+                       "0",
+                       "100",
+                       "120",
+                       "60",
+                       "180")
 
@@
 
-row.names(N_rates) <- c("N0", "N100", "N120", "N60", "N180")
+row.names(N_rates) <- c("0", "100", "120", "60", "180")
 

### 2018-04-29 R/plot_estimates.R
Format plots to match other plot styles

@@ -17,8 +17,9 @@
 #' @export
 plot_estimates <- function(x) {
   par(mfrow = c(1, 1))
-  if (class(x) != "summary.mcmc")
+  if (class(x) != "summary.mcmc") {
     x <- summary(x)
+  }
   n <- dim(x$statistics)[1]
   par(mar = c(2, 7, 4, 1))
   plot(
@@ -28,9 +29,10 @@ plot_estimates <- function(x) {
     ylab = "",
     xlim = range(x$quantiles) * 1.2,
     pch = 19,
-    main = "Posterior means and 95% credible intervals"
+    main = "Posterior means and 95% credible intervals",
+    bty = "L"
   )
-  axis(2, at = n:1, rownames(x$statistics), las = 2)
+  axis(side = 2, at = n:1, rownames(x$statistics), las = 2)
   arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
   abline(v = 0, lty = 2)
 }

### 2018-04-30 R/plot_estimates_paper.R
Add function to generate estimates and 95%CI for paper

@@ -6,6 +6,7 @@
 #'
 #' @name plot_estimates_paper
 #' @param x An\code{\link[coda]{mcmc.list}} object
+#' @param main_title Main title for the plot
 #'
 #' @examples \dontrun{
 #' # Plot posterior means and credible intervals
@@ -15,26 +16,23 @@
 #' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
 #'
 #' @export
-plot_estimates_paper <- function(x) {
-  par(mfrow = c(1, 1))
+plot_estimates_paper <- function(x, main_title = "") {
   if (class(x) != "summary.mcmc") {
     x <- summary(x)
   }
-  z <- x$statistics[-1, ]
-  zz <- x$quantiles[-1, ]
-  n <- dim(z)[1]
-  par(mar = c(2, 7, 3, 1))
+  n <- dim(x$statistics)[1]
+  par(mar = c(2, 8, 3, 1))
   plot(
-    z[, 1],
+    x$statistics[, 1],
     n:1,
     yaxt = "n",
     ylab = "",
     xlim = range(x$quantiles) * 1.2,
     pch = 19,
-    main = "",
+    main = main_title,
     bty = "L"
   )
-  axis(side = 2, at = n:1, rownames(z), las = 2)
-  arrows(zz[, 1], n:1, zz[, 5], n:1, code = 0)
+  axis(side = 2, at = n:1, rownames(x$statistics), las = 2)
+  arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
   abline(v = 0, lty = 2)
 }

### 2018-04-30 analysis/paper/paper.Rmd
Add new figure for estimates/95%CI

--- 2018-04-29 analysis/paper/paper.Rmd
@@
 library(bookdown)
+library(coda)
 library(knitr)
@@
                                          linetype = "solid"),
-        axis.title.x = element_blank())
+        axis.title.x = element_blank(),
+        strip.background = element_blank())
 
@@
         legend.position = "none",
-        axis.title.x = element_blank(),)
+        axis.title.x = element_blank(),
+        strip.background = element_blank(),
+        strip.text.x = element_blank())
 
@@
         axis.line = element_line(colour = "black"),
-        legend.position = "none")
+        legend.position = "none",
+        strip.background = element_blank(),
+        strip.text.x = element_blank())
 
@@
                                          linetype = "solid"),
-        axis.title.x = element_blank()) +
+        axis.title.x = element_blank(),
+        strip.background = element_blank()) +
   guides(linetype = guide_legend(ncol = 2),
@@
         axis.line = element_line(colour = "black"),
-        axis.title.x = element_blank()) +
+        axis.title.x = element_blank(),
+        strip.background = element_blank()) +
   facet_grid(. ~ YEAR,
@@
         axis.line = element_line(colour = "black"),
-        axis.title.x = element_blank()) +
+        axis.title.x = element_blank(),
+        strip.background = element_blank(),
+        strip.text.x = element_blank()) +
   facet_grid(. ~ YEAR,
@@
   ylab("Leaf Severity AUDPS") +
-  theme_bw() +
+  theme_classic() +
   theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
+        axis.line = element_line(colour = "black"),
+        strip.background = element_blank(),
+        strip.text.x = element_blank()) +
   facet_grid(. ~ YEAR,
@@
 grid.arrange(p10, p11, p12, ncol = 1, nrow = 3)
+```
+
+##### Estimates plot
+
+```{r estimates-plot, fig.cap="A forest plot of 95% confidence intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE).
+Five different nitrogen treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+
+models <- readRDS("../data/derived_data/models.Rds")
+
+par(mfcol = c(3, 2))
+
+plot_estimates_paper(models[[1]], main_title = "2015")
+mtext("Tiller Incidence", side = 2, line = 6)
+
+plot_estimates_paper(models[[2]])
+mtext("Tiller Severity", side = 2, line = 6)
+
+plot_estimates_paper(models[[3]])
+mtext("Leaf Severity", side = 2, line = 6)
+
+plot_estimates_paper(models[[4]], main_title = "2016")
+
+plot_estimates_paper(models[[5]])
+
+plot_estimates_paper(models[[6]])
+
 ```

### 2018-05-01 R/plot_estimates_paper.R
Clean up axis names for graph in ms

@@ -18,7 +18,7 @@
 #' @export
 plot_estimates_paper <- function(x, main_title = "") {
   if (class(x) != "summary.mcmc") {
-    x <- summary(x)
+    x <- coda:::summary.mcmc.list(x)
   }
   n <- dim(x$statistics)[1]
   par(mar = c(2, 8, 3, 1))
@@ -32,7 +32,12 @@ plot_estimates_paper <- function(x, main_title = "") {
     main = main_title,
     bty = "L"
   )
-  axis(side = 2, at = n:1, rownames(x$statistics), las = 2)
+
+  # extract treatment names and clean them up for the graph
+  trt_names <- substr(rownames(x$statistics)[-1], 5, nchar(x$statistics)[-1])
+  axis_names <- c("(Intercept)", trt_names)
+
+  axis(side = 2, at = n:1, axis_names, las = 2)
   arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
   abline(v = 0, lty = 2)
 }

### 2018-05-01 R/plot_estimates.R
specify coda package's summary function

@@ -18,7 +18,7 @@
 plot_estimates <- function(x) {
   par(mfrow = c(1, 1))
   if (class(x) != "summary.mcmc") {
-    x <- summary(x)
+    x <- coda:::summary.mcmc.list(x)
   }
   n <- dim(x$statistics)[1]
   par(mar = c(2, 7, 3, 1))

### 2018-05-01 analysis/paper/paper.Rmd
Several fixes and edits to paper
- Remove coda from libraries, should be called in functions from package, not here

- Add agricolae to citations

- Update figure references

- Add IRRI Biometrics group to list of people thanked

- Make years bold at top of ggplot2 graphs

- FIX the issue with the severity graphs showing the wrong percent values

- Correct figure references to follow same convention throughout

- Fix Posterior means figure caption

@@
 library(bookdown)
-library(coda)
 library(knitr)
@@
 
-Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity.
+Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using the R package `agricolae` [@R2018; @deMendiburu2017].
 Because the severity data were collected on an unevenly spaced categorical scale, they were converted to the midpoint value of the percent range.
 
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@R2018; @MCMCglmm2010].
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@MCMCglmm2010].
 Six models were created where the the dependent variables were 2015 tiller ShB incidence, 2015 tiller ShB severity, 2015 leaf ShB severity; 2016 tiller ShB incidence, 2016 tiller ShB severity; 2016 leaf ShB severity, respectively.
@@
 
-In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N120, flooded treatment (Figure \@ref(fig:figure-1)).
-The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Figure \@ref(fig:TShB-N-inc)).
-However, water management was not significantly different (Figure \@ref(fig:TShB-W-inc)).
+In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N120 treatment (Figure \@ref(fig:ShB-N-progress)).
+The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Figure \@ref(fig:TShB-N-inc; fig:estimates-plot)).
+However, water management was not significantly different (Figure \@ref(fig:TShB-W-inc; fig:estimates-plot)).
 
@@
 
-Tiller ShB severity remained below 2% (Figure \@ref(fig:figure-2)).
-Both the N100 and N120 treatments were significantly different than the control N0 treatment (Figure \@ref(fig:TShB-N-sev)).
-However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:TShB-w-sev)).
+Tiller ShB severity remained below 2% (Figure \@ref(fig:fig:ShB-N-progress; fig:fig:ShB-W-progress)).
+Both the N100 and N120 treatments were significantly different than the control N0 treatment (Figure \@ref(fig:N-sev; fig:estimates-plot)).
+However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:TShB-w-sev; fig:estimates-plot)).
 
@@
 
-Severity of leaf ShB remained low, less than 0.4% across all treatments (Figure \@ref(fig:figure-3))).
-Both the N100 and N120 treatments were significantly different than the N0 treatment (Figure \@ref(fig:LShB-N-sev)).
-However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:LShB-W-sev)).
+Severity of leaf ShB remained low, less than 0.4% across all treatments (Figure \@ref(fig:ShB-W-progress; fig:ShB-N-progress))).
+Both the N100 and N120 treatments were significantly different than the N0 treatment (Figure \@ref(fig:ShB-N-box; fig:estimates-plot)).
+However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:ShB-W-box; fig:estimates-plot)).
 
@@
 
-The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180, flooded treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:figure-1)).
-The nitrogen treatment N180, was significantly different than the control N60 treatment (Figure \@ref(fig:TShB-N-inc)).
-As in the 2015 study, water management did not significantly differ \@ref(fig:TShB-W-inc)).
+The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:ShB-N-progress)).
+The nitrogen treatment N180, was significantly different than the control N60 treatment (Figure \@ref(fig:ShB-N-box; fig:estimates-plot)).
+As in the 2015 study, water management did not significantly differ \@ref(fig:ShB-W-box; fig:estimates-plot)).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded
-In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:TShB-N-sev)).
-The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:TShB-W-sev)).
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Figure \@ref(fig:ShB-N-progress). 
+In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:ShB-N-box; fig:estimates-plot)).
+The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:ShB-W-box; fig:estimates-plot)).
 
@@
 
-In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:LShB-W-sev), \@ref(fig:LShB-N-sev)).
+In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:ShB-W-box; fig:estimates-plot), \@ref(fig:ShB-N-box; fig:estimates-plot)).
 
@@
 In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology.
-In only one instance were we able to detect any effect of AWD on ShB (Figure \@ref(fig:TShB-sev)).
+In only one instance were we able to detect any effect of AWD on ShB (Figure \@ref(fig:estimates-plot)).
 In the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on tiller ShB severity.
 
-The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Figure \@ref(fig:TShB-inc)).
+The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Figure \@ref(fig:ShB-W-progress; fig:ShB-N-progress)).
 
@@
 
-The authors wish to thank Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
+The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
 We would also like to thank Dale Amozola, Paul Escandor and P.
@@
         axis.title.x = element_blank(),
-        strip.background = element_blank())
+        strip.background = element_blank(),
+        strip.text.x = element_text(face = "bold"))
 
@@
                geom = "point") +
-  scale_y_continuous(labels = function(x) paste0(x*100),
-                     limits = c(0, 1),
-                     name = "Tiller Severity (%)") +
+  scale_y_continuous(name = "Tiller Severity (%)") +
   xlab("Days After Inoculation") +
@@
                geom = "point") +
-  scale_y_continuous(labels = function(x) paste0(x*100),
-                     limits = c(0, 1),
-                     name = "Leaf Severity (%)") +
+  scale_y_continuous(name = "Leaf Severity (%)") +
   xlab("Days After Inoculation") +
@@
 
-##### Tiller ShB N progress
+##### ShB N progress
 
@@
         axis.title.x = element_blank(),
-        strip.background = element_blank()) +
+        strip.background = element_blank(),
+        strip.text.x = element_text(face = "bold")) +
   guides(linetype = guide_legend(ncol = 2),
@@
                geom = "point") +
-  scale_y_continuous(labels = function(x) paste0(x*100),
-                     limits = c(0, 1),
-                     name = "Tiller Severity (%)") +
+  scale_y_continuous(name = "Tiller Severity (%)") +
   facet_grid(. ~ YEAR,
@@
 
-```{r ShB-W-inc, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+```{r ShB-W-box, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
@@
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+
 p7 <- ggplot(AUDPS,
@@
         axis.title.x = element_blank(),
-        strip.background = element_blank()) +
+        strip.background = element_blank(),
+        strip.text.x = element_text(face = "bold")) +
   facet_grid(. ~ YEAR,
@@
 
-```{r ShB-N-sev, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+```{r ShB-N-box, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
@@
 
-```{r estimates-plot, fig.cap="A forest plot of 95% confidence intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE).
+```{r estimates-plot, fig.cap="Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE) on sheath blight tiller incidence, tiller severity and leaf severity.
 Five different nitrogen treatments were applied to split plots depending on the experiment.

### 2018-05-01 analysis/paper/paper.Rmd
Add labels to plots and fix more references to plots

@@
 
-In 2015 the incidence of tiller ShB remained low throughout the growing season only reaching 15% in 2015 in the N120 treatment (Figure \@ref(fig:ShB-N-progress)).
-The nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Figure \@ref(fig:TShB-N-inc; fig:estimates-plot)).
-However, water management was not significantly different (Figure \@ref(fig:TShB-W-inc; fig:estimates-plot)).
+In 2015 the incidence of tiller ShB remained low throughout the growing season (Figure \@ref(fig:ShB-W-progress)a, \@ref(fig:ShB-N-progress)a).
+Water management was not significantly different (Figure \@ref(fig:ShB-W-box)a, \@ref(fig:estimates-plot)a).
+However, the nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Figure \@ref(fig:ShB-N-box)a, \@ref(fig:estimates-plot)a).
 
@@
 
-Tiller ShB severity remained below 2% (Figure \@ref(fig:fig:ShB-N-progress; fig:fig:ShB-W-progress)).
-Both the N100 and N120 treatments were significantly different than the control N0 treatment (Figure \@ref(fig:N-sev; fig:estimates-plot)).
-However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:TShB-w-sev; fig:estimates-plot)).
+Tiller ShB severity remained below 2% (Figure \@ref(fig:ShB-N-progress)c, \@ref(fig:ShB-W-progress)c).
+Both the N100 and N120 treatments were significantly different than the control N0 treatment (Figure \@ref(fig:ShB-N-box)c, \@ref(fig:estimates-plot)c).
+However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:ShB-W-box)c, \@ref(fig:estimates-plot)c).
 
@@
 
-Severity of leaf ShB remained low, less than 0.4% across all treatments (Figure \@ref(fig:ShB-W-progress; fig:ShB-N-progress))).
-Both the N100 and N120 treatments were significantly different than the N0 treatment (Figure \@ref(fig:ShB-N-box; fig:estimates-plot)).
-However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:ShB-W-box; fig:estimates-plot)).
+Severity of leaf ShB remained low, less than 0.4% across all treatments (Figure \@ref(fig:ShB-W-progress)e, \@ref(fig:ShB-N-progress)e).
+Both the N100 and N120 treatments were significantly different than the N0 treatment (Figure \@ref(fig:ShB-N-box)e, \@ref(fig:estimates-plot)e).
+However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:ShB-W-box)e, \@ref(fig:estimates-plot)e).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:ShB-N-progress)).
-The nitrogen treatment N180, was significantly different than the control N60 treatment (Figure \@ref(fig:ShB-N-box; fig:estimates-plot)).
-As in the 2015 study, water management did not significantly differ \@ref(fig:ShB-W-box; fig:estimates-plot)).
+The nitrogen treatment N180, was significantly different than the control N60 treatment (Figure \@ref(fig:ShB-N-box), \@ref(fig:estimates-plot)).
+As in the 2015 study, water management did not significantly differ \@ref(fig:ShB-W-box), \@ref(fig:estimates-plot)).
 
@@
 As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Figure \@ref(fig:ShB-N-progress). 
-In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:ShB-N-box; fig:estimates-plot)).
-The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:ShB-W-box; fig:estimates-plot)).
+In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:ShB-N-box), \@ref(fig:estimates-plot)).
+The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:ShB-W-box), \@ref(fig:estimates-plot)).
 
@@
 
-In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:ShB-W-box; fig:estimates-plot), \@ref(fig:ShB-N-box; fig:estimates-plot)).
+In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:ShB-W-box), \@ref(fig:estimates-plot), \@ref(fig:ShB-N-box) \@ref(fig:estimates-plot)).
 
@@
 In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology.
-In only one instance were we able to detect any effect of AWD on ShB (Figure \@ref(fig:estimates-plot)).
-In the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment, which may indicate a possible adverse effect of using AWD on tiller ShB severity.
+In only one instance were we able to detect any effect of AWD on ShB (Figure \@ref(fig:estimates-plot)), where in the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment.
+This may may indicate a possible adverse effect of using AWD on tiller ShB severity.
 
-The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Figure \@ref(fig:ShB-W-progress; fig:ShB-N-progress)).
+The effects of N rates on sheath blight were to be expected, where higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
+However, in 2016 tiller and leaf severity had no detectable differences due to the N rate.
+
+The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Figures \@ref(fig:ShB-W-progress), \@ref(fig:ShB-N-progress), \@ref(fig:ShB-W-box), \@ref(fig:ShB-N-box)).
+The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
+It is possible that the mechanical transplanter could increase ShB spread in the canopy as compared with traditional manual transplanting.
+This however was not investigated as a part of this study but could bear further research.
 
@@
 
-p1 <- ggplot(RAW_data,
-       aes(x = DAI,
-           y = TShB_incidence,
-           group = WMGT,
-           shape = WMGT,
+p1_anot <- data.frame(
+  label = c("a", "b"),
+  YEAR   = c(2015, 2016),
+  x = c(60, 60),
+  y = c(1, 1)
+)
+
+p1 <- ggplot(data = RAW_data,
+             aes(
+               x = DAI,
+               y = TShB_incidence
+             )) +
+  geom_text(
+    data = p1_anot,
+     mapping = aes(x = x,
+                   y = y,
+                   label = label)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = WMGT,
                linetype = WMGT)) +
   stat_summary(fun.y = "mean",
-               geom = "line") +
-  stat_summary(fun.y = "mean",
-               geom = "point") +
-  scale_y_continuous(labels = function(x) paste0(x*100),
+               geom = "point",
+               aes(group = WMGT,
+               shape = WMGT)) +
+  scale_y_continuous(
+    labels = function(x)
+      paste0(x * 100),
     limits = c(0, 1),
-                     name = "Tiller Incidence (%)") +
+    name = "Tiller Incidence (%)"
+  ) +
   xlab("Days After Inoculation") +
@@
   theme_classic() +
-  theme(panel.grid.major = element_blank(),
+  theme(
+    panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  theme(panel.grid.major = element_blank(),
+    axis.line = element_line(colour = "black")
+  ) +
+  theme(
+    panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
@@
     legend.position = c(x = 0.065, y = 0.76),
-        legend.background = element_rect(color = "black", 
+    legend.background = element_rect(
+      color = "black",
       size = 0.5,
-                                         linetype = "solid"),
+      linetype = "solid"
+    ),
     axis.title.x = element_blank(),
     strip.background = element_blank(),
-        strip.text.x = element_text(face = "bold"))
+    strip.text.x = element_text(face = "bold")
+  )
+
+p2_anot <- data.frame(
+  label = c("c", "d"),
+  YEAR   = c(2015, 2016),
+  x = c(60, 60),
+  y = c(10, 10)
+)
 
@@
              aes(x = DAI,
-                 y = PERC_TIL_ShB,
-                 group = WMGT,
-                 shape = WMGT,
+                 y = PERC_TIL_ShB)) +
+  geom_text(
+    data = p2_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = WMGT,
                    linetype = WMGT)) +
   stat_summary(fun.y = "mean",
-               geom = "line") +
-  stat_summary(fun.y = "mean",
-               geom = "point") +
+               geom = "point",
+               aes(group = WMGT,
+                   shape = WMGT)) +
   scale_y_continuous(name = "Tiller Severity (%)") +
@@
 
+p3_anot <- data.frame(
+  label = c("e", "f"),
+  YEAR   = c(2015, 2016),
+  x = c(60, 60),
+  y = c(10, 10)
+)
+
 p3 <- ggplot(RAW_data,
              aes(x = DAI,
-                 y = PERC_LEAF_ShB,
-                 group = WMGT,
-                 shape = WMGT,
+                 y = PERC_LEAF_ShB)) +
+  geom_text(
+    data = p3_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = WMGT,
                    linetype = WMGT)) +
   stat_summary(fun.y = "mean",
-               geom = "line") +
-  stat_summary(fun.y = "mean",
-               geom = "point") +
+               geom = "point",
+               aes(group = WMGT,
+                   shape = WMGT)) +
   scale_y_continuous(name = "Leaf Severity (%)") +
@@
 
-##### ShB N progress
+##### ShB W progress
 
@@
 
-p4 <- ggplot(RAW_data,
-             aes(x = DAI,
-                 y = TShB_incidence,
-                 group = NRTE,
-                 shape = NRTE,
+p4_anot <- data.frame(
+  label = c("a", "b"),
+  YEAR   = c(2015, 2016),
+  x = c(60, 60),
+  y = c(1, 1)
+)
+
+p4 <- ggplot(data = RAW_data,
+             aes(
+               x = DAI,
+               y = TShB_incidence
+             )) +
+  geom_text(
+    data = p4_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = NRTE,
                    linetype = NRTE)) +
   stat_summary(fun.y = "mean",
-               geom = "line") +
-  stat_summary(fun.y = "mean",
-               geom = "point") +
-  scale_y_continuous(labels = function(x) paste0(x*100),
+               geom = "point",
+               aes(group = NRTE,
+                   shape = NRTE)) +
+  scale_y_continuous(
+    labels = function(x)
+      paste0(x * 100),
     limits = c(0, 1),
-                     name = "Tiller Incidence (%)") +
+    name = "Tiller Incidence (%)"
+  ) +
+  xlab("Days After Inoculation") +
   facet_grid(. ~ YEAR,
              scales = "free_x") +
-  labs(linetype = "N Rate",
-       shape = "N Rate") +
+  labs(linetype = "Irrigation",
+       shape = "Irrigation") +
   theme_classic() +
-  theme(panel.grid.major = element_blank(),
+  theme(
+    panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
-        axis.line = element_line(colour = "black")) +
-  theme(panel.grid.major = element_blank(),
+    axis.line = element_line(colour = "black")
+  ) +
+  theme(
+    panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"),
-        legend.position = c(x = 0.095, y = 0.69),
-        legend.background = element_rect(color = "black", 
+    legend.position = c(x = 0.065, y = 0.76),
+    legend.background = element_rect(
+      color = "black",
       size = 0.5,
-                                         linetype = "solid"),
+      linetype = "solid"
+    ),
     axis.title.x = element_blank(),
     strip.background = element_blank(),
-        strip.text.x = element_text(face = "bold")) +
-  guides(linetype = guide_legend(ncol = 2),
-         shape = guide_legend(ncol = 2))
+    strip.text.x = element_text(face = "bold")
+  )
+
+p5_anot <- data.frame(
+  label = c("c", "d"),
+  YEAR   = c(2015, 2016),
+  x = c(60, 60),
+  y = c(10, 10)
+)
 
@@
              aes(x = DAI,
-                 y = PERC_TIL_ShB,
-                 group = NRTE,
-                 shape = NRTE,
+                 y = PERC_TIL_ShB)) +
+  geom_text(
+    data = p5_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = NRTE,
                    linetype = NRTE)) +
   stat_summary(fun.y = "mean",
-               geom = "line") +
-  stat_summary(fun.y = "mean",
-               geom = "point") +
+               geom = "point",
+               aes(group = NRTE,
+                   shape = NRTE)) +
   scale_y_continuous(name = "Tiller Severity (%)") +
+  xlab("Days After Inoculation") +
   facet_grid(. ~ YEAR,
              scales = "free_x") +
-  labs(linetype = "N Rate",
-       shape = "N Rate") +
+  labs(linetype = "Irrigation",
+       shape = "Irrigation") +
   theme_classic() +
@@
 
+p6_anot <- data.frame(
+  label = c("e", "f"),
+  YEAR   = c(2015, 2016),
+  x = c(60, 60),
+  y = c(10, 10)
+)
+
 p6 <- ggplot(RAW_data,
              aes(x = DAI,
-                 y = PERC_LEAF_ShB,
-                 group = NRTE,
-                 shape = NRTE,
+                 y = PERC_LEAF_ShB)) +
+  geom_text(
+    data = p6_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
+  stat_summary(fun.y = "mean",
+               geom = "line",
+               aes(group = NRTE,
                    linetype = NRTE)) +
   stat_summary(fun.y = "mean",
-               geom = "line") +
-  stat_summary(fun.y = "mean",
-               geom = "point") +
+               geom = "point",
+               aes(group = NRTE,
+                   shape = NRTE)) +
   scale_y_continuous(name = "Leaf Severity (%)") +
@@
              scales = "free_x") +
-  labs(linetype = "N Rate",
-       shape = "N Rate") +
+  labs(linetype = "Irrigation",
+       shape = "Irrigation") +
   theme_classic() +
@@
 
+p7_anot <- data.frame(
+  label = c("a", "b"),
+  YEAR   = c(2015, 2016),
+  x = c(2.5, 2.5),
+  y = c(15, 15)
+)
+
 p7 <- ggplot(AUDPS,
@@
   geom_boxplot() +
+  geom_text(
+    data = p7_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
   ylab("Tiller Incidence AUDPS") +
@@
 
+p8_anot <- data.frame(
+  label = c("c", "d"),
+  YEAR   = c(2015, 2016),
+  x = c(2.5, 2.5),
+  y = c(32, 32)
+)
+
 p8 <- ggplot(AUDPS,
@@
   geom_boxplot() +
+  geom_text(
+    data = p8_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
   ylab("Tiller Severity AUDPS") +
@@
 
+p9_anot <- data.frame(
+  label = c("e", "f"),
+  YEAR   = c(2015, 2016),
+  x = c(2.5, 2.5),
+  y = c(10, 10)
+)
+
 p9 <- ggplot(AUDPS,
@@
   geom_boxplot() +
+  geom_text(
+    data = p9_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
   xlab("Treatment") +
@@
 In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+
+p10_anot <- data.frame(
+  label = c("a", "b"),
+  YEAR   = c(2015, 2016),
+  x = c(3.5, 2.5),
+  y = c(14, 14)
+)
+
 p10 <- ggplot(AUDPS,
@@
   geom_boxplot() +
-  xlab("Treatment") +
+  geom_text(
+    data = p10_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
   ylab("Tiller Incidence AUDPS") +
@@
 
+p11_anot <- data.frame(
+  label = c("c", "d"),
+  YEAR   = c(2015, 2016),
+  x = c(3.5, 2.5),
+  y = c(32, 32)
+)
+
 p11 <- ggplot(AUDPS,
-              aes(x = NRTE, y = TShB_percent_AUDPS)) +
+             aes(x = NRTE, y = TShB_sev_AUDPS)) +
   geom_boxplot() +
+  geom_text(
+    data = p11_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
   ylab("Tiller Severity AUDPS") +
@@
 
+p12_anot <- data.frame(
+  label = c("e", "f"),
+  YEAR   = c(2015, 2016),
+  x = c(3.5, 2.5),
+  y = c(7, 7)
+)
+
 p12 <- ggplot(AUDPS,
-              aes(x = NRTE, y = LShB_percent_AUDPS)) +
+             aes(x = NRTE, y = LShB_sev_AUDPS)) +
   geom_boxplot() +
+  geom_text(
+    data = p12_anot,
+    mapping = aes(x = x,
+                  y = y,
+                  label = label)) +
   xlab("Treatment") +
@@
 mtext("Tiller Incidence", side = 2, line = 6)
+mtext(side = 3, line = 0, adj = 1, "a", cex = 0.75)
 
@@
 mtext("Tiller Severity", side = 2, line = 6)
+mtext(side = 3, line = 0, adj = 1, "c", cex = 0.75)
 
@@
 mtext("Leaf Severity", side = 2, line = 6)
+mtext(side = 3, line = 0, adj = 1, "e", cex = 0.75)
 
 plot_estimates_paper(models[[4]], main_title = "2016")
+mtext(side = 3, line = 0, adj = 1, "b", cex = 0.75)
 
 plot_estimates_paper(models[[5]])
+mtext(side = 3, line = 0, adj = 1, "d", cex = 0.75)
 
 plot_estimates_paper(models[[6]])
+mtext(side = 3, line = 0, adj = 1, "f", cex = 0.75)
 

### 2018-05-02 analysis/paper/paper.Rmd
Fix Figure 2 legend

@@
              scales = "free_x") +
-  labs(linetype = "Irrigation",
-       shape = "Irrigation") +
+  labs(linetype = "N Rate",
+       shape = "N Rate") +
   theme_classic() +
@@
     panel.grid.minor = element_blank(),
-    axis.line = element_line(colour = "black")
-  ) +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.065, y = 0.76),
+    legend.position = c(x = 0.1,
+                        y = 0.7),
     legend.background = element_rect(
@@
     strip.text.x = element_text(face = "bold")
-  )
+  ) +
+  guides(linetype = guide_legend(ncol = 2),
+         shape = guide_legend(ncol = 2))
 

### 2018-05-02 analysis/paper/paper.Rmd
Clean up graph code for Figure 1

@@
     panel.grid.minor = element_blank(),
-    axis.line = element_line(colour = "black")
-  ) +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"),
@@
              scales = "free_x") +
-  labs(linetype = "Irrigation",
-       shape = "Irrigation") +
   theme_classic() +

### 2018-05-02 analysis/paper/paper.Rmd
Replace "Figure" with "Fig." and reference sub-plots

@@
 
-In 2015 the incidence of tiller ShB remained low throughout the growing season (Figure \@ref(fig:ShB-W-progress)a, \@ref(fig:ShB-N-progress)a).
-Water management was not significantly different (Figure \@ref(fig:ShB-W-box)a, \@ref(fig:estimates-plot)a).
-However, the nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Figure \@ref(fig:ShB-N-box)a, \@ref(fig:estimates-plot)a).
+In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig.
+\@ref(Fig.:ShB-W-progress)a, \@ref(Fig.:ShB-N-progress)a).
+Water management was not significantly different (Fig.
+\@ref(Fig.:ShB-W-box)a, \@ref(Fig.:estimates-plot)a).
+However, the nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
+\@ref(Fig.:ShB-N-box)a, \@ref(Fig.:estimates-plot)a).
 
@@
 
-Tiller ShB severity remained below 2% (Figure \@ref(fig:ShB-N-progress)c, \@ref(fig:ShB-W-progress)c).
-Both the N100 and N120 treatments were significantly different than the control N0 treatment (Figure \@ref(fig:ShB-N-box)c, \@ref(fig:estimates-plot)c).
-However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:ShB-W-box)c, \@ref(fig:estimates-plot)c).
+Tiller ShB severity remained below 2% (Fig.
+\@ref(Fig.:ShB-N-progress)c, \@ref(Fig.:ShB-W-progress)c).
+Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig.
+\@ref(Fig.:ShB-N-box)c, \@ref(Fig.:estimates-plot)c).
+However, the AWD water management was not significantly different from the FLD treatment (Fig.
+\@ref(Fig.:ShB-W-box)c, \@ref(Fig.:estimates-plot)c).
 
@@
 
-Severity of leaf ShB remained low, less than 0.4% across all treatments (Figure \@ref(fig:ShB-W-progress)e, \@ref(fig:ShB-N-progress)e).
-Both the N100 and N120 treatments were significantly different than the N0 treatment (Figure \@ref(fig:ShB-N-box)e, \@ref(fig:estimates-plot)e).
-However, the AWD water management was not significantly different from the FLD treatment (Figure \@ref(fig:ShB-W-box)e, \@ref(fig:estimates-plot)e).
+Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig.
+\@ref(Fig.:ShB-W-progress)e, \@ref(Fig.:ShB-N-progress)e).
+Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig.
+\@ref(Fig.:ShB-N-box)e, \@ref(Fig.:estimates-plot)e).
+However, the AWD water management was not significantly different from the FLD treatment (Fig.
+\@ref(Fig.:ShB-W-box)e, \@ref(Fig.:estimates-plot)e).
 
@@
 
-The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:ShB-N-progress)).
-The nitrogen treatment N180, was significantly different than the control N60 treatment (Figure \@ref(fig:ShB-N-box), \@ref(fig:estimates-plot)).
-As in the 2015 study, water management did not significantly differ \@ref(fig:ShB-W-box), \@ref(fig:estimates-plot)).
+The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig.
+\@ref(Fig.:ShB-N-progress)b).
+The nitrogen treatment N180, was significantly different than the control N60 treatment (Fig.
+\@ref(Fig.:ShB-N-box)b, \@ref(Fig.:estimates-plot)b).
+As in the 2015 study, water management did not significantly differ \@ref(Fig.:ShB-W-box)b, \@ref(Fig.:estimates-plot)b).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Figure \@ref(fig:ShB-N-progress). 
-In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:ShB-N-box), \@ref(fig:estimates-plot)).
-The AWD water management, which was lower than the FLD treatment, was also significantly different (Figure \@ref(fig:ShB-W-box), \@ref(fig:estimates-plot)).
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(Fig.:ShB-N-progress)d). 
+In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig.
+\@ref(Fig.:ShB-N-box)d), \@ref(Fig.:estimates-plot)d).
+The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig.
+\@ref(Fig.:ShB-W-box)d, \@ref(Fig.:estimates-plot)d).
 
@@
 
-In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Figures \@ref(fig:ShB-W-box), \@ref(fig:estimates-plot), \@ref(fig:ShB-N-box) \@ref(fig:estimates-plot)).
+In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
+\@ref(Fig.:ShB-W-box)f, \@ref(Fig.:estimates-plot)f, \@ref(Fig.:ShB-N-box)f \@ref(Fig.:estimates-plot)f).
 
@@
 In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology.
-In only one instance were we able to detect any effect of AWD on ShB (Figure \@ref(fig:estimates-plot)), where in the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment.
+In only one instance were we able to detect any effect of AWD on ShB (Fig.
+\@ref(Fig.:estimates-plot)d), where in the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment.
 This may may indicate a possible adverse effect of using AWD on tiller ShB severity.
@@
 
-The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Figures \@ref(fig:ShB-W-progress), \@ref(fig:ShB-N-progress), \@ref(fig:ShB-W-box), \@ref(fig:ShB-N-box)).
+The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig.
+\@ref(Fig.:ShB-W-progress)a:b, \@ref(Fig.:ShB-N-progress)c:d, \@ref(Fig.:ShB-W-box)a:b, \@ref(Fig.:ShB-N-box)c:d).
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
@@
 plot_estimates_paper(models[[1]], main_title = "2015")
-mtext("Tiller Incidence", side = 2, line = 6)
-mtext(side = 3, line = 0, adj = 1, "a", cex = 0.75)
+mtext(text = "Tiller Incidence", side = 2, line = 6)
+mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
 
 plot_estimates_paper(models[[2]])
-mtext("Tiller Severity", side = 2, line = 6)
-mtext(side = 3, line = 0, adj = 1, "c", cex = 0.75)
+mtext(text = "Tiller Severity", side = 2, line = 6)
+mtext(text = "c", side = 3, line = 0, adj = 1, cex = 0.75)
 
 plot_estimates_paper(models[[3]])
-mtext("Leaf Severity", side = 2, line = 6)
-mtext(side = 3, line = 0, adj = 1, "e", cex = 0.75)
+mtext(text = "Leaf Severity", side = 2, line = 6)
+mtext(text = "e", side = 3, line = 0, adj = 1, cex = 0.75)
 
 plot_estimates_paper(models[[4]], main_title = "2016")
-mtext(side = 3, line = 0, adj = 1, "b", cex = 0.75)
+mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
 
 plot_estimates_paper(models[[5]])
-mtext(side = 3, line = 0, adj = 1, "d", cex = 0.75)
+mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
 
 plot_estimates_paper(models[[6]])
-mtext(side = 3, line = 0, adj = 1, "f", cex = 0.75)
+mtext(text = "f", side = 3, line = 0, adj = 1, cex = 0.75)
 

### 2018-05-02 analysis/paper/paper.Rmd
Replace "nitrogen" with "N"

@@
 [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10\%.
-The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009, @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
+The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009, @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
@@
 
-The plot design was a split-plot design with four replicates where irrigation was the main plot and nitrogen (N) rate was the split-plot.
+The plot design was a split-plot design with four replicates where irrigation was the main plot and N rate was the split-plot.
 
@@
 
-The split-plot treatment rates of nitrogen were N0 (no nitrogen supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Table \@ref(tab:N-rates)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Table \@ref(tab:N-rates)).
 
@@
 
-Split-plot N rates differed from the 2015 rates with only two nitrogen treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Table \@ref(tab:N-rates)).
+Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Table \@ref(tab:N-rates)).
 
@@
 Six models were created where the the dependent variables were 2015 tiller ShB incidence, 2015 tiller ShB severity, 2015 leaf ShB severity; 2016 tiller ShB incidence, 2016 tiller ShB severity; 2016 leaf ShB severity, respectively.
-The independent variables were the irrigation management and nitrogen rate and replicate was treated as a random variable.
+The independent variables were the irrigation management and N rate and replicate was treated as a random variable.
 The base levels (control treatments) for the analyses for 2015 were: N rate, 0 kg/ha; irrigation management, FLD and for 2016 were: N rate, 60 kg/ha; irrigation management, FLD.
@@
 \@ref(Fig.:ShB-W-box)a, \@ref(Fig.:estimates-plot)a).
-However, the nitrogen treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
+However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
 \@ref(Fig.:ShB-N-box)a, \@ref(Fig.:estimates-plot)a).
@@
 \@ref(Fig.:ShB-N-progress)b).
-The nitrogen treatment N180, was significantly different than the control N60 treatment (Fig.
+The N treatment N180, was significantly different than the control N60 treatment (Fig.
 \@ref(Fig.:ShB-N-box)b, \@ref(Fig.:estimates-plot)b).
@@
 
-In 2016 the neither of the treatments, nitrogen rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
+In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
 \@ref(Fig.:ShB-W-box)f, \@ref(Fig.:estimates-plot)f, \@ref(Fig.:ShB-N-box)f \@ref(Fig.:estimates-plot)f).

### 2018-05-02 analysis/paper/paper.Rmd
Replace "Table" with "Tab."

@@
     i <<- i + 1
-    paste('\n\nTable ', i, ': ', x, sep = '')
+    paste('\n\nTab. ', i, ': ', x, sep = '')
     # The : before Table tells pandoc to wrap your caption in <caption></caption>
@@
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Table \@ref(tab:N-rates)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab.
+\@ref(tab:N-rates)).
 
@@
 
-Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Table \@ref(tab:N-rates)).
+Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Tab.
+\@ref(tab:N-rates)).
 

### 2018-05-02 analysis/paper/paper.Rmd
Edits to statistical analysis section for clarity

@@
 Six models were created where the the dependent variables were 2015 tiller ShB incidence, 2015 tiller ShB severity, 2015 leaf ShB severity; 2016 tiller ShB incidence, 2016 tiller ShB severity; 2016 leaf ShB severity, respectively.
-The independent variables were the irrigation management and N rate and replicate was treated as a random variable.
+The independent variables were the irrigation management and N rate with replicate treated as a random variable.
 The base levels (control treatments) for the analyses for 2015 were: N rate, 0 kg/ha; irrigation management, FLD and for 2016 were: N rate, 60 kg/ha; irrigation management, FLD.
-Four MCMC chains were run for 55,000 steps, with the first 5000 discarded as burn in.
+Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn in.
 The remaining 50,000 samples were thinned by taking every tenth sample resulting in 5,000 independent draws from the posterior distribution of the parameters of the model.

### 2018-05-02 analysis/paper/paper.Rmd
Correct "Fig.:" to "fig:"

@@
 In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig.
-\@ref(Fig.:ShB-W-progress)a, \@ref(Fig.:ShB-N-progress)a).
+\@ref(fig:ShB-W-progress)a, \@ref(fig:ShB-N-progress)a).
 Water management was not significantly different (Fig.
-\@ref(Fig.:ShB-W-box)a, \@ref(Fig.:estimates-plot)a).
+\@ref(fig:ShB-W-box)a, \@ref(fig:estimates-plot)a).
 However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
-\@ref(Fig.:ShB-N-box)a, \@ref(Fig.:estimates-plot)a).
+\@ref(fig:ShB-N-box)a, \@ref(fig:estimates-plot)a).
 
@@
 Tiller ShB severity remained below 2% (Fig.
-\@ref(Fig.:ShB-N-progress)c, \@ref(Fig.:ShB-W-progress)c).
+\@ref(fig:ShB-N-progress)c, \@ref(fig:ShB-W-progress)c).
 Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig.
-\@ref(Fig.:ShB-N-box)c, \@ref(Fig.:estimates-plot)c).
+\@ref(fig:ShB-N-box)c, \@ref(fig:estimates-plot)c).
 However, the AWD water management was not significantly different from the FLD treatment (Fig.
-\@ref(Fig.:ShB-W-box)c, \@ref(Fig.:estimates-plot)c).
+\@ref(fig:ShB-W-box)c, \@ref(fig:estimates-plot)c).
 
@@
 Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig.
-\@ref(Fig.:ShB-W-progress)e, \@ref(Fig.:ShB-N-progress)e).
+\@ref(fig:ShB-W-progress)e, \@ref(fig:ShB-N-progress)e).
 Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig.
-\@ref(Fig.:ShB-N-box)e, \@ref(Fig.:estimates-plot)e).
+\@ref(fig:ShB-N-box)e, \@ref(fig:estimates-plot)e).
 However, the AWD water management was not significantly different from the FLD treatment (Fig.
-\@ref(Fig.:ShB-W-box)e, \@ref(Fig.:estimates-plot)e).
+\@ref(fig:ShB-W-box)e, \@ref(fig:estimates-plot)e).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig.
-\@ref(Fig.:ShB-N-progress)b).
+\@ref(fig:ShB-N-progress)b).
 The N treatment N180, was significantly different than the control N60 treatment (Fig.
-\@ref(Fig.:ShB-N-box)b, \@ref(Fig.:estimates-plot)b).
-As in the 2015 study, water management did not significantly differ \@ref(Fig.:ShB-W-box)b, \@ref(Fig.:estimates-plot)b).
+\@ref(fig:ShB-N-box)b, \@ref(fig:estimates-plot)b).
+As in the 2015 study, water management did not significantly differ \@ref(fig:ShB-W-box)b, \@ref(fig:estimates-plot)b).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(Fig.:ShB-N-progress)d). 
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:ShB-N-progress)d). 
 In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig.
-\@ref(Fig.:ShB-N-box)d), \@ref(Fig.:estimates-plot)d).
+\@ref(fig:ShB-N-box)d), \@ref(fig:estimates-plot)d).
 The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig.
-\@ref(Fig.:ShB-W-box)d, \@ref(Fig.:estimates-plot)d).
+\@ref(fig:ShB-W-box)d, \@ref(fig:estimates-plot)d).
 
@@
 In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
-\@ref(Fig.:ShB-W-box)f, \@ref(Fig.:estimates-plot)f, \@ref(Fig.:ShB-N-box)f \@ref(Fig.:estimates-plot)f).
+\@ref(fig:ShB-W-box)f, \@ref(fig:estimates-plot)f, \@ref(fig:ShB-N-box)f \@ref(fig:estimates-plot)f).
 
@@
 In only one instance were we able to detect any effect of AWD on ShB (Fig.
-\@ref(Fig.:estimates-plot)d), where in the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment.
+\@ref(fig:estimates-plot)d), where in the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment.
 This may may indicate a possible adverse effect of using AWD on tiller ShB severity.
@@
 The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig.
-\@ref(Fig.:ShB-W-progress)a:b, \@ref(Fig.:ShB-N-progress)c:d, \@ref(Fig.:ShB-W-box)a:b, \@ref(Fig.:ShB-N-box)c:d).
+\@ref(fig:ShB-W-progress)a:b, \@ref(fig:ShB-N-progress)c:d, \@ref(fig:ShB-W-box)a:b, \@ref(fig:ShB-N-box)c:d).
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].

### 2018-05-02 analysis/paper/paper.Rmd
More edits to statistical analysis section
New para for describing the model runs and checking
Edits to Discussion section

@@
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using the R package `agricolae` [@R2018; @deMendiburu2017].
-Because the severity data were collected on an unevenly spaced categorical scale, they were converted to the midpoint value of the percent range.
+The severity data were converted to the midpoint perctn value of the scale range.
 
@@
 The base levels (control treatments) for the analyses for 2015 were: N rate, 0 kg/ha; irrigation management, FLD and for 2016 were: N rate, 60 kg/ha; irrigation management, FLD.
+
 Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn in.
@@
 In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology.
-In only one instance were we able to detect any effect of AWD on ShB (Fig.
-\@ref(fig:estimates-plot)d), where in the 2016 experiment the tiller ShB severity was significantly lower for AWD than the traditional FLD treatment.
-This may may indicate a possible adverse effect of using AWD on tiller ShB severity.
+In only one instance were we able to detect any effect of AWD on ShB.
+In the 2016 experiment the tiller ShB severity was significantly lower for AWD than FLD (Fig.
+\@ref(fig:ShB-W-box)d, \@ref(fig:estimates-plot)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.
 
-The effects of N rates on sheath blight were to be expected, where higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
+The findings of the effects of N rates on sheath blight were to be expected, where higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
 However, in 2016 tiller and leaf severity had no detectable differences due to the N rate.
+However, it should be noted that the levels of leaf severity remained low (< 1%) throughout the growing season in all treatments for both years.
 

### 2018-05-02 analysis/paper/paper.Rmd
Fix figure cross-refs

@@
 \@ref(fig:ShB-N-box)b, \@ref(fig:estimates-plot)b).
-As in the 2015 study, water management did not significantly differ \@ref(fig:ShB-W-box)b, \@ref(fig:estimates-plot)b).
+As in the 2015 study, water management did not significantly differ (Fig.
+\@ref(fig:ShB-W-box)b, \@ref(fig:estimates-plot)b).
 
@@
 In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig.
-\@ref(fig:ShB-N-box)d), \@ref(fig:estimates-plot)d).
+\@ref(fig:ShB-N-box)d, \@ref(fig:estimates-plot)d).
 The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig.
@@
 In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
-\@ref(fig:ShB-W-box)f, \@ref(fig:estimates-plot)f, \@ref(fig:ShB-N-box)f \@ref(fig:estimates-plot)f).
+\@ref(fig:ShB-W-box)f, \@ref(fig:estimates-plot)f, \@ref(fig:ShB-N-box)f, \@ref(fig:estimates-plot)f).
 

### 2018-05-02 analysis/paper/paper.Rmd
Spell check and clean up list of control/base treatemtns

@@
 
-Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastamosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
+Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastomosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
 Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
@@
 [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10\%.
-The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009, @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
+The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
@@
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using the R package `agricolae` [@R2018; @deMendiburu2017].
-The severity data were converted to the midpoint perctn value of the scale range.
+The severity data were converted to the midpoint percent value of the scale range.
 
@@
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were: N rate, 0 kg/ha; irrigation management, FLD and for 2016 were: N rate, 60 kg/ha; irrigation management, FLD.
+The base levels (control treatments) for the analyses for 2015 were N rate - N0; irrigation management - FLD and for 2016, N rate - N60; irrigation management - FLD.
 

### 2018-05-02 analysis/paper/paper.Rmd
Edits to Data collection for clarity
Also move data collection and statistical analysis up a level in headdings

@@
 
-### Data Collection {-}
+## Data Collection {-}
 
-Two sample areas per plot (1m x 1m) were assessed.
-For nine hills per sample, the total number of tillers per hill and number of tillers with ShB (incidence) were measured.
-Tiller ShB severity was measured for four tillers per hill and six leaves tiller using the rating scale.
+In both experiments, two sample areas, sized 1m x 1m, per plot were assessed.
+the total number of tillers per hill and number of tillers with ShB (incidence) were measured for nine hills per sample area.
+Tiller ShB severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
+The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
+Severity was considered to be the amount of leaf or sheath tissue covered by ShB lesions.
 Leaves were rated as green (living) having at least XXX% living tissue or dead, defined as having less than XXX% living tissue.
+The same rating methodology was used in both experiments.
 Five disease assessments were made in the 2015 experiment and four disease assessments were made in the 2016 experiment, respectively.
 
-Disease rating was the same in both experiments using the same disease assessment scale for field evaluation developed at IRRI where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
-Where severity was considered to be the amount of leaf or sheath tissue covered by ShB lesions.
-
-### Statistical Analysis {-}
+## Statistical Analysis {-}
 
@@
 
-```{r ShB-W-progress, fig.cap="Sheath blight progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+```{r ShB-W-progress, fig.cap="Sheath blight progress for 2015 and 2016 experiments.
+Disease progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).

### 2018-05-02 analysis/paper/paper.Rmd
Edit Acknowledgments

@@
 Lapis for their technical support in the field.
-Lastly, Michael Noel, who helped design and manage the first year of the project but passed away in September 2016.
+Lastly, we would like to remember Michael Noel, who was a part of the plant disease management team at IRRI and who helped design and manage the first year of the project but passed away in September 2016.
 

### 2018-05-02 analysis/paper/paper.Rmd
Replace Table and Figure with "Tab" and "Fig"

@@
 library(bookdown)
+library(captioner)
 library(knitr)
@@
 
-# Tables {-}
+```{r table-caps}
+table_nums <- captioner(prefix = "Tab.")
 
-```{r N-rates}
-kable(N_rates,
+tab.1_cap <- table_nums(name = "tab_1", 
                         caption = "Nitrogen application rates for 2015 and 2016.
@@
 Treatments were applied in splits, basal, tillering and panicle initiation growth stages.")
+```
+
+# Tables {-}\
+
+`r table_nums("tab_1")`
+```{r N-rates, fig.cap=tab.1_cap}
+kable(N_rates)
 
@@
 
-```{r ShB-W-progress, fig.cap="Sheath blight progress for 2015 and 2016 experiments.
+```{r figure-caps}
+figure_nums <- captioner(prefix = "Fig.")
+
+fig.1_cap <- figure_nums(name = "fig_1", 
+                        caption = "Sheath blight progress for 2015 and 2016 experiments.
 Disease progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Points represent the mean of four replications."}
+Points represent the mean of four replications.")
+
+fig.2_cap <- figure_nums(name = "fig_2", 
+                        caption = "Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+Five different nitrogen treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
+Points represent the mean of four replications.")
+
+fig.3_cap <- figure_nums(name = "fig_3", 
+                        caption = "Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).")
+
+fig.4_cap <- figure_nums(name = "fig_4", 
+                        caption = "Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Five different nitrogen treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
+
+fig.5_cap <- figure_nums(name = "fig_5", 
+                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE) on sheath blight tiller incidence, tiller severity and leaf severity.
+Five different nitrogen treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
+
+```
+
+`r figure_nums("fig_1")`
+```{r ShB-W-progress, fig.cap="fig.1_cap"}
 
@@
 ##### ShB W progress
-
-```{r ShB-N-progress, fig.cap="Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Five different nitrogen treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Points represent the mean of four replications."}
+`r figure_nums("fig_2")`
+```{r ShB-N-progress, fig.cap="fig.2_cap"}
 
@@
 
-```{r ShB-W-box, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+`r figure_nums("fig_3")`
+```{r ShB-W-box, fig.cap="fig.3_cap"}
 
@@
 ##### ShB boxplot - NRTE
-
-```{r ShB-N-box, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
-Five different nitrogen treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+`r figure_nums("fig_4")`
+```{r ShB-N-box, fig.cap="fig.4_cap"}
 
@@
 ##### Estimates plot
-
-```{r estimates-plot, fig.cap="Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE) on sheath blight tiller incidence, tiller severity and leaf severity.
-Five different nitrogen treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+`r figure_nums("fig_5")`
+```{r estimates-plot, fig.cap="fig.5_cap"}
 

### 2018-05-02 R/plot_estimates.R
Analyse interaction of WMGT and NRTE
This necessitated changes to the estimates plot functions to fit the text on the left-side in the plot area as well

@@ -21,7 +21,8 @@ plot_estimates <- function(x) {
     x <- coda:::summary.mcmc.list(x)
   }
   n <- dim(x$statistics)[1]
-  par(mar = c(2, 7, 3, 1))
+  par(mar = c(2, 11, 3, 1),
+      cex = 0.5)
   plot(
     x$statistics[, 1],
     n:1,

### 2018-05-02 R/plot_estimates_paper.R

@@ -21,7 +21,8 @@ plot_estimates_paper <- function(x, main_title = "") {
     x <- coda:::summary.mcmc.list(x)
   }
   n <- dim(x$statistics)[1]
-  par(mar = c(2, 8, 3, 1))
+  par(mar = c(2, 11, 3, 1),
+      cex = 0.5)
   plot(
     x$statistics[, 1],
     n:1,

### 2018-05-03 R/plot_estimates_paper.R
Update axis names for paper estimates plot

@@ -22,7 +22,7 @@ plot_estimates_paper <- function(x, main_title = "") {
   }
   n <- dim(x$statistics)[1]
   par(mar = c(2, 11, 3, 1),
-      cex = 0.5)
+      cex = 0.7)
   plot(
     x$statistics[, 1],
     n:1,
@@ -35,10 +35,10 @@ plot_estimates_paper <- function(x, main_title = "") {
   )
 
   # extract treatment names and clean them up for the graph
-  trt_names <- substr(rownames(x$statistics)[-1], 5, nchar(x$statistics)[-1])
-  axis_names <- c("(Intercept)", trt_names)
+  row.names(x$statistics) <- gsub(pattern = "WMGT", "", row.names(x$statistics))
+  row.names(x$statistics) <- gsub(pattern = "NRTE", "", row.names(x$statistics))
 
-  axis(side = 2, at = n:1, axis_names, las = 2)
+  axis(side = 2, at = n:1, row.names(x$statistics), las = 2)
   arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
   abline(v = 0, lty = 2)
 }

### 2018-05-03 analysis/paper/paper.Rmd
Fix crossrefs

@@
 )
-
-# table captions
-tn <- local({
-  i = 0
-  function(x) {
-    i <<- i + 1
-    paste('\n\nTab. ', i, ': ', x, sep = '')
-    # The : before Table tells pandoc to wrap your caption in <caption></caption>
-  }
-})
-knitr::knit_hooks$set(tab.cap = function(before, options, envir) {
-  if (!before)
-    tn(options$tab.cap)
-})
-default_output_hook = knitr::knit_hooks$get("output")
-knitr::knit_hooks$set(output = function(x, options) {
-  if (is.null(options$tab.cap) == F)  
-    x
-  else
-    default_output_hook(x,options)
-})
 
@@
 The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab.
-\@ref(tab:N-rates)).
+\@ref(tab:tab_1)).
 
@@
 Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied (Tab.
-\@ref(tab:N-rates)).
+\@ref(tab:tab_1)).
 
@@
 In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig.
-\@ref(fig:ShB-W-progress)a, \@ref(fig:ShB-N-progress)a).
+\@ref(fig:fig_1)a, \@ref(fig:fig_2)a).
 Water management was not significantly different (Fig.
-\@ref(fig:ShB-W-box)a, \@ref(fig:estimates-plot)a).
+\@ref(fig:fig_3)a, \@ref(fig:fig_5)a).
 However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
-\@ref(fig:ShB-N-box)a, \@ref(fig:estimates-plot)a).
+\@ref(fig:fig_4)a, \@ref(fig:fig_5)a).
 
@@
 Tiller ShB severity remained below 2% (Fig.
-\@ref(fig:ShB-N-progress)c, \@ref(fig:ShB-W-progress)c).
+\@ref(fig:fig_2)c, \@ref(fig:fig_1)c).
 Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig.
-\@ref(fig:ShB-N-box)c, \@ref(fig:estimates-plot)c).
+\@ref(fig:fig_4)c, \@ref(fig:fig_5)c).
 However, the AWD water management was not significantly different from the FLD treatment (Fig.
-\@ref(fig:ShB-W-box)c, \@ref(fig:estimates-plot)c).
+\@ref(fig:fig_3)c, \@ref(fig:fig_5)c).
 
@@
 Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig.
-\@ref(fig:ShB-W-progress)e, \@ref(fig:ShB-N-progress)e).
+\@ref(fig:fig_1)e, \@ref(fig:fig_2)e).
 Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig.
-\@ref(fig:ShB-N-box)e, \@ref(fig:estimates-plot)e).
+\@ref(fig:fig_4)e, \@ref(fig:fig_5)e).
 However, the AWD water management was not significantly different from the FLD treatment (Fig.
-\@ref(fig:ShB-W-box)e, \@ref(fig:estimates-plot)e).
+\@ref(fig:fig_3)e, \@ref(fig:fig_5)e).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig.
-\@ref(fig:ShB-N-progress)b).
+\@ref(fig:fig_2)b).
 The N treatment N180, was significantly different than the control N60 treatment (Fig.
-\@ref(fig:ShB-N-box)b, \@ref(fig:estimates-plot)b).
+\@ref(fig:fig_4)b, \@ref(fig:fig_5)b).
 As in the 2015 study, water management did not significantly differ (Fig.
-\@ref(fig:ShB-W-box)b, \@ref(fig:estimates-plot)b).
+\@ref(fig:fig_3)b, \@ref(fig:fig_5)b).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:ShB-N-progress)d). 
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:fig_2)d). 
 In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig.
-\@ref(fig:ShB-N-box)d, \@ref(fig:estimates-plot)d).
+\@ref(fig:fig_4)d, \@ref(fig:fig_5)d).
 The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig.
-\@ref(fig:ShB-W-box)d, \@ref(fig:estimates-plot)d).
+\@ref(fig:fig_3)d, \@ref(fig:fig_5)d).
 
@@
 In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
-\@ref(fig:ShB-W-box)f, \@ref(fig:estimates-plot)f, \@ref(fig:ShB-N-box)f, \@ref(fig:estimates-plot)f).
+\@ref(fig:fig_3)f, \@ref(fig:fig_5)f, \@ref(fig:fig_4)f, \@ref(fig:fig_5)f).
 
@@
 In the 2016 experiment the tiller ShB severity was significantly lower for AWD than FLD (Fig.
-\@ref(fig:ShB-W-box)d, \@ref(fig:estimates-plot)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.
+\@ref(fig:fig_3)d, \@ref(fig:fig_5)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.
 
@@
 The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig.
-\@ref(fig:ShB-W-progress)a:b, \@ref(fig:ShB-N-progress)c:d, \@ref(fig:ShB-W-box)a:b, \@ref(fig:ShB-N-box)c:d).
+\@ref(fig:fig_1)a:b, \@ref(fig:fig_2)c:d, \@ref(fig:fig_3)a:b, \@ref(fig:fig_4)c:d).
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
@@
 
-# Tables {-}\
+# Tables {-}
 
@@
 `r figure_nums("fig_1")`
-```{r ShB-W-progress, fig.cap="fig.1_cap"}
+```{r fig_1, fig.cap="fig.1_cap"}
 
@@
 
-##### ShB W progress
+##### ShB N progress
 `r figure_nums("fig_2")`
-```{r ShB-N-progress, fig.cap="fig.2_cap"}
+```{r fig_2, fig.cap="fig.2_cap"}
 
@@
 `r figure_nums("fig_3")`
-```{r ShB-W-box, fig.cap="fig.3_cap"}
+```{r fig_3, fig.cap="fig.3_cap"}
 
@@
 `r figure_nums("fig_4")`
-```{r ShB-N-box, fig.cap="fig.4_cap"}
+```{r fig_4, fig.cap="fig.4_cap"}
 
@@
 `r figure_nums("fig_5")`
-```{r estimates-plot, fig.cap="fig.5_cap"}
+```{r fig_5, fig.cap="fig.5_cap"}
 

### 2018-05-03 analysis/paper/paper.Rmd
Add a bit more about evaluting the models

@@
 The remaining 50,000 samples were thinned by taking every tenth sample resulting in 5,000 independent draws from the posterior distribution of the parameters of the model.
-The `coda` [@coda2006] package was used to provide utilities to check convergence using visual inspection of graphs and the Gelman-Rubin test.
+The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test.
 All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
@@
 
+### The Interaction of Irrigation and N Management
+
 ## 2016 Experiment {-}
@@
 \@ref(fig:fig_3)f, \@ref(fig:fig_5)f, \@ref(fig:fig_4)f, \@ref(fig:fig_5)f).
+
+### The Interaction of Irrigation and N Management
 

### 2018-05-07 R/plot_estimates.R
Update static docs
Add new analysis methods to vignette #3

@@ -21,7 +21,7 @@ plot_estimates <- function(x) {
     x <- coda:::summary.mcmc.list(x)
   }
   n <- dim(x$statistics)[1]
-  par(mar = c(2, 11, 3, 1),
+  par(mar = c(2, 15, 3, 1),
       cex = 0.5)
   plot(
     x$statistics[, 1],
@@ -33,6 +33,11 @@ plot_estimates <- function(x) {
     main = "Posterior means and 95% credible intervals",
     bty = "L"
   )
+
+  # extract treatment names and clean them up for the graph
+  row.names(x$statistics) <- gsub(pattern = "WMGT", "", row.names(x$statistics))
+  row.names(x$statistics) <- gsub(pattern = "NRTE", "", row.names(x$statistics))
+
   axis(side = 2, at = n:1, rownames(x$statistics), las = 2)
   arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
   abline(v = 0, lty = 2)

### 2018-05-07 R/plot_estimates_paper.R

@@ -21,7 +21,7 @@ plot_estimates_paper <- function(x, main_title = "") {
     x <- coda:::summary.mcmc.list(x)
   }
   n <- dim(x$statistics)[1]
-  par(mar = c(2, 11, 3, 1),
+  par(mar = c(2, 15, 3, 1),
       cex = 0.7)
   plot(
     x$statistics[, 1],

### 2018-05-08 analysis/paper/paper.Rmd
add "RCBD" to statement about design
Correct paper so that it properly builds

@@
 
-The plot design was a split-plot design with four replicates where irrigation was the main plot and N rate was the split-plot.
+The plot design was a split-plot randomised complete block design with four replicates where irrigation was the main plot and N rate was the split-plot.
 
@@
 
-par(mfcol = c(3, 2))
+par(mfcol = c(2, 2))
 
@@
 
-plot_estimates_paper(models[[3]])
-mtext(text = "Leaf Severity", side = 2, line = 6)
-mtext(text = "e", side = 3, line = 0, adj = 1, cex = 0.75)
-
-plot_estimates_paper(models[[4]], main_title = "2016")
+plot_estimates_paper(models[[3]], main_title = "2016")
 mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
 
-plot_estimates_paper(models[[5]])
+plot_estimates_paper(models[[4]])
 mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
-
-plot_estimates_paper(models[[6]])
-mtext(text = "f", side = 3, line = 0, adj = 1, cex = 0.75)
 

### 2018-06-21 R/plot_estimates.R
Revert plot sizes for no interactions and update documentation

@@ -2,7 +2,7 @@
 #' @title Plot MCMCglmm estimates
 #'
 #' @description Plot estimates of posterior distributions and credible
-#'  intervals of MCMCglmm outputs
+#'  intervals of \pkg{MCMCglmm} outputs
 #'
 #' @name plot_estimates
 #' @param x An\code{\link[coda]{mcmc.list}} object
@@ -21,7 +21,7 @@ plot_estimates <- function(x) {
     x <- summary(x)
   }
   n <- dim(x$statistics)[1]
-  graphics::par(mar = c(2, 15, 3, 1),
+  graphics::par(mar = c(2, 8, 3, 1),
       cex = 0.5)
   graphics::plot(
     x$statistics[, 1],

### 2018-06-21 R/plot_estimates_paper.R

@@ -2,7 +2,7 @@
 #' @title Plot MCMCglmm estimates for publication
 #'
 #' @description Plot estimates of posterior distributions and credible
-#'  intervals of MCMCglmm outputs sans intercept for publication figure
+#'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
 #'
 #' @name plot_estimates_paper
 #' @param x An\code{\link[coda]{mcmc.list}} object
@@ -21,7 +21,7 @@ plot_estimates_paper <- function(x, main_title = "") {
     x <- summary(x)
   }
   n <- dim(x$statistics)[1]
-  graphics::par(mar = c(2, 15, 3, 1),
+  graphics::par(mar = c(2, 8, 3, 1),
       cex = 0.7)
   graphics::plot(
     x$statistics[, 1],

### 2018-06-21 analysis/paper/paper.Rmd
Edit abstract grammar and spelling

@@
 Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
-We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did differ significantly by irrigation treament but leaf sheath blight severity did not.
-Our findings suggests that farmers can adopt water saving technologies without risking increased sheath blight incidence.
+We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did differ significantly by irrigation treatment, but leaf sheath blight severity did not.
+Our findings suggest that farmers can adopt water saving technologies without risking increased sheath blight incidence.
 We suggest that further cross-cutting research in this area is warranted.

### 2018-07-06 R/plot_estimates.R
Add plots for leaf estimates

@@ -9,13 +9,13 @@
 #'
 #' @examples \dontrun{
 #' # Plot posterior means and credible intervals
-#' plot_estimates(m1)
+#' plot_tiller_estimates(m1)
 #'}
 #'
 #' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
 #'
 #' @export
-plot_estimates <- function(x) {
+plot_tiller_estimates <- function(x) {
   graphics::par(mfrow = c(1, 1))
   if (class(x) != "summary.mcmc") {
     x <- summary(x)
@@ -41,3 +41,48 @@ plot_estimates <- function(x) {
   graphics::arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
   graphics::abline(v = 0, lty = 2)
 }
+
+
+#' @title Plot MCMCglmm estimates
+#'
+#' @description Plot estimates of posterior distributions and credible
+#'  intervals of \pkg{MCMCglmm} outputs
+#'
+#' @name plot_estimates
+#' @param x An\code{\link[coda]{mcmc.list}} object
+#'
+#' @examples \dontrun{
+#' # Plot posterior means and credible intervals
+#' plot_leaf_estimates(m1)
+#'}
+#'
+#' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
+#'
+#' @export
+plot_leaf_estimates <- function(x) {
+  graphics::par(mfrow = c(1, 1))
+  if (class(x) != "summary.mcmc") {
+    x <- summary(x)
+  }
+  n <- dim(x$statistics)[1]
+  graphics::par(mar = c(2, 15, 3, 1))
+  graphics::plot(
+    x$statistics[, 1],
+    n:1,
+    yaxt = "n",
+    ylab = "",
+    xlim = range(x$quantiles) * 1.2,
+    pch = 19,
+    main = "Posterior means and 95% credible intervals",
+    bty = "L"
+  )
+
+  # extract treatment names and clean them up for the graph
+  row.names(x$statistics) <- gsub(pattern = "WMGT", "", row.names(x$statistics))
+  row.names(x$statistics) <- gsub(pattern = "NRTE", "", row.names(x$statistics))
+
+  graphics::axis(side = 2, at = n:1, rownames(x$statistics), las = 2)
+  graphics::arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
+  graphics::abline(v = 0, lty = 2)
+}
+

### 2018-07-07 analysis/paper/paper.Rmd
Update paper with input from Nancy

@@
 
-Trays of NSIC Rc222, a short-season inbred irrigated lowland rice variety with 114 day maturity when transplanted were established on 19 December 2014.
-Trays were randomised and transplanted using a mechanical transplanter on 9 January 2015.
+Trays of NSIC Rc222 were seeded on 19 December 2014.
+NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted were established.
+The variety is commonly grown by farmers in the area, having moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro.
+Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20cm within and between rows.
 
@@
 Nurseries of NSIC Rc222 were established on 7 January 2016 experiments.
-Seedlings were transplanted by hand 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+Seedlings were transplanted by hand from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
 
@@
 The severity data were converted to the midpoint percent value of the scale range.
+
+The correlations between tiller sheath ShB incidence and tiller and leaf ShB severity were tested using Spearman’s correlation test, `cor.test`, [@R2018].
+No correlation was found, so the analysis was completed for each variable independently with no assumed interaction.
 
@@
                         caption = "Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Five different nitrogen treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
 Points represent the mean of four replications.")
@@
 Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
-Five different nitrogen treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
 
 fig.5_cap <- figure_nums(name = "fig_5", 
-                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and nitrogen rate (NRTE) on sheath blight tiller incidence, tiller severity and leaf severity.
-Five different nitrogen treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
+                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity.
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
 
+fig.6_cap <- figure_nums(name = "fig_6", 
+                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity.
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
 ```
@@
 
-##### Estimates plot
+##### Tiller estimates plots
+
 `r figure_nums("fig_5")`
@@
 
-plot_estimates_paper(models[[1]], main_title = "2015")
+plot_tiller_estimates_paper(models[[1]], main_title = "2015")
 mtext(text = "Tiller Incidence", side = 2, line = 6)
@@
 
-plot_estimates_paper(models[[2]])
+plot_tiller_estimates_paper(models[[2]])
 mtext(text = "Tiller Severity", side = 2, line = 6)
@@
 
-plot_estimates_paper(models[[3]], main_title = "2016")
+plot_tiller_estimates_paper(models[[4]], main_title = "2016")
 mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
 
-plot_estimates_paper(models[[4]])
+plot_tiller_estimates_paper(models[[5]])
 mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
+
+```
+
+##### Leaf estimates plots
+
+`r figure_nums("fig_6")`
+```{r fig_6, fig.cap="fig.5_cap"}
+
+par(mfcol = c(1, 2))
+
+plot_tiller_estimates_paper(models[[3]], main_title = "2015")
+mtext(text = "Leaf Severity", side = 2, line = 6)
+mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
+
+plot_tiller_estimates_paper(models[[6]], main_title = "2016")
+mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
 

### 2018-07-07 R/plot_estimates.R
Fix errors in plotting estimate functions

@@ -1,10 +1,10 @@
 
-#' @title Plot MCMCglmm estimates
+#' @title Plot MCMCglmm tiller estimates
 #'
 #' @description Plot estimates of posterior distributions and credible
 #'  intervals of \pkg{MCMCglmm} outputs
 #'
-#' @name plot_estimates
+#' @name plot_tiller_estimates
 #' @param x An\code{\link[coda]{mcmc.list}} object
 #'
 #' @examples \dontrun{
@@ -43,12 +43,12 @@ plot_tiller_estimates <- function(x) {
 }
 
 
-#' @title Plot MCMCglmm estimates
+#' @title Plot MCMCglmm leaf estimates
 #'
 #' @description Plot estimates of posterior distributions and credible
 #'  intervals of \pkg{MCMCglmm} outputs
 #'
-#' @name plot_estimates
+#' @name plot_leaf_estimates
 #' @param x An\code{\link[coda]{mcmc.list}} object
 #'
 #' @examples \dontrun{

### 2018-07-07 R/plot_estimates_paper.R

@@ -1,10 +1,10 @@
 
-#' @title Plot MCMCglmm estimates for publication
+#' @title Plot MCMCglmm tiller estimates for publication
 #'
 #' @description Plot estimates of posterior distributions and credible
 #'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
 #'
-#' @name plot_estimates_paper
+#' @name plot_tiller_estimates_paper
 #' @param x An\code{\link[coda]{mcmc.list}} object
 #' @param main_title Main title for the plot
 #'
@@ -43,12 +43,12 @@ plot_tiller_estimates_paper <- function(x, main_title = "") {
 }
 
 
-#' @title Plot MCMCglmm estimates for publication
+#' @title Plot MCMCglmm leaf estimates for publication
 #'
 #' @description Plot estimates of posterior distributions and credible
 #'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
 #'
-#' @name plot_estimates_paper
+#' @name plot_leaf_estimates_paper
 #' @param x An\code{\link[coda]{mcmc.list}} object
 #' @param main_title Main title for the plot
 #'

### 2018-08-07 analysis/paper/paper.Rmd
Update pkgdown site

@@
   bookdown::word_document2:
-    #keep_tex: yes
     toc: no

### 2018-09-18 analysis/paper/paper.Rmd
Update pkgdown site
Fixes analysis document
Fixes captions in the analysis document and uses new figures from unthinned MCMC

@@
 ---
-title: Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?
+title: "Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?"
 author: |
@@
     toc: no
-    fig_caption: yes
     reference_docx: "../templates/template.docx"
-  always_allow_html: yes
-header-includes:
-   \usepackage{endfloat}
-   \usepackage{setspace}\doublespacing
-   \usepackage{lineno}
-   \linenumbers
 ---
@@
 library(bookdown)
-library(captioner)
 library(knitr)
@@
 The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab.
-\@ref(tab:tab_1)).
+\@ref(tab:tab-1)).
 
@@
 Trays of NSIC Rc222 were seeded on 19 December 2014.
-NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted were established.
+NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted, were established.
 The variety is commonly grown by farmers in the area, having moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro.
@@
 Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied (Tab.
-\@ref(tab:tab_1)).
+\@ref(tab:tab-1)).
 
@@
 Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn in.
-The remaining 50,000 samples were thinned by taking every tenth sample resulting in 5,000 independent draws from the posterior distribution of the parameters of the model.
+The remaining 50,000 samples were used to determine the posterior distribution of the parameters of the model.
 The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test.
@@
 In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig.
-\@ref(fig:fig_1)a, \@ref(fig:fig_2)a).
+\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
 Water management was not significantly different (Fig.
-\@ref(fig:fig_3)a, \@ref(fig:fig_5)a).
+\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
 However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
-\@ref(fig:fig_4)a, \@ref(fig:fig_5)a).
+\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
 
@@
 Tiller ShB severity remained below 2% (Fig.
-\@ref(fig:fig_2)c, \@ref(fig:fig_1)c).
+\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
 Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig.
-\@ref(fig:fig_4)c, \@ref(fig:fig_5)c).
+\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
 However, the AWD water management was not significantly different from the FLD treatment (Fig.
-\@ref(fig:fig_3)c, \@ref(fig:fig_5)c).
+\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
 
@@
 Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig.
-\@ref(fig:fig_1)e, \@ref(fig:fig_2)e).
+\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
 Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig.
-\@ref(fig:fig_4)e, \@ref(fig:fig_5)e).
+\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
 However, the AWD water management was not significantly different from the FLD treatment (Fig.
-\@ref(fig:fig_3)e, \@ref(fig:fig_5)e).
+\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig.
-\@ref(fig:fig_2)b).
+\@ref(fig:fig-2)b).
 The N treatment N180, was significantly different than the control N60 treatment (Fig.
-\@ref(fig:fig_4)b, \@ref(fig:fig_5)b).
+\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
 As in the 2015 study, water management did not significantly differ (Fig.
-\@ref(fig:fig_3)b, \@ref(fig:fig_5)b).
+\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:fig_2)d). 
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:fig-2)d). 
 In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig.
-\@ref(fig:fig_4)d, \@ref(fig:fig_5)d).
+\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
 The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig.
-\@ref(fig:fig_3)d, \@ref(fig:fig_5)d).
+\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
 
@@
 In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
-\@ref(fig:fig_3)f, \@ref(fig:fig_5)f, \@ref(fig:fig_4)f, \@ref(fig:fig_5)f).
+\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
 
@@
 In the 2016 experiment the tiller ShB severity was significantly lower for AWD than FLD (Fig.
-\@ref(fig:fig_3)d, \@ref(fig:fig_5)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.
+\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.
 
@@
 The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig.
-\@ref(fig:fig_1)a:b, \@ref(fig:fig_2)c:d, \@ref(fig:fig_3)a:b, \@ref(fig:fig_4)c:d).
+\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
@@
 
-```{r table-caps}
-table_nums <- captioner(prefix = "Tab.")
+# Tables {-}
 
-tab.1_cap <- table_nums(name = "tab_1", 
+```{r N-rates}
+
+kable(N_rates,
       caption = "Nitrogen application rates for 2015 and 2016.
@@
 Treatments were applied in splits, basal, tillering and panicle initiation growth stages.")
-```
-
-# Tables {-}
-
-`r table_nums("tab_1")`
-```{r N-rates, fig.cap=tab.1_cap}
-kable(N_rates)
 
@@
 
-```{r figure-caps}
-figure_nums <- captioner(prefix = "Fig.")
-
-fig.1_cap <- figure_nums(name = "fig_1", 
-                        caption = "Sheath blight progress for 2015 and 2016 experiments.
+```{r fig-1, fig.cap="Sheath blight progress for 2015 and 2016 experiments.
 Disease progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Points represent the mean of four replications.")
-
-fig.2_cap <- figure_nums(name = "fig_2", 
-                        caption = "Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Points represent the mean of four replications.")
-
-fig.3_cap <- figure_nums(name = "fig_3", 
-                        caption = "Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).")
-
-fig.4_cap <- figure_nums(name = "fig_4", 
-                        caption = "Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
-Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
-
-fig.5_cap <- figure_nums(name = "fig_5", 
-                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity.
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
-
-fig.6_cap <- figure_nums(name = "fig_6", 
-                        caption = "Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity.
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).")
-```
-
-`r figure_nums("fig_1")`
-```{r fig_1, fig.cap="fig.1_cap"}
+Points represent the mean of four replications."}
 
@@
 ##### ShB N progress
-`r figure_nums("fig_2")`
-```{r fig_2, fig.cap="fig.2_cap"}
+
+```{r fig-2, fig.cap="Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
+Points represent the mean of four replications."}
 
@@
 
-`r figure_nums("fig_3")`
-```{r fig_3, fig.cap="fig.3_cap"}
+```{r fig-3, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
 
@@
 ##### ShB boxplot - NRTE
-`r figure_nums("fig_4")`
-```{r fig_4, fig.cap="fig.4_cap"}
+```{r fig-4, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
+Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
 
@@
 
-`r figure_nums("fig_5")`
-```{r fig_5, fig.cap="fig.5_cap"}
+```{r fig-5, fig.cap="Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity.
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
 
@@
 
-`r figure_nums("fig_6")`
-```{r fig_6, fig.cap="fig.5_cap"}
+```{r fig-6, fig.cap="Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity.
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
 

### 2018-10-06 analysis/paper/paper.Rmd
Updates pkgdown site

@@
   echo = FALSE,
+  relative_path = TRUE,
   comment = "#>",

### 2018-10-06 analysis/paper/paper.Rmd
Replaces ShB with sheath blight in document

@@
 
-Sheath blight (ShB) disease (*Rhizoctonia solani* Kühn), anastomosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
+Sheath blight disease (*Rhizoctonia solani* Kühn), anastomosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
 Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
@@
 
-Because of the well documented effects of irrigation and N on ShB, we established field experiments to study what effects AWD irrigation technologies and N could have upon ShB incidence and severity in tropical rice.
+Because of the well documented effects of irrigation and N on sheath blight, we established field experiments to study what effects AWD irrigation technologies and N could have upon sheath blight incidence and severity in tropical rice.
 
@@
 In both experiments, two sample areas, sized 1m x 1m, per plot were assessed.
-the total number of tillers per hill and number of tillers with ShB (incidence) were measured for nine hills per sample area.
-Tiller ShB severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
+the total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area.
+Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
 The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
-Severity was considered to be the amount of leaf or sheath tissue covered by ShB lesions.
+Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
 Leaves were rated as green (living) having at least XXX% living tissue or dead, defined as having less than XXX% living tissue.
@@
 
-The correlations between tiller sheath ShB incidence and tiller and leaf ShB severity were tested using Spearman’s correlation test, `cor.test`, [@R2018].
+The correlations between tiller sheath sheath blight incidence and tiller and leaf sheath blight severity were tested using Spearman’s correlation test, `cor.test`, [@R2018].
 No correlation was found, so the analysis was completed for each variable independently with no assumed interaction.
@@
 As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@MCMCglmm2010].
-Six models were created where the the dependent variables were 2015 tiller ShB incidence, 2015 tiller ShB severity, 2015 leaf ShB severity; 2016 tiller ShB incidence, 2016 tiller ShB severity; 2016 leaf ShB severity, respectively.
+Six models were created where the the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
@@
 
-In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig.
+In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.
 \@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
@@
 
-Tiller ShB severity remained below 2% (Fig.
+Tiller sheath blight severity remained below 2% (Fig.
 \@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
@@
 
-Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig.
+Severity of leaf sheath blight remained low, less than 0.4% across all treatments (Fig.
 \@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
@@
 
-In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig.
+In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf sheath blight severity (Fig.
 \@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
@@
 
-In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology.
-In only one instance were we able to detect any effect of AWD on ShB.
-In the 2016 experiment the tiller ShB severity was significantly lower for AWD than FLD (Fig.
-\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.
+In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology.
+In only one instance were we able to detect any effect of AWD on sheath blight.
+In the 2016 experiment the tiller sheath blight severity was significantly lower for AWD than FLD (Fig.
+\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under conditions where there is high sheath blight pressure.
 
@@
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
-It is possible that the mechanical transplanter could increase ShB spread in the canopy as compared with traditional manual transplanting.
+It is possible that the mechanical transplanter could increase sheath blight spread in the canopy as compared with traditional manual transplanting.
 This however was not investigated as a part of this study but could bear further research.

### 2018-10-06 analysis/paper/paper.Rmd
Edit discussion

@@
 
-In both experiments we were unable to detect any significant effect of AWD on sheath blight that would cause increases in the disease, which could hinder adoption of the technology.
+In both experiments we were unable to detect any significant effect of AWD on sheath blight that led to increases in the disease, which could hinder adoption of the technology.
 In only one instance were we able to detect any effect of AWD on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was significantly lower for AWD than FLD (Fig.
+In the 2016 experiment the tiller sheath blight severity was significantly lower for the AWD treatment than FLD treatment (Fig.
 \@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under conditions where there is high sheath blight pressure.
 
-The findings of the effects of N rates on sheath blight were to be expected, where higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
-However, in 2016 tiller and leaf severity had no detectable differences due to the N rate.
+The findings of the effects of N rates on sheath blight were as expected.
+Higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
+In 2016 tiller and leaf severity had no detectable differences due to the N rate.
 However, it should be noted that the levels of leaf severity remained low (< 1%) throughout the growing season in all treatments for both years.
+
+The combination of the irrigation and N rates did not appear to increase the disease severity or incidence.
+In 2015 there were no significant differences in the interaction of irrigation and N.
+However, in the 2016 experiment the combination of AWD-N180 was significantly different, lower, than the FLD-N60 combination treatment.
 
@@
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
-It is possible that the mechanical transplanter could increase sheath blight spread in the canopy as compared with traditional manual transplanting.
-This however was not investigated as a part of this study but could bear further research.
 

### 2018-11-01 analysis/paper/paper.Rmd
Edits to paper

@@
 Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
-We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did differ significantly by irrigation treatment, but leaf sheath blight severity did not.
+We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did clearly differ statistically by irrigation treatment, but leaf sheath blight severity did not.
 Our findings suggest that farmers can adopt water saving technologies without risking increased sheath blight incidence.
 We suggest that further cross-cutting research in this area is warranted.
+All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
 bibliography: references.bib
@@
 Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions he disease can cause up to 50\% yield losses [@Marchetti1991].
+Under conducive conditions the disease can cause up to 50 \% yield losses [@Marchetti1991].
 Studies by Savary et al.
-[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10\%.
+[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10 \%.
 The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for irrigated rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40% of irrigation water [@Bouman2001; @Feng2007].
-In AWD rice, fields are exposed to several dry phases during the growth period without exposing the plants to water stress.
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40 \% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
 In order to avoid yield decline under AWD “safe” thresholds have been developed.
 Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [@Richards2014].
-Fields are furthermore kept flooded during the flowering period.
-As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50% [@Yan2005; @Sander2015].
+Fields are furthermore kept flooded during the flowering period to avoid plant stress.
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 \% [@Yan2005; @Sander2015].
 
-The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and the Philippines, plan to widely apply AWD to local rice production [@MOEF2015].
-However, a change in water regime in rice fields on large scale might encompass different other effects, for example related to plant health.
+The AWD technology has been identified as promising climate-smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
+Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
+However, a change like this in the water regime in rice fields on a large scale might trigger different other effects, for example changes in disease intensity or severity.
 
-Because of the well documented effects of irrigation and N on sheath blight, we established field experiments to study what effects AWD irrigation technologies and N could have upon sheath blight incidence and severity in tropical rice.
+While the effects of climate change directly on rice disease have been studied [@Duku2016XXXX CITATION XXXX] the effects of mitigation practices have not.
+And because of the well documented effects of irrigation practices (CITATION XXXX) and N on sheath blight (CITATION XXXX); we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
 
@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, longitude 121&deg; 15' E) in the 2015 and 2016 dry seasons.
-For 2016 changes were made to optimize the experiment based on findings from the 2015 experiment.
-Details were as follows.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, longitude 121&deg; 15' E) in 2015 and 2016 dry seasons from December to May.
+In the 2016 experiment changes were made to optimize the experiment based on findings from the 2015 experiment.
+The differences are detailed in the following sections.
 
@@
 
-The plot design was a split-plot randomised complete block design with four replicates where irrigation was the main plot and N rate was the split-plot.
+The plot design was a split-plot randomised complete block design with four replicates where irrigation was the main plot treatment and N rate was the split-plot treatment.
 
-The main plot treatments were alternate wetting and drying (AWD) and continuously flooded (FLD) or farmers' practice as the control treatment.
+The main plot treatments were alternate wetting and drying (AWD) and continuously flooded or farmers' practice as the control treatment.
 The main plot size was 12m x 12m (144 sq m), with a split-plot size of 5m x 5m (25 sq m).
@@
 Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
-In FLD plots a standing water layer of 3-5cm was maintained throughout the growing season.
+In flooded plots a standing water layer of 3-5cm was maintained throughout the growing season.
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab.
-\@ref(tab:tab-1)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits) and N120 (120 kg per ha applied as urea in three splits) (Tab. \@ref(tab:tab-1)).
 
@@
 Trays of NSIC Rc222 were seeded on 19 December 2014.
-NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted, were established.
-The variety is commonly grown by farmers in the area, having moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro.
+NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted.
+The variety is commonly grown by farmers in the area, having good yields and moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro.
 Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20cm within and between rows.
@@
 
-An isolate of *Rhizoctonia solani* AG1-1a from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
+An isolate of *Rhizoctonia solani* AG1-1a previously isolated from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
 The isolate was transferred to 90mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C).
@@
 
-The experiment followed the same split-plot design as described for the 2015 experiment.
+The 2016 experiment followed the same split-plot design as described for the 2015 experiment.
 However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
@@
 
-Nurseries of NSIC Rc222 were established on 7 January 2016 experiments.
-Seedlings were transplanted by hand from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+Nurseries of NSIC Rc222 were established on 7 January 2016.
+Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
 
@@
 
-Based on the 2015 results, the inoculation methods were modified in 2016 to increase the amount of inoculum applied to a smaller area.
+Based on the 2015 results, the inoculation methods were modified in 2016 to increase the amount of inoculum and applied to a smaller area.
 Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1m x 1m) per plot, where one bottle contained 151g inoculum.
@@
 In both experiments, two sample areas, sized 1m x 1m, per plot were assessed.
-the total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area.
+The total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area.
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1% severity; 2 - 1 to 5%; 3 - 5 to 15%; 4 - 15 to 50%; 5 - 50 to 100%.
+The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1 \% severity; 2 - 1 to 5 \%; 3 - 5 to 15 \%; 4 - 15 to 50 \%; 5 - 50 to 100 \%.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
-Leaves were rated as green (living) having at least XXX% living tissue or dead, defined as having less than XXX% living tissue.
+Leaves were rated as green (living) having at least XXX \% living tissue or dead, defined as having less than XXX \% living tissue.
 The same rating methodology was used in both experiments.
@@
 Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using the R package `agricolae` [@R2018; @deMendiburu2017].
-The severity data were converted to the midpoint percent value of the scale range.
+Due to the scale used for collection, the severity data were converted to the midpoint percent value of the scale range for each value.
 
@@
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were N rate - N0; irrigation management - FLD and for 2016, N rate - N60; irrigation management - FLD.
+The base levels (control treatments) for the analyses for 2015 were: N rate - N0, irrigation management - flooded and for 2016 they were: N rate - N60, irrigation management - flooded.
 
@@
 The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test.
-All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
 
@@
 \@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
-Water management was not significantly different (Fig.
+Water management was not statistically clearly different (Fig.
 \@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig.
+However, the N treatments, N100 and N120, were both statistically clearly different when compared with the control N0 treatment (Fig.
 \@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
@@
 \@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
-Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig.
+Both the N100 and N120 treatments were statistically clearly different than the control N0 treatment (Fig.
 \@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not significantly different from the FLD treatment (Fig.
+However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.
 \@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
@@
 \@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig.
+Both the N100 and N120 treatments were statistically clearly different than the N0 treatment (Fig.
 \@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-However, the AWD water management was not significantly different from the FLD treatment (Fig.
+However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.
 \@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
@@
 \@ref(fig:fig-2)b).
-The N treatment N180, was significantly different than the control N60 treatment (Fig.
+The N treatment N180, was statistically clearly different than the control N60 treatment (Fig.
 \@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
-As in the 2015 study, water management did not significantly differ (Fig.
+As in the 2015 study, water management did not statistically clearly differ (Fig.
 \@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:fig-2)d). 
-In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig.
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig.
+\@ref(fig:fig-2)d).
+In 2016 the N180 treatment was statistically clearly different from the N60 treatment, with N180 severity being higher (Fig.
 \@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig.
+The AWD water management, which was lower than the flooded treatment, was also statistically clearly different (Fig.
 \@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
@@
 
-In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf sheath blight severity (Fig.
+In 2016 the neither of the treatments, N rate or water management, were statistically clearly different from the control treatments for leaf sheath blight severity (Fig.
 \@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
@@
 
-In both experiments we were unable to detect any significant effect of AWD on sheath blight that led to increases in the disease, which could hinder adoption of the technology.
-In only one instance were we able to detect any effect of AWD on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was significantly lower for the AWD treatment than FLD treatment (Fig.
-\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under conditions where there is high sheath blight pressure.
+In both experiments we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
+In fact, in only one instance were we able to detect any clear effect of AWD on sheath blight.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than flooded treatment (Fig.
+\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
 
-The findings of the effects of N rates on sheath blight were as expected.
+The findings of the effects of N rates on sheath blight were as expected in both experiments.
 Higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
-In 2016 tiller and leaf severity had no detectable differences due to the N rate.
-However, it should be noted that the levels of leaf severity remained low (< 1%) throughout the growing season in all treatments for both years.
+However, in the 2016 experiment there were no detectable differences due to the N rate tiller and leaf severity.
 
-The combination of the irrigation and N rates did not appear to increase the disease severity or incidence.
-In 2015 there were no significant differences in the interaction of irrigation and N.
-However, in the 2016 experiment the combination of AWD-N180 was significantly different, lower, than the FLD-N60 combination treatment.
+The combination of the irrigation and N rates did not appear to increase the disease severity or incidence in either experiment.
+In 2015 there were no clear differences in the interaction of irrigation and N rate between any of the three treatments.
+However, in the 2016 experiment the combination of AWD-N180 was clearly different, being lower, than the flooded-N60 combination treatment.
 
-The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig.
+By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment appear to have improved the experiment.
+The the sheath blight incidence increased and the variability of sheath blight in the plots decreased (Fig.
 \@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
-The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
+
+It should be noted that the levels of leaf severity remained low (< 1 \%) throughout the growing season in all treatments for both years.
+As AWD can only feasibly be implemented in the dry season, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
+However, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases.
+
+The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000]. As manual transplanting becomes less common XXXXX...
+
+Sheath blight has been predicted to XXXXX due to the effects of climate change (XXXXXX 20XX).
+
+While sheath blight remains an important disease in rice production with little resistance available in current varieties, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease.
 
@@
 Lapis for their technical support in the field.
-Lastly, we would like to remember Michael Noel, who was a part of the plant disease management team at IRRI and who helped design and manage the first year of the project but passed away in September 2016.
+Lastly, we would like to remember our teammate Michael Noel, a part of the plant disease management team at IRRI and who helped design and managed the first year of the project but passed away in September 2016.
 
@@
 In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Treatments were applied in splits, basal, tillering and panicle initiation growth stages.")
-
+Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
 ```
@@
 
+##### Sheath blight progress for water management treatments
+
 ```{r fig-1, fig.cap="Sheath blight progress for 2015 and 2016 experiments.
@@
 Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
-Points represent the mean of four replications."}
+Points represent the mean observations of four replications."}
 
@@
 
-##### ShB N progress
+##### Sheath blight progress for N treatments
 
@@
 In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
-Points represent the mean of four replications."}
+Points represent the mean observations of four replications."}
 
@@
 
-##### ShB boxplot - WMGT
+##### Sheath Blight Incidence Boxplot for water management
 
@@
 
-##### ShB boxplot - NRTE
+##### Tiller sheath blight incidence boxplot for N rate
 ```{r fig-4, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
@@
 
-##### Tiller estimates plots
+##### Tiller Estimates Plots
 
@@
 mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
-
 ```
@@
 mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
-
 ```

### 2018-11-01 analysis/paper/paper.Rmd
Replace spaces with non-breaking

@@
 Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions the disease can cause up to 50 \% yield losses [@Marchetti1991].
+Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
 Studies by Savary et al.
-[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10 \%.
+[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10 &nbsp;\%.
 The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40 \% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
@@
 Fields are furthermore kept flooded during the flowering period to avoid plant stress.
-As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 \% [@Yan2005; @Sander2015].
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
 
@@
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits) and N120 (120 kg per ha applied as urea in three splits) (Tab. \@ref(tab:tab-1)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits) and N120 (120 kg per ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:tab-1)).
 
@@
 
-Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied (Tab.
-\@ref(tab:tab-1)).
+Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied (Tab.&nbsp;\@ref(tab:tab-1)).
 
@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1 \% severity; 2 - 1 to 5 \%; 3 - 5 to 15 \%; 4 - 15 to 50 \%; 5 - 50 to 100 \%.
+The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1&nbsp;\% severity; 2 - 1 to 5&nbsp;\%; 3 - 5 to 15&nbsp;\%; 4 - 15 to 50&nbsp;\%; 5 - 50 to 100&nbsp;\%.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
-Leaves were rated as green (living) having at least XXX \% living tissue or dead, defined as having less than XXX \% living tissue.
+Leaves were rated as green (living) having at least XXX&nbsp;\% living tissue or dead, defined as having less than XXX&nbsp;\% living tissue.
 The same rating methodology was used in both experiments.
@@
 
-In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.
-\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
-Water management was not statistically clearly different (Fig.
-\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the N treatments, N100 and N120, were both statistically clearly different when compared with the control N0 treatment (Fig.
-\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
+In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.&nbsp;\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
+Water management was not statistically clearly different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
+However, the N treatments, N100 and N120, were both statistically clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
 
@@
 
-Tiller sheath blight severity remained below 2% (Fig.
-\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
-Both the N100 and N120 treatments were statistically clearly different than the control N0 treatment (Fig.
-\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.
-\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
+Tiller sheath blight severity remained below 2&nbsp;\% (Fig.&nbsp;\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
+Both the N100 and N120 treatments were statistically clearly different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
+However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
 
@@
 
-Severity of leaf sheath blight remained low, less than 0.4% across all treatments (Fig.
-\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-Both the N100 and N120 treatments were statistically clearly different than the N0 treatment (Fig.
-\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.
-\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
+Severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
+Both the N100 and N120 treatments were statistically clearly different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
+However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
 
@@
 
-The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig.
-\@ref(fig:fig-2)b).
-The N treatment N180, was statistically clearly different than the control N60 treatment (Fig.
-\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
-As in the 2015 study, water management did not statistically clearly differ (Fig.
-\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
+The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Fig.&nbsp;\@ref(fig:fig-2)b).
+The N treatment N180, was statistically clearly different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
+As in the 2015 study, water management did not statistically clearly differ (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig.
-\@ref(fig:fig-2)d).
-In 2016 the N180 treatment was statistically clearly different from the N60 treatment, with N180 severity being higher (Fig.
-\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the flooded treatment, was also statistically clearly different (Fig.
-\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
+In 2016 the N180 treatment was statistically clearly different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
+The AWD water management, which was lower than the flooded treatment, was also statistically clearly different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
 
@@
 
-In 2016 the neither of the treatments, N rate or water management, were statistically clearly different from the control treatments for leaf sheath blight severity (Fig.
-\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
+In 2016 the neither of the treatments, N rate or water management, were statistically clearly different from the control treatments for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
 
@@
 In fact, in only one instance were we able to detect any clear effect of AWD on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than flooded treatment (Fig.
-\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
 
@@
 By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment appear to have improved the experiment.
-The the sheath blight incidence increased and the variability of sheath blight in the plots decreased (Fig.
-\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
+The the sheath blight incidence increased and the variability of sheath blight in the plots decreased (Fig.&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
 
@@
 
-```{r fig-5, fig.cap="Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity.
+```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity.
 Five different N treatments were applied to split plots depending on the experiment.
@@
 
-```{r fig-6, fig.cap="Posterior means and 95% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity.
+```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity.
 Five different N treatments were applied to split plots depending on the experiment.
@@
 # which R packages and versions?
-devtools::session_info()
+sessioninfo::session_info()
 ```

### 2018-11-01 analysis/paper/paper.Rmd
Fixes more spaces, captions and adds Duku 2016 ref

@@
 In order to avoid yield decline under AWD “safe” thresholds have been developed.
-Under safe AWD irrigation water is applied when the field water level reaches 15cm below the soil surface [@Richards2014].
+Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
 Fields are furthermore kept flooded during the flowering period to avoid plant stress.
@@
 
-While the effects of climate change directly on rice disease have been studied [@Duku2016XXXX CITATION XXXX] the effects of mitigation practices have not.
+While the effects of climate change directly on rice disease have been studied [@Duku2016 CITATION XXXX] the effects of mitigation practices have not.
 And because of the well documented effects of irrigation practices (CITATION XXXX) and N on sheath blight (CITATION XXXX); we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
@@
 The main plot treatments were alternate wetting and drying (AWD) and continuously flooded or farmers' practice as the control treatment.
-The main plot size was 12m x 12m (144 sq m), with a split-plot size of 5m x 5m (25 sq m).
-Replication size was 12m x 24m (288 sq m) with a buffer of 1m per split-plot for a whole experiment size of 1,152 sq m.
+The main plot size was 12&nbsp;m x 12&nbsp;m (144 sq m), with a split-plot size of 5&nbsp;m x 5&nbsp;m (25 sq m).
+Replication size was 12&nbsp;m x 24&nbsp;m (288 sq m) with a buffer of 1&nbsp;m per split-plot for a whole experiment size of 1,152 sq m.
 
-Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15cm below the soil surface irrigation water was applied to a level of 5cm.
-In flooded plots a standing water layer of 3-5cm was maintained throughout the growing season.
+Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
+In flooded plots a standing water layer of 3-5&nbsp;cm was maintained throughout the growing season.
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits) and N120 (120 kg per ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:tab-1)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg per ha applied as urea in three splits) and N120 (120&nbsp;kg per ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 The variety is commonly grown by farmers in the area, having good yields and moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro.
-Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20cm within and between rows.
+Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20&nbsp;cm within and between rows.
 
@@
 An isolate of *Rhizoctonia solani* AG1-1a previously isolated from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
-The isolate was transferred to 90mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C).
+The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C).
 Glass bottles of autoclaved rice grain and hull substrate were prepared and plugs of the culture were transferred from Petri dishes to the autoclaved substrate and incubated at room temperature for two weeks.
 
-The plots were inoculated 20 days after transplanting by spreading 151g of inoculum over the split-plot area with a 1m buffer on either end (4m x 11m).
+The plots were inoculated 20 days after transplanting by spreading 151&nbsp;g of inoculum over the split-plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
 
@@
 However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
-The main plot sizes were: Block 1 (B1) 21m x 20.5m (412.5 sq m) and Block 2 (B2) 20.25m x 21.6m (437.4 sq m).
-The split-plot sizes were B1 21m x 10.25m (215.25 sq m), B2 20.25m x 10.8m (218.7 sq m).
-The replication sizes were B1 - 42m x 20.5m (861 sq m) and B2 - 40.5m x 21.6m (874.8 sq m).
+The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4 sq m).
+The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25 sq m), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7 sq m).
+The replication sizes were B1 - 42m x 20.5&nbsp;m (861 sq m) and B2 - 40.5m x 21.6&nbsp;m (874.8 sq m).
 A buffer 0.5m per split-plot was used and the overall experiment size was 3471.6 sq m.
 
-Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied (Tab.&nbsp;\@ref(tab:tab-1)).
+Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg per ha as urea split into two applications) and N180 (180&nbsp;kg per ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 Nurseries of NSIC Rc222 were established on 7 January 2016.
-Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
+Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20&nbsp;cm within and between rows.
 
@@
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg per ha N (N100) and 180&nbsp;kg per ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg per ha N (N60) and 180&nbsp;kg per ha N (N180).
 Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
@@
 Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180).
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg per ha N (N100) and 180&nbsp;kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg per ha N (N60) and 180&nbsp;kg per ha N (N180).
 Points represent the mean observations of four replications."}
@@
 Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100 kg per ha N (N100) and 180 kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60 kg per ha N (N60) and 180 kg per ha N (N180)."}
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg per ha N (N100) and 180&nbsp;kg per ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg per ha N (N60) and 180&nbsp;kg per ha N (N180)."}
 

### 2018-11-02 analysis/paper/paper.Rmd
More nonbroken spaces and SI unit corrections

@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg; 11' N, longitude 121&deg; 15' E) in 2015 and 2016 dry seasons from December to May.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E) in 2015 and 2016 dry seasons from December to May.
 In the 2016 experiment changes were made to optimize the experiment based on findings from the 2015 experiment.
@@
 The main plot treatments were alternate wetting and drying (AWD) and continuously flooded or farmers' practice as the control treatment.
-The main plot size was 12&nbsp;m x 12&nbsp;m (144 sq m), with a split-plot size of 5&nbsp;m x 5&nbsp;m (25 sq m).
-Replication size was 12&nbsp;m x 24&nbsp;m (288 sq m) with a buffer of 1&nbsp;m per split-plot for a whole experiment size of 1,152 sq m.
+The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2), with a split-plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2).
+Replication size was 12&nbsp;m&nbsp;x&nbsp;24&nbsp;m (288&nbsp;m^2) with a buffer of 1&nbsp;m per split-plot for a whole experiment size of 1,152&nbsp;m^2.
 
@@
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg per ha applied as urea in three splits) and N120 (120&nbsp;kg per ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N_rate)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
-The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4 sq m).
-The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25 sq m), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7 sq m).
-The replication sizes were B1 - 42m x 20.5&nbsp;m (861 sq m) and B2 - 40.5m x 21.6&nbsp;m (874.8 sq m).
-A buffer 0.5m per split-plot was used and the overall experiment size was 3471.6 sq m.
+The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2).
+The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2).
+The replication sizes were B1 - 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2) and B2 - 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2).
+A buffer 0.5&nbsp;m per split-plot was used and the overall experiment size was 3471.6&nbsp;m^2.
 
-Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg per ha as urea split into two applications) and N180 (180&nbsp;kg per ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
+Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 Based on the 2015 results, the inoculation methods were modified in 2016 to increase the amount of inoculum and applied to a smaller area.
-Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1m x 1m) per plot, where one bottle contained 151g inoculum.
-A total amount of 1,510g of inoculum was applied to a 1m x 1m area.
+Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1&nbsp;m&nbsp;x&nbsp;1&nbsp;m) per plot, where one bottle contained 151&nbsp;g inoculum.
+A total amount of 1,510&nbsp;g of inoculum was applied to a 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m area.
 
@@
 
-In both experiments, two sample areas, sized 1m x 1m, per plot were assessed.
+In both experiments, two sample areas, sized 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m, per plot were assessed.
 The total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area.
@@
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg per ha N (N100) and 180&nbsp;kg per ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg per ha N (N60) and 180&nbsp;kg per ha N (N180).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180).
 Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
@@
 Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg per ha N (N100) and 180&nbsp;kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg per ha N (N60) and 180&nbsp;kg per ha N (N180).
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180).
 Points represent the mean observations of four replications."}
@@
 Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg per ha N (N100) and 180&nbsp;kg per ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg per ha N (N60) and 180&nbsp;kg per ha N (N180)."}
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180)."}
 

### 2018-11-02 analysis/paper/paper.Rmd
Update analysis/paper/paper.Rmd

@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1&nbsp;\% severity; 2 - 1 to 5&nbsp;\%; 3 - 5 to 15&nbsp;\%; 4 - 15 to 50&nbsp;\%; 5 - 50 to 100&nbsp;\%.
+The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1&nbsp;\% severity; 2 - 1 to 5&nbsp;\% severity; 3 - 5 to 15&nbsp;\% severity; 4 - 15 to 50&nbsp;\% severity; 5 - 50 to 100&nbsp;\% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
@@
 In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.&nbsp;\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
-Water management was not statistically clearly different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the N treatments, N100 and N120, were both statistically clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
+Water management was not clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
+However, the N treatments, N100 and N120, were both clearly statistically different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
 
@@
 Tiller sheath blight severity remained below 2&nbsp;\% (Fig.&nbsp;\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
-Both the N100 and N120 treatments were statistically clearly different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
+Both the N100 and N120 treatments were clearly statistically different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
+However, the AWD water management was not clearly statistically different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
 
@@
 Severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-Both the N100 and N120 treatments were statistically clearly different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-However, the AWD water management was not statistically clearly different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
+Both the N100 and N120 treatments were clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
+However, the AWD water management was not clearly statistically different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Fig.&nbsp;\@ref(fig:fig-2)b).
-The N treatment N180, was statistically clearly different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
-As in the 2015 study, water management did not statistically clearly differ (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
+The N treatment N180, was clearly statistically different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
+As in the 2015 study, water management did not clearly statistically differ (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
 
@@
 As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
-In 2016 the N180 treatment was statistically clearly different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the flooded treatment, was also statistically clearly different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
+In 2016 the N180 treatment was clearly statistically different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
+The AWD water management, which was lower than the flooded treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
 
@@
 
-In 2016 the neither of the treatments, N rate or water management, were statistically clearly different from the control treatments for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
+In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
 
@@
 Lapis for their technical support in the field.
-Lastly, we would like to remember our teammate Michael Noel, a part of the plant disease management team at IRRI and who helped design and managed the first year of the project but passed away in September 2016.
+Lastly, we would like to remember our team mate Michael Noel, a part of the plant disease management team at IRRI and who helped design and managed the first year of the project but passed away in September 2016.
 

### 2018-11-02 analysis/paper/paper.Rmd
adds references and replaced flooded with puddled

@@
 However, the mismanagement of these two management practices may trigger sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
-To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water saving (alternate wetting and drying) regime and traditional flood irrigation regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
+To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
 Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
@@
 Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
-Fields are furthermore kept flooded during the flowering period to avoid plant stress.
+Fields are furthermore kept puddled during the flowering period to avoid plant stress.
 As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
@@
 
-While the effects of climate change directly on rice disease have been studied [@Duku2016 CITATION XXXX] the effects of mitigation practices have not.
+While the effects of climate change directly on rice disease have been studied [@luo1998effects; @Duku2016] the effects of mitigation practices have not.
 And because of the well documented effects of irrigation practices (CITATION XXXX) and N on sheath blight (CITATION XXXX); we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
@@
 
-The main plot treatments were alternate wetting and drying (AWD) and continuously flooded or farmers' practice as the control treatment.
+The main plot treatments were alternate wetting and drying (AWD) and continuously puddled or farmers' practice as the control treatment.
 The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2), with a split-plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2).
@@
 Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
-In flooded plots a standing water layer of 3-5&nbsp;cm was maintained throughout the growing season.
+In puddled plots a standing water layer of 3-5&nbsp;cm was maintained throughout the growing season.
 
@@
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were: N rate - N0, irrigation management - flooded and for 2016 they were: N rate - N60, irrigation management - flooded.
+The base levels (control treatments) for the analyses for 2015 were: N rate - N0, irrigation management - puddled and for 2016 they were: N rate - N60, irrigation management - puddled
 
@@
 Both the N100 and N120 treatments were clearly statistically different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not clearly statistically different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
+However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
 
@@
 Both the N100 and N120 treatments were clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-However, the AWD water management was not clearly statistically different from the flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
+However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
 
@@
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
 In 2016 the N180 treatment was clearly statistically different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the flooded treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
+The AWD water management, which was lower than the puddled treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
 
@@
 In both experiments we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
-In fact, in only one instance were we able to detect any clear effect of AWD on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than flooded treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
+In fact, in only one instance were we able to detect any statistically clear effect of AWD on sheath blight.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
 
@@
 Higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
-However, in the 2016 experiment there were no detectable differences due to the N rate tiller and leaf severity.
+However, in the 2016 experiment there were no clear differences due to the N rate tiller and leaf severity.
 
@@
 In 2015 there were no clear differences in the interaction of irrigation and N rate between any of the three treatments.
-However, in the 2016 experiment the combination of AWD-N180 was clearly different, being lower, than the flooded-N60 combination treatment.
+However, in the 2016 experiment the combination of AWD-N180 was clearly different, being lower, than the puddled-N60 combination treatment.
 
@@
 
-The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000]. As manual transplanting becomes less common XXXXX...
+The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
+Manually transplanted rice had higher apparent infection rates than direct seeded rice.
+As manual transplanting becomes less common due to labor constraints, sheath blight risk may be decreased.
 
-Sheath blight has been predicted to XXXXX due to the effects of climate change (XXXXXX 20XX).
-
-While sheath blight remains an important disease in rice production with little resistance available in current varieties, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease.
+Climate change is predicted to decrease sheath blight risk in the Korean peninsula over the longer term.
+However, over the next 10 - 20 years the risk is predicted to remain the same as from 2000 - 2010 [@kim2015predicting].
+Therefore, it is likely to remain an important diease in the near future with little resistance available in current varieties.
+However, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease.
 
@@
 Disease progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD).
+Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD).
 Points represent the mean observations of four replications."}
@@
 Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
-Main plot irrigation treatments were permanently flooded (FLD) and alternate wetting and drying (AWD)."}
+Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD)."}
 

### 2018-11-02 analysis/2017 APPS abstract/README.Rmd
Replace "Flooded" with "Puddled"

--- 2017-04-10 doc/APPS/README.Rmd
@@
 Water and nitrogen management play vital roles in rice production.
-However, the mismanagement of these two management practices may trigger plant disease epidemics such as sheath blight of rice, caused by Rhizoctonia solani, which is favoured by wet conditions, high relative humidity, and high nitrogen fertiliser levels.
+However, the mismanagement of either may trigger plant disease epidemics such as sheath blight of rice, caused by Rhizoctonia solani, which is favoured by wet conditions, high relative humidity, and high nitrogen fertiliser levels.
+
 In order to understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes in the dry seasons of 2015 and 2016.
-The main plot irrigation treatments in both experiments were: flooded, maintaining 10cm standing water through the season and alternate wetting and drying (AWD) a water saving technology described by the International Rice Research Institute (IRRI).
+The main plot irrigation treatments in both experiments were: puddled, maintaining 10cm standing water through the season and alternate wetting and drying (AWD), a water saving technology developed by the International Rice Research Institute (IRRI) and partners as adaptation strategy for water-scarce environments.
 In 2015 the split plots were nitrogen (N) applications applied as 0 kg ha-1, 120 kg ha–1, and 150 kg ha–1 total N.
-In 2016 changes were made between seasons to address issues that were previously discovered in 2015.
+In 2016 changes were made to address issues discovered in 2015.
 In 2016 split plots were N applications at 60 kg ha-1 and 180 kg ha-1 total N.
 Nitrogen was applied in splits in both seasons.
+
 Disease scoring was the same in both experiments using a sheath blight assessment scale for field evaluation developed at IRRI to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
-Five and four disease assessments were made in 2015 and 2016 respectively.
+Five and four disease assessments were made in 2015 and 2016, respectively.
 Data were analysed using the area under the disease progress stairs (AUDPS) and multivariate generalised linear mixed models.
 We were unable to detect any differences in disease in either experiment due to irrigation methods, N rates or the interaction of the two treatments in either season.
-Our findings indicate that farmers can safely adopt AWD technology without risk of increasing sheath blight disease.
+Our findings indicate that farmers can safely adopt the AWD technology without risk of increasing sheath blight disease.
 

### 2018-11-02 analysis/2017 APPS abstract/README.Rmd
Replace more "flooded" with "puddled"

@@
 In order to understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with two irrigation regimes in the dry seasons of 2015 and 2016.
-The main plot irrigation treatments in both experiments were: puddled, maintaining 10cm standing water through the season and alternate wetting and drying (AWD), a water saving technology developed by the International Rice Research Institute (IRRI) and partners as adaptation strategy for water-scarce environments.
+The main plot irrigation treatments in both experiments were: flooded, maintaining 10cm standing water through the season and alternate wetting and drying (AWD), a water saving technology developed by the International Rice Research Institute (IRRI) and partners as adaptation strategy for water-scarce environments.
 In 2015 the split plots were nitrogen (N) applications applied as 0 kg ha-1, 120 kg ha–1, and 150 kg ha–1 total N.

### 2018-11-02 data-raw/README.Rmd
Revert "Remove TRT from data"
This reverts commit 0ef1212ad5f9cc39d60170add9de06a3e5dde5cd.
Update static docs
Replace more "flooded" with "puddled"

--- 2018-04-26 data-raw/README.Rmd
@@
 _rice.awd.pests_
+
+*Note* TRT is created here as a combination of the main plot/split plot
+treatment. This is used in place of plot numbers to keep the data in order.
+However, it is not used in the final analysis as a treatment effect.
 
@@
 DS2016[is.na(DS2016)] <- 0
-
-# Replace "Flooded" with "FLD" -------------------------------------------------
-DS2016$WMGT[which(DS2016$WMGT == "Flooded")] = "FLD"
 
@@
 
+# Arrange NRTE values
+AUDPS$NRTE <-
+  forcats::fct_relevel(AUDPS$NRTE,
+                       "N0",
+                       "N100",
+                       "N120",
+                       "N60",
+                       "N180")
+
 # Save data for inclusion in the package ---------------------------------------

### 2018-11-02 data-raw/README.Rmd
Replace more FLD with PDL

@@
 DS2015$TRT <- NA
-DS2015$TRT[which(DS2015$WMGT == "FLD" &
-                   DS2015$NRTE == 0)] = "FLD_N0"
-DS2015$TRT[which(DS2015$WMGT == "FLD" &
-                   DS2015$NRTE == 100)] = "FLD_N100"
-DS2015$TRT[which(DS2015$WMGT == "FLD" &
-                   DS2015$NRTE == 120)] = "FLD_N120"
+DS2015$TRT[which(DS2015$WMGT == "PDL" &
+                   DS2015$NRTE == 0)] = "PDL_N0"
+DS2015$TRT[which(DS2015$WMGT == "PDL" &
+                   DS2015$NRTE == 100)] = "PDL_N100"
+DS2015$TRT[which(DS2015$WMGT == "PDL" &
+                   DS2015$NRTE == 120)] = "PDL_N120"
 DS2015$TRT[which(DS2015$WMGT == "AWD" &
@@
 DS2016$TRT <- NA
-DS2016$TRT[which(DS2016$WMGT == "FLD" &
-                   DS2016$NRTE == 60)] = "FLD_N60"
-DS2016$TRT[which(DS2016$WMGT == "FLD" &
-                   DS2016$NRTE == 180)] = "FLD_N180"
+DS2016$TRT[which(DS2016$WMGT == "PDL" &
+                   DS2016$NRTE == 60)] = "PDL_N60"
+DS2016$TRT[which(DS2016$WMGT == "PDL" &
+                   DS2016$NRTE == 180)] = "PDL_N180"
 DS2016$TRT[which(DS2016$WMGT == "AWD" &
@@
     "AWD_N180",
-    "FLD_N0",
-    "FLD_N100",
-    "FLD_N120",
-    "FLD_N60",
-    "FLD_N180"
+    "PDL_N0",
+    "PDL_N100",
+    "PDL_N120",
+    "PDL_N60",
+    "PDL_N180"
   )

### 2018-11-02 analysis/paper/paper.Rmd
Correct formatting of superscript and dashes throughout

@@
 However, the mismanagement of these two management practices may trigger sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
-To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
+To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split--plot experiments with a water saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
 Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
@@
 Our findings suggest that farmers can adopt water saving technologies without risking increased sheath blight incidence.
-We suggest that further cross-cutting research in this area is warranted.
+We suggest that further cross--disciplinary research in this area is warranted.
 All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
@@
 Studies by Savary et al.
-[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5-10 &nbsp;\%.
+[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5--10 &nbsp;\%.
 The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15-40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
@@
 
-The AWD technology has been identified as promising climate-smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
+The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
 Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
@@
 
-The plot design was a split-plot randomised complete block design with four replicates where irrigation was the main plot treatment and N rate was the split-plot treatment.
+The plot design was a split--plot randomised complete block design with four replicates where irrigation was the main plot treatment and N rate was the split--plot treatment.
 
 The main plot treatments were alternate wetting and drying (AWD) and continuously puddled or farmers' practice as the control treatment.
-The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2), with a split-plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2).
-Replication size was 12&nbsp;m&nbsp;x&nbsp;24&nbsp;m (288&nbsp;m^2) with a buffer of 1&nbsp;m per split-plot for a whole experiment size of 1,152&nbsp;m^2.
+The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2^), with a split--plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2^).
+Replication size was 12&nbsp;m&nbsp;x&nbsp;24&nbsp;m (288&nbsp;m^2^) with a buffer of 1&nbsp;m per split--plot for a whole experiment size of 1,152&nbsp;m^2^.
 
 Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
-In puddled plots a standing water layer of 3-5&nbsp;cm was maintained throughout the growing season.
+In puddled plots a standing water layer of 3--5&nbsp;cm was maintained throughout the growing season.
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N_rate)).
+The split--plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 
-An isolate of *Rhizoctonia solani* AG1-1a previously isolated from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
+An isolate of *Rhizoctonia solani* AG1--1a previously isolated from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
 The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C).
@@
 
-The plots were inoculated 20 days after transplanting by spreading 151&nbsp;g of inoculum over the split-plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
+The plots were inoculated 20 days after transplanting by spreading 151&nbsp;g of inoculum over the split--plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
 
@@
 
-The 2016 experiment followed the same split-plot design as described for the 2015 experiment.
+The 2016 experiment followed the same split--plot design as described for the 2015 experiment.
 However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
-The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2).
-The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2).
-The replication sizes were B1 - 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2) and B2 - 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2).
-A buffer 0.5&nbsp;m per split-plot was used and the overall experiment size was 3471.6&nbsp;m^2.
+The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2^).
+The split--plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2^), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2^).
+The replication sizes were B1 --- 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2^) and B2 --- 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2^).
+A buffer 0.5&nbsp;m per split--plot was used and the overall experiment size was 3471.6&nbsp;m^2^.
 
-Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
+split--plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where 0 - no disease; 1 - trace to 1&nbsp;\% severity; 2 - 1 to 5&nbsp;\% severity; 3 - 5 to 15&nbsp;\% severity; 4 - 15 to 50&nbsp;\% severity; 5 - 50 to 100&nbsp;\% severity.
+The scale is an unequally spaced categorical scale where 0 -- no disease; 1 -- trace to 1&nbsp;\% severity; 2 -- 1 to 5&nbsp;\% severity; 3 -- 5 to 15&nbsp;\% severity; 4 -- 15 to 50&nbsp;\% severity; 5 -- 50 to 100&nbsp;\% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
@@
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were: N rate - N0, irrigation management - puddled and for 2016 they were: N rate - N60, irrigation management - puddled
+The base levels (control treatments) for the analyses for 2015 were: N rate -- N0, irrigation management -- puddled and for 2016 they were: N rate -- N60, irrigation management -- puddled
 
@@
 The remaining 50,000 samples were used to determine the posterior distribution of the parameters of the model.
-The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test.
+The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman--Rubin test.
 
@@
 In 2015 there were no clear differences in the interaction of irrigation and N rate between any of the three treatments.
-However, in the 2016 experiment the combination of AWD-N180 was clearly different, being lower, than the puddled-N60 combination treatment.
+However, in the 2016 experiment the combination of AWD--N180 was clearly different, being lower, than the PDL--N60 combination treatment.
 
@@
 Climate change is predicted to decrease sheath blight risk in the Korean peninsula over the longer term.
-However, over the next 10 - 20 years the risk is predicted to remain the same as from 2000 - 2010 [@kim2015predicting].
+However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@kim2015predicting].
 Therefore, it is likely to remain an important diease in the near future with little resistance available in current varieties.
@@
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid--point percentage value to calculate the AUDPS.
 Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD)."}
@@
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid--point percentage value to calculate the AUDPS.
 Five different N treatments were applied to split plots depending on the experiment.

### 2018-11-02 analysis/paper/paper.Rmd
Wordsmithing and other minor edits

@@
 We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did clearly differ statistically by irrigation treatment, but leaf sheath blight severity did not.
-Our findings suggest that farmers can adopt water saving technologies without risking increased sheath blight incidence.
+Our findings indicate that farmers can adopt water saving technologies without risking increased sheath blight incidence.
 We suggest that further cross--disciplinary research in this area is warranted.
@@
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
-In order to avoid yield decline under AWD “safe” thresholds have been developed.
+In order to avoid yield decline under AWD "safe"" thresholds have been developed.
 Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
@@
 The 2016 experiment followed the same split--plot design as described for the 2015 experiment.
-However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment.
+However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment due to differences in the blocks.
 The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2^).
@@
 
-split--plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
+Split--plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
 
@@
 Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1&nbsp;m&nbsp;x&nbsp;1&nbsp;m) per plot, where one bottle contained 151&nbsp;g inoculum.
-A total amount of 1,510&nbsp;g of inoculum was applied to a 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m area.
+A total amount of 1,510&nbsp;g of inoculum was applied to each 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m area.
 
@@
 
-Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using the R package `agricolae` [@R2018; @deMendiburu2017].
-Due to the scale used for collection, the severity data were converted to the midpoint percent value of the scale range for each value.
+Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 3.5.0 [@R2018], package `agricolae`, version 1.2-8, [@deMendiburu2017].
+Due to the use of a severity scale for data collection, the severity data were converted to the midpoint percent value of the scale range for each value.
 
@@
 
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@MCMCglmm2010].
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@MCMCglmm2010], version 2.26.
 Six models were created where the the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
@@
 Water management was not clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the N treatments, N100 and N120, were both clearly statistically different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
+However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly statistically different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
 
@@
 Tiller sheath blight severity remained below 2&nbsp;\% (Fig.&nbsp;\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
-Both the N100 and N120 treatments were clearly statistically different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
+Both the N100 and N120 treatment effects caused the tiller severity to be higher and clearly statistically different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
 However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
@@
 Severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-Both the N100 and N120 treatments were clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
+As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
 However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Fig.&nbsp;\@ref(fig:fig-2)b).
-The N treatment N180, was clearly statistically different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
+The N treatment N180 value was higher and clearly statistically different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
 As in the 2015 study, water management did not clearly statistically differ (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
@@
 As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
-In 2016 the N180 treatment was clearly statistically different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
+In 2016 the N180 treatment was again higher and clearly statistically different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
 The AWD water management, which was lower than the puddled treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
@@
 
-In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
+In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments, N60 and puddling water management, for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
 
@@
 By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment appear to have improved the experiment.
-The the sheath blight incidence increased and the variability of sheath blight in the plots decreased (Fig.&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
+The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Fig.&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
+Based on these results, it is suggested that the methods used in the 2016 experiment should be adopted in any further studies of this kind.
 
 It should be noted that the levels of leaf severity remained low (< 1 \%) throughout the growing season in all treatments for both years.
-As AWD can only feasibly be implemented in the dry season, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
+As AWD can only feasibly be implemented in the dry season.
+Therefor, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
 However, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases.
 
-The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
+As the rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
 Manually transplanted rice had higher apparent infection rates than direct seeded rice.
-As manual transplanting becomes less common due to labor constraints, sheath blight risk may be decreased.
+As manual transplanting becomes less common due to labor constraints, sheath blight risk may be decreased (CITATION XXXX) due changes in establishment practices.
+A combination of AWD and directd seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
 
@@
 
-The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
+The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
 We would also like to thank Dale Amozola, Paul Escandor and P.

### 2018-11-02 analysis/paper/paper.Rmd
Remove an errant "
wordsmithing

@@
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
-In order to avoid yield decline under AWD "safe"" thresholds have been developed.
+In order to avoid yield decline under AWD "safe" thresholds have been developed.
 Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
@@
 Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
-However, a change like this in the water regime in rice fields on a large scale might trigger different other effects, for example changes in disease intensity or severity.
+However, a change like this in the water regime in rice fields on a large scale might trigger different other unintended effects, for example changes in disease intensity or severity.
 

### 2018-11-02 analysis/paper/paper.Rmd
Fix "kgkg / ^"

@@
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180).
 Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
@@
 Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180).
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180).
 Points represent the mean observations of four replications."}
@@
 Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180)."}
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
 

### 2018-11-04 analysis/paper/paper.Rmd
Update abstract statement about disease scoring

@@
 To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split--plot experiments with a water saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
-Disease was scored in the same way in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
+Disease was scored using the same methodology in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
 We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did clearly differ statistically by irrigation treatment, but leaf sheath blight severity did not.

### 2018-11-04 analysis/paper/paper.Rmd
Update Rmd file

@@
 We suggest that further cross--disciplinary research in this area is warranted.
-All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
+All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests>.
 bibliography: references.bib
@@
 
+Add statement here... XXXXX
+
 # Discussion {-}
@@
 However, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease.
+
+Readers may find a reproducible research compendium that recreates this paper, that includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
 

### 2018-11-04 README.Rmd
Update DOCKER instructions in README
Update badge links

@@
 ```
-[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/openplantpathology/rice.awd.pests/commits/master)
+[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master)
 [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
@@
 [![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
-[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/phytopathology/rice_awd_pests?branch=master&svg=true)](https://ci.appveyor.com/project/phytopathology/rice_awd_pests)
+[![Build status](https://ci.appveyor.com/api/projects/status/mh6s2n35fgry2hjo/branch/master?svg=true)](https://ci.appveyor.com/project/adamhsparks/rice-awd-pests-9lo9u/branch/master)
 
@@
 
-    docker run -dp 8787:8787 adamhsparks/rice_awd_pests
+    docker run -dp 8787:8787 adamhsparks/rice-awd-pests
 

### 2018-11-04 README.Rmd
Fix badges and links (again)

@@
 [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) 
-[![Travis-CI Build Status](https://travis-ci.org/openplantpathology/rice_awd_pests.svg?branch=master)](https://travis-ci.org/openplantpathology/rice_awd_pests)
+[![Travis-CI Build Status](https://travis-ci.org/adamhsparks/rice_awd_pests.svg?branch=master)](https://travis-ci.org/adamhsparks/rice_awd_pests)
 [![Build status](https://ci.appveyor.com/api/projects/status/mh6s2n35fgry2hjo/branch/master?svg=true)](https://ci.appveyor.com/project/adamhsparks/rice-awd-pests-9lo9u/branch/master)
@@
 publication. The files hosted at
-<https://github.com/openplantpathology/rice_awd_pests> are the development
+<https://github.com/adamhsparks/rice_awd_pests> are the development
 versions and may have changed since the report was published.
@@
 ```
-git clone https://github.com/openplantpathology/rice_awd_pests.git
+git clone https://github.com/adamhsparks/rice_awd_pests.git
 ```

### 2018-11-04 data-raw/README.Rmd
Update data
Replaces FLD with PDL

@@
 
-devtools::use_data(RAW_data,
+usethis::use_data(RAW_data,
                   compress = "bzip2",
@@
 
-devtools::use_data(AUDPS,
+usethis::use_data(AUDPS,
                   compress = "bzip2",
@@
 
-devtools::use_data(N_rates,
+usethis::use_data(N_rates,
                   compress = "bzip2",

### 2018-11-05 analysis/paper/paper.Rmd
Add section on interaction of treatments to results

@@
 
-Add statement here... XXXXX
+The interaction of irrigation treatment AWD with N rate N0 in 2015 or N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
+For leaf severity in the 2015 experiment the interaction was not clearly different.
+In 2016 the interaction of N180 and N180 was clearly lower than the control puddled irrigation and N60 rate.
 

### 2018-11-06 analysis/paper/paper.Rmd
Update figures and remove old figures

@@
     axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.065, y = 0.76),
+    legend.position = c(x = 0.068, y = 0.76),
     legend.background = element_rect(
@@
     axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.1,
+    legend.position = c(x = 0.11,
                         y = 0.7),

### 2018-11-13 analysis/paper/paper.Rmd
Update description of a leaf

@@
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
-Leaves were rated as green (living) having at least XXX&nbsp;\% living tissue or dead, defined as having less than XXX&nbsp;\% living tissue.
+A leaf was considered living if at least 50&nbsp;% of its area was not brown or dark brown due to natural senescence.
+A leaf that was yellow green or light green due to a disease, such as tungro or nitrogen deficiency was still considered a living leaf.
 The same rating methodology was used in both experiments.

### 2018-12-21 analysis/paper/paper.Rmd
Update pkgdown and paper.Rmd

@@
 
-Sheath blight disease (*Rhizoctonia solani* Kühn), anastomosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
-Frank) Donk.] of rice is an economically important disease worldwide throughout tropical and temperate production areas.
+Sheath blight disease, caused by (*Rhizoctonia solani* Kühn), anastomosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
+Frank) Donk.], of rice is an economically important disease worldwide throughout tropical and temperate production areas.
 Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
 Studies by Savary et al.
-[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5--10 &nbsp;\%.
-The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011] fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
+[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5--10 &nbsp;\% annually.
+The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
@@
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
-In order to avoid yield decline under AWD "safe" thresholds have been developed.
+In order to avoid yield decline under AWD, "safe" thresholds have been developed.
 Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
-Fields are furthermore kept puddled during the flowering period to avoid plant stress.
+Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress.
 As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
@@
 Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
-However, a change like this in the water regime in rice fields on a large scale might trigger different other unintended effects, for example changes in disease intensity or severity.
+However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example changes in disease intensity or severity.
 
 While the effects of climate change directly on rice disease have been studied [@luo1998effects; @Duku2016] the effects of mitigation practices have not.
-And because of the well documented effects of irrigation practices (CITATION XXXX) and N on sheath blight (CITATION XXXX); we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
+And because of the well documented effects of irrigation practices [@] and N on sheath blight (CITATION XXXX); we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
 

### 2018-12-21 analysis/paper/paper.Rmd
Updates to paper.Rmd

@@
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Liping2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.

### 2018-12-21 analysis/paper/paper.Rmd
Update paper

@@
 While the effects of climate change directly on rice disease have been studied [@luo1998effects; @Duku2016] the effects of mitigation practices have not.
-And because of the well documented effects of irrigation practices [@] and N on sheath blight (CITATION XXXX); we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
+And because of the well documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight; we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
 
 # Materials and Methods {-}
+
+## Experimental Site {-}
 
@@
 The differences are detailed in the following sections.
+
+## Pathogen {-}
+
+An isolate of *Rhizoctonia solani* belonging to anasomosis group AG1--1a previously isolated from infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
+The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C) for five days.
+Glass bottles of autoclaved rice grain and hull substrate (1/5, w/w) were prepared and plugs of the culture were transferred from Petri dishes to the autoclaved substrate and incubated at room temperature for two weeks and used to inoculate the plots [@Castilla1996].
+
+## Host Plant {-}
+
+NSIC Rc222 an inbred semi-dwarf, high-yielding variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted was used in both experiments.
+The variety is commonly grown by farmers in the area, having good yields and moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro and no known resistance to sheath blight.
 
@@
 Trays of NSIC Rc222 were seeded on 19 December 2014.
-NSIC Rc222 is an inbred variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted.
-The variety is commonly grown by farmers in the area, having good yields and moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro.
 Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20&nbsp;cm within and between rows.
 
-### Inoculum Preparation and Application {-}
+### Inoculation Procedure {-}
 
-An isolate of *Rhizoctonia solani* AG1--1a previously isolated from infected rice was maintained on potato dextrose agar (PDA) medium in tubes.
-The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C).
-Glass bottles of autoclaved rice grain and hull substrate were prepared and plugs of the culture were transferred from Petri dishes to the autoclaved substrate and incubated at room temperature for two weeks.
-
-The plots were inoculated 20 days after transplanting by spreading 151&nbsp;g of inoculum over the split--plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
+The plots were inoculated 20 days after transplanting by applying 151&nbsp;g of inoculum over the split--plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
 
@@
 
-### Inoculum Preparation and Application {-}
+### Inoculation Procedure {-}
 
-Based on the 2015 results, the inoculation methods were modified in 2016 to increase the amount of inoculum and applied to a smaller area.
+Based on the 2015 results, the inoculum application methods were modified in 2016 to increase the amount of inoculum and applied to a smaller area.
 Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1&nbsp;m&nbsp;x&nbsp;1&nbsp;m) per plot, where one bottle contained 151&nbsp;g inoculum.

### 2018-12-21 analysis/paper/paper.Rmd
Update paper and template

@@
   dev = c("postscript"),
-  fig.width = 6.85,
-  fig.height = 6.85,
-  out.width = "100%",
   dpi = 300
@@
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Liping2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.

### 2019-06-17 R/plot_estimates.R
Import coda to pass checks

@@ -5,13 +5,14 @@
 #'  intervals of \pkg{MCMCglmm} outputs
 #'
 #' @name plot_tiller_estimates
-#' @param x An\code{\link[coda]{mcmc.list}} object
+#' @param x A \code{\link[coda]{mcmc.list}} object
 #'
 #' @examples \dontrun{
 #' # Plot posterior means and credible intervals
 #' plot_tiller_estimates(m1)
 #'}
 #'
+#' @import coda
 #' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
 #'
 #' @export
@@ -49,7 +50,7 @@ plot_tiller_estimates <- function(x) {
 #'  intervals of \pkg{MCMCglmm} outputs
 #'
 #' @name plot_leaf_estimates
-#' @param x An\code{\link[coda]{mcmc.list}} object
+#' @param x A \code{\link[coda]{mcmc.list}} object
 #'
 #' @examples \dontrun{
 #' # Plot posterior means and credible intervals

### 2019-06-17 R/plot_estimates_paper.R

@@ -5,7 +5,7 @@
 #'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
 #'
 #' @name plot_tiller_estimates_paper
-#' @param x An\code{\link[coda]{mcmc.list}} object
+#' @param x A \code{\link[coda]{mcmc.list}} object
 #' @param main_title Main title for the plot
 #'
 #' @examples \dontrun{
@@ -49,7 +49,7 @@ plot_tiller_estimates_paper <- function(x, main_title = "") {
 #'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
 #'
 #' @name plot_leaf_estimates_paper
-#' @param x An\code{\link[coda]{mcmc.list}} object
+#' @param x A \code{\link[coda]{mcmc.list}} object
 #' @param main_title Main title for the plot
 #'
 #' @examples \dontrun{

### 2019-06-17 analysis/paper/paper.Rmd
Update figure sizes and legend positions and padding

@@
   comment = "#>",
-  fig.path = "../figures/",
-  dev = c("postscript"),
+  fig.path = "figures/",
+  fig.width = 3.31,
+  dev = c("postscript", "png"),
   dpi = 300
@@
 
-Readers may find a reproducible research compendium that recreates this paper, that includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2018].
+Readers may find a reproducible research compendium that recreates this paper, that includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2019].
 
@@
        shape = "Irrigation") +
-  theme_classic() +
+  theme_classic(base_size = 8) +
   theme(
@@
     axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.068, y = 0.76),
+    legend.position = c(x = 0.101, y = 0.74),
+    legend.key.size = unit(0, 'lines'),
     legend.background = element_rect(
@@
              scales = "free_x") +
-  theme_classic() +
+  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
        shape = "N Rate") +
-  theme_classic() +
+  theme_classic(base_size = 8) +
   theme(
@@
     axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.11,
+    legend.position = c(x = 0.15,
                         y = 0.7),
+    legend.key.size = unit(0, 'lines'),
     legend.background = element_rect(
@@
   ylab("Tiller Incidence AUDPS") +
-  theme_classic() +
+  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Tiller Severity AUDPS") +
-  theme_classic() +
+  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Leaf Severity AUDPS") +
-  theme_classic() +
+  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),

### 2019-06-17 analysis/paper/paper.Rmd
Knit PDF document

@@
 output:
-  bookdown::word_document2:
+  bookdown::pdf_document2:
     toc: no
-    reference_docx: "../templates/template.docx"
+    fig_caption: yes
+    #reference_docx: "../templates/template.docx"
 ---
@@
 library(gridExtra)
+library(pander)
 library(rice.awd.pests)
@@
 The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
-We would also like to thank Dale Amozola, Paul Escandor and P.
+We would also like to thank D.
+Amozola, P.
+Escandor and P.
 Lapis for their technical support in the field.
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line. 
+##### pagebreak  -->
 
 # References {-}
-<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
+<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document:   -->
 <div id="refs"></div>
-
-##### pagebreak
 
@@
 
-kable(N_rates,
+pander(N_rates,
       caption = "Nitrogen application rates for 2015 and 2016.
@@
 ```
-
-##### pagebreak
 
@@
 Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD).
-Points represent the mean observations of four replications."}
+Points represent the mean observations of four replications.", fig.width=3.31}
 

### 2019-07-23 analysis/paper/paper.Rmd
Specify UTF8 in LaTeX header

@@
     #reference_docx: "../templates/template.docx"
+header-includes:
+  - \usepackage[T1]{fontenc}
+  - \usepackage[utf8]{inputenc}
 ---

### 2019-07-23 analysis/paper/paper.Rmd
Declare Unicode Char 2500;

--- 2019-06-17 analysis/paper/paper.Rmd
@@
     #reference_docx: "../templates/template.docx"
+header-includes:
+  - \usepackage[T1]{fontenc}
+  - \usepackage[utf8]{inputenc}
+  - \DeclareUnicodeCharacter{2500}{\mbox{\vrule height2.2ptdepth-1.8ptwidth.5em}}
 ---

### 2019-07-24 analysis/paper/paper.Rmd
Update Dockerfile Rocker Version

@@
   Water and nitrogen management play vital roles in rice production.
-However, the mismanagement of these two management practices may trigger sheath blight of rice, caused by _Rhizoctonia solani_, which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
+However, the mismanagement of these two crop inputs may trigger the development of sheath blight of rice, caused by _Thanatephorus cucumeris_ (strain AG1-IA), which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
 To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split--plot experiments with a water saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
@@
 
-Sheath blight disease, caused by (*Rhizoctonia solani* Kühn), anastomosis group 1 [(teleomorph: *Thanatephorus cucumeris* (A.B.
-Frank) Donk.], of rice is an economically important disease worldwide throughout tropical and temperate production areas.
+Sheath blight disease, caused by (*Thanatephorus cucumeris*  (A.B.
+Frank) Donk.), anastomosis group 1, of rice is an economically important disease worldwide throughout tropical and temperate production areas.
 Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
-Studies by Savary et al.
-[-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5--10 &nbsp;\% annually.
-The disease is best managed through an integrated disease management approach which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
+Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5--10 &nbsp;\% annually.
+The disease is best managed through an integrated disease management approach, which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 

### 2019-07-30 data-raw/README.Rmd
Update raw-data README

@@
 ---
-title: "Clean 2015 Raw Data"
-output: github_document
+title: "Clean and Process Raw Data"
+output:
+  github_document:
+    pandoc_args: --webtex
 ---
@@
 
+# Load Libraries
+
+```{r libraries}
+library(tidyverse)
+library(agricolae)
+library(usethis)
+```
+
 # 2015 experiment
 
-```{r}
+Preprocess 2015 data for all assessment dates
 
-library(readr)
-library(dplyr)
-
-# Preprocess 2015 data for all assessment dates
-
+```{r 2015Exp}
 files <-
@@
 
-  x <- dplyr::arrange(x, REP, TRT)
+  x <- arrange(x, REP, TRT)
 
@@
     x %>%
-    dplyr::mutate(TShB_incidence = NTShB / NTIL)
+    mutate(TShB_incidence = NTShB / NTIL)
 
   TShB_incidence <-
-    x %>% dplyr::select(REP,
+    x %>% select(REP,
                         TRT,
@@
       x %>%
-      dplyr::select(
+      select(
         TRT,
@@
       ) %>%
-      tidyr::gather(LEAF,
+      gather(LEAF,
                     LEAF_ShB,
-                    dplyr::starts_with("SL"))
+                    starts_with("SL"))
 
@@
 
-  z <- dplyr::bind_rows(TIL)
-  x <- dplyr::left_join(TShB_incidence, z)
+  z <- bind_rows(TIL)
+  x <- left_join(TShB_incidence, z)
 
@@
 # Run reformat function for all 2015 files -------------------------------------
-DS2015 <- purrr::map_df(files, reformat)
+DS2015 <- map_df(files, reformat)
 
@@
 
-DS2015$YEAR <- lubridate::year(DS2015$DATE)
+DS2015$YEAR <- year(DS2015$DATE)
 
@@
 DS2015 <-
-  DS2015 %>% dplyr::select(
+  DS2015 %>% select(
     YEAR,
@@
 
-DS2015 <- tibble::as_tibble(dplyr::arrange(DS2015, ASMT, PLOT))
+DS2015 <- arrange(DS2015, ASMT, PLOT)
 
@@
 # First assessment -------------------------------------------------------------
-DS2016_A1 <- readr::read_csv("data/DS2016_Raw_1.csv")
+DS2016_A1 <- read_csv("data/DS2016_Raw_1.csv")
 # Fill missing values in NTIL and NTShB
 DS2016_A1 <-
-  DS2016_A1 %>% tidyr::fill(NTIL)
+  DS2016_A1 %>% fill(NTIL)
 DS2016_A1 <-
-  DS2016_A1 %>% tidyr::fill(NTShB)
+  DS2016_A1 %>% fill(NTShB)
 
@@
 # Second assessement -----------------------------------------------------------
-DS2016_A2 <- readr::read_csv("data/DS2016_Raw_2.csv")
+DS2016_A2 <- read_csv("data/DS2016_Raw_2.csv")
 DS2016_A2 <-
-  DS2016_A2 %>% tidyr::fill(NTIL)
+  DS2016_A2 %>% fill(NTIL)
 DS2016_A2 <-
-  DS2016_A2 %>% tidyr::fill(NTShB)
+  DS2016_A2 %>% fill(NTShB)
 
@@
 # Third assessement ------------------------------------------------------------
-DS2016_A3 <- readr::read_csv("data/DS2016_Raw_3.csv")
+DS2016_A3 <- read_csv("data/DS2016_Raw_3.csv")
 DS2016_A3 <-
-  DS2016_A3 %>% tidyr::fill(NTIL)
+  DS2016_A3 %>% fill(NTIL)
 DS2016_A3 <-
-  DS2016_A3 %>% tidyr::fill(NTShB)
+  DS2016_A3 %>% fill(NTShB)
 
@@
 # Fourth assessment ------------------------------------------------------------
-DS2016_A4 <- readr::read_csv("data/DS2016_Raw_4.csv")
+DS2016_A4 <- read_csv("data/DS2016_Raw_4.csv")
 DS2016_A4 <-
-  DS2016_A4 %>% tidyr::fill(NTIL)
+  DS2016_A4 %>% fill(NTIL)
 DS2016_A4 <-
-  DS2016_A4 %>% tidyr::fill(NTShB)
+  DS2016_A4 %>% fill(NTShB)
 
@@
   DS2016 %>%
-  tidyr::gather(
+  gather(
     LEAF,
     LEAF_ShB,
-    dplyr::starts_with("ShBL"),
+    starts_with("ShBL"),
     -DATE,
@@
   DS2016 %>%
-  dplyr::group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
-  dplyr::mutate(TShB_incidence = NTShB / NTIL)
+  group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
+  mutate(TShB_incidence = NTShB / NTIL)
 
-DS2016 <- dplyr::rename(DS2016, TIL_ShB = NSHShB)
+DS2016 <- rename(DS2016, TIL_ShB = NSHShB)
 
-DS2016$YEAR <- lubridate::year(DS2016$DATE)
+DS2016$YEAR <- year(DS2016$DATE)
 DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)
@@
 DS2016 <-
-  DS2016 %>% dplyr::select(
+  DS2016 %>% select(
     YEAR,
@@
 
-DS2016 <- tibble::as_tibble(dplyr::arrange(DS2016, ASMT, PLOT))
+DS2016 <- as_tibble(arrange(DS2016, ASMT, PLOT))
 
@@
 
-DAYS_2016 <- lubridate::time_length(DATE_1 - DATE_2, unit = "day")
+DAYS_2016 <- time_length(DATE_1 - DATE_2, unit = "day")
 DS2016$DAYS <-
@@
 
-# Calculating Area Under the Disease Progress Stairs (AUDPS)
+# Calculating Disease Severity Index and Area Under the Disease Progress Stairs (AUDPS)
 
 Because the data were collected on an ordinal scale, but not evenly spaced,
-the data are converted to the midpoint value of the percent range for severity
-and then the AUDPS is calculated from that. See lines 544 and 559 for this.
-
-After that the AUDPS is calculated using functionality from the _agricolae_
-package.
+the data are converted to the midpoint value of the percent range for disease
+severity index and then the AUDPS is calculated from that.
 
@@
 
-RAW_data <- tibble::as_tibble(rbind(as.data.frame(DS2015),
+RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
                                     as.data.frame(DS2016)))
@@
 RAW_data$NRTE <-
-  forcats::fct_relevel(RAW_data$NRTE,
+  fct_relevel(RAW_data$NRTE,
                        "0",
@@
 RAW_data$TRT <-
-  forcats::fct_relevel(
+  fct_relevel(
     RAW_data$TRT,
@@
 RAW_data <-
-  dplyr::mutate(
+  mutate(
     RAW_data,
-    PERC_TIL_ShB = dplyr::case_when(
+    PERC_TIL_ShB = case_when(
       TIL_ShB == 0 ~ 0,
@@
 RAW_data <-
-  dplyr::mutate(
+  mutate(
     RAW_data,
-    PERC_LEAF_ShB = dplyr::case_when(
+    PERC_LEAF_ShB = case_when(
       LEAF_ShB == 0 ~ 0,
@@
 
+# add column with midpoint +1  % leaf ShB severity -----------------------------
+RAW_data <-
+  mutate(
+    RAW_data,
+    PERC_LEAF_ShB = case_when(
+      LEAF_ShB == 0 ~ 1,
+      LEAF_ShB == 1 ~ 2.5,
+      LEAF_ShB == 2 ~ 10,
+      LEAF_ShB == 3 ~ 32.5,
+      LEAF_ShB == 4 ~ 75,
+      TRUE ~ 100
+    )
+  )
+
 DS2015 <- subset(RAW_data, YEAR == "2015")
 DS2016 <- subset(RAW_data, YEAR == "2016")
+```
 
+# Calculate disease index values
+See K. S. Chiang et al. 2017
+
+DSI<sub>Modified</sub> = Mid<sub><em>Q</em></sub> + <em>R</em>/Total Number of Observations * (Mid<sub><em>Q+1</em></sub> - Mid<sub><em>Q</em></sub>)
+
+```{r DSI}
+TShB_sev_15 <- 
+  DS2015 %>%
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
+  arrange(PLOT) %>% 
+  mutate(DSI = PERC_TIL_ShB + ())
+```
+
+```{r AUDPS}
 # calculate AUDPS values -------------------------------------------------------
@@
 
-# 2015 Tiller incidence setup --------------------------------------------------
-TShB_inc_15 <-
+# 2015 Tiller incidence AUDPS --------------------------------------------------
+TShb_inc_15 <-
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
-  dplyr::arrange(PLOT)
-
-TShB_inc_wide <-
-  reshape2::dcast(TShB_inc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_incidence")
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(
+    .funs = funs(mean(., na.rm = TRUE)),
+    .vars = vars(PLOT_TShB_incidence = TShB_incidence)
+  ) %>%
+  arrange(PLOT) %>%
+  group_by(YEAR, REP, TRT, PLOT) %>%
+  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))
 
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
+  arrange(PLOT)
 
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
+  arrange(PLOT)
 
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_LShB_severity = LEAF_ShB)) %>%
+  arrange(PLOT)
 
@@
   DS2015 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
+  arrange(PLOT)
 
@@
 TShB_inc_AUDPS <-
-  agricolae::audps(evaluation = TShB_inc_wide[, 2:6],
-                   dates = dplyr::pull(TShB_inc_15[1:5, 6]))
+  audps(evaluation = TShB_inc_wide[, 2:6],
+                   dates = pull(TShB_inc_15[1:5, 6]))
 
 TShB_sev_AUDPS <-
-  agricolae::audps(evaluation = TShB_sev_wide[, 2:6],
-                   dates = dplyr::pull(TShB_sev_15[1:5, 6]))
+  audps(evaluation = TShB_sev_wide[, 2:6],
+                   dates = pull(TShB_sev_15[1:5, 6]))
 
 LShB_sev_AUDPS <-
-  agricolae::audps(evaluation = LShB_sev_wide[, 2:6],
-                   dates = dplyr::pull(LShB_sev_15[1:5, 6]))
+  audps(evaluation = LShB_sev_wide[, 2:6],
+                   dates = pull(LShB_sev_15[1:5, 6]))
 
 TShB_percent_AUDPS <-
-  agricolae::audps(evaluation = TShB_perc_wide[, 2:6],
-        dates = dplyr::pull(TShB_perc_15[1:5, 6]))
+  audps(evaluation = TShB_perc_wide[, 2:6],
+        dates = pull(TShB_perc_15[1:5, 6]))
 
 LShB_percent_AUDPS <-
-  agricolae::audps(evaluation = LShB_perc_wide[, 2:6],
-        dates = dplyr::pull(LShB_perc_15[1:5, 6]))
+  audps(evaluation = LShB_perc_wide[, 2:6],
+        dates = pull(LShB_perc_15[1:5, 6]))
 
 AUDPS_15 <-
-  tibble::as_tibble(
+  as_tibble(
     cbind(
@@
 
-ShB_15 <- dplyr::left_join(TShB_inc_15, AUDPS_15, by = "PLOT")
+ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")
 
@@
   DS2016 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_TShB_incidence = TShB_incidence)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
+  arrange(PLOT)
 
@@
   DS2016 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_TShB_severity = TIL_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
+  arrange(PLOT)
 
@@
   DS2016 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
+  arrange(PLOT)
 
@@
   DS2016 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_LShB_severity = LEAF_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_LShB_severity = LEAF_ShB)) %>%
+  arrange(PLOT)
 
@@
   DS2016 %>%
-  dplyr::group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  dplyr::summarise_at(.funs = dplyr::funs(mean(., na.rm = TRUE)),
-                      .vars = dplyr::vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
-  dplyr::arrange(PLOT)
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
+  arrange(PLOT)
 
@@
 TShB_inc_AUDPS <-
-  agricolae::audps(evaluation = TShB_inc_wide[, 2:5],
-                   dates = dplyr::pull(TShB_inc_16[1:4, 6]))
+  audps(evaluation = TShB_inc_wide[, 2:5],
+                   dates = pull(TShB_inc_16[1:4, 6]))
 
 TShB_sev_AUDPS <-
-  agricolae::audps(evaluation = TShB_sev_wide[, 2:5],
-                   dates = dplyr::pull(TShB_sev_16[1:4, 6]))
+  audps(evaluation = TShB_sev_wide[, 2:5],
+                   dates = pull(TShB_sev_16[1:4, 6]))
 
 LShB_sev_AUDPS <-
-  agricolae::audps(evaluation = LShB_sev_wide[, 2:5],
-                   dates = dplyr::pull(LShB_sev_16[1:4, 6]))
+  audps(evaluation = LShB_sev_wide[, 2:5],
+                   dates = pull(LShB_sev_16[1:4, 6]))
 
 TShB_percent_AUDPS <-
-  agricolae::audps(evaluation = TShB_perc_wide[, 2:5],
-                   dates = dplyr::pull(TShB_perc_16[1:4, 6]))
+  audps(evaluation = TShB_perc_wide[, 2:5],
+                   dates = pull(TShB_perc_16[1:4, 6]))
 
 LShB_percent_AUDPS <-
-  agricolae::audps(evaluation = LShB_perc_wide[, 2:5],
-                   dates = dplyr::pull(LShB_perc_16[1:4, 6]))
+  audps(evaluation = LShB_perc_wide[, 2:5],
+                   dates = pull(LShB_perc_16[1:4, 6]))
 
 AUDPS_16 <-
-  tibble::as_tibble(
+  as_tibble(
     cbind(
@@
 
-ShB_16 <- dplyr::left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))
+ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))
 
 # Merge AUDPS data for graphing ------------------------------------------------
-AUDPS <- tibble::as_data_frame(tibble::as_tibble(rbind(ShB_15, ShB_16)))
-AUDPS <- tidyr::separate(data = AUDPS, col = TRT,
+AUDPS <- as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
+AUDPS <- separate(data = AUDPS, col = TRT,
                          sep = "_",
                          into = c("WMGT", "NRTE"))
-AUDPS <- dplyr::mutate_at(.tbl = AUDPS,
+AUDPS <- mutate_at(.tbl = AUDPS,
                               .funs = factor,
@@
 AUDPS$NRTE <-
-  forcats::fct_relevel(AUDPS$NRTE,
+  fct_relevel(AUDPS$NRTE,
                        "N0",
@@
 
-usethis::use_data(RAW_data,
+use_data(RAW_data,
                   compress = "bzip2",
@@
 
-usethis::use_data(AUDPS,
+use_data(AUDPS,
                   compress = "bzip2",
@@
 
-usethis::use_data(N_rates,
+use_data(N_rates,
                   compress = "bzip2",

### 2019-07-31 data-raw/README.Rmd
Update data-raw README

@@
 library(usethis)
+library(lubridate)
 ```
@@
 ```{r 2015Exp}
+# Preprocess 2015 data for all assessment dates
+
 files <-
@@
   DS2015 %>%
-  mutate(
-    DAI = case_when(
-      ASMT == 1 ~ 14,
+  mutate(DAI = case_when(ASMT == 1 ~ 14,
                          ASMT == 2 ~ 22,
@@
                          ASMT == 4 ~ 49,
-      ASMT == 5 ~ 62,
-    )
-  )
+                         ASMT == 5 ~ 62))
 
@@
     NRTE
-  )
+  ) %>% 
+  mutate(REP = as.integer(REP),
+         HILL = as.integer(HILL))
 
@@
 rm(files, reformat)
-
 ```
@@
 
+ Preprocess 2016 data for all assessments
+
+1. Cleanup date format and fill empty dates
+2. Fill empty NTIL (for same hill, not missing values)
+3. Fill empty NTShB (for same hill, not missing values)
+4. Add column with number of days after inoculation (DAI)
+
 ```{r}
-# Preprocess 2016 data for all assessments
-#
-# 1. Cleanup date format and fill empty dates
-# 2. Fill empty NTIL (for same hill, not missing values)
-# 3. Fill empty NTShB (for same hill, not missing values)
-# 4. Add column with number of days after inoculation (DAI)
+library(tidyverse)
+library(agricolae)
+library(usethis)
+library(lubridate)
 
@@
 
-DS2016 <- as_tibble(arrange(DS2016, ASMT, PLOT))
+DS2016 <- arrange(DS2016, ASMT, PLOT)
 
@@
 
-RAW_data <- as_tibble(rbind(as.data.frame(DS2015),
-                                    as.data.frame(DS2016)))
+RAW_data <- bind_rows(DS2015, DS2016)
 
 # convert columns to factor ----------------------------------------------------
-RAW_data$YEAR <- factor(RAW_data$YEAR)
-RAW_data$ASMT <- factor(RAW_data$ASMT)
-RAW_data$PLOT <- factor(RAW_data$PLOT)
-RAW_data$REP <- factor(RAW_data$REP)
-RAW_data$TRT <- factor(RAW_data$TRT)
-RAW_data$WMGT <- factor(RAW_data$WMGT)
-RAW_data$NRTE <- factor(RAW_data$NRTE)
-RAW_data$SMPL <- factor(RAW_data$SMPL)
-RAW_data$HILL <- factor(RAW_data$HILL)
-RAW_data$TIL <- factor(RAW_data$TIL)
-RAW_data$LEAF <- factor(RAW_data$LEAF)
+RAW_data <-
+  RAW_data %>%
+  mutate(
+    YEAR = as.factor(YEAR),
+    ASMT = as.factor(ASMT),
+    PLOT = as.factor(PLOT),
+    REP = as.factor(REP),
+    TRT = as.factor(TRT),
+    WMGT = as.factor(WMGT),
+    NRTE = as.factor(NRTE),
+    SMPL = as.factor(SMPL),
+    HILL = as.factor(HILL),
+    TIL = as.factor(TIL),
+    LEAF = as.factor(LEAF)
+  )
 
@@
 
+# add column with midpoint +1  % tiller ShB severity ---------------------------
+
+RAW_data <-
+  mutate(
+    RAW_data,
+    PERC_TIL_ShB_1 = case_when(
+      TIL_ShB == 0 ~ 1,
+      TIL_ShB == 1 ~ 2.5,
+      TIL_ShB == 2 ~ 10,
+      TIL_ShB == 3 ~ 32.5,
+      TIL_ShB == 4 ~ 75,
+      TRUE ~ 100
+    )
+  )
+
 # add column with midpoint % leaf ShB severity ---------------------------------
@@
     RAW_data,
-    PERC_LEAF_ShB = case_when(
+    PERC_LEAF_ShB_1 = case_when(
       LEAF_ShB == 0 ~ 1,
@@
 ```{r DSI}
-TShB_sev_15 <- 
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
-  arrange(PLOT) %>% 
-  mutate(DSI = PERC_TIL_ShB + ())
+#DS2015 <- 
+#  DS2015 %>% 
+#  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>% 
+#  mutate(TShB_DSI = (TIL_ShB + )/
 ```
@@
 
-# 2015 Tiller incidence AUDPS --------------------------------------------------
-TShb_inc_15 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(
-    .funs = funs(mean(., na.rm = TRUE)),
-    .vars = vars(PLOT_TShB_incidence = TShB_incidence)
-  ) %>%
-  arrange(PLOT) %>%
-  group_by(YEAR, REP, TRT, PLOT) %>%
-  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))
-
-# 2015 Tiller Severity AUDPS ---------------------------------------------------
 TShB_sev_15 <-
@@
 
-# Calculate 2015 AUDPS ---------------------------------------------------------
-
-TShB_inc_AUDPS <-
-  audps(evaluation = TShB_inc_wide[, 2:6],
-                   dates = pull(TShB_inc_15[1:5, 6]))
+TShb_inc_15 <-
+  DS2015 %>%
+  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
+  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
+               .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
+  arrange(PLOT) %>%
+  group_by(YEAR, REP, TRT, PLOT) %>%
+  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))
 

### 2020-03-09 data-raw/README.Rmd
Fix issue in 2015 Tiller ShB incidence AUDPS on line 714

@@
   summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
+                      .vars = vars(PLOT_TShB_percent = PERC_TIL_ShB)) %>%
   arrange(PLOT)
@@
 TShB_perc_wide <-
-  reshape2::dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")
+  reshape2::dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_percent")
 
@@
   summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
+                      .vars = vars(PLOT_LShB_percent = PERC_LEAF_ShB)) %>%
   arrange(PLOT)
@@
 LShB_perc_wide <-
-  reshape2::dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")
+  reshape2::dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_percent")
 
-TShb_inc_15 <-
+TShB_inc_15 <-
   DS2015 %>%
@@
   summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))
+
+TShB_inc_AUDPS <-  pull(TShB_inc_15, AUDPS)
 
@@
 TShB_perc_wide <-
-  reshape2::dcast(TShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")
+  reshape2::dcast(TShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_percent")
 
@@
 LShB_perc_wide <-
-  reshape2::dcast(LShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")
+  reshape2::dcast(LShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_LShB_percent")
 

### 2020-05-19 README.Rmd
Correct link in README

@@
 publication. The files hosted at
-<https://github.com/adamhsparks/rice_awd_pests> are the development
+<https://github.com/adamhsparks/rice_AWD_ShB_analysis> are the development
 versions and may have changed since the report was published.

### 2020-05-19 README.Rmd
Remove Travis and Appveyor

@@
 [![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
-[![Travis-CI Build Status](https://travis-ci.org/adamhsparks/rice_awd_pests.svg?branch=master)](https://travis-ci.org/adamhsparks/rice_awd_pests)
-[![Build status](https://ci.appveyor.com/api/projects/status/mh6s2n35fgry2hjo/branch/master?svg=true)](https://ci.appveyor.com/project/adamhsparks/rice-awd-pests-9lo9u/branch/master)
 

### 2020-05-19 README.Rmd
Add GitHub Actions

@@
 ```
-[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master)
-[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
-[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/)
+
+[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master) [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
+[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) ![R-CMD-check](https://github.com/adamhsparks/rice_AWD_ShB_analysis/workflows/R-CMD-check/badge.svg)
 

### 2020-05-19 README.Rmd
fix another link in README
Update name of package

@@
 
-Once the download is complete, open the `rice.awd.pests.Rproj` in RStudio to
+Once the download is complete, open the `rice.awd.shb.Rproj` in RStudio to
 begin working with the package and compendium files.
@@
 
-    docker run -dp 8787:8787 adamhsparks/rice-awd-pests
+    docker run -dp 8787:8787 adamhsparks/rice_AWD_ShB_analysis
 

### 2020-05-19 README.Rmd
Fix instructions for cloning
Update link to personal site
Spellcheck and remove extra "/" in a URL

@@
 ```
-git clone https://github.com/adamhsparks/rice_awd_pests.git
+git clone https://github.com/adamhsparks/rice_AWD_ShB_analysis.git
 ```
@@
 markdown document, and knit them to produce the results in the paper. More
-information about using RStudio in Docker is avaiable at the
+information about using RStudio in Docker is available at the
 [Rocker](https://github.com/rocker-org)
@@
 (+61) 7.4631.1948   adam.sparks@usq.edu.au  
-https://staffprofile.usq.edu.au/Profile/Adam-Sparks
+https://adamhsparks.com/

### 2020-05-19 data-raw/README.Rmd
clean up line breaks and fix warnings in R code

@@
 
-The raw data are located in the `data` folder of the installed
-_rice.awd.pests_
+The raw data are located in the `data` folder of the installed _rice.awd.shb_
 
-*Note* TRT is created here as a combination of the main plot/split plot
-treatment. This is used in place of plot numbers to keep the data in order.
+*Note* TRT is created here as a combination of the main plot/split plot treatment.
+This is used in place of plot numbers to keep the data in order. 
 However, it is not used in the final analysis as a treatment effect.
@@
 # Merge AUDPS data for graphing ------------------------------------------------
-AUDPS <- as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
+AUDPS <- as.data.frame(as_tibble(rbind(ShB_15, ShB_16)))
 AUDPS <- separate(data = AUDPS, col = TRT,

### 2020-06-11 data-raw/README.Rmd
Clean up data-raw files

--- 2019-07-31 data-raw/README.Rmd
@@
 ---
-title: "Clean and Process Raw Data"
+title: "Data Raw Files"
 output:
@@
 
-The raw data are located in the `data` folder of the installed
-_rice.awd.pests_
-
-*Note* TRT is created here as a combination of the main plot/split plot
-treatment. This is used in place of plot numbers to keep the data in order.
-However, it is not used in the final analysis as a treatment effect.
-
-# Load Libraries
-
-```{r libraries}
-library(tidyverse)
-library(agricolae)
-library(usethis)
-library(lubridate)
-```
-
-# 2015 experiment
-
-Preprocess 2015 data for all assessment dates
-
-```{r 2015Exp}
-# Preprocess 2015 data for all assessment dates
-
-files <-
-  list.files("data", pattern = "^DS2015_Raw", full.names = TRUE)
-
-reformat <- function(files) {
-  x <- read_csv(
-    files,
-    cols(
-      col_character(),
-      col_character(),
-      col_character(),
-      col_character(),
-      col_character(),
-      col_character(),
-      col_double(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer(),
-      col_integer()
-    ),
-    col_names = TRUE
-  )
-  x[is.na(x)] <- 0
-
-  x <- arrange(x, REP, TRT)
-
-  # add plot numbers
-  x$PLOT <- rep(1:24, each = 18)
-
-  # Calculate tiller sheath blight incidence -----------------------------------
-  x <-
-    x %>%
-    mutate(TShB_incidence = NTShB / NTIL)
-
-  TShB_incidence <-
-    x %>% select(REP,
-                 TRT,
-                 WMGT,
-                 NRTE,
-                 SMPL,
-                 HILL,
-                 HGHT,
-                 NTIL,
-                 NTShB,
-                 TShB_incidence)
-
-  # Gather tillers--------------------------------------------------------------
-  TIL <- vector(mode = "list", length = 4)
-
-  for (i in 1:4) {
-    y <-
-      x %>%
-      select(
-        TRT,
-        REP,
-        WMGT,
-        SMPL,
-        NRTE,
-        HILL,
-        paste0("TIL", i),
-        paste0("GL", i),
-        paste0("DL", i),
-        paste0("SHB", i),
-        paste0("SLA", i),
-        paste0("SLB", i),
-        paste0("SLC", i),
-        paste0("SLD", i),
-        paste0("SLE", i),
-        paste0("SLF", i)
-      ) %>%
-      gather(LEAF,
-             LEAF_ShB,
-             starts_with("SL"))
-
-    names(y)[7] <- "TIL"
-    names(y)[8] <- "GL"
-    names(y)[9] <- "DL"
-    names(y)[10] <- "TIL_ShB"
-
-    y$LEAF[y$LEAF == paste0("SLA", i)] <- 1
-    y$LEAF[y$LEAF == paste0("SLB", i)] <- 2
-    y$LEAF[y$LEAF == paste0("SLC", i)] <- 3
-    y$LEAF[y$LEAF == paste0("SLD", i)] <- 4
-    y$LEAF[y$LEAF == paste0("SLE", i)] <- 5
-    y$LEAF[y$LEAF == paste0("SLF", i)] <- 6
-
-    TIL[[i]] <- y
-  }
-
-  z <- bind_rows(TIL)
-  x <- left_join(TShB_incidence, z)
-
-  # Add dates ------------------------------------------------------------------
-
-  switch(
-    files,
-    "data/DS2015_Raw_22DAI.csv" = {
-      DATE <- rep(as.Date("2015-02-12", origin = "1970-01-01"),
-                  times = nrow(x))
-      ASMT <- rep(1, times = nrow(x))
-      visit <- data.frame(DATE, ASMT, x)
-    },
-    "data/DS2015_Raw_35DAI.csv" = {
-      DATE <- rep(as.Date("2015-02-20", origin = "1970-01-01"),
-                  times = nrow(x))
-      ASMT <- rep(2, times = nrow(x))
-      visit <- data.frame(DATE, ASMT, x)
-    },
-    "data/DS2015_Raw_49DAI.csv" = {
-      DATE <- rep(as.Date("2015-03-05", origin = "1970-01-01"),
-                  times = nrow(x))
-      ASMT <- rep(3, times = nrow(x))
-      visit <- data.frame(DATE, ASMT, x)
-    },
-    "data/DS2015_Raw_62DAI.csv" = {
-      DATE <- rep(as.Date("2015-03-19", origin = "1970-01-01"),
-                  times = nrow(x))
-      ASMT <- rep(4, times = nrow(x))
-      visit <- data.frame(DATE, ASMT, x)
-    },
-    "data/DS2015_Raw_83DAI.csv" = {
-      DATE <- rep(as.Date("2015-04-01", origin = "1970-01-01"),
-                  times = nrow(x))
-      ASMT <- rep(5, times = nrow(x))
-      visit <- data.frame(DATE, ASMT, x)
-    }
-  )
-}
-
-# Run reformat function for all 2015 files -------------------------------------
-DS2015 <- map_df(files, reformat)
-
-# Add days after inoculation column
-DS2015 <-
-  DS2015 %>%
-  mutate(DAI = case_when(ASMT == 1 ~ 14,
-                         ASMT == 2 ~ 22,
-                         ASMT == 3 ~ 35,
-                         ASMT == 4 ~ 49,
-                         ASMT == 5 ~ 62))
-
-# Replace "N*" with a number for NRTE ------------------------------------------
-DS2015$NRTE[which(DS2015$NRTE == "N0")] <- 0
-DS2015$NRTE[which(DS2015$NRTE == "N1")] <- 100
-DS2015$NRTE[which(DS2015$NRTE == "N2")] <- 120
-
-# Add treatment numbers --------------------------------------------------------
-DS2015$TRT <- NA
-DS2015$TRT[which(DS2015$WMGT == "PDL" &
-                   DS2015$NRTE == 0)] = "PDL_N0"
-DS2015$TRT[which(DS2015$WMGT == "PDL" &
-                   DS2015$NRTE == 100)] = "PDL_N100"
-DS2015$TRT[which(DS2015$WMGT == "PDL" &
-                   DS2015$NRTE == 120)] = "PDL_N120"
-DS2015$TRT[which(DS2015$WMGT == "AWD" &
-                   DS2015$NRTE == 0)] = "AWD_N0"
-DS2015$TRT[which(DS2015$WMGT == "AWD" &
-                   DS2015$NRTE == 100)] = "AWD_N100"
-DS2015$TRT[which(DS2015$WMGT == "AWD" &
-                   DS2015$NRTE == 120)] = "AWD_N120"
-
-DS2015$YEAR <- year(DS2015$DATE)
-
-DS2015$PLOT <- rep(1:24, each = 432)
-
-# Arrange columns --------------------------------------------------------------
-DS2015 <-
-  DS2015 %>% select(
-    YEAR,
-    DATE,
-    ASMT,
-    DAI,
-    REP,
-    PLOT,
-    TRT,
-    SMPL,
-    HILL,
-    TIL,
-    LEAF,
-    GL,
-    DL,
-    TShB_incidence,
-    TIL_ShB,
-    LEAF_ShB,
-    WMGT,
-    NRTE
-  ) %>% 
-  mutate(REP = as.integer(REP),
-         HILL = as.integer(HILL))
-
-DS2015$LEAF_ShB <- as.numeric(DS2015$LEAF_ShB)
-
-DS2015 <- arrange(DS2015, ASMT, PLOT)
-
-# Create new columns of days to calcluate AUDPS -------------------------------
-
-DAYS <- as.numeric(substr(files, 17, 18))
-
-DS2015$DAYS <- c(rep(0, 10368), rep(diff(DAYS), each = 10368))
-
-rm(files, reformat)
-```
-
-# 2016 experiment
-
- Preprocess 2016 data for all assessments
-
-1. Cleanup date format and fill empty dates
-2. Fill empty NTIL (for same hill, not missing values)
-3. Fill empty NTShB (for same hill, not missing values)
-4. Add column with number of days after inoculation (DAI)
-
-```{r}
-library(tidyverse)
-library(agricolae)
-library(usethis)
-library(lubridate)
-
-# First assessment -------------------------------------------------------------
-DS2016_A1 <- read_csv("data/DS2016_Raw_1.csv")
-# Fill missing values in NTIL and NTShB
-DS2016_A1 <-
-  DS2016_A1 %>% fill(NTIL)
-DS2016_A1 <-
-  DS2016_A1 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A1[, 1] <- as.Date("2016-03-15", origin = "1970-01-01")
-DS2016_A1$ASMT <- rep(1, nrow(DS2016_A1))
-DS2016_A1$PLOT <- rep(1:16, each = 72)
-
-# Fill days after inoculation
-DS2016_A1$DAI <- rep(14, nrow(DS2016_A1))
-
-# Second assessement -----------------------------------------------------------
-DS2016_A2 <- read_csv("data/DS2016_Raw_2.csv")
-DS2016_A2 <-
-  DS2016_A2 %>% fill(NTIL)
-DS2016_A2 <-
-  DS2016_A2 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A2[, 1] <- as.Date("2016-03-29", origin = "1970-01-01")
-DS2016_A2$ASMT <- rep(2, nrow(DS2016_A2))
-DS2016_A2$PLOT <- rep(1:16, each = 72)
-
-# Fill days after inoculation
-DS2016_A2$DAI <- rep(28, nrow(DS2016_A2))
-
-# Third assessement ------------------------------------------------------------
-DS2016_A3 <- read_csv("data/DS2016_Raw_3.csv")
-DS2016_A3 <-
-  DS2016_A3 %>% fill(NTIL)
-DS2016_A3 <-
-  DS2016_A3 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A3[, 1] <- as.Date("2016-04-12", origin = "1970-01-01")
-DS2016_A3$ASMT <- rep(3, nrow(DS2016_A3))
-DS2016_A3$PLOT <- rep(1:16, each = 72)
-
-# Fill days after inoculation
-DS2016_A3$DAI <- rep(43, nrow(DS2016_A3))
-
-# Fourth assessment ------------------------------------------------------------
-DS2016_A4 <- read_csv("data/DS2016_Raw_4.csv")
-DS2016_A4 <-
-  DS2016_A4 %>% fill(NTIL)
-DS2016_A4 <-
-  DS2016_A4 %>% fill(NTShB)
-
-# Fill dates
-DS2016_A4[, 1] <- as.Date("2016-04-26", origin = "1970-01-01")
-DS2016_A4$ASMT <- rep(4, nrow(DS2016_A4))
-DS2016_A4$PLOT <- rep(1:16, each = 72)
-
-# Fill days after inoculation
-DS2016_A4$DAI <- rep(59, nrow(DS2016_A4))
-
-# Combine all assessments ------------------------------------------------------
-DS2016 <- rbind(
-  as.data.frame(DS2016_A1),
-  as.data.frame(DS2016_A2),
-  as.data.frame(DS2016_A3),
-  as.data.frame(DS2016_A4)
-)
-
-# Set any NA values to 0, per Dr. Castilla on 060317 ---------------------------
-# "We used to put zeroes on the data sheets, but Dr. Savary later suggested that
-# we leave the cells blank because it has caused difficulties in proof reading
-# the data. We also found more mistakes in data encoding when there are a lot
-# of zeroes."
-# Set any NA values to 0, per Dr. Castilla on 060317 ---------------------------
-
-DS2016[is.na(DS2016)] <- 0
-
-# Replace "N*" with a number for NRTE ------------------------------------------
-DS2016$NRTE[which(DS2016$NRTE == "N1")] = 60
-DS2016$NRTE[which(DS2016$NRTE == "N2")] = 180
-
-# Add treatment numbers --------------------------------------------------------
-DS2016$TRT <- NA
-DS2016$TRT[which(DS2016$WMGT == "PDL" &
-                   DS2016$NRTE == 60)] = "PDL_N60"
-DS2016$TRT[which(DS2016$WMGT == "PDL" &
-                   DS2016$NRTE == 180)] = "PDL_N180"
-DS2016$TRT[which(DS2016$WMGT == "AWD" &
-                   DS2016$NRTE == 60)] = "AWD_N60"
-DS2016$TRT[which(DS2016$WMGT == "AWD" &
-                   DS2016$NRTE == 180)] = "AWD_N180"
-
-DS2016 <-
-  DS2016 %>%
-  gather(
-    LEAF,
-    LEAF_ShB,
-    starts_with("ShBL"),
-    -DATE,
-    -ASMT,
-    -DAI,
-    -PLOT,
-    -TRT,
-    -REP,
-    -WMGT,
-    -SMPL,
-    -NRTE,
-    -HILL,
-    -NTIL,
-    -GL,
-    -DL,
-    -NTShB,
-    -NSHShB,
-    -TIL
-  )
-
-# reclassify LEAF column to leaf numbers 1...6
-
-DS2016$LEAF[DS2016$LEAF == "ShBL1"] <- 1
-DS2016$LEAF[DS2016$LEAF == "ShBL2"] <- 2
-DS2016$LEAF[DS2016$LEAF == "ShBL3"] <- 3
-DS2016$LEAF[DS2016$LEAF == "ShBL4"] <- 4
-DS2016$LEAF[DS2016$LEAF == "ShBL5"] <- 5
-DS2016$LEAF[DS2016$LEAF == "ShBL6"] <- 6
-
-# before classifying incidence, set any values where there are more infected
-# tillers in the hill than there are tillers to NA for both columns
-
-DS2016$NTIL[DS2016$NTIL < DS2016$NTShB] <- NA
-DS2016$NTShB[is.na(DS2016$NTIL)] <- NA
-
-# calculate tiller sheath blight incidence
-DS2016 <-
-  DS2016 %>%
-  group_by(DATE, ASMT, DAI, REP, PLOT, TRT, WMGT, NRTE, SMPL, HILL) %>%
-  mutate(TShB_incidence = NTShB / NTIL)
-
-DS2016 <- rename(DS2016, TIL_ShB = NSHShB)
-
-DS2016$YEAR <- year(DS2016$DATE)
-DS2016$LEAF_ShB <- as.numeric(DS2016$LEAF_ShB)
-
-DS2016 <-
-  DS2016 %>% select(
-    YEAR,
-    DATE,
-    ASMT,
-    DAI,
-    REP,
-    PLOT,
-    TRT,
-    SMPL,
-    HILL,
-    TIL,
-    LEAF,
-    GL,
-    DL,
-    TShB_incidence,
-    TIL_ShB,
-    LEAF_ShB,
-    WMGT,
-    NRTE
-  )
-
-DS2016 <- arrange(DS2016, ASMT, PLOT)
-
-# Create new columns of days to calcluate AUDPS -------------------------------
-
-DATE_1_2016 <- DATE_2_2016 <- DS2016$DATE
-DATE_1_2016[which(DATE_1_2016 == min(DATE_1_2016))] <- NA
-DATE_2_2016[which(DATE_2_2016 == max(DATE_2_2016))] <- NA
-
-DATE_1 <- na.omit(DATE_1_2016)
-DATE_2 <- na.omit(DATE_2_2016)
-
-DAYS_2016 <- time_length(DATE_1 - DATE_2, unit = "day")
-DS2016$DAYS <-
-  c(rep(0, nrow(DS2016) - length(DAYS_2016)), DAYS_2016)
-
-# cleanup workspace ------------------------------------------------------------
-
-rm(
-  DS2016_A1,
-  DS2016_A2,
-  DS2016_A3,
-  DS2016_A4,
-  DATE_1,
-  DATE_1_2016,
-  DATE_2,
-  DATE_2_2016,
-  DAYS_2016
-)
-
-# Arrange columns --------------------------------------------------------------
-DS2016 <-
-  DS2016 %>% select(
-    YEAR,
-    DATE,
-    ASMT,
-    DAI,
-    REP,
-    PLOT,
-    TRT,
-    SMPL,
-    HILL,
-    TIL,
-    LEAF,
-    GL,
-    DL,
-    TShB_incidence,
-    TIL_ShB,
-    LEAF_ShB,
-    WMGT,
-    NRTE,
-    DAYS
-  )
-```
-
-# Calculating Disease Severity Index and Area Under the Disease Progress Stairs (AUDPS)
-
-Because the data were collected on an ordinal scale, but not evenly spaced,
-the data are converted to the midpoint value of the percent range for disease
-severity index and then the AUDPS is calculated from that.
-
-Last, the data are saved in the package for use analysis, which is detailed
-in the package [vingettes](../vignettes).
-
-```{r}
-# Join the 2015 and 2016 Data into one Tibble ----------------------------------
-
-RAW_data <- bind_rows(DS2015, DS2016)
-
-# convert columns to factor ----------------------------------------------------
-RAW_data <-
-  RAW_data %>%
-  mutate(
-    YEAR = as.factor(YEAR),
-    ASMT = as.factor(ASMT),
-    PLOT = as.factor(PLOT),
-    REP = as.factor(REP),
-    TRT = as.factor(TRT),
-    WMGT = as.factor(WMGT),
-    NRTE = as.factor(NRTE),
-    SMPL = as.factor(SMPL),
-    HILL = as.factor(HILL),
-    TIL = as.factor(TIL),
-    LEAF = as.factor(LEAF)
-  )
-
-# reorder the treatments by level/year - low to high, 2015-2016 for graphs -----
-RAW_data$NRTE <-
-  fct_relevel(RAW_data$NRTE,
-              "0",
-              "100",
-              "120",
-              "60",
-              "180")
-
-RAW_data$TRT <-
-  fct_relevel(
-    RAW_data$TRT,
-    "AWD_N0",
-    "AWD_N100",
-    "AWD_N120",
-    "AWD_N60",
-    "AWD_N180",
-    "PDL_N0",
-    "PDL_N100",
-    "PDL_N120",
-    "PDL_N60",
-    "PDL_N180"
-  )
-
-# add column with midpoint % tiller ShB severity -------------------------------
-RAW_data <-
-  mutate(
-    RAW_data,
-    PERC_TIL_ShB = case_when(
-      TIL_ShB == 0 ~ 0,
-      TIL_ShB == 1 ~ 1,
-      TIL_ShB == 2 ~ 2.5,
-      TIL_ShB == 3 ~ 10,
-      TIL_ShB == 4 ~ 32.5,
-      TRUE ~ 75
-    )
-  )
-
-# add column with midpoint +1  % tiller ShB severity ---------------------------
-
-RAW_data <-
-  mutate(
-    RAW_data,
-    PERC_TIL_ShB_1 = case_when(
-      TIL_ShB == 0 ~ 1,
-      TIL_ShB == 1 ~ 2.5,
-      TIL_ShB == 2 ~ 10,
-      TIL_ShB == 3 ~ 32.5,
-      TIL_ShB == 4 ~ 75,
-      TRUE ~ 100
-    )
-  )
-
-# add column with midpoint % leaf ShB severity ---------------------------------
-RAW_data <-
-  mutate(
-    RAW_data,
-    PERC_LEAF_ShB = case_when(
-      LEAF_ShB == 0 ~ 0,
-      LEAF_ShB == 1 ~ 1,
-      LEAF_ShB == 2 ~ 2.5,
-      LEAF_ShB == 3 ~ 10,
-      LEAF_ShB == 4 ~ 32.5,
-      TRUE ~ 75
-    )
-  )
-
-# add column with midpoint +1  % leaf ShB severity -----------------------------
-RAW_data <-
-  mutate(
-    RAW_data,
-    PERC_LEAF_ShB_1 = case_when(
-      LEAF_ShB == 0 ~ 1,
-      LEAF_ShB == 1 ~ 2.5,
-      LEAF_ShB == 2 ~ 10,
-      LEAF_ShB == 3 ~ 32.5,
-      LEAF_ShB == 4 ~ 75,
-      TRUE ~ 100
-    )
-  )
-
-DS2015 <- subset(RAW_data, YEAR == "2015")
-DS2016 <- subset(RAW_data, YEAR == "2016")
-```
-
-# Calculate disease index values
-See K. S. Chiang et al. 2017
-
-DSI<sub>Modified</sub> = Mid<sub><em>Q</em></sub> + <em>R</em>/Total Number of Observations * (Mid<sub><em>Q+1</em></sub> - Mid<sub><em>Q</em></sub>)
-
-```{r DSI}
-#DS2015 <- 
-#  DS2015 %>% 
-#  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>% 
-#  mutate(TShB_DSI = (TIL_ShB + )/
-```
-
-```{r AUDPS}
-# calculate AUDPS values -------------------------------------------------------
-
-# 2015 AUDPS -------------------------------------------------------------------
-
-TShB_sev_15 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
-  arrange(PLOT)
-
-TShB_sev_wide <-
-  reshape2::dcast(TShB_sev_15, PLOT ~ ASMT, value.var = "PLOT_TShB_severity")
-
-TShB_perc_15 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
-  arrange(PLOT)
-
-TShB_perc_wide <-
-  reshape2::dcast(TShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")
-
-# 2015 Leaf Severity setup -----------------------------------------------------
-LShB_sev_15 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_LShB_severity = LEAF_ShB)) %>%
-  arrange(PLOT)
-
-LShB_sev_wide <-
-  reshape2::dcast(LShB_sev_15, PLOT ~ ASMT, value.var = "PLOT_LShB_severity")
-
-LShB_perc_15 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAI, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
-  arrange(PLOT)
-
-LShB_perc_wide <-
-  reshape2::dcast(LShB_perc_15, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")
-
-TShb_inc_15 <-
-  DS2015 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-               .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
-  arrange(PLOT) %>%
-  group_by(YEAR, REP, TRT, PLOT) %>%
-  summarise(AUDPS = audps(PLOT_TShB_incidence, DAYS))
-
-TShB_sev_AUDPS <-
-  audps(evaluation = TShB_sev_wide[, 2:6],
-                   dates = pull(TShB_sev_15[1:5, 6]))
-
-LShB_sev_AUDPS <-
-  audps(evaluation = LShB_sev_wide[, 2:6],
-                   dates = pull(LShB_sev_15[1:5, 6]))
-
-TShB_percent_AUDPS <-
-  audps(evaluation = TShB_perc_wide[, 2:6],
-        dates = pull(TShB_perc_15[1:5, 6]))
-
-LShB_percent_AUDPS <-
-  audps(evaluation = LShB_perc_wide[, 2:6],
-        dates = pull(LShB_perc_15[1:5, 6]))
-
-AUDPS_15 <-
-  as_tibble(
-    cbind(
-      PLOT = 1:24,
-      TShB_inc_AUDPS,
-      TShB_sev_AUDPS,
-      TShB_percent_AUDPS,
-      LShB_sev_AUDPS,
-      LShB_percent_AUDPS
-    )
-  )
-
-AUDPS_15$PLOT <- as.character(AUDPS_15$PLOT)
-TShB_inc_15$PLOT <- as.character(TShB_inc_15$PLOT)
-
-ShB_15 <- left_join(TShB_inc_15, AUDPS_15, by = "PLOT")
-
-# 2016 AUDPS -------------------------------------------------------------------
-
-# 2016 Tiller Incidence setup --------------------------------------------------
-TShB_inc_16 <-
-  DS2016 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_incidence = TShB_incidence)) %>%
-  arrange(PLOT)
-
-TShB_inc_wide <-
-  reshape2::dcast(TShB_inc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_incidence")
-
-TShB_sev_16 <-
-  DS2016 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_severity = TIL_ShB)) %>%
-  arrange(PLOT)
-
-TShB_sev_wide <-
-  reshape2::dcast(TShB_sev_16, PLOT ~ ASMT, value.var = "PLOT_TShB_severity")
-
-# 2016 Tiller Severity setup ---------------------------------------------------
-
-TShB_perc_16 <-
-  DS2016 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_TShB_PERCENT = PERC_TIL_ShB)) %>%
-  arrange(PLOT)
-
-TShB_perc_wide <-
-  reshape2::dcast(TShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_TShB_PERCENT")
-
-# 2016 Leaf Severity setup -----------------------------------------------------
-
-LShB_sev_16 <-
-  DS2016 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_LShB_severity = LEAF_ShB)) %>%
-  arrange(PLOT)
-
-LShB_sev_wide <-
-  reshape2::dcast(LShB_sev_16, PLOT ~ ASMT, value.var = "PLOT_LShB_severity")
-
-LShB_perc_16 <-
-  DS2016 %>%
-  group_by(YEAR, REP, TRT, PLOT, ASMT, DAYS) %>%
-  summarise_at(.funs = funs(mean(., na.rm = TRUE)),
-                      .vars = vars(PLOT_LShB_PERCENT = PERC_LEAF_ShB)) %>%
-  arrange(PLOT)
-
-LShB_perc_wide <-
-  reshape2::dcast(LShB_perc_16, PLOT ~ ASMT, value.var = "PLOT_LShB_PERCENT")
-
-# 2016 AUDPS -------------------------------------------------------------------
-
-TShB_inc_AUDPS <-
-  audps(evaluation = TShB_inc_wide[, 2:5],
-                   dates = pull(TShB_inc_16[1:4, 6]))
-
-TShB_sev_AUDPS <-
-  audps(evaluation = TShB_sev_wide[, 2:5],
-                   dates = pull(TShB_sev_16[1:4, 6]))
-
-LShB_sev_AUDPS <-
-  audps(evaluation = LShB_sev_wide[, 2:5],
-                   dates = pull(LShB_sev_16[1:4, 6]))
-
-TShB_percent_AUDPS <-
-  audps(evaluation = TShB_perc_wide[, 2:5],
-                   dates = pull(TShB_perc_16[1:4, 6]))
-
-LShB_percent_AUDPS <-
-  audps(evaluation = LShB_perc_wide[, 2:5],
-                   dates = pull(LShB_perc_16[1:4, 6]))
-
-AUDPS_16 <-
-  as_tibble(
-    cbind(
-      PLOT = 1:16,
-      TShB_inc_AUDPS,
-      TShB_sev_AUDPS,
-      TShB_percent_AUDPS,
-      LShB_sev_AUDPS,
-      LShB_percent_AUDPS
-    )
-  )
-
-# add plot numbers to merge with the remaining treatment data
-AUDPS_16$PLOT <- as.character(AUDPS_16$PLOT)
-TShB_inc_16$PLOT <- as.character(TShB_inc_16$PLOT)
-
-ShB_16 <- left_join(TShB_inc_16, AUDPS_16, by = c("PLOT" = "PLOT"))
-
-# Merge AUDPS data for graphing ------------------------------------------------
-AUDPS <- as_data_frame(as_tibble(rbind(ShB_15, ShB_16)))
-AUDPS <- separate(data = AUDPS, col = TRT,
-                         sep = "_",
-                         into = c("WMGT", "NRTE"))
-AUDPS <- mutate_at(.tbl = AUDPS,
-                              .funs = factor,
-                              .vars = c("WMGT", "NRTE"))
-
-# Arrange NRTE values
-AUDPS$NRTE <-
-  fct_relevel(AUDPS$NRTE,
-                       "N0",
-                       "N100",
-                       "N120",
-                       "N60",
-                       "N180")
-
-# Save data for inclusion in the package ---------------------------------------
-
-if (!dir.exists("../data")) {
-  dir.create("../data", recursive = TRUE)
-}
-
-use_data(RAW_data,
-                  compress = "bzip2",
-                  overwrite = TRUE)
-
-use_data(AUDPS,
-                  compress = "bzip2",
-                  overwrite = TRUE)
-```
-
-# N rates
-
-Create a `tibble` of N rates and time of application used in this study.
-
-```{r N_rates}
-
-Year <- as.integer(c(2015,
-                     2015,
-                     2015,
-                     2016,
-                     2016))
-
-`Total N (kg/ha)` <- as.integer(c(0,
-                                  100,
-                                  120,
-                                  60,
-                                  180))
-
-`Basal N (kg/ha)` <- as.integer(c(0,
-                                  60,
-                                  60,
-                                  30,
-                                  60))
-
-`Tillering N (kg/ha)` <- as.integer(c(0,
-                                      20,
-                                      30,
-                                      30,
-                                      60))
-
-`Panicle Initiation N (kg/ha)` <- as.integer(c(0,
-                                               20,
-                                               30,
-                                               0,
-                                               60))
-
-N_rates <- cbind(Year,
-                 `Total N (kg/ha)`,
-                 `Basal N (kg/ha)`,
-                 `Tillering N (kg/ha)`,
-                 `Panicle Initiation N (kg/ha)`)
-
-row.names(N_rates) <- c("N0", "N100", "N120", "N60", "N180")
-
-use_data(N_rates,
-                  compress = "bzip2",
-                  overwrite = TRUE)
-```
-
-# Colophon
-
-```{r}
-sessioninfo::session_info()
-```
+Two files in this directory detail the pre-processing of disease data, [import_and_preprocess.md](import_and_preprocess.md) and an R script, [IRRI_weather_data.R](IRRI_weather_data.R) that imports weather data for 2015 and 2016 and runs statistical checks to ensure that the dry seasons in each year are not statistically different.

### 2020-06-11 data-raw/IRRI_weather_data.R

@@ -1,8 +1,9 @@
-library(magrittr)
-library(BayesianFirstAid)
+library("magrittr")
+library("BayesianFirstAid")
+
 `%notin%` = function(x,y) !(x %in% y)
 
-l <- list.files(path = "~/Downloads/Fwd__Weather_data",
+l <- list.files(path = "data/Fwd__Weather_data",
                 full.names = TRUE)
 f <- purrr::map(l, readxl::read_excel,
                 sheet = 13,

### 2020-06-12 R/data.R
Remove data import from data-raw to vingettes
Moves raw data to Zenodo and the Rmd into the vignettes where it downloads the data from Zenodo.

Standardises author names across vignettes as well

@@ -1,19 +1,20 @@
 
-#' A Tidy Data Frame of Area Under the Disease Progress Stairs for Sheath Blight Observations
+#' A Data Frame of Area Under the Disease Progress Curve and Stairs for Sheath Blight Observations
 #'
 #' A dataset containing the alternate wetting and drying study data observations
-#' and calculated Area Under the Disease Progress Stairs (AUDPS)
+#' and calculated Area Under the Disease Progress Curve (AUDPC) and Stairs
+#' (AUDPS)
 #'
-"AUDPS"
+"AUDPC_S"
 
-#' A Tidy Data frame of Raw Data for Sheath Blight Observations
+#' A Data frame of Raw Data for Sheath Blight Observations
 #'
 #' A dataset containing the alternate wetting and drying study data observations
 #' organised into a tidy data frame.
 #'
 "RAW_data"
 
-#' A data.frame of Nitrogen Rates and Split Application Timings
+#' A Data Frame of Nitrogen Rates and Split Application Timings
 #'
 #' A dataset containing the N rates and time of application split organised
 #' into a tidy data frame.

### 2020-06-12 analysis/paper/paper.Rmd
update author list formatting and fix graph code in paper

@@
 author: |
-  | Adam H. Sparks^[Corresponding author: Adam.Sparks@usq.edu.au]  \textsuperscript{1\dag}, Nancy P. Castilla \textsuperscript{1}, Bjorn Ole Sander \textsuperscript{1}
-  | \textsuperscript{1}International Rice Research Institute, Crop and Environmental Sciences Division, Los Baños, Laguna, Philippines, 4031
-  | \textsuperscript{\dag} Current Address: University of Southern Queensland, Centre for Crop Health, West Street, Tooowoomba, Queensland, Australia, 4350
+  | Adam H. Sparks^[Corresponding author: Adam.Sparks@usq.edu.au] \textsuperscript{1\dag}, Nancy P. Castilla \textsuperscript{1}, Bjoern Ole Sander \textsuperscript{1}
+  | \textsuperscript{1}International Rice Research Institute,
+  | Crop and Environmental Sciences Division, Los Baños, Laguna, Philippines, 4031
+  | \textsuperscript{\dag} Current Address: University of Southern Queensland,
+  | Centre for Crop Health, West Street,
+  | Tooowoomba, Queensland, Australia, 4350
 csl: "../templates/european-journal-of-plant-pathology.csl" # Insert path for the bib-style
@@
 
-library(bookdown)
-library(knitr)
-library(ggplot2)
-library(ggpubr)
-library(grid)
-library(gridExtra)
-library(pander)
-library(rice.awd.pests)
+library("bookdown")
+library("knitr")
+library("ggplot2")
+library("ggpubr")
+library("grid")
+library("gridExtra")
+library("pander")
+library("rice.awd.shb")
 ```
@@
 
-The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr Rachel King of the University of Southern Queensland Statistical Consulting Unit for her insightful comments on the analysis of this paper.
+The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr R.
+King and Mr D.
+Burrell of the University of Southern Queensland Statistical Consulting Unit for their insightful comments on the analysis of this paper.
 We would also like to thank D.
@@
 Lapis for their technical support in the field.
-Lastly, we would like to remember our team mate Michael Noel, a part of the plant disease management team at IRRI and who helped design and managed the first year of the project but passed away in September 2016.
+Lastly, we would like to remember our team mate Michael Noel, an integral part of our plant disease management team at IRRI and who helped design and managed the first season of the project but passed away in September 2016.
 
@@
 
-p7 <- ggplot(AUDPS,
+p7 <- ggplot(AUDPC_S,
              aes(x = WMGT, y = TShB_inc_AUDPS)) +
@@
 
-p8 <- ggplot(AUDPS,
+p8 <- ggplot(AUDPC_S,
              aes(x = WMGT, y = TShB_sev_AUDPS)) +
@@
 
-p9 <- ggplot(AUDPS,
+p9 <- ggplot(AUDPC_S,
              aes(x = WMGT, y = LShB_sev_AUDPS)) +
@@
 
-p10 <- ggplot(AUDPS,
+p10 <- ggplot(AUDPC_S,
              aes(x = NRTE, y = TShB_inc_AUDPS)) +
@@
 
-p11 <- ggplot(AUDPS,
+p11 <- ggplot(AUDPC_S,
              aes(x = NRTE, y = TShB_sev_AUDPS)) +
@@
 
-p12 <- ggplot(AUDPS,
+p12 <- ggplot(AUDPC_S,
              aes(x = NRTE, y = LShB_sev_AUDPS)) +

### 2020-06-12 data-raw/README.Rmd
Clean up README for data-raw directory

@@
 
-Two files in this directory detail the pre-processing of disease data, [import_and_preprocess.md](import_and_preprocess.md) and an R script, [IRRI_weather_data.R](IRRI_weather_data.R) that imports weather data for 2015 and 2016 and runs statistical checks to ensure that the dry seasons in each year are not statistically different.
+One file exists in this directory, [IRRI_weather_data.R](IRRI_weather_data.R).
+It imports weather data for 2015 and 2016 and runs statistical checks to ensure that the dry seasons in each year are not statistically different.
+They were not.

### 2020-06-12 README.Rmd
Clean up README and add data DOI

@@
 
-The files at the URL above will generate the results as found in the
-publication. The files hosted at
-<https://github.com/adamhsparks/rice_AWD_ShB_analysis> are the development
-versions and may have changed since the report was published.
+The files at the URL above will generate the results as found in the publication.
+The files hosted at <https://github.com/adamhsparks/rice_AWD_ShB_analysis> are the development versions and may have changed since the report was published.
+
+### Data DOI:
+
+[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3889800.svg)](https://doi.org/10.5281/zenodo.3889800)
+
+The raw data from this project are released and publicly available from Zenodo under a [Creative Commons Attribution 4.0 International](http://creativecommons.org/licenses/by/4.0/legalcode) licence.
 
@@
 
-This repository is our research compendium for our analysis of the effects of
-alternate wetting and drying irrigation technology on rice sheath blight
-disease. The compendium contains all data, code, and text associated with the
-publication. The `Rmd` files in the `analysis/paper/` directory contain details
-of how all the analyses reported in the paper were conducted, as well as
-instructions on how to rerun the analysis to reproduce the results. The
-`data/` directory in the `analysis/` directory contains all the raw data. The
-`data-raw` directory contains a README.Rmd, which when knit generates the data
-used in the analysis of the paper and places `.rda` files in `data/` for the
-analysis.
+This repository is our research compendium for our analysis of the effects of alternate wetting and drying irrigation technology on rice sheath blight disease.
+The compendium contains all data, code, and text associated with the publication.
+The `Rmd` files in the `analysis/paper/` directory contain details of how all the analyses reported in the paper were conducted, as well as instructions on how to rerun the analysis to reproduce the results.
+The `data/` directory in the `analysis/` directory contains all the raw data.
+The `data-raw` directory contains extra files to check weather for differences between seasons, that are not included in the actual analysis.
 
@@
 
-- a Rmd file and Markdown file detailing how the raw data was handled and
-Area Under the Disease Progress Stairs (AUDPS) was calculated for analysis and
-the .Rda files used in the analysis were generated
+- a IRRI_weather_data.R, a file used to check weather data from IRRI weather stations to ensure that there was no significant difference in weather between seasons
 
@@
 
-- the manuscript as submitted (in MS Word format) and it's Rmd source file
+- the manuscript as submitted (in PDF format) and it's Rmd source file
 
-- all the data files (in CSV file format, in the `data/` directory)
-
-- supplementary information source files (in R markdown format) and executed
-versions
+- supplementary information source files (in R markdown format) and executed versions
 
@@
 
-This repository is organized as an R package. There are a few R functions in
-this package that were used to generate some of the diagnostic plots related to
-the analysis. However, for the most part I simply used the R package
-structure to help manage dependencies, to take advantage of continuous
-integration for automated code testing, and so I didn't have to think too much
+This repository is organized as an R package.
+There are a few R functions in this package that were used to generate some of the diagnostic plots related to the analysis.
+However, for the most part I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much
 about how to organise the files.
 
-To download the package source as you see it on GitHub, for offline browsing,
-use this line at the shell prompt (assuming you have Git installed on your
-computer):
+To download the package source as you see it on GitHub, for offline browsing, use this line at the shell prompt (assuming you have Git installed on your computer):
 
@@
 
-Once the download is complete, open the `rice.awd.shb.Rproj` in RStudio to
-begin working with the package and compendium files.
+Once the download is complete, open the `rice.awd.shb.Rproj` in RStudio to begin working with the package and compendium files.
 
-The package has a number of dependencies on other R packages, and programs
-outside of R. These are listed at the bottom of this README. Installing these
-can be time-consuming and complicated, so we've used a Docker image. The Docker
-image includes all the necessary software, code and data to run our analysis.
-The Docker image may give a quicker entry point to the project, and is more
-self-contained, so might save some fiddling with installing things.
+The package has a number of dependencies on other R packages, and programs outside of R.
+These are listed at the bottom of this README.
+Installing these can be time-consuming and complicated, so we've used a Docker image.
+The Docker image includes all the necessary software, code and data to run our analysis.
+The Docker image may give a quicker entry point to the project, and is more self-contained, so might save some fiddling with installing things.
 
@@
 
-A Docker image is a lightweight GNU/Linux virtual computer that can be run as a
-piece of software on Windows and OSX (and other Linux systems). To capture the
-complete computational environment used for this project we have a Dockerfile
-that specifies how to make the Docker image that we developed this project in.
-The Docker image includes all of the software dependencies needed to run the
-code in this project, as well as the R package and other compendium files. To
-launch the Docker image for this project, first, 
-[install Docker](https://docs.docker.com/installation/) on your computer. At the
-Docker prompt, enter:
+A Docker image is a lightweight GNU/Linux virtual computer that can be run as a piece of software on Windows and OSX (and other Linux systems).
+To capture the complete computational environment used for this project we have a Dockerfile that specifies how to make the Docker image that we developed this project in.
+The Docker image includes all of the software dependencies needed to run the code in this project, as well as the R package and other compendium files.
+To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer.
+At the Docker prompt, enter:
 
@@
 
-This will start a server instance of RStudio. Then open your web browser at
-localhost:8787 or or run `docker-machine ip default` in the shell to find the
+This will start a server instance of RStudio.
+Then open your web browser at localhost:8787 or or run `docker-machine ip default` in the shell to find the
 correct IP address, and log in with rstudio/rstudio.
 
-Once logged in, use the Files pane (bottom right) open the folder for this
-project, and open the `.Rproj` file for this project. Once that's open, you'll
-see the `analysis/paper` directory in the Files pane where you can find the R
-markdown document, and knit them to produce the results in the paper. More
-information about using RStudio in Docker is available at the
-[Rocker](https://github.com/rocker-org)
+Once logged in, use the Files pane (bottom right) open the folder for this project, and open the `.Rproj` file for this project.
+Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R
+markdown document, and knit them to produce the results in the paper.
+More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org)
 [wiki](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image) pages.
 
-We developed and tested the package on this Docker container, so this is the
-only platform that we're confident it works on, and so recommend to anyone
-wanting to use this package to generate the vignettes, etc.
+We developed and tested the package on this Docker container, so this is the only platform that we're confident it works on, and so recommend to anyone wanting to use this package to generate the vignettes, etc.
 
@@
 
-Code: [MIT](http://opensource.org/licenses/MIT) year: 
-`r format(Sys.Date(), "%Y")`, copyright holder: Adam Sparks
+Code: [MIT](http://opensource.org/licenses/MIT) year: `r format(Sys.Date(), "%Y")`, copyright holder: Adam Sparks
 
-Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
-requested in reuse
+Data: [CC-4.0](http://creativecommons.org/licenses/by/4.0/legalcode) attribution requested in reuse
 
@@
 
-I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu
-17.10. See the colophon section of the docx file in `analysis/paper` for a
-full list of the packages that this project depends on.
+I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu 17.10.
+See the colophon section of the docx file in `analysis/paper` for a full list of the packages that this project depends on.
 

### 2020-06-12 README.Rmd
Remove R CMD checks. Rely on Docker

@@
 
-[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master) [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/)
-[![Licence](https://img.shields.io/github/license/mashape/apistatus.svg)](http://choosealicense.com/licenses/mit/) ![R-CMD-check](https://github.com/adamhsparks/rice_AWD_ShB_analysis/workflows/R-CMD-check/badge.svg)
+[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-brightgreen.svg)](https://github.com/adamhsparks/rice.awd.pests/commits/master) [![minimal R version](https://img.shields.io/badge/R%3E%3D-`r as.character(getRversion())`-brightgreen.svg)](https://cran.r-project.org/) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3889800.svg)](https://doi.org/10.5281/zenodo.3889800)
 

### 2020-06-17 analysis/paper/paper.Rmd
Each sentence on new line, add references and introduction material

@@
 We suggest that further cross--disciplinary research in this area is warranted.
-All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests>.
+All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://doi.org/>.
 bibliography: references.bib
@@
 
+Climate change will bring changes to the environments in which our food crops are produced in [@Reyer2013].
+Rice (*Oryza sativa*) is the most widely grown cereal crop in a diverse set of environments globally and will will have to adapt to changing environments where it is grown as a result.
+
+Climate change will affect the diseases that occur in rice as well as the crop itself.
+Many studies have been conducted *in silico* that examine how diseases may change with the climate.
+Rice blast is one of the most frequently studied [@Luo1998; @Duku2016].
+As well as
+
+In-field studies have focused on the effects of temperature on bacterial blight [@Webb2010] and the effects of drought [@Dossa2017].
+The effects of climate change on sheath blight have been examined by Kim et al. [-@Kim2015], where
+
 Sheath blight disease, caused by (*Thanatephorus cucumeris*  (A.B.
@@
 The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
-Various countries, *e.g.*, Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
+Various countries, *e.g.* Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
 However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example changes in disease intensity or severity.
 
-While the effects of climate change directly on rice disease have been studied [@luo1998effects; @Duku2016] the effects of mitigation practices have not.
+While the effects of climate change directly on rice disease have been studied, the effects of mitigation practices have not.
 And because of the well documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight; we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
@@
 
-Irrigation in AWD plots was determined by the water level in plots, *i.e.*, when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
+Irrigation in AWD plots was determined by the water level in plots, *i.e.* when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
 In puddled plots a standing water layer of 3--5&nbsp;cm was maintained throughout the growing season.
@@
 
-## 2015 Experiment
+## 2015 Experiment {-}
 
@@
 
-### The Interaction of Irrigation and N Management
+### The Interaction of Irrigation and N Management {-}
 
@@
 
-### The Interaction of Irrigation and N Management
+### The Interaction of Irrigation and N Management {-}
 
 The interaction of irrigation treatment AWD with N rate N0 in 2015 or N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
-For leaf severity in the 2015 experiment the interaction was not clearly different.
-In 2016 the interaction of N180 and N180 was clearly lower than the control puddled irrigation and N60 rate.
+For leaf severity in the 2015 experiment the interaction was not clearly different. In 2016 the interaction of N180 and N180 was clearly lower than the control puddled irrigation and N60 rate.
 
@@
 It should be noted that the levels of leaf severity remained low (< 1 \%) throughout the growing season in all treatments for both years.
-As AWD can only feasibly be implemented in the dry season.
-Therefor, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
+Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
 However, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases.
@@
 Climate change is predicted to decrease sheath blight risk in the Korean peninsula over the longer term.
-However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@kim2015predicting].
+However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@Kim2015].
 Therefore, it is likely to remain an important diease in the near future with little resistance available in current varieties.
@@
 
-Readers may find a reproducible research compendium that recreates this paper, that includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://github.com/openplantpathology/rice_awd_pests> [@Sparks2019].
+Readers may find a reproducible research compendium that recreates this paper, that includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2019].
 
@@
 
-The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr R.
-King and Mr D.
+The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr.
+R.
+King and Mr.
+D.
 Burrell of the University of Southern Queensland Statistical Consulting Unit for their insightful comments on the analysis of this paper.
-We would also like to thank D.
-Amozola, P.
-Escandor and P.
-Lapis for their technical support in the field.
+We would also like to thank Mr. D. Amozola, Mr. P. Escandor and Mr. P. Lapis for their technical support in the field.
 Lastly, we would like to remember our team mate Michael Noel, an integral part of our plant disease management team at IRRI and who helped design and managed the first season of the project but passed away in September 2016.

### 2020-06-24 analysis/paper/paper.Rmd
Spelling checks and set two column layout

@@
 
+\twocolumn
+
 # Introduction {-}
@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E) in 2015 and 2016 dry seasons from December to May.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Ba\~nos, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E) in 2015 and 2016 dry seasons from December to May.
 In the 2016 experiment changes were made to optimize the experiment based on findings from the 2015 experiment.
@@
 
-An isolate of *Rhizoctonia solani* belonging to anasomosis group AG1--1a previously isolated from infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
+An isolate of *Thanatephorus cucumeris* infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
 The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C) for five days.
@@
 The remaining 50,000 samples were used to determine the posterior distribution of the parameters of the model.
-The `coda` [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman--Rubin test.
+The `coda` version 0.19-3 [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman--Rubin test.
 
@@
 As manual transplanting becomes less common due to labor constraints, sheath blight risk may be decreased (CITATION XXXX) due changes in establishment practices.
-A combination of AWD and directd seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
+A combination of AWD and direct seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
 
@@
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document:   -->
+
 <div id="refs"></div>
+\onecolumn
 

### 2020-06-25 analysis/paper/paper.Rmd
Flesh out introduction and add references

@@
 
+**Keywords** Disease $\cdot$ Sheath blight $\cdot$ *Thanatephorus cucumeris*
+
 \twocolumn
 
+# Key Message {-}
+
+* The effects of AWD on sheath blight disease incidence and severity were investigated.
+
+* AWD had no detectable effect on either sheath blight incidence or sheath blight severity.
+
+* The interaction of AWD and nitrogen management had no detectable effect on either sheath blight incidence or sheath blight severity.
+
+* The adoption of AWD technologies will not lead to increased sheath blight incidence or sheath blight severity.
+
 # Introduction {-}
+
+Rice is mainly produced in Asia with over 90&nbsp;% of production in Asia [@GRiSP2013] and uses the largest amount of any agricultural commodity [@Dawe2005; @GRiSP2013].
 
@@
 
-Climate change will affect the diseases that occur in rice as well as the crop itself.
-Many studies have been conducted *in silico* that examine how diseases may change with the climate.
-Rice blast is one of the most frequently studied [@Luo1998; @Duku2016].
-As well as
-
-In-field studies have focused on the effects of temperature on bacterial blight [@Webb2010] and the effects of drought [@Dossa2017].
-The effects of climate change on sheath blight have been examined by Kim et al. [-@Kim2015], where
+Rice's reliance on freely available water water, coupled with the effects of climate change mean that rice production practices will have to adapt to use new practices to produce more units of food with less water inputs.
 
@@
 Various countries, *e.g.* Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
-However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example changes in disease intensity or severity.
+However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example changes in disease incidence or severity.
+
+Many studies have been conducted *in silico* that examine how diseases may change with a changing climate.
+Rice blast is perhaps the the most frequently studied rice disease in regards to the effects of climate change [@Luo1995; @Luo1998; @Kim2015; @Duku2016; @Viswanath2017].
+However, Kim *et al.* [-@Kim2015] have modelled the effects of climate change on sheath blight with epidemics predicted to decrease by 2100 in their study, which focused on the Korean peninsula.
+
+Some *in-situ* studies of the effects of climate change on rice diseases have focused on the effects of temperature on bacterial blight [@Webb2010] and the effects of drought [@Dossa2017].
 
 While the effects of climate change directly on rice disease have been studied, the effects of mitigation practices have not.
-And because of the well documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight; we established field experiments to study what effects AWD irrigation technologies and N fertilisation in combination could have on sheath blight incidence and severity in tropical rice production.
+Rice farmers may be hesitant to adopt water saving technologies because changing rice production practices could have unintended effects on the diseases that occur in the rice crop.
+This is a reasonable concern because of the well documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight.
+In order to gain a better understanding of what the effects of adopting AWD on rice sheath blight may be, we established field experiments that incorporated irrigation technology and N fertilisation.
+
+We hypothesized that AWD would not have a positive effect on sheath blight incidence and severity in tropical rice production that would deter farmers from adopting it.
 
@@
 However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@Kim2015].
-Therefore, it is likely to remain an important diease in the near future with little resistance available in current varieties.
+Therefore, it is likely to remain an important disease in the near future with little resistance available in current varieties.
 However, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease.
@@
 # Notes {-}
+
+## Author Contributions {-}
+
+AHS and BOS conceived the topic.
+AHS and NPC conceived the research.
+NPC conducted the field work in 2016.
+AHS conducted the data analysis.
+All the authors contributed to the writing of the manuscript.
 

### 2020-06-25 analysis/paper/paper.Rmd
Add keywords, key message, clean up figures, add references

@@
 While the effects of climate change directly on rice disease have been studied, the effects of mitigation practices have not.
-Rice farmers may be hesitant to adopt water saving technologies because changing rice production practices could have unintended effects on the diseases that occur in the rice crop.
+Rice farmers may be hesitant to adopt water saving technologies because changing rice production practices could have unintended effects on the pests and diseases that occur in the rice crop.
 This is a reasonable concern because of the well documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight.
@@
 
-Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 3.5.0 [@R2018], package `agricolae`, version 1.2-8, [@deMendiburu2017].
+Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 4.0.0 [@R2020], package `agricolae`, version 1.3-3, [@agricolae2020].
 Due to the use of a severity scale for data collection, the severity data were converted to the midpoint percent value of the scale range for each value.
 
-The correlations between tiller sheath sheath blight incidence and tiller and leaf sheath blight severity were tested using Spearman’s correlation test, `cor.test`, [@R2018].
+The correlations between tiller sheath sheath blight incidence and tiller and leaf sheath blight severity were tested using Spearman’s correlation test, `cor.test`, [@R2020].
 No correlation was found, so the analysis was completed for each variable independently with no assumed interaction.
 
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm` [@MCMCglmm2010], version 2.26.
+As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm`, version 2.29, [@MCMCglmm2010].
 Six models were created where the the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
@@
 The interaction of irrigation treatment AWD with N rate N0 in 2015 or N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
-For leaf severity in the 2015 experiment the interaction was not clearly different. In 2016 the interaction of N180 and N180 was clearly lower than the control puddled irrigation and N60 rate.
+For leaf severity in the 2015 experiment the interaction was not clearly different.
+In 2016 the interaction of N180 and N180 was clearly lower than the control puddled irrigation and N60 rate.
 
@@
 In both experiments we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
-In fact, in only one instance were we able to detect any statistically clear effect of AWD on sheath blight.
+In only one instance were we able to detect any statistically clear effect of AWD on sheath blight.
 In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
@@
 
-Climate change is predicted to decrease sheath blight risk in the Korean peninsula over the longer term.
+Diseases are the only issue that farmers face when growing rice.
+Recently, Lorica *et al.* [@Lorica2020] have also found that AWD did not affect rodent damage in crops.
+Findings such as these are useful as IRRI promotes water-saving technologies like AWD because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
+
+Climate change is predicted to decrease sheath blight risk in the Korean peninsula over the longer term [@Kim2015].
 However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@Kim2015].
@@
 
-Readers may find a reproducible research compendium that recreates this paper, that includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2019].
+# Notes {-}
 
-# Notes {-}
+## Reproducibility Statement {-}
+
+Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2019].
 
@@
 <div id="refs"></div>
+
 \onecolumn
@@
 
-##### Sheath blight progress for water management treatments
+##### Sheath blight progress for water management treatments {-}
+\\
 
@@
 
-##### Sheath blight progress for N treatments
+##### Sheath blight progress for N treatments {-}
+\\
 
@@
 
-##### Sheath Blight Incidence Boxplot for water management
+##### Sheath Blight Incidence Boxplot for water management {-}
+\\
 
@@
 
-##### Tiller sheath blight incidence boxplot for N rate
+##### Tiller sheath blight incidence boxplot for N rate {-}
+\\
+
 ```{r fig-4, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
@@
 
-##### Tiller Estimates Plots
+##### Tiller Estimates Plots {-}
+\\
 
@@
 mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
+par(mfcol = c(1, 1))
 ```
 
-##### Leaf estimates plots
+##### Leaf estimates plots {-}
+\\
 
@@
 
-par(mfcol = c(1, 2))
-
+par(mfcol = c(2, 1))
 plot_tiller_estimates_paper(models[[3]], main_title = "2015")
@@
 
-##### pagebreak
+<!-- ##### pagebreak -->
 
-### Colophon {-}
+\newpage
+
+# Colophon {-}
 

### 2020-06-25 analysis/paper/paper.Rmd
Clean up table and document text

@@
 
-The split--plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N_rate)).
+The split--plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N-rates)).
 
@@
 
-Split--plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N_rate)).
+Split--plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N-rates)).
 
@@
 Both the N100 and N120 treatment effects caused the tiller severity to be higher and clearly statistically different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-5)c).
+However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-6)a).
 
@@
 As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-5)e).
+However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
 
-### The Interaction of Irrigation and N Management {-}
+## The Interaction of Irrigation and N Management {-}
+
+The interaction of irrigation treatment AWD with N rate N0 in 2015 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity.
+For leaf severity the interaction of irrigation and N management was not clearly different from the control puddled irrigation and N60 nitrogen rate.
 
@@
 In 2016 the N180 treatment was again higher and clearly statistically different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the puddled treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d).
+The AWD water management, which was lower than the puddled treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-6)b).
 
@@
 
-In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments, N60 and puddling water management, for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)f, \@ref(fig:fig-4)f, \@ref(fig:fig-5)f).
+In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments, N60 and puddling water management, for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)b, \@ref(fig:fig-4)b, \@ref(fig:fig-7)b).
 
-### The Interaction of Irrigation and N Management {-}
+## The Interaction of Irrigation and N Management {-}
 
-The interaction of irrigation treatment AWD with N rate N0 in 2015 or N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
-For leaf severity in the 2015 experiment the interaction was not clearly different.
-In 2016 the interaction of N180 and N180 was clearly lower than the control puddled irrigation and N60 rate.
+The interaction of irrigation treatment AWD with N rate of N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
+In the 2016 experiment the interactions were not clearly different for leaf severity from the control puddled irrigation and N60.
+In 2016 the interaction of N180 and AWD was clearly lower than the control puddled irrigation and N60 rate.
 
@@
 In both experiments we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
-In only one instance were we able to detect any statistically clear effect of AWD on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight pressure.
+In only one instance were we able to detect any statistically clear effect of AWD alone on sheath blight.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
 
@@
 
-It should be noted that the levels of leaf severity remained low (< 1 \%) throughout the growing season in all treatments for both years.
+It should be noted that the levels of leaf severity remained low (< 1&nbsp;\%) throughout the growing season in all treatments for both years.
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
@@
 
-# Tables {-}
+# Table {-}
 
 ```{r N-rates}
-
+colnames(N_rates) <-
+  c(
+    "Total",
+    "Basal",
+    "Tillering",
+    "Panicle Initiation"
+  )
 pander(N_rates,
-      caption = "Nitrogen application rates for 2015 and 2016.
+       caption = "(#tab:N-rates) Nitrogen application rates for 2015 and 2016 in kilograms per hectare.
 Five different nitrogen treatments were applied depending on the experiment.
@@
 
+\newpage
+
 # Figures {-}
-
-##### Sheath blight progress for water management treatments {-}
-\\
 
@@
 ```
-
-##### Sheath blight progress for N treatments {-}
-\\
 
@@
 
-##### Sheath Blight Incidence Boxplot for water management {-}
-\\
-
 ```{r fig-3, fig.cap="Sheath blight progress was measured in the 2015 at five assessment points and 2016 experiment at four points.
@@
 ```
-
-##### Tiller sheath blight incidence boxplot for N rate {-}
-\\
 
@@
 
-##### Tiller Estimates Plots {-}
-\\
-
-```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity.
+```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight incidence and tiller severity for 2015 (a) and 2016 (b).
 Five different N treatments were applied to split plots depending on the experiment.
@@
 
-par(mfcol = c(2, 2))
+par(mfcol = c(2, 1))
 
-plot_tiller_estimates_paper(models[[1]], main_title = "2015")
-mtext(text = "Tiller Incidence", side = 2, line = 6)
+plot_tiller_estimates_paper(models[[1]])
 mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
 
-plot_tiller_estimates_paper(models[[2]])
-mtext(text = "Tiller Severity", side = 2, line = 6)
-mtext(text = "c", side = 3, line = 0, adj = 1, cex = 0.75)
-
-plot_tiller_estimates_paper(models[[4]], main_title = "2016")
+plot_tiller_estimates_paper(models[[4]])
 mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
 
-plot_tiller_estimates_paper(models[[5]])
-mtext(text = "d", side = 3, line = 0, adj = 1, cex = 0.75)
 par(mfcol = c(1, 1))
@@
 
-##### Leaf estimates plots {-}
-\\
-
-```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity.
+```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight severity for 2015 (a) and 2016 (b).
 Five different N treatments were applied to split plots depending on the experiment.
@@
 par(mfcol = c(2, 1))
-plot_tiller_estimates_paper(models[[3]], main_title = "2015")
-mtext(text = "Leaf Severity", side = 2, line = 6)
+
+plot_tiller_estimates_paper(models[[2]])
 mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
 
-plot_tiller_estimates_paper(models[[6]], main_title = "2016")
+plot_tiller_estimates_paper(models[[5]])
+mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
+par(mfcol = c(1, 1))
+```
+
+```{r fig-7, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on leaf sheath blight severity for 2015 (a) and 2016 (b).
+Five different N treatments were applied to split plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
+
+par(mfcol = c(2, 1))
+plot_tiller_estimates_paper(models[[3]])
+mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
+
+plot_tiller_estimates_paper(models[[6]])
 mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
@@
 
-<!-- ##### pagebreak -->
+\newpage
 
-\newpage
+<!-- Use for MS Word ##### pagebreak -->
 

### 2020-06-25 analysis/paper/paper.Rmd
Clean up text and add a bit more content to discussion

@@
 Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
-Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5--10 &nbsp;\% annually.
+Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 -- 10&nbsp;\% annually.
 The disease is best managed through an integrated disease management approach, which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15--40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 -- 40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Ba\~nos, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E) in 2015 and 2016 dry seasons from December to May.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E) in 2015 and 2016 dry seasons from December to May.
 In the 2016 experiment changes were made to optimize the experiment based on findings from the 2015 experiment.
@@
 Irrigation in AWD plots was determined by the water level in plots, *i.e.* when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
-In puddled plots a standing water layer of 3--5&nbsp;cm was maintained throughout the growing season.
+In puddled plots a standing water layer of 3 -- 5&nbsp;cm was maintained throughout the growing season.
 
@@
 
-It should be noted that the levels of leaf severity remained low (< 1&nbsp;\%) throughout the growing season in all treatments for both years.
+It should be noted that the levels of leaf severity remained low (<&nbsp;1&nbsp;\%) throughout the growing season in all treatments for both years.
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
-However, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases.
+However, it should be noted that normally it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
+However, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.
 
@@
 Manually transplanted rice had higher apparent infection rates than direct seeded rice.
-As manual transplanting becomes less common due to labor constraints, sheath blight risk may be decreased (CITATION XXXX) due changes in establishment practices.
+As manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due changes in establishment practices.
 A combination of AWD and direct seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
@@
 Diseases are the only issue that farmers face when growing rice.
-Recently, Lorica *et al.* [@Lorica2020] have also found that AWD did not affect rodent damage in crops.
-Findings such as these are useful as IRRI promotes water-saving technologies like AWD because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
+Recently, Lorica *et al.* [-@Lorica2020] have also found that AWD did not affect rodent damage in crops.
+The findings our research along with those of Lorica *et al.* [-@Lorica2020] highlight the need for cross-disciplinary research that examines what the effects of new technologies that are being developed to adapt to and mitigate climate change on the pests and diseases that occur in rice.
+Ultimately these findings are useful as IRRI promotes AWD as water-saving technologies because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
 
-Climate change is predicted to decrease sheath blight risk in the Korean peninsula over the longer term [@Kim2015].
+Climate change is predicted to decrease sheath blight risk over the longer term [@Kim2015].
 However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@Kim2015].

### 2020-06-25 analysis/paper/paper.Rmd
Edits in the Discussion for clarity and update a references

@@
 
-As the rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
-Manually transplanted rice had higher apparent infection rates than direct seeded rice.
-As manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due changes in establishment practices.
+The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
+Manually transplanted rice has been found to have higher apparent infection rates than direct seeded rice.
+Therefore, as manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due changes in establishment practices.
 A combination of AWD and direct seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
@@
 
-Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2019].
+Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2020].
+The data are freely and openly available from <https://doi.org/10.5281/zenodo.3889800> [@Sparks2020a].
 

### 2020-06-25 analysis/paper/preprint-pdf.Rmd
Plant Dis format; Split pre-print and paper Rmds for PDF and Word out

--- 2020-06-25 analysis/paper/paper.Rmd
@@
   | Tooowoomba, Queensland, Australia, 4350
-csl: "../templates/european-journal-of-plant-pathology.csl" # Insert path for the bib-style
+csl: "../templates/plant_disease.csl" # Insert path for the bib-style
 abstract: |
@@
 We suggest that further cross--disciplinary research in this area is warranted.
-All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://doi.org/>.
 bibliography: references.bib
@@
   fig.path = "figures/",
-  fig.width = 3.31,
+  fig.width = 3.25,
   dev = c("postscript", "png"),
@@
 
-**Keywords** Disease $\cdot$ Sheath blight $\cdot$ *Thanatephorus cucumeris*
+**Keywords** Rice $\cdot$ Water Management $\cdot$ Nitrogen Management $\cdot$ Sheath Blight $\cdot$ *Thanatephorus cucumeris*
 
@@
 Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
-Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 -- 10&nbsp;\% annually.
+Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10&nbsp;\% annually.
 The disease is best managed through an integrated disease management approach, which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 -- 40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 to 40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
@@
 
-## 2015 Experiment {-}
-
-### Experimental Design {-}
+## 2015 Experimental Design {-}
 
@@
 Irrigation in AWD plots was determined by the water level in plots, *i.e.* when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
-In puddled plots a standing water layer of 3 -- 5&nbsp;cm was maintained throughout the growing season.
+In puddled plots a standing water layer of 3 to 5&nbsp;cm was maintained throughout the growing season.
 
 The split--plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N-rates)).
-
-### Crop Establishment {-}
 
@@
 
-### Inoculation Procedure {-}
-
 The plots were inoculated 20 days after transplanting by applying 151&nbsp;g of inoculum over the split--plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
 
-## 2016 Experiment {-}
-
-### Experimental Design {-}
+## 2016 Experimental Design {-}
 
@@
 
-### Crop Establishment {-}
-
 Nurseries of NSIC Rc222 were established on 7 January 2016.
 Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20&nbsp;cm within and between rows.
-
-### Inoculation Procedure {-}
 
@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where 0 -- no disease; 1 -- trace to 1&nbsp;\% severity; 2 -- 1 to 5&nbsp;\% severity; 3 -- 5 to 15&nbsp;\% severity; 4 -- 15 to 50&nbsp;\% severity; 5 -- 50 to 100&nbsp;\% severity.
+The scale is an unequally spaced categorical scale where (i) 0 -- no disease; (ii) 1 -- trace to 1&nbsp;\% severity; (iii) 2 -- 1 to 5&nbsp;\% severity; (iv) 3 -- 5 to 15&nbsp;\% severity; (v) 4 -- 15 to 50&nbsp;\% severity; and (vi) 5 -- 50 to 100&nbsp;\% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
@@
 
-### Tiller Sheath Blight Incidence {-}
-
 In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.&nbsp;\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
@@
 However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly statistically different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
-
-### Tiller Sheath Blight Severity {-}
 
@@
 
-### Leaf Sheath Blight Severity {-}
-
 Severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
@@
 However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
-
-## The Interaction of Irrigation and N Management {-}
 
@@
 
-### Tiller Sheath Blight Incidence {-}
-
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Fig.&nbsp;\@ref(fig:fig-2)b).
@@
 As in the 2015 study, water management did not clearly statistically differ (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
-
-### Tiller Sheath Blight Severity {-}
 
@@
 
-### Leaf Sheath Blight Severity {-}
-
 In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments, N60 and puddling water management, for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)b, \@ref(fig:fig-4)b, \@ref(fig:fig-7)b).
-
-## The Interaction of Irrigation and N Management {-}
 
@@
 Climate change is predicted to decrease sheath blight risk over the longer term [@Kim2015].
-However, over the next 10 -- 20 years the risk is predicted to remain the same as from 2000 -- 2010 [@Kim2015].
+However, over the next 10 to 20 years the risk is predicted to remain the same as from 2000 to 2010 [@Kim2015].
 Therefore, it is likely to remain an important disease in the near future with little resistance available in current varieties.
@@
 
-# Notes {-}
+# Acknowledgments {-}
 
-## Reproducibility Statement {-}
+The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr.
+R.
+King and Mr.
+D.
+Burrell of the University of Southern Queensland Statistical Consulting Unit for their insightful comments on the analysis of this paper.
 
-Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2020].
-The data are freely and openly available from <https://doi.org/10.5281/zenodo.3889800> [@Sparks2020a].
+We would also like to thank Dr. J. Villa, Mr. B. Macasero, Mr. D. Amozola, Mr. P. Escandor and Mr. P. Lapis for their technical support in the field.
 
-## Author Contributions {-}
+Funding for this research was provided through the CGIAR Research Program on rice agri-food systems Global Rice Science Partnership (GRiSP).
+
+Lastly, we would like to remember our team mate Michael Noel, an integral part of our plant disease management team at IRRI and who helped design and managed the first season of the project but passed away in September 2016.
 
@@
 
-## Acknowledgments {-}
-
-The authors wish to thank the IRRI Biometrics group for their input in the design of the experiments and Dr.
-R.
-King and Mr.
-D.
-Burrell of the University of Southern Queensland Statistical Consulting Unit for their insightful comments on the analysis of this paper.
-We would also like to thank Mr. D. Amozola, Mr. P. Escandor and Mr. P. Lapis for their technical support in the field.
-Lastly, we would like to remember our team mate Michael Noel, an integral part of our plant disease management team at IRRI and who helped design and managed the first season of the project but passed away in September 2016.
-
 <!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line. 
@@
 
-# References {-}
+# Literature Cited {-}
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document: -->
@@
 <div id="refs"></div>
+
+# Author-Recommended Internet Resources {-}
+
+Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2020].
+The data are freely and openly available from <https://doi.org/10.5281/zenodo.3889800> [@Sparks2020a].
 

### 2020-06-25 analysis/paper/paper.Rmd
Update Authors' list to use lua

@@
 title: "Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?"
-author: |
-  | Adam H. Sparks^[Corresponding author: Adam.Sparks@usq.edu.au] \textsuperscript{1\dag}, Nancy P. Castilla \textsuperscript{1}, Bjoern Ole Sander \textsuperscript{1}
-  | \textsuperscript{1}International Rice Research Institute,
-  | Crop and Environmental Sciences Division, Los Baños, Laguna, Philippines, 4031
-  | \textsuperscript{\dag} Current Address: University of Southern Queensland,
-  | Centre for Crop Health, West Street,
-  | Tooowoomba, Queensland, Australia, 4350
-csl: "../templates/european-journal-of-plant-pathology.csl" # Insert path for the bib-style
+author:
+  - Adam H. Sparks:
+      email: Adam.Sparks@usq.edu.au
+      correspondence: true
+      institute: [IRRI, USQ]
+  - name: Nancy P. Castilla
+    institute: IRRI
+    email: n.castilla@irri.org
+    correspondence: false
+  - name: B. Ole Sander
+    institute: IRRI
+    email: b.sander@irri.org
+    correspondence: false
+institute:
+  - IRRI: International Rice Research Institute, Los Baños, Laguna, Philippines, 4031
+  - USQ: CURRENT ADDRESS -- University of Southern Queensland, Centre for Crop Health, Toowoomba, Qld 4350, Australia
+date: "`r format(Sys.time(), '%d %B, %Y')`"
+output:
+  bookdown::word_document2:
+    toc: no
+    fig_caption: yes
+    reference_docx: "../templates/template.docx"
+    pandoc_args:
+      - '--lua-filter=scholarly-metadata.lua'
+      - '--lua-filter=author-info-blocks.lua'
+csl: "../templates/plant_disease.csl" # Insert path for the bib-style
+bibliography: references.bib
 abstract: |
@@
 However, the mismanagement of these two crop inputs may trigger the development of sheath blight of rice, caused by _Thanatephorus cucumeris_ (strain AG1-IA), which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
-To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split--plot experiments with a water saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
+To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water-saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
 Disease was scored using the same methodology in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
 We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did clearly differ statistically by irrigation treatment, but leaf sheath blight severity did not.
-Our findings indicate that farmers can adopt water saving technologies without risking increased sheath blight incidence.
-We suggest that further cross--disciplinary research in this area is warranted.
-All data generated from this project and code used for analysis are available as a reproducible research compendium from <https://doi.org/>.
-bibliography: references.bib
-output:
-  bookdown::pdf_document2:
-    toc: no
-    fig_caption: yes
-    #reference_docx: "../templates/template.docx"
-header-includes:
-  - \usepackage[T1]{fontenc}
-  - \usepackage[utf8]{inputenc}
-  - \DeclareUnicodeCharacter{2500}{\mbox{\vrule height2.2ptdepth-1.8ptwidth.5em}}
+Our findings indicate that farmers can adopt water-saving technologies without risking increased sheath blight incidence.
+We suggest that further cross-disciplinary research in this area is warranted.
+keywords: |
+  Rice; Water Management; Nitrogen Management; Sheath Blight; *Thanatephorus cucumeris*
+highlights: |
+  * The effects of AWD on sheath blight disease incidence and severity were investigated.
+  * AWD had no detectable effect on either sheath blight incidence or sheath blight severity.
+  * The interaction of AWD and nitrogen management had no detectable effect on either sheath blight incidence or sheath blight severity.
+  * The adoption of AWD technologies will not lead to increased sheath blight incidence or sheath blight severity.
 ---
@@
 
-**Keywords** Disease $\cdot$ Sheath blight $\cdot$ *Thanatephorus cucumeris*
-
-\twocolumn
-
-# Key Message {-}
-
-* The effects of AWD on sheath blight disease incidence and severity were investigated.
-
-* AWD had no detectable effect on either sheath blight incidence or sheath blight severity.
-
-* The interaction of AWD and nitrogen management had no detectable effect on either sheath blight incidence or sheath blight severity.
-
-* The adoption of AWD technologies will not lead to increased sheath blight incidence or sheath blight severity.
+##### pagebreak
 
@@
 
-Rice is mainly produced in Asia with over 90&nbsp;% of production in Asia [@GRiSP2013] and uses the largest amount of any agricultural commodity [@Dawe2005; @GRiSP2013].
+Rice is mainly produced in Asia with over 90&nbsp;% of production occurring there [@GRiSP2013] and uses the largest amount of any agricultural commodity [@Dawe2005; @GRiSP2013].
 
 Climate change will bring changes to the environments in which our food crops are produced in [@Reyer2013].
-Rice (*Oryza sativa*) is the most widely grown cereal crop in a diverse set of environments globally and will will have to adapt to changing environments where it is grown as a result.
+Rice (*Oryza sativa*) is the most widely grown cereal crop in a diverse set of environments globally and will have to adapt to changing environments where it is grown as a result.
 
-Rice's reliance on freely available water water, coupled with the effects of climate change mean that rice production practices will have to adapt to use new practices to produce more units of food with less water inputs.
+Rice's reliance on freely available water, coupled with the effects of climate change mean that rice production practices will have to adapt to use new practices to produce more units of food with fewer water inputs.
 
@@
 Frank) Donk.), anastomosis group 1, of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
-Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 -- 10&nbsp;\% annually.
+Under conducive conditions, the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
+Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10&nbsp;\% annually.
 The disease is best managed through an integrated disease management approach, which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 -- 40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 to 40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
-In order to avoid yield decline under AWD, "safe" thresholds have been developed.
+To avoid yield decline under AWD, "safe" thresholds have been developed.
 Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
 Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress.
-As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
 
-The AWD technology has been identified as promising climate smart practice for different rice growing regions that can stabilize rice production in water scarce areas as well as help reduce the carbon footprint of rice production.
+The AWD technology has been identified as promising climate-smart practice for different rice-growing regions that can stabilize rice production in water-scarce areas, as well as help, reduce the carbon footprint of rice production.
 Various countries, *e.g.* Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
-However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example changes in disease incidence or severity.
+However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example, changes in disease incidence or severity.
 
 Many studies have been conducted *in silico* that examine how diseases may change with a changing climate.
-Rice blast is perhaps the the most frequently studied rice disease in regards to the effects of climate change [@Luo1995; @Luo1998; @Kim2015; @Duku2016; @Viswanath2017].
+Rice blast is perhaps the most frequently studied rice disease in regards to the effects of climate change [@Luo1995; @Luo1998; @Kim2015; @Duku2016; @Viswanath2017].
 However, Kim *et al.* [-@Kim2015] have modelled the effects of climate change on sheath blight with epidemics predicted to decrease by 2100 in their study, which focused on the Korean peninsula.
@@
 While the effects of climate change directly on rice disease have been studied, the effects of mitigation practices have not.
-Rice farmers may be hesitant to adopt water saving technologies because changing rice production practices could have unintended effects on the pests and diseases that occur in the rice crop.
-This is a reasonable concern because of the well documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight.
-In order to gain a better understanding of what the effects of adopting AWD on rice sheath blight may be, we established field experiments that incorporated irrigation technology and N fertilisation.
+Rice farmers may be hesitant to adopt water-saving technologies because changing rice production practices could have unintended effects on the pests and diseases that occur in the rice crop.
+This is a reasonable concern because of the well-documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight.
+To gain a better understanding of what the effects of adopting AWD on rice sheath blight could have, we established field experiments that incorporated irrigation technology and N fertilisation.
 
@@
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E) in 2015 and 2016 dry seasons from December to May.
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E).
+The climate is classified as humid-tropical with wet season starting in early June to December and dry season between December and late May.
+The experiments were both established in the dry seasons of 2015 and 2016.
 In the 2016 experiment changes were made to optimize the experiment based on findings from the 2015 experiment.
@@
 
-## 2015 Experiment {-}
+## 2015 Experimental Design {-}
 
-### Experimental Design {-}
-
-The plot design was a split--plot randomised complete block design with four replicates where irrigation was the main plot treatment and N rate was the split--plot treatment.
+The plot design was a split-plot randomised complete block design with four replicates where irrigation was the main plot treatment and N rate was the split-plot treatment.
 
 The main plot treatments were alternate wetting and drying (AWD) and continuously puddled or farmers' practice as the control treatment.
-The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2^), with a split--plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2^).
-Replication size was 12&nbsp;m&nbsp;x&nbsp;24&nbsp;m (288&nbsp;m^2^) with a buffer of 1&nbsp;m per split--plot for a whole experiment size of 1,152&nbsp;m^2^.
+The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2^), with a split-plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2^).
+Replication size was 12&nbsp;m&nbsp;x&nbsp;24&nbsp;m (288&nbsp;m^2^) with a buffer of 1&nbsp;m per split-plot for a whole experiment size of 1,152&nbsp;m^2^.
 
 Irrigation in AWD plots was determined by the water level in plots, *i.e.* when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
-In puddled plots a standing water layer of 3 -- 5&nbsp;cm was maintained throughout the growing season.
+In puddled plots, a standing water layer of 3 to 5&nbsp;cm was maintained throughout the growing season.
 
-The split--plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N-rates)).
-
-### Crop Establishment {-}
+The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N-rates)).
 
@@
 
-### Inoculation Procedure {-}
+The plots were inoculated 20 days after transplanting by applying 151&nbsp;g of inoculum over the split-plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
 
-The plots were inoculated 20 days after transplanting by applying 151&nbsp;g of inoculum over the split--plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
+## 2016 Experimental Design {-}
 
-## 2016 Experiment {-}
+The 2016 experiment followed the same split-plot design as described for the 2015 experiment.
+However, the plot size was increased and due to these changes, the replicate sizes are not equal as necessitated by the use of a larger area for the experiment due to differences in the blocks.
+The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2^).
+The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2^), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2^).
+The replication sizes were B1 --- 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2^) and B2 --- 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2^).
+A buffer 0.5&nbsp;m per split-plot was used and the overall experiment size was 3471.6&nbsp;m^2^.
 
-### Experimental Design {-}
-
-The 2016 experiment followed the same split--plot design as described for the 2015 experiment.
-However, the plot size was increased and due to these changes, the replicate sizes are are not equal as necessitated by the use of a larger area for the experiment due to differences in the blocks.
-The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2^).
-The split--plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2^), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2^).
-The replication sizes were B1 --- 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2^) and B2 --- 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2^).
-A buffer 0.5&nbsp;m per split--plot was used and the overall experiment size was 3471.6&nbsp;m^2^.
-
-Split--plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg&nbsp;/&nbsp;ha as urea split into two applications) and N180 (180&nbsp;kg&nbsp;/&nbsp;ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N-rates)).
-
-### Crop Establishment {-}
+split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg/ha as urea split into two applications) and N180 (180&nbsp;kg/ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N-rates)).
 
@@
 Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20&nbsp;cm within and between rows.
-
-### Inoculation Procedure {-}
 
@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where 0 -- no disease; 1 -- trace to 1&nbsp;\% severity; 2 -- 1 to 5&nbsp;\% severity; 3 -- 5 to 15&nbsp;\% severity; 4 -- 15 to 50&nbsp;\% severity; 5 -- 50 to 100&nbsp;\% severity.
+The scale is an unequally spaced categorical scale where (i) 0 --- no disease; (ii) 1 --- trace to 1&nbsp;\% severity; (iii) 2 --- 1 to 5&nbsp;\% severity; (iv) 3 --- 5 to 15&nbsp;\% severity; (v) 4 --- 15 to 50&nbsp;\% severity; and (vi) 5 --- 50 to 100&nbsp;\% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
 A leaf was considered living if at least 50&nbsp;% of its area was not brown or dark brown due to natural senescence.
-A leaf that was yellow green or light green due to a disease, such as tungro or nitrogen deficiency was still considered a living leaf.
+A leaf that was yellow-green or light green due to a disease, such as tungro or nitrogen deficiency was still considered a living leaf.
 The same rating methodology was used in both experiments.
@@
 
-Area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 4.0.0 [@R2020], package `agricolae`, version 1.3-3, [@agricolae2020].
+The area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 4.0.0 [@R2020], package `agricolae`, version 1.3-3, [@agricolae2020].
 Due to the use of a severity scale for data collection, the severity data were converted to the midpoint percent value of the scale range for each value.
 
-The correlations between tiller sheath sheath blight incidence and tiller and leaf sheath blight severity were tested using Spearman’s correlation test, `cor.test`, [@R2020].
+The correlations between tiller sheath blight incidence and tiller and leaf sheath blight severity were tested using Spearman’s correlation test, `cor.test`, [@R2020].
 No correlation was found, so the analysis was completed for each variable independently with no assumed interaction.
@@
 As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm`, version 2.29, [@MCMCglmm2010].
-Six models were created where the the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
+Six models were created where the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were: N rate -- N0, irrigation management -- puddled and for 2016 they were: N rate -- N60, irrigation management -- puddled
+The base levels (control treatments) for the analyses for 2015 were: N rate --- N0, irrigation management --- puddled and for 2016 they were: N rate --- N60, irrigation management --- puddled
 
-Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn in.
+Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn-in.
 The remaining 50,000 samples were used to determine the posterior distribution of the parameters of the model.
-The `coda` version 0.19-3 [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman--Rubin test.
+The `coda` version 0.19-3 [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test.
 
@@
 
-### Tiller Sheath Blight Incidence {-}
-
 In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.&nbsp;\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
-Water management was not clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly statistically different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
-
-### Tiller Sheath Blight Severity {-}
+Water management was not clearly different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
+However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
 
@@
 
-### Leaf Sheath Blight Severity {-}
-
-Severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
+The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
 As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
 However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
-
-## The Interaction of Irrigation and N Management {-}
 
@@
 
-### Leaf Sheath Blight Severity {-}
-
 In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments, N60 and puddling water management, for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)b, \@ref(fig:fig-4)b, \@ref(fig:fig-7)b).
 
-## The Interaction of Irrigation and N Management {-}
-
 The interaction of irrigation treatment AWD with N rate of N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
-In the 2016 experiment the interactions were not clearly different for leaf severity from the control puddled irrigation and N60.
+In the 2016 experiment, the interactions were not clearly different for leaf severity from the control puddled irrigation and N60.
 In 2016 the interaction of N180 and AWD was clearly lower than the control puddled irrigation and N60 rate.
@@
 
-In both experiments we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
+In both experiments, we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
 In only one instance were we able to detect any statistically clear effect of AWD alone on sheath blight.
@@
 Higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
-However, in the 2016 experiment there were no clear differences due to the N rate tiller and leaf severity.
+However, in the 2016 experiment, there were no clear differences due to the N rate tiller and leaf severity.
 
@@
 In 2015 there were no clear differences in the interaction of irrigation and N rate between any of the three treatments.
-However, in the 2016 experiment the combination of AWD--N180 was clearly different, being lower, than the PDL--N60 combination treatment.
+However, in the 2016 experiment, the combination of AWD--N180 was clearly different, being lower, than the PDL--N60 combination treatment.
 
@@
 The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
-Manually transplanted rice has been found to have higher apparent infection rates than direct seeded rice.
-Therefore, as manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due changes in establishment practices.
-A combination of AWD and direct seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
+Manually transplanted rice has been found to have higher apparent infection rates than direct-seeded rice.
+Therefore, as manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due to changes in establishment practices.
+A combination of AWD and direct-seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
 
@@
 
-# Notes {-}
-
-## Reproducibility Statement {-}
-
-Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2020].
-The data are freely and openly available from <https://doi.org/10.5281/zenodo.3889800> [@Sparks2020a].
-
-## Author Contributions {-}
-
-AHS and BOS conceived the topic.
-AHS and NPC conceived the research.
-NPC conducted the field work in 2016.
-AHS conducted the data analysis.
-All the authors contributed to the writing of the manuscript.
-
-## Acknowledgments {-}
+# Acknowledgments {-}
 
@@
 Burrell of the University of Southern Queensland Statistical Consulting Unit for their insightful comments on the analysis of this paper.
-We would also like to thank Mr. D. Amozola, Mr. P. Escandor and Mr. P. Lapis for their technical support in the field.
-Lastly, we would like to remember our team mate Michael Noel, an integral part of our plant disease management team at IRRI and who helped design and managed the first season of the project but passed away in September 2016.
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line. 
-##### pagebreak  -->
+We would also like to thank Dr. J. Villa, Mr. B. Macasero, Mr. D. Amozola, Mr. P. Escandor and Mr. P. Lapis for their technical support in the field.
 
-# References {-}
+Funding for this research was provided through the CGIAR Research Program on rice agri-food systems Global Rice Science Partnership (GRiSP).
+
+Lastly, we would like to remember our teammate Michael Noel, an integral part of our plant disease management team at IRRI and who helped design and managed the first season of the project but passed away in September 2016.
+
+AHS and BOS conceived the topic. AHS and NPC conceived the research. NPC conducted the fieldwork in 2016. AHS conducted the data analysis. All the authors contributed to the writing of the manuscript.
+
+<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line. -->
+##### pagebreak
+
+# Literature Cited {-}
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document: -->
@@
 
-\onecolumn
+# Author-Recommended Internet Resources {-}
+
+Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2020].
+The data are freely and openly available from <https://doi.org/10.5281/zenodo.3889800> [@Sparks2020a].
+
+##### pagebreak
 
@@
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).
 Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
@@
 
-\newpage
+##### pagebreak
 
@@
 ```{r fig-2, fig.cap="Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180).
+Five different N treatments were applied to split-plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).
 Points represent the mean observations of four replications."}
@@
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid--point percentage value to calculate the AUDPS.
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
 Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD)."}
@@
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid--point percentage value to calculate the AUDPS.
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
+Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Five different N treatments were applied to split-plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180)."}
 
@@
 ```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight incidence and tiller severity for 2015 (a) and 2016 (b).
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
+Five different N treatments were applied to split-plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180)."}
 
@@
 ```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight severity for 2015 (a) and 2016 (b).
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
+Five different N treatments were applied to split-plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180)."}
 
@@
 ```{r fig-7, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on leaf sheath blight severity for 2015 (a) and 2016 (b).
-Five different N treatments were applied to split plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
+Five different N treatments were applied to split-plots depending on the experiment.
+In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180)."}
 

### 2020-06-27 R/data.R
Clean up data preprocessing file and saved data files

@@ -1,11 +1,10 @@
 
-#' A Data Frame of Area Under the Disease Progress Curve and Stairs for Sheath Blight Observations
+#' A Data Frame of Area Under the Disease Progress Stairs for Sheath Blight Observations
 #'
 #' A dataset containing the alternate wetting and drying study data observations
-#' and calculated Area Under the Disease Progress Curve (AUDPC) and Stairs
-#' (AUDPS)
+#' and calculated Area Under the Disease Progress Stairs (AUDPS)
 #'
-"AUDPC_S"
+"AUDPS"
 
 #' A Data frame of Raw Data for Sheath Blight Observations
 #'

### 2020-06-27 R/plot_estimates.R
Remove MCMCglmm and associated items

@@ -1,89 +1,0 @@
-
-#' @title Plot MCMCglmm tiller estimates
-#'
-#' @description Plot estimates of posterior distributions and credible
-#'  intervals of \pkg{MCMCglmm} outputs
-#'
-#' @name plot_tiller_estimates
-#' @param x A \code{\link[coda]{mcmc.list}} object
-#'
-#' @examples \dontrun{
-#' # Plot posterior means and credible intervals
-#' plot_tiller_estimates(m1)
-#'}
-#'
-#' @import coda
-#' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
-#'
-#' @export
-plot_tiller_estimates <- function(x) {
-  graphics::par(mfrow = c(1, 1))
-  if (class(x) != "summary.mcmc") {
-    x <- summary(x)
-  }
-  n <- dim(x$statistics)[1]
-  graphics::par(mar = c(2, 7, 4, 1))
-  graphics::plot(
-    x$statistics[, 1],
-    n:1,
-    yaxt = "n",
-    ylab = "",
-    xlim = range(x$quantiles) * 1.2,
-    pch = 19,
-    main = "Posterior means and 95% credible intervals",
-    bty = "L"
-  )
-
-  # extract treatment names and clean them up for the graph
-  row.names(x$statistics) <- gsub(pattern = "WMGT", "", row.names(x$statistics))
-  row.names(x$statistics) <- gsub(pattern = "NRTE", "", row.names(x$statistics))
-
-  graphics::axis(side = 2, at = n:1, rownames(x$statistics), las = 2)
-  graphics::arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
-  graphics::abline(v = 0, lty = 2)
-}
-
-
-#' @title Plot MCMCglmm leaf estimates
-#'
-#' @description Plot estimates of posterior distributions and credible
-#'  intervals of \pkg{MCMCglmm} outputs
-#'
-#' @name plot_leaf_estimates
-#' @param x A \code{\link[coda]{mcmc.list}} object
-#'
-#' @examples \dontrun{
-#' # Plot posterior means and credible intervals
-#' plot_leaf_estimates(m1)
-#'}
-#'
-#' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
-#'
-#' @export
-plot_leaf_estimates <- function(x) {
-  graphics::par(mfrow = c(1, 1))
[…]

### 2020-06-27 R/plot_estimates_paper.R

@@ -1,88 +1,0 @@
-
-#' @title Plot MCMCglmm tiller estimates for publication
-#'
-#' @description Plot estimates of posterior distributions and credible
-#'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
-#'
-#' @name plot_tiller_estimates_paper
-#' @param x A \code{\link[coda]{mcmc.list}} object
-#' @param main_title Main title for the plot
-#'
-#' @examples \dontrun{
-#' # Plot posterior means and credible intervals
-#' plot_estimates(m1)
-#'}
-#'
-#' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
-#'
-#' @export
-plot_tiller_estimates_paper <- function(x, main_title = "") {
-  if (class(x) != "summary.mcmc") {
-    x <- summary(x)
-  }
-  n <- dim(x$statistics)[1]
-  graphics::par(mar = c(2, 7, 4, 1))
-  graphics::plot(
-    x$statistics[, 1],
-    n:1,
-    yaxt = "n",
-    ylab = "",
-    xlim = range(x$quantiles) * 1.2,
-    pch = 19,
-    main = main_title,
-    bty = "L"
-  )
-
-  # extract treatment names and clean them up for the graph
-  row.names(x$statistics) <- gsub(pattern = "WMGT", "", row.names(x$statistics))
-  row.names(x$statistics) <- gsub(pattern = "NRTE", "", row.names(x$statistics))
-
-  graphics::axis(side = 2, at = n:1, row.names(x$statistics), las = 2)
-  graphics::arrows(x$quantiles[, 1], n:1, x$quantiles[, 5], n:1, code = 0)
-  graphics::abline(v = 0, lty = 2)
-}
-
-
-#' @title Plot MCMCglmm leaf estimates for publication
-#'
-#' @description Plot estimates of posterior distributions and credible
-#'  intervals of \pkg{MCMCglmm} outputs sans intercept for publication figure
-#'
-#' @name plot_leaf_estimates_paper
-#' @param x A \code{\link[coda]{mcmc.list}} object
-#' @param main_title Main title for the plot
-#'
-#' @examples \dontrun{
-#' # Plot posterior means and credible intervals
-#' plot_estimates(m1)
-#'}
-#'
-#' @author Titus von der Malsburg, \email{malsburg@uni-potsdam.de}
-#'
-#' @export
[…]

### 2020-06-27 R/rice.awd.pests.R

@@ -1,25 +1,0 @@
-
-#' Reproducible Research Compendium for Analysing Effects of Water Management and Nitrogen on Rice Sheath Blight and Insect Populations
-#'
-#' @description
-#' Provides a research compendium of analysis associated with experiments
-#' conducted at the International Rice Research Institute (IRRI), Los Baños,
-#' Calabarzon, Philippines in the dry seasons of 2015 and 2016. The experiments
-#' were designed to test the effects of alternate wetting and drying irrigation
-#' management on rice sheath blight disease. The plots were split plot with an
-#' irrigation main plot and nitrogen sub-plot treatments.
-#'
-#' @name rice.awd.pests-package
-#' @author Adam H Sparks and Nancy P Castilla and Michael Noel
-#' @docType package
-#'
-#' @seealso
-#'\strong{Useful links:}
-#' \itemize{
-#' \item{\url{https://github.com/phytopathology/rice_awd_pests}}
-#' \item{Report bugs at
-#'  \url{https://github.com/phytopathology/rice_awd_pests/issues}}
-#' \item{Research compendium website
-#'  \url{https://phytopathology.github.io/rice_awd_pests/}}
-#' }
-NULL

### 2020-06-27 analysis/paper/paper.Rmd
Update saved models for paper

@@
 ```{r N-rates}
+N_rates <- N_rates[, -1]
 colnames(N_rates) <-
@@
 
-p7 <- ggplot(AUDPC_S,
+p7 <- ggplot(AUDPS,
              aes(x = WMGT, y = TShB_inc_AUDPS)) +
@@
 
-p8 <- ggplot(AUDPC_S,
-             aes(x = WMGT, y = TShB_sev_AUDPS)) +
+p8 <- ggplot(AUDPS,
+             aes(x = WMGT, y = TShB_percent_AUDPS)) +
   geom_boxplot() +
@@
 
-p9 <- ggplot(AUDPC_S,
-             aes(x = WMGT, y = LShB_sev_AUDPS)) +
+p9 <- ggplot(AUDPS,
+             aes(x = WMGT, y = LShB_percent_AUDPS)) +
   geom_boxplot() +
@@
 
-p10 <- ggplot(AUDPC_S,
+p10 <- ggplot(AUDPS,
              aes(x = NRTE, y = TShB_inc_AUDPS)) +
@@
 
-p11 <- ggplot(AUDPC_S,
-             aes(x = NRTE, y = TShB_sev_AUDPS)) +
+p11 <- ggplot(AUDPS,
+             aes(x = NRTE, y = TShB_percent_AUDPS)) +
   geom_boxplot() +
@@
 
-p12 <- ggplot(AUDPC_S,
-             aes(x = NRTE, y = LShB_sev_AUDPS)) +
+p12 <- ggplot(AUDPS,
+             aes(x = NRTE, y = LShB_percent_AUDPS)) +
   geom_boxplot() +
@@
 In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180)."}
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).", eval=FALSE}
 

### 2020-06-28 analysis/paper/paper.Rmd
Fix issues knitting paper

@@
              aes(x = DAI,
-                 y = PERC_TIL_ShB)) +
+                 y = PERCENT_TIL_ShB)) +
   geom_text(
@@
              aes(x = DAI,
-                 y = PERC_LEAF_ShB)) +
+                 y = PERCENT_LEAF_ShB)) +
   geom_text(
@@
 p7 <- ggplot(AUDPS,
-             aes(x = WMGT, y = TShB_inc_AUDPS)) +
+             aes(x = WMGT, y = TShB_incidence_AUDPS)) +
   geom_boxplot() +
@@
 p10 <- ggplot(AUDPS,
-             aes(x = NRTE, y = TShB_inc_AUDPS)) +
+             aes(x = NRTE, y = TShB_incidence_AUDPS)) +
   geom_boxplot() +

### 2020-07-06 analysis/paper/paper.Rmd
Fix colnames so that paper knits

@@
              aes(x = DAI,
-                 y = PERCENT_TIL_ShB)) +
+                 y = TIL_ShB)) +
   geom_text(
@@
                    shape = WMGT)) +
-  scale_y_continuous(name = "Tiller Severity (%)") +
+  scale_y_continuous(name = "Tiller Severity (0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
              aes(x = DAI,
-                 y = PERCENT_LEAF_ShB)) +
+                 y = LEAF_ShB)) +
   geom_text(
@@
                    shape = WMGT)) +
-  scale_y_continuous(name = "Leaf Severity (%)") +
+  scale_y_continuous(name = "Leaf Severity (0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
                    shape = NRTE)) +
-  scale_y_continuous(name = "Tiller Severity (%)") +
+  scale_y_continuous(name = "Tiller Severity 0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
                    shape = NRTE)) +
-  scale_y_continuous(name = "Leaf Severity (%)") +
+  scale_y_continuous(name = "Leaf Severity (0 - 5 scale)") +
   xlab("Days After Inoculation") +

### 2020-07-07 analysis/paper/paper.Rmd
Fix tables and edit statistical analysis methods

@@
 To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water-saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
-Disease was scored using the same methodology in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers were counted per hill.
-We were unable to detect any difference in the incidence of tiller sheath blight due to irrigation, tiller and leaf sheath blight did clearly differ statistically by irrigation treatment, but leaf sheath blight severity did not.
+Disease was scored using the same methodology in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers was counted per hill.
+We were unable to detect any clear differences in the incidence or severity of tiller sheath blight due to irrigation treatment.
+Leaf severity for the AWD treatment was clearly lower in the 2015 trial but higher in 2016.
+However, the level of disease severity remained low in both years, < 1&nbsp;%.
 Our findings indicate that farmers can adopt water-saving technologies without risking increased sheath blight incidence.
@@
 library("gridExtra")
-library("pander")
+library("flextable")
 library("rice.awd.shb")
@@
 
-Sheath blight disease, caused by (*Thanatephorus cucumeris* (A.B.
-Frank) Donk.), anastomosis group 1, of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions, the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
+Sheath blight disease, caused by *Thanatephorus cucumeris* (A.B.
+Frank) Donk.
+anastomosis group 1 IA, of rice is an economically important disease worldwide throughout tropical and temperate production areas.
+Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
 Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10&nbsp;\% annually.
@@
 This is a reasonable concern because of the well-documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight.
-To gain a better understanding of what the effects of adopting AWD on rice sheath blight could have, we established field experiments that incorporated irrigation technology and N fertilisation.
+To gain a better understanding of what the effects of adopting AWD on rice sheath blight could have, we established field experiments that incorporated irrigation technology and N fertilisation to create a conducive environment for the disease to develop.
 
@@
 The experiments were both established in the dry seasons of 2015 and 2016.
-In the 2016 experiment changes were made to optimize the experiment based on findings from the 2015 experiment.
+In the 2016 experiment changes were made in inoculation techniques, fertilisation rates and plot sizes to optimize the experiment based on findings from the 2015 experiment.
 The differences are detailed in the following sections.
@@
 
-An isolate of *Thanatephorus cucumeris* infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
+An isolate of _Thanatephorus cucumeris_ (strain AG1-IA) infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
 The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C) for five days.
@@
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:N-rates)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:Table-1)).
 
@@
 The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2^), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2^).
-The replication sizes were B1 --- 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2^) and B2 --- 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2^).
+The replication sizes were B1 -- 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2^) and B2 -- 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2^).
 A buffer 0.5&nbsp;m per split-plot was used and the overall experiment size was 3471.6&nbsp;m^2^.
 
-split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg/ha as urea split into two applications) and N180 (180&nbsp;kg/ha in three splits) being applied (Tab.&nbsp;\@ref(tab:N-rates)).
+split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg/ha as urea split into two applications) and N180 (180&nbsp;kg/ha in three splits) being applied (Tab.&nbsp;\@ref(tab:Table-1)).
 
@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where (i) 0 --- no disease; (ii) 1 --- trace to 1&nbsp;\% severity; (iii) 2 --- 1 to 5&nbsp;\% severity; (iv) 3 --- 5 to 15&nbsp;\% severity; (v) 4 --- 15 to 50&nbsp;\% severity; and (vi) 5 --- 50 to 100&nbsp;\% severity.
+The scale is an unequally spaced categorical scale where (i) 0 -- no disease; (ii) 1 -- trace to 1&nbsp;\% severity; (iii) 2 -- 1 to 5&nbsp;\% severity; (iv) 3 -- 5 to 15&nbsp;\% severity; (v) 4 -- 15 to 50&nbsp;\% severity; and (vi) 5 -- 50 to 100&nbsp;\% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
@@
 The area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 4.0.0 [@R2020], package `agricolae`, version 1.3-3, [@agricolae2020].
-Due to the use of a severity scale for data collection, the severity data were converted to the midpoint percent value of the scale range for each value.
 
-The correlations between tiller sheath blight incidence and tiller and leaf sheath blight severity were tested using Spearman’s correlation test, `cor.test`, [@R2020].
-No correlation was found, so the analysis was completed for each variable independently with no assumed interaction.
-
-As most of the data's residuals did not meet assumptions for normality, the analysis was carried out using Bayesian multivariate generalised linear mixed models implemented in the R package `MCMCglmm`, version 2.29, [@MCMCglmm2010].
+Bayesian multivariate mixed models were fitted using the contributed R package `brms`, version 0.70, [@Buerkner2018; @Buerkner2017].
 Six models were created where the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
 The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were: N rate --- N0, irrigation management --- puddled and for 2016 they were: N rate --- N60, irrigation management --- puddled
+The base levels (control treatments) for the analyses for 2015 were: N rate -- N0, irrigation management -- puddled and for 2016 they were: N rate -- N60, irrigation management -- puddled.
 
-Four MCMC chains were run for 55,000 steps with the first 5000 discarded as burn-in.
-The remaining 50,000 samples were used to determine the posterior distribution of the parameters of the model.
-The `coda` version 0.19-3 [@coda2006] package was used to provide utilities to check MCMC chain convergence using visual inspection of resulting trace graphs and the Gelman-Rubin test.
+Weakly informative priors and families were set for the fixed effects in each model while the random effects and intercept were selected automatically (Tab.&nbsp;\@ref(tab:Table-2)).
+Four chains were run with a warmup of 5000 and 8000 iterations.
+Model fit was evaluated visually using `pp_check()` and `describe_posterior()`.
+Further fitness was evaluated using the `describe_posterior()` function from bayestestR, version 0.70, [@Makowski2019].
 
@@
 
-# Table {-}
+# Tables {-}
 
-```{r N-rates}
+```{r Table-1}
 N_rates <- N_rates[, -1]
 colnames(N_rates) <-
-  c(
-    "Total",
+  c("Total",
     "Basal",
     "Tillering",
-    "Panicle Initiation"
-  )
-pander(N_rates,
-       caption = "(#tab:N-rates) Nitrogen application rates for 2015 and 2016 in kilograms per hectare.
+    "Panicle Initiation")
+N_rates <- flextable(as.data.frame(N_rates))
+
+N_rates <-
+  set_caption (N_rates,
+               caption = 
+    "(\\#tab:Table-1) Nitrogen application rates for 2015 and 2016 in kilograms per hectare.
 Five different nitrogen treatments were applied depending on the experiment.
@@
 In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).
-Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
+Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications."
+    )
+
+N_rates
+```
+
+```{r Table-2}
+priors <- "
+Year | Fixed Effect     | distribution | mean | sd | brmsfamily  | adapt_delta | max_treedepth
+2015 | Tiller Incidence | normal       | 0    | 1  | gaussian    | 0.9999      | 15
+2015 | Tiller Severity  | normal       | 0    | 1  | skew_normal | 0.9999      | 10
+2015 | Leaf Severity    | normal       | 1    | 3  | hurdle_gamma| 0.99        | 10
+2016 | Tiller Incidence | normal       | 0    | 2  | hurdle_gamma| 0.9999      | 10
+2016 | Tiller Severity  | normal       | 0    | 1  | hurdle_gamma| 0.99        | 15
+2016 | Leaf Severity    | normal       | 0    | 2  | hurdle_gamma| 0.999       | 10
+"
+
+priors <- read.delim(
+  textConnection(priors),
+  header = FALSE,
+  sep = "|",
+  strip.white = TRUE,
+  stringsAsFactors = FALSE
+)
+names(priors) <- unname(as.list(priors[1, ])) # put headers on
+priors <- priors[-1, ] # remove first row
+row.names(priors) <- NULL
+priors <- flextable(as.data.frame(priors))
+priors <- set_caption(priors,
+                      caption =
+    "(\\#tab:Table-2) Details of models used to detect differences between irrigation methods, alternate wetting and drying (AWD) and traditional puddling, and nitrogen fertilisation rates.
+Values are for the fixed effect prior values, family, adapt_delta and max_treedepth as used in the contributed R package, brms, function brm() to fit Bayesian models."
+    )
+priors
 ```

### 2020-07-07 analysis/paper/paper.Rmd
edits to figures

@@
 Water management was not clearly different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)a, \@ref(fig:fig-5)a).
+However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-5)a, \@ref(fig:fig-5)a).
 
@@
 
-```{r fig-1, fig.cap="Sheath blight progress for 2015 and 2016 experiments.
-Disease progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years.
+```{r fig-1, fig.cap="Sheath blight disease progress curves for 2015 and 2016 experiments.
+Disease progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season of both years.
 Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD).
@@
   x = c(60, 60),
-  y = c(10, 10)
+  y = c(5, 5)
 )
@@
                    shape = WMGT)) +
-  scale_y_continuous(name = "Tiller Severity (0 - 5 scale)") +
+  scale_y_continuous(limits = c(0, 5),
+                     name = "Tiller Severity (0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
                    shape = WMGT)) +
-  scale_y_continuous(name = "Leaf Severity (0 - 5 scale)") +
+  scale_y_continuous(limits = c(0, 5),
+                     name = "Leaf Severity (0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
                    shape = NRTE)) +
-  scale_y_continuous(name = "Tiller Severity 0 - 5 scale)") +
+  scale_y_continuous(limits = c(0, 5),
+                     name = "Tiller Severity 0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
                    shape = NRTE)) +
-  scale_y_continuous(name = "Leaf Severity (0 - 5 scale)") +
+  scale_y_continuous(limits = c(0, 5),
+                     name = "Leaf Severity (0 - 5 scale)") +
   xlab("Days After Inoculation") +
@@
 Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS).
-Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid-point percentage value to calculate the AUDPS.
+Sheath blight severity was rated on an unevenly spaced ordinal scale from zero to five.
 Main plot irrigation treatments were permanently puddled (PDL) and alternate wetting and drying (AWD)."}
-
 p7_anot <- data.frame(
@@
   x = c(2.5, 2.5),
-  y = c(15, 15)
+  y = c(5, 5)
 )
@@
   x = c(2.5, 2.5),
-  y = c(32, 32)
+  y = c(55, 55)
 )
@@
   x = c(2.5, 2.5),
-  y = c(10, 10)
+  y = c(8, 8)
 )
@@
   x = c(3.5, 2.5),
-  y = c(14, 14)
+  y = c(5, 5)
 )
@@
   x = c(3.5, 2.5),
-  y = c(32, 32)
+  y = c(55, 55)
 )
@@
   x = c(3.5, 2.5),
-  y = c(7, 7)
+  y = c(8, 8)
 )
@@
 
-```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight incidence and tiller severity for 2015 (a) and 2016 (b).
+```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight incidence for 2015 (a) and 2016 (b).
 Five different N treatments were applied to split-plots depending on the experiment.
@@
 
-par(mfcol = c(2, 1))
+p_13 <- mcmc_plot(models[[1]], pars = c("WMGT", "NRTE"))
+p_13 <- p_13 +
+  annotate(geom = "text",
+           x = 1.35,
+           y = 3.5,
+           label = "a")
 
-plot_tiller_estimates_paper(models[[1]])
-mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
+p_14 <- mcmc_plot(models[[4]], pars = c("WMGT", "NRTE"))
+p_14 <- p_14 +
+  annotate(geom = "text",
+           x = 0.8,
+           y = 2.5,
+           label = "b")
 
-plot_tiller_estimates_paper(models[[4]])
-mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
-
-par(mfcol = c(1, 1))
+grid.arrange(p_13, p_14, ncol = 1, nrow = 2)
 ```
@@
 
-par(mfcol = c(2, 1))
+p_15 <- mcmc_plot(models[[2]], pars = c("WMGT", "NRTE"))
+p_15 <- p_15 +
+  annotate(geom = "text",
+           x = 4.25,
+           y = 3.5,
+           label = "a")
 
-plot_tiller_estimates_paper(models[[2]])
-mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
+p_16 <- mcmc_plot(models[[5]], pars = c("WMGT", "NRTE"))
+p_16 <- p_16 +
+  annotate(geom = "text",
+           x = 0.6,
+           y = 2.5,
+           label = "b")
 
-plot_tiller_estimates_paper(models[[5]])
-mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
-par(mfcol = c(1, 1))
+grid.arrange(p_15, p_16, ncol = 1, nrow = 2)
 ```
 
-```{r fig-7, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on leaf sheath blight severity for 2015 (a) and 2016 (b).
+```{r fig-7, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight severity for 2015 (a) and 2016 (b).
 Five different N treatments were applied to split-plots depending on the experiment.
@@
 
-par(mfcol = c(2, 1))
-plot_tiller_estimates_paper(models[[3]])
-mtext(text = "a", side = 3, line = 0, adj = 1, cex = 0.75)
+p_17 <- mcmc_plot(models[[3]], pars = c("WMGT", "NRTE"))
+p_17 <- p_17 +
+  annotate(geom = "text",
+           x = 1.3,
+           y = 3.5,
+           label = "a")
 
-plot_tiller_estimates_paper(models[[6]])
-mtext(text = "b", side = 3, line = 0, adj = 1, cex = 0.75)
+p_18 <- mcmc_plot(models[[6]], pars = c("WMGT", "NRTE"))
+p_18 <- p_18 +
+  annotate(geom = "text",
+           x = 1,
+           y = 2.5,
+           label = "b")
+
+grid.arrange(p_17, p_18, ncol = 1, nrow = 2)
 ```

### 2020-07-07 analysis/paper/paper.Rmd
Update figure code and figures
Adds mcmc_plots to paper and updates descriptions of these figures

@@
 ```{r Setup..., message=FALSE, warning=FALSE, include=FALSE}
-
 knitr::opts_chunk$set(
@@
 library("bookdown")
+library("brms")
 library("knitr")
@@
 library("rice.awd.shb")
+
+theme_set(theme_classic(base_size = 14))
 ```
@@
                   label = label)) +
-  stat_summary(fun.y = "mean",
+  stat_summary(fun = "mean",
                geom = "line",
@@
                    linetype = WMGT)) +
-  stat_summary(fun.y = "mean",
+  stat_summary(fun = "mean",
                geom = "point",
@@
        shape = "Irrigation") +
-  theme_classic(base_size = 8) +
   theme(
@@
              scales = "free_x") +
-  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
                    linetype = NRTE)) +
-  stat_summary(fun.y = "mean",
+  stat_summary(fun = "mean",
                geom = "point",
@@
        shape = "N Rate") +
-  theme_classic(base_size = 8) +
   theme(
@@
   x = c(2.5, 2.5),
-  y = c(5, 5)
+  y = c(15, 15)
 )
@@
   ylab("Tiller Incidence AUDPS") +
-  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Tiller Severity AUDPS") +
-  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
   ylab("Leaf Severity AUDPS") +
-  theme_classic(base_size = 8) +
   theme(panel.grid.major = element_blank(),
@@
   x = c(3.5, 2.5),
-  y = c(5, 5)
+  y = c(15, 15)
 )
@@
 In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).", eval=FALSE}
+In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).", eval=TRUE}
 
@@
            y = 3.5,
-           label = "a")
+           label = "a") +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.line = element_line(colour = "black"),
+    legend.position = c(x = 0.101, y = 0.74),
+    legend.key.size = unit(0, 'lines'),
+    legend.background = element_rect(
+      color = "black",
+      size = 0.5,
+      linetype = "solid"
+    ),
+    axis.title.x = element_blank(),
+    strip.background = element_blank(),
+    strip.text.x = element_text(face = "bold")
+  )
 
@@
   annotate(geom = "text",
-           x = 0.8,
+           x = 0.215,
            y = 2.5,
-           label = "b")
+           label = "b") +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.line = element_line(colour = "black"),
+    legend.position = c(x = 0.101, y = 0.74),
+    legend.key.size = unit(0, 'lines'),
+    legend.background = element_rect(
+      color = "black",
+      size = 0.5,
+      linetype = "solid"
+    ),
+    axis.title.x = element_blank(),
+    strip.background = element_blank(),
+    strip.text.x = element_text(face = "bold")
+  )
 
@@
   annotate(geom = "text",
-           x = 0.6,
+           x = 0.15,
            y = 2.5,
-           label = "b")
+           label = "b") +
+  theme(
+    panel.grid.major = element_blank(),
+    panel.grid.minor = element_blank(),
+    axis.line = element_line(colour = "black"),
+    legend.position = c(x = 0.101, y = 0.74),
+    legend.key.size = unit(0, 'lines'),
+    legend.background = element_rect(
+      color = "black",
+      size = 0.5,
+      linetype = "solid"
+    ),
+    axis.title.x = element_blank(),
+    strip.background = element_blank(),
+    strip.text.x = element_text(face = "bold")
+  )
 
@@
   annotate(geom = "text",
-           x = 1,
+           x = 0.4,
            y = 2.5,

### 2020-07-07 README.Rmd
Clean up README

@@
 
-M. Noel
+Michael Noel
 
@@
 This repository is organized as an R package.
-There are a few R functions in this package that were used to generate some of the diagnostic plots related to the analysis.
-However, for the most part I simply used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much
-about how to organise the files.
+Mostly I used the R package structure to help manage dependencies, to take advantage of continuous integration for automated code testing, and so I didn't have to think too much about how to organise the files.
 
@@
 
-    docker run -dp 8787:8787 adamhsparks/rice_AWD_ShB_analysis
+    docker run -dp 8787:8787 adamhsparks/rice-awd-shb
 
@@
 Once logged in, use the Files pane (bottom right) open the folder for this project, and open the `.Rproj` file for this project.
-Once that's open, you'll see the `analysis/paper` directory in the Files pane where you can find the R
-markdown document, and knit them to produce the results in the paper.
+Once that's open, you'll see the `analysis/paper` directory in the "Files" pane where you can find the Rmarkdown document, and knit it to produce the results in the paper.
 More information about using RStudio in Docker is available at the [Rocker](https://github.com/rocker-org)
@@
 
-I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS and Ubuntu 17.10.
+I used [RStudio](http://www.rstudio.com/products/rstudio/) on MacOS.
 See the colophon section of the docx file in `analysis/paper` for a full list of the packages that this project depends on.

### 2020-07-07 README.Rmd
standardise name across repositories

@@
 The files at the URL above will generate the results as found in the publication.
-The files hosted at <https://github.com/adamhsparks/rice_AWD_ShB_analysis> are the development versions and may have changed since the report was published.
+The files hosted at <https://github.com/adamhsparks/rice_awd_shb> are the development versions and may have changed since the report was published.
 
@@
 ```
-git clone https://github.com/adamhsparks/rice_AWD_ShB_analysis.git
+git clone https://github.com/adamhsparks/rice_awd_shb.git
 ```

### 2020-07-08 README.Rmd
Correct repository names to sync with Dockerhub

@@
 The files at the URL above will generate the results as found in the publication.
-The files hosted at <https://github.com/adamhsparks/rice_awd_shb> are the development versions and may have changed since the report was published.
+The files hosted at <https://github.com/adamhsparks/rice-awd-shb> are the development versions and may have changed since the report was published.
 
@@
 ```
-git clone https://github.com/adamhsparks/rice_awd_shb.git
+git clone https://github.com/adamhsparks/rice-awd-shb.git
 ```

### 2020-07-08 analysis/paper/paper.Rmd
Add ROPE tables to doc output

@@
 library("flextable")
+library("pander")
 library("rice.awd.shb")
+library("bayestestR")
+library("here")
 
 theme_set(theme_classic(base_size = 14))
+
+LSev15 <- readRDS(here("analysis/data/derived_data/LSev15.Rds"))
+LSev16 <- readRDS(here("analysis/data/derived_data/LSev16.Rds"))
+TInc15 <- readRDS(here("analysis/data/derived_data/TInc15.Rds"))
+TInc16 <- readRDS(here("analysis/data/derived_data/TInc16.Rds"))
+TSev15 <- readRDS(here("analysis/data/derived_data/TSev15.Rds"))
+TSev16 <- readRDS(here("analysis/data/derived_data/TSev16.Rds"))
 ```
@@
 
-Bayesian multivariate mixed models were fitted using the contributed R package `brms`, version 0.70, [@Buerkner2018; @Buerkner2017].
+Bayesian multivariate mixed models were fitted using the contributed R package `MCMCglmm`, version 2.29, [@Hadfield2010].
 Six models were created where the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
@@
 
+##### pagebreak
+
 ```{r Table-2}
-priors <- "
-Year | Fixed Effect     | distribution | mean | sd | brmsfamily  | adapt_delta | max_treedepth
-2015 | Tiller Incidence | normal       | 0    | 1  | gaussian    | 0.9999      | 15
-2015 | Tiller Severity  | normal       | 0    | 1  | skew_normal | 0.9999      | 10
-2015 | Leaf Severity    | normal       | 1    | 3  | hurdle_gamma| 0.99        | 10
-2016 | Tiller Incidence | normal       | 0    | 2  | hurdle_gamma| 0.9999      | 10
-2016 | Tiller Severity  | normal       | 0    | 1  | hurdle_gamma| 0.99        | 15
-2016 | Leaf Severity    | normal       | 0    | 2  | hurdle_gamma| 0.999       | 10
-"
+flextable(rbind(rope(TInc15),
+                rope(TSev15),
+                rope(LSev15)))
+```
 
-priors <- read.delim(
-  textConnection(priors),
-  header = FALSE,
-  sep = "|",
-  strip.white = TRUE,
-  stringsAsFactors = FALSE
-)
-names(priors) <- unname(as.list(priors[1, ])) # put headers on
-priors <- priors[-1, ] # remove first row
-row.names(priors) <- NULL
-priors <- flextable(as.data.frame(priors))
-priors <- set_caption(priors,
-                      caption =
-    "(\\#tab:Table-2) Details of models used to detect differences between irrigation methods, alternate wetting and drying (AWD) and traditional puddling, and nitrogen fertilisation rates.
-Values are for the fixed effect prior values, family, adapt_delta and max_treedepth as used in the contributed R package, brms, function brm() to fit Bayesian models."
-    )
-priors
+##### pagebreak
+
+```{r Table-3}
+flextable(rbind(rope(TInc16),
+                rope(TSev16),
+                rope(LSev16)))
 ```
@@
 
-```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight incidence for 2015 (a) and 2016 (b).
-Five different N treatments were applied to split-plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).", eval=TRUE}
-
-models <- readRDS("../data/derived_data/models.Rds")
-
-p_13 <- mcmc_plot(models[[1]], pars = c("WMGT", "NRTE"))
-p_13 <- p_13 +
-  annotate(geom = "text",
-           x = 1.35,
-           y = 3.5,
-           label = "a") +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.101, y = 0.74),
-    legend.key.size = unit(0, 'lines'),
-    legend.background = element_rect(
-      color = "black",
-      size = 0.5,
-      linetype = "solid"
-    ),
-    axis.title.x = element_blank(),
-    strip.background = element_blank(),
-    strip.text.x = element_text(face = "bold")
-  )
-
-p_14 <- mcmc_plot(models[[4]], pars = c("WMGT", "NRTE"))
-p_14 <- p_14 +
-  annotate(geom = "text",
-           x = 0.215,
-           y = 2.5,
-           label = "b") +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.101, y = 0.74),
-    legend.key.size = unit(0, 'lines'),
-    legend.background = element_rect(
-      color = "black",
-      size = 0.5,
-      linetype = "solid"
-    ),
-    axis.title.x = element_blank(),
-    strip.background = element_blank(),
-    strip.text.x = element_text(face = "bold")
-  )
-
-grid.arrange(p_13, p_14, ncol = 1, nrow = 2)
-```
-
-```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight severity for 2015 (a) and 2016 (b).
-Five different N treatments were applied to split-plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).", eval=TRUE}
-
-p_15 <- mcmc_plot(models[[2]], pars = c("WMGT", "NRTE"))
-p_15 <- p_15 +
-  annotate(geom = "text",
-           x = 4.25,
-           y = 3.5,
-           label = "a") +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.101, y = 0.74),
-    legend.key.size = unit(0, 'lines'),
-    legend.background = element_rect(
-      color = "black",
-      size = 0.5,
-      linetype = "solid"
-    ),
-    axis.title.x = element_blank(),
-    strip.background = element_blank(),
-    strip.text.x = element_text(face = "bold")
-  )
-
-p_16 <- mcmc_plot(models[[5]], pars = c("WMGT", "NRTE"))
-p_16 <- p_16 +
-  annotate(geom = "text",
-           x = 0.15,
-           y = 2.5,
-           label = "b") +
-  theme(
-    panel.grid.major = element_blank(),
-    panel.grid.minor = element_blank(),
-    axis.line = element_line(colour = "black"),
-    legend.position = c(x = 0.101, y = 0.74),
-    legend.key.size = unit(0, 'lines'),
-    legend.background = element_rect(
-      color = "black",
-      size = 0.5,
-      linetype = "solid"
-    ),
-    axis.title.x = element_blank(),
-    strip.background = element_blank(),
-    strip.text.x = element_text(face = "bold")
-  )
-
-grid.arrange(p_15, p_16, ncol = 1, nrow = 2)
-```
-
-```{r fig-7, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on tiller sheath blight severity for 2015 (a) and 2016 (b).
-Five different N treatments were applied to split-plots depending on the experiment.
-In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
-In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).", eval=TRUE}
-
-p_17 <- mcmc_plot(models[[3]], pars = c("WMGT", "NRTE"))
-p_17 <- p_17 +
-  annotate(geom = "text",
-           x = 1.3,
-           y = 3.5,
-           label = "a")
-
-p_18 <- mcmc_plot(models[[6]], pars = c("WMGT", "NRTE"))
-p_18 <- p_18 +
-  annotate(geom = "text",
-           x = 0.4,
-           y = 2.5,
-           label = "b")
-
-grid.arrange(p_17, p_18, ncol = 1, nrow = 2)
-```
-
 \newpage

### 2020-07-08 analysis/paper/paper.Rmd
Remove brms from library calls

@@
 library("bookdown")
-library("brms")
 library("knitr")

### 2020-07-09 analysis/paper/paper.Rmd
add rstanarm to paper library loading

@@
 library("bayestestR")
+library("rstanarm")
 library("here")
@@
 Bayesian multivariate mixed models were fitted using the contributed R package `MCMCglmm`, version 2.29, [@Hadfield2010].
-Six models were created where the dependent variables were 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
-The independent variables were the irrigation management and N rate with replicate treated as a random variable.
-The base levels (control treatments) for the analyses for 2015 were: N rate -- N0, irrigation management -- puddled and for 2016 they were: N rate -- N60, irrigation management -- puddled.
+Six models were created where the dependent variables were: 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
+The independent variables were the irrigation management (WMGT) and N rate (NRTE) and the interaction of WMGT and NRTE with replicate treated as a random variable.
+The base levels (control treatments) for the analyses for 2015 were: N rate -- N0, irrigation management -- puddled.
+For for 2016 the base level values were: N rate -- N60, irrigation management -- puddled.
 
-Weakly informative priors and families were set for the fixed effects in each model while the random effects and intercept were selected automatically (Tab.&nbsp;\@ref(tab:Table-2)).
-Four chains were run with a warmup of 5000 and 8000 iterations.
-Model fit was evaluated visually using `pp_check()` and `describe_posterior()`.
-Further fitness was evaluated using the `describe_posterior()` function from bayestestR, version 0.70, [@Makowski2019].
+The same weakly informative priors were set for the fixed and random effects in all models, $V = 1$, $nu = 0.02$.
+Models were run for 60,000 iterations with every ten being selected.
+Model fit was evaluated using `plot.MCMCglmm()` and `summary.MCMCglmm()`.
 
@@
 Water management was not clearly different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the effects of N treatments N100 and N120 on tiller incidence caused both to be higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-5)a, \@ref(fig:fig-5)a).
+However, the effect of the N treatments N120 on tiller incidence was higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-5)a, \@ref(fig:fig-5)a).
 
@@
 As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
+The AWD water management was clearly lower than the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
 
-The interaction of irrigation treatment AWD with N rate N0 in 2015 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity.
-For leaf severity the interaction of irrigation and N management was not clearly different from the control puddled irrigation and N60 nitrogen rate.
+The interaction of irrigation treatment and nitrogen fertilisation was not clearly different for any of the three response variables analysed.
 

### 2020-07-09 analysis/paper/paper.Rmd
Add tables and captions for test for equivalence for 2015 and 2016

@@
   Water and nitrogen management play vital roles in rice production.
-However, the mismanagement of these two crop inputs may trigger the development of sheath blight of rice, caused by _Thanatephorus cucumeris_ (strain AG1-IA), which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
+However, the mismanagement of these two crop inputs may trigger the development of sheath blight of rice, caused by *Thanatephorus cucumeris* (strain AG1-IA), which is favored by wet conditions, high relative humidity, and high nitrogen fertilizer levels.
 To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water-saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
@@
 library("flextable")
-library("pander")
 library("rice.awd.shb")
 library("bayestestR")
-library("rstanarm")
 library("here")
@@
     "Panicle Initiation")
-N_rates <- flextable(as.data.frame(N_rates))
-
-N_rates <-
-  set_caption (N_rates,
+x <- flextable(as.data.frame(N_rates))
+x <- fontsize(x, part = "header", size = 10)
+x <- font(x, part = "header", fontname = "Times")
+x <- font(x, fontname = "Times")
+x <- fontsize(x, size = 10)
+x <-
+  set_caption (x,
                caption = 
-    "(\\#tab:Table-1) Nitrogen application rates for 2015 and 2016 in kilograms per hectare.
+    "(\\#tab:Table-1) Nitrogen application rates for 2015 and 2016 experiments in kilograms per hectare.
 Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg/ha N (N100) and 180&nbsp;kg/ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg/ha N (N60) and 180&nbsp;kg/ha N (N180).
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg/ha N (N100) and 180 kg/ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg/ha N (N60) and 180 kg/ha N (N180).
 Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications."
     )
-
-N_rates
+x
 ```
@@
 ```{r Table-2}
-flextable(rbind(rope(TInc15),
-                rope(TSev15),
-                rope(LSev15)))
+x <- rbind(
+  equivalence_test(TInc15, range = c(-0.1, 0.1)),
+  equivalence_test(TSev15, range = c(-0.1, 0.1)),
+  equivalence_test(LSev15, range = c(-0.1, 0.1))
+)
+
+x$ROPE_Percentage <- round(x$ROPE_Percentage * 100, 2)
+
+x <-
+  cbind(
+    "Response" = rep(c("T. Inc.", "T. Sev.", "L. Sev."),
+                     each = 4),
+    subset(x, select = -c(CI, Effects, Cleaned_Parameter)))
+
+names(x) <- gsub("_", " ", names(x))
+
+x <- flextable(x)
+x <- fontsize(x, part = "header", size = 10)
+x <- font(x, part = "header", fontname = "Times")
+x <- font(x, fontname = "Times")
+x <- fontsize(x, size = 10)
+x <- set_caption(x, 
+  "(\\#tab:Table 2) An 89 % test for practical equivalence for 2015 experiment.
+Response variables are shown as T.
+Inc., Tiller Incidence; T.
+Sev., Tiller Severity; L.
+Sev., Leaf Severity.
+The parameters are WMGTAWD, irrigation treatment AWD; NRTEN100, nitrogen rate of 100 k/ha; NRTEN120 kg/ha.
+ROPE low and ROPE high provide the limits of the Region of Practical Equivalence (ROPE).
+ROPE Percentage is the proportion of the Highest Density Interval (HDI) that lies inside the ROPE.
+All points within this interval have a higher probability of density than points outside the interval.
+ROPE Equivalence is the test result, either \"rejected\", \"accepted\" or \"undecided\".
+\"HDI Low\" and \"HDI High\" are the lower and upper HDI limits for the parameters."
+  )
+x
 ```
@@
 ```{r Table-3}
-flextable(rbind(rope(TInc16),
-                rope(TSev16),
-                rope(LSev16)))
+x <- rbind(equivalence_test(TInc16),
+           equivalence_test(TSev16),
+           equivalence_test(LSev16))
+
+x$ROPE_Percentage <- round(x$ROPE_Percentage * 100, 2)
+
+x <-
+  cbind(
+    "Response" = rep(
+      c("T. Inc.", "T. Sev.", "L. Sev."),
+                     each = 3),
+    subset(x, select = -c(CI, Effects, Cleaned_Parameter)))
+
+names(x) <- gsub("_", " ", names(x))
+
+x <- flextable(x)
+x <- fontsize(x, part = "header", size = 10)
+x <- font(x, part = "header", fontname = "Times")
+x <- font(x, fontname = "Times")
+x <- fontsize(x, size = 10)
+x <- set_caption(x, 
+  "(\\#tab:Table 2) An 89 % test for practical equivalence for 2015 experiment.
+Response variables are shown as T.
+Inc., Tiller Incidence; T.
+Sev., Tiller Severity; L.
+Sev., Leaf Severity.
+The parameters are WMGTAWD, irrigation treatment AWD; and NRTEN180, nitrogen rate of 180 k/ha.
+ROPE low and ROPE high provide the limits of the Region of Practical Equivalence (ROPE).
+ROPE Percentage is the proportion of the Highest Density Interval (HDI) that lies inside the ROPE.
+All points within this interval have a higher probability of density than points outside the interval.
+ROPE Equivalence is the test result, either \"rejected\", \"accepted\" or \"undecided\".
+\"HDI Low\" and \"HDI High\" are the lower and upper HDI limits for the parameters.")
+x
 ```

### 2020-07-09 analysis/paper/paper.Rmd
Flesh out stats methods and results, update figure files

@@
 
-theme_set(theme_classic(base_size = 14))
+theme_set(theme_classic(base_size = 8))
 
@@
 
-Bayesian multivariate mixed models were fitted using the contributed R package `MCMCglmm`, version 2.29, [@Hadfield2010].
+The contributed R package, rstanarm (version 2.19.3), [@Brilleman2018; @Goodrich2020], was used to fit Bayesian generalized linear models with water management and nitrogen fertilisation as fixed effects and replicate as a random effect.
 Six models were created where the dependent variables were: 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
@@
 For for 2016 the base level values were: N rate -- N60, irrigation management -- puddled.
+The same weakly informative priors were set for the fixed and random effects in all models, location = 0, scale = 10.
+Model fitness was evaluated using `mcmc_trace()` and `pp_check()` from bayesplot, version 1.7.2, [@Gabry2019] as well as summary information.
 
-The same weakly informative priors were set for the fixed and random effects in all models, $V = 1$, $nu = 0.02$.
-Models were run for 60,000 iterations with every ten being selected.
-Model fit was evaluated using `plot.MCMCglmm()` and `summary.MCMCglmm()`.
+The resulting models were tested using a test for equivalency using `equivalence_test()` from bayestestR, version 0.7.0, [@Makowski2019] to evaluate whether differences between the sheath blight responses varied between the water and nitrogen management treatments (Tab.&nbsp;\@ref(tab:Table-2), Tab.&nbsp;(tab:Table-3)).
+The Test for Practical Equivalence is based on the Highest Density Interval (HDI) plus the Region of Practical Equivalence (ROPE) decision rule, *HDI+ROPE decision rule* and checks whether parameter values should be accepted or rejected against the null hypothesis, the ROPE [@Kruschke2018].
+To do this, it checks the percentage of the 89&nbsp;% HDI that is in the null region ROPE.
+If this amount is sufficiently low, the null hypothesis is rejected.
+If the amount is large enough, the null hypothesis is accepted.
+
+## Hypothesis {-}
+
+We hypothesised that higher amounts of nitrogen would increase the incidence and severity of sheath blight, while alternate wetting and drying would decrease the disease incidence and severity.
 
@@
 In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.&nbsp;\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
-Water management was not clearly different (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a).
-However, the effect of the N treatments N120 on tiller incidence was higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-5)a, \@ref(fig:fig-5)a).
+Water management was undecided in the test for equivalency (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a) between the AWD and puddled treatments.
+However, the effect of the N treatments of both N100 and N120 on tiller incidence were higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-5)a, \@ref(fig:fig-5)a).
 
 Tiller sheath blight severity remained below 2&nbsp;\% (Fig.&nbsp;\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
-Both the N100 and N120 treatment effects caused the tiller severity to be higher and clearly statistically different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not clearly statistically different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-6)a).
+Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
+However, the AWD water management was not clearly the same or different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-6)a).
 
 The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly statistically different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-The AWD water management was clearly lower than the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
-
-The interaction of irrigation treatment and nitrogen fertilisation was not clearly different for any of the three response variables analysed.
+As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
+The AWD water management treatment was again undecided (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
 
@@
 The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Fig.&nbsp;\@ref(fig:fig-2)b).
-The N treatment N180 value was higher and clearly statistically different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
-As in the 2015 study, water management did not clearly statistically differ (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
+The N treatment N180 value was higher and clearly different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
+As in the 2015 study, water management treatment was undecided (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
 
 As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
-In 2016 the N180 treatment was again higher and clearly statistically different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the puddled treatment, was also clearly statistically different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-6)b).
+In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
+The AWD water management, which was lower than the puddled treatment, was also clearly different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-6)b).
 
-In 2016 the neither of the treatments, N rate or water management, were clearly statistically different from the control treatments, N60 and puddling water management, for leaf sheath blight severity (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)b, \@ref(fig:fig-4)b, \@ref(fig:fig-7)b).
-
-The interaction of irrigation treatment AWD with N rate of N180 in 2016 was not clearly different from the control puddled irrigation and N60 for tiller incidence or severity in either experiment.
-In the 2016 experiment, the interactions were not clearly different for leaf severity from the control puddled irrigation and N60.
-In 2016 the interaction of N180 and AWD was clearly lower than the control puddled irrigation and N60 rate.
+In 2016 the higher N rate, N180, were clearly different, higher, than the control treatments, N60.
+However the water management treatment was undecided (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)b, \@ref(fig:fig-4)b, \@ref(fig:fig-7)b).
 
@@
 x <- set_caption(x, 
-  "(\\#tab:Table 2) An 89 % test for practical equivalence for 2015 experiment.
+  "(\\#tab:Table-2) An 89 % test for practical equivalence for 2015 experiment.
 Response variables are shown as T.
@@
 x <- set_caption(x, 
-  "(\\#tab:Table 2) An 89 % test for practical equivalence for 2015 experiment.
+  "(\\#tab:Table-3) An 89 % test for practical equivalence for 2015 experiment.
 Response variables are shown as T.

### 2020-07-10 analysis/paper/paper.Rmd
Update paper with references to tables and figures

@@
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Tab.&nbsp;\@ref(tab:Table-1)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Table&nbsp;\@ref(tab:Table-1)).
 
@@
 
-split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg/ha as urea split into two applications) and N180 (180&nbsp;kg/ha in three splits) being applied (Tab.&nbsp;\@ref(tab:Table-1)).
+split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg/ha as urea split into two applications) and N180 (180&nbsp;kg/ha in three splits) being applied (Table&nbsp;\@ref(tab:Table-1)).
 
@@
 A leaf was considered living if at least 50&nbsp;% of its area was not brown or dark brown due to natural senescence.
-A leaf that was yellow-green or light green due to a disease, such as tungro or nitrogen deficiency was still considered a living leaf.
+A leaf that was yellow-green or light green due to a disease, such as tungro or N deficiency was still considered a living leaf.
 The same rating methodology was used in both experiments.
@@
 
-The area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R, version 4.0.0 [@R2020], package `agricolae`, version 1.3-3, [@agricolae2020].
+The area under the disease progress stairs (AUDPS) [@simko2012area] was calculated for both disease incidence and severity using R (version 4.0.0), [@R2020], package `agricolae`, (version 1.3-3), [@agricolae2020].
 
-The contributed R package, rstanarm (version 2.19.3), [@Brilleman2018; @Goodrich2020], was used to fit Bayesian generalized linear models with water management and nitrogen fertilisation as fixed effects and replicate as a random effect.
+The contributed R package, rstanarm (version 2.19.3), [@Brilleman2018; @Goodrich2020], was used to fit Bayesian generalized linear models with water management and N fertilisation as fixed effects and replicate as a random effect.
 Six models were created where the dependent variables were: 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
@@
 The same weakly informative priors were set for the fixed and random effects in all models, location = 0, scale = 10.
-Model fitness was evaluated using `mcmc_trace()` and `pp_check()` from bayesplot, version 1.7.2, [@Gabry2019] as well as summary information.
+Model fitness was evaluated using `mcmc_trace()` and `pp_check()` from the contributed package, bayesplot (version 1.7.2), [@Gabry2019] as well as summary information.
 
-The resulting models were tested using a test for equivalency using `equivalence_test()` from bayestestR, version 0.7.0, [@Makowski2019] to evaluate whether differences between the sheath blight responses varied between the water and nitrogen management treatments (Tab.&nbsp;\@ref(tab:Table-2), Tab.&nbsp;(tab:Table-3)).
-The Test for Practical Equivalence is based on the Highest Density Interval (HDI) plus the Region of Practical Equivalence (ROPE) decision rule, *HDI+ROPE decision rule* and checks whether parameter values should be accepted or rejected against the null hypothesis, the ROPE [@Kruschke2018].
+The resulting models were tested using a test for equivalency using `equivalence_test()` from the contributed package, bayestestR (version 0.7.0), [@Makowski2019] to evaluate whether differences between the sheath blight responses varied between the water and N management treatments.
+The "Test for Practical Equivalence" is based on the Highest Density Interval (HDI) plus the Region of Practical Equivalence (ROPE) decision rule [@Kruschke2014; @Kruschke2018], *HDI+ROPE decision rule* and checks whether parameter values should be accepted or rejected against the null hypothesis, the ROPE.
 To do this, it checks the percentage of the 89&nbsp;% HDI that is in the null region ROPE.
@@
 
-In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Fig.&nbsp;\@ref(fig:fig-1)a, \@ref(fig:fig-2)a).
-Water management was undecided in the test for equivalency (Fig.&nbsp;\@ref(fig:fig-3)a, \@ref(fig:fig-5)a) between the AWD and puddled treatments.
-However, the effect of the N treatments of both N100 and N120 on tiller incidence were higher and clearly different when compared with the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-5)a, \@ref(fig:fig-5)a).
+In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Figure&nbsp;\@ref(fig:fig-1)a; Table&nbsp;\@ref(tab:Table-2)).
+Water management was undecided in the test for equivalency (Figure&nbsp;\@ref(fig:fig-3)a; Table&nbsp;\@ref(tab:Table-2)) between the AWD and puddled treatments.
+However, the effect of the N treatments of both N100 and N120 on tiller incidence were higher and clearly different when compared with the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)a, \@ref(tab:Table-2)).
 
-Tiller sheath blight severity remained below 2&nbsp;\% (Fig.&nbsp;\@ref(fig:fig-2)c, \@ref(fig:fig-1)c).
-Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)c, \@ref(fig:fig-5)c).
-However, the AWD water management was not clearly the same or different from the puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)c, \@ref(fig:fig-6)a).
+Tiller sheath blight severity remained below 2&nbsp;\% (Figure&nbsp;\@ref(fig:fig-1)c, \@ref(fig:fig-2)c).
+Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)c; Table&nbsp;\@ref(tab:Table-2)).
+However, the AWD water management was not clearly the same or different from the puddled treatment (Figure&nbsp;\@ref(fig:fig-3)c; Table&nbsp;\@ref(tab:Table-2)).
 
-The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Fig.&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly different than the N0 treatment (Fig.&nbsp;\@ref(fig:fig-4)e, \@ref(fig:fig-5)e).
-The AWD water management treatment was again undecided (Fig.&nbsp;\@ref(fig:fig-3)e, \@ref(fig:fig-7)a).
+The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Figure&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
+As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
+The AWD water management treatment was again undecided (Figure&nbsp;\@ref(fig:fig-3)e; Table&nbsp;\@ref(tab:Table-2)).
 
@@
 
-The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Fig.&nbsp;\@ref(fig:fig-2)b).
-The N treatment N180 value was higher and clearly different than the control N60 treatment (Fig.&nbsp;\@ref(fig:fig-4)b, \@ref(fig:fig-5)b).
-As in the 2015 study, water management treatment was undecided (Fig.&nbsp;\@ref(fig:fig-3)b, \@ref(fig:fig-5)b).
+The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Figure&nbsp;\@ref(fig:fig-2)b).
+The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure&nbsp;\@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-3).
+As in the 2015 study, water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Fig.&nbsp;\@ref(fig:fig-2)d).
-In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Fig.&nbsp;\@ref(fig:fig-4)d, \@ref(fig:fig-5)d).
-The AWD water management, which was lower than the puddled treatment, was also clearly different (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-6)b).
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Figure&nbsp;\@ref(fig:fig-2)d).
+In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Figure&nbsp;\@ref(fig:fig-4)d; Table&nbsp;\@ref(tab:Table-3)).
+The AWD water management, which was lower than the puddled treatment, was also clearly different (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
 
 In 2016 the higher N rate, N180, were clearly different, higher, than the control treatments, N60.
-However the water management treatment was undecided (Fig.&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-5)b, \@ref(fig:fig-4)b, \@ref(fig:fig-7)b).
+However the water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-2)).
 
@@
 
-In both experiments, we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology.
+In both experiments, we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology, or decreases that would favour it except in one case.
 In only one instance were we able to detect any statistically clear effect of AWD alone on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Fig.&nbsp;\@ref(fig:fig-3)d, \@ref(fig:fig-5)d), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
+In all other cases the difference was unclear.
 
@@
 By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment appear to have improved the experiment.
-The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Fig.&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
+The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
 Based on these results, it is suggested that the methods used in the 2016 experiment should be adopted in any further studies of this kind.
@@
 Therefore, it is likely to remain an important disease in the near future with little resistance available in current varieties.
-However, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease.
+Given the results of the N treatments showing clear effects, in most cases increasing the amount and severity of disease, we would argue that this suggests that there is no reason AWD could not be adopted.
+Therefore, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease and should be adopted given the other benefits that it provides.
 
@@
 x <- font(x, fontname = "Times")
-x <- fontsize(x, size = 10)
+x <- fontsize(x, size = 12)
+x <- autofit(x)
 x <- set_caption(x, 

### 2020-07-10 analysis/paper/paper.Rmd
Add acknowledgements for Nick
Grammar corrections and other edits for flow

@@
 Frank) Donk.
-anastomosis group 1 IA, of rice is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
+anastomosis group 1 IA, of rice, is an economically important disease worldwide throughout tropical and temperate production areas.
+Under conducive conditions, the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
 Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10&nbsp;\% annually.
@@
 Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E).
-The climate is classified as humid-tropical with wet season starting in early June to December and dry season between December and late May.
+The climate is classified as humid-tropical with the wet season starting in early June to December and dry season between December and late May.
 The experiments were both established in the dry seasons of 2015 and 2016.
@@
 
-NSIC Rc222 an inbred semi-dwarf, high-yielding variety released by the Philippine Rice Research Institute (PhilRice), with a 114 day maturity when transplanted was used in both experiments.
+NSIC Rc222, an inbred semi-dwarf high-yielding variety, released by the Philippine Rice Research Institute (PhilRice), with a 114-day maturity when transplanted was used in both experiments.
 The variety is commonly grown by farmers in the area, having good yields and moderate resistance to brown plant hopper, green leaf hopper and yellow stem borer, but susceptibility to tungro and no known resistance to sheath blight.
@@
 In both experiments, two sample areas, sized 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m, per plot were assessed.
-The total number of tillers per hill and number of tillers with sheath blight (incidence) were measured for nine hills per sample area.
+The total number of tillers per hill and number of tillers with sheath blight (incidence) was measured for nine hills per sample area.
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
@@
 In both experiments, we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology, or decreases that would favour it except in one case.
-In only one instance were we able to detect any statistically clear effect of AWD alone on sheath blight.
-In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
-In all other cases the difference was unclear.
+In the 2016, experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
+In all other cases, the difference was unclear.
 
 The findings of the effects of N rates on sheath blight were as expected in both experiments.
-Higher rates of N caused an increase in disease incidence and severity in 2015 and in tiller incidence in 2016.
-However, in the 2016 experiment, there were no clear differences due to the N rate tiller and leaf severity.
+Higher rates of N caused an increase in disease incidence and severity in all of the cases examined.
 
-The combination of the irrigation and N rates did not appear to increase the disease severity or incidence in either experiment.
-In 2015 there were no clear differences in the interaction of irrigation and N rate between any of the three treatments.
-However, in the 2016 experiment, the combination of AWD--N180 was clearly different, being lower, than the PDL--N60 combination treatment.
-
-By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment appear to have improved the experiment.
+By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment improved the experiment.
 The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
@@
 However, it should be noted that normally it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
-However, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.
+Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.
 
@@
 Climate change is predicted to decrease sheath blight risk over the longer term [@Kim2015].
-However, over the next 10 to 20 years the risk is predicted to remain the same as from 2000 to 2010 [@Kim2015].
-Therefore, it is likely to remain an important disease in the near future with little resistance available in current varieties.
-Given the results of the N treatments showing clear effects, in most cases increasing the amount and severity of disease, we would argue that this suggests that there is no reason AWD could not be adopted.
+However, over the next 10 to 20 years the risk is predicted to remain the same as from 2000 to 2010 in research that has been conducted on the matter to date [@Kim2015].
+Therefore, it is likely to remain an important disease into the near future with little resistance available in currently available varieties.
+Given the results of the N treatments showing clear effects, in most cases increasing the amount and severity of the disease, we would argue that this suggests that there is no reason AWD could not be adopted as we were unable to detect any clear differences due to irrigation management in most of the cases.
 Therefore, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease and should be adopted given the other benefits that it provides.
@@
 Burrell of the University of Southern Queensland Statistical Consulting Unit for their insightful comments on the analysis of this paper.
+Also thanks to Dr.
+N.
+Tierney of Monash University for the discussion and ideas on the analysis.
 
@@
 
-AHS and BOS conceived the topic. AHS and NPC conceived the research. NPC conducted the fieldwork in 2016. AHS conducted the data analysis. All the authors contributed to the writing of the manuscript.
+AHS and BOS conceived the topic.
+AHS and NPC conceived the research.
+NPC assisted in the field work in 2015 and conducted the field work in 2016.
+AHS conducted the data analysis.
+All the authors contributed to the writing of the manuscript.
 

### 2020-07-13 analysis/paper/paper.Rmd
Update paper title
Update descriptions of models in vignettes and paper

@@
 ---
-title: "Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?"
+title: "Effects of Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates on Sheath Blight of Rice"
 author:
@@
 
-The contributed R package, rstanarm (version 2.19.3), [@Brilleman2018; @Goodrich2020], was used to fit Bayesian generalized linear models with water management and N fertilisation as fixed effects and replicate as a random effect.
+The contributed R package, rstanarm (version 2.19.3), [@Brilleman2018; @Goodrich2020], was used to fit Bayesian generalized linear models with water management and N fertilisation as fixed effects and replicate with main plot nested within replicate as random effects.
 Six models were created where the dependent variables were: 2015 tiller sheath blight incidence, 2015 tiller sheath blight severity, 2015 leaf sheath blight severity; 2016 tiller sheath blight incidence, 2016 tiller sheath blight severity; 2016 leaf sheath blight severity, respectively.
@@
 Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)c; Table&nbsp;\@ref(tab:Table-2)).
-However, the AWD water management was not clearly the same or different from the puddled treatment (Figure&nbsp;\@ref(fig:fig-3)c; Table&nbsp;\@ref(tab:Table-2)).
+However, the AWD water management was undecided whether it was different than the puddled treatment (Figure&nbsp;\@ref(fig:fig-3)c; Table&nbsp;\@ref(tab:Table-2)).
 
@@
 In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Figure&nbsp;\@ref(fig:fig-4)d; Table&nbsp;\@ref(tab:Table-3)).
-The AWD water management, which was lower than the puddled treatment, was also clearly different (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
+The AWD water management, which was lower than the puddled treatment, was undecided (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
 
@@
 The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
-Based on these results, it is suggested that the methods used in the 2016 experiment should be adopted in any further studies of this kind.
+The use of differing levels of N did provide information about the effects of N on the disease, but it reduced the power to find the effects of the irrigation.
+Using a high rate of N, _e.g._ 180&nbsp;k/ha, for the entire study would help ensure that enough disease occurs to be able to detect differences in the irrigation treatments.
+We would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the data.
 

### 2020-07-30 README.Rmd
Back to MCMCglmm we go
Update README
Paper is knitted to MS Word, not PDF
fix code formatting in README
another code formatting change in README
Update instructions for using Docker

@@
 
-- the manuscript as submitted (in PDF format) and it's Rmd source file
+- the manuscript as submitted (in MS Word format) and it's Rmd source file
 
@@
 To launch the Docker image for this project, first, [install Docker](https://docs.docker.com/installation/) on your computer.
-At the Docker prompt, enter:
+Then at a command line prompt, use the following commands to start the instance.
 
-    docker run -dp 8787:8787 adamhsparks/rice-awd-shb
+```bash
+docker pull adamhsparks/rice-awd-shb:main
+docker run -dp 8787:8787 rice-awd-shb
+```
 
 This will start a server instance of RStudio.
-Then open your web browser at localhost:8787 or or run `docker-machine ip default` in the shell to find the
-correct IP address, and log in with rstudio/rstudio.
+Then open your web browser at localhost:8787 or or run `docker-machine ip default` in the shell to find the correct IP address, and log in with rstudio/rstudio.
 

### 2020-08-11 analysis/paper/paper.Rmd
Address Ole's first comment in abstract
Clarify what was lower and higher and where no differences were detectable
replace spaces before %

@@
 We were unable to detect any clear differences in the incidence or severity of tiller sheath blight due to irrigation treatment.
-Leaf severity for the AWD treatment was clearly lower in the 2015 trial but higher in 2016.
+Leaf severity for the AWD treatment was clearly lower than traditional puddling in the 2015 trial but we were unable to detect any clear differences in 2016.
 However, the level of disease severity remained low in both years, < 1&nbsp;%.
@@
 anastomosis group 1 IA, of rice, is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions, the disease can cause up to 50&nbsp;\% yield losses [@Marchetti1991].
-Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10&nbsp;\% annually.
+Under conducive conditions, the disease can cause up to 50\% yield losses [@Marchetti1991].
+Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10\% annually.
 The disease is best managed through an integrated disease management approach, which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 to 40&nbsp;\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 to 40\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
@@
 Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress.
-As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50 &nbsp;\% [@Yan2005; @Sander2015].
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50 \% [@Yan2005; @Sander2015].
 
@@
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where (i) 0 -- no disease; (ii) 1 -- trace to 1&nbsp;\% severity; (iii) 2 -- 1 to 5&nbsp;\% severity; (iv) 3 -- 5 to 15&nbsp;\% severity; (v) 4 -- 15 to 50&nbsp;\% severity; and (vi) 5 -- 50 to 100&nbsp;\% severity.
+The scale is an unequally spaced categorical scale where (i) 0 -- no disease; (ii) 1 -- trace to 1\% severity; (iii) 2 -- 1 to 5\% severity; (iv) 3 -- 5 to 15\% severity; (v) 4 -- 15 to 50\% severity; and (vi) 5 -- 50 to 100\% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
@@
 
-Tiller sheath blight severity remained below 2&nbsp;\% (Figure&nbsp;\@ref(fig:fig-1)c, \@ref(fig:fig-2)c).
+Tiller sheath blight severity remained below 2\% (Figure&nbsp;\@ref(fig:fig-1)c, \@ref(fig:fig-2)c).
 Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)c; Table&nbsp;\@ref(tab:Table-2)).
@@
 
-It should be noted that the levels of leaf severity remained low (<&nbsp;1&nbsp;\%) throughout the growing season in all treatments for both years.
+It should be noted that the levels of leaf severity remained low (<&nbsp;1\%) throughout the growing season in all treatments for both years.
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.

### 2020-08-11 analysis/paper/paper.Rmd
Delete a stray "and"

@@
 The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Figure&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were and clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
+As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
 The AWD water management treatment was again undecided (Figure&nbsp;\@ref(fig:fig-3)e; Table&nbsp;\@ref(tab:Table-2)).

### 2020-08-11 analysis/paper/paper.Rmd
Delete "normally"

@@
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
-However, it should be noted that normally it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
+However, it should be noted that it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
 Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.

### 2020-08-11 analysis/paper/paper.Rmd
Incorporate Ole's suggested edits and clarify statistical results text

@@
 The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Figure&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values and were clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
+As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values that were clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
 The AWD water management treatment was again undecided (Figure&nbsp;\@ref(fig:fig-3)e; Table&nbsp;\@ref(tab:Table-2)).
@@
 The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure&nbsp;\@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-3).
-As in the 2015 study, water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
+As in the 2015 study, water management treatment was undecided with no clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
 
@@
 In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Figure&nbsp;\@ref(fig:fig-4)d; Table&nbsp;\@ref(tab:Table-3)).
-The AWD water management, which was lower than the puddled treatment, was undecided (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
+The AWD water management did not show statistically clear differences from the puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
 
@@
 In both experiments, we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology, or decreases that would favour it except in one case.
-In the 2016, experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
-In all other cases, the difference was unclear.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
+In all other cases, no significant differences were observed.
 
@@
 
-By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment improved the experiment.
+By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment improved the experiment by decreasing the variability in the results leading to more clear differences in the observations.
 The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
-The use of differing levels of N did provide information about the effects of N on the disease, but it reduced the power to find the effects of the irrigation.
+The use of different levels of N did provide information about the effects of N on the disease, but it reduced the statistical power to find the effects of the irrigation.
 Using a high rate of N, _e.g._ 180&nbsp;k/ha, for the entire study would help ensure that enough disease occurs to be able to detect differences in the irrigation treatments.
@@
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
-However, it should be noted that it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy in the wet season.
-Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy reducing the moisture for the fungus to infect and disperse the infective propagules.
+However, it should be noted that often it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season.
+Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy field reducing the moisture for the fungus to infect and disperse the infective propagules.
 
@@
 Therefore, as manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due to changes in establishment practices.
-A combination of AWD and direct-seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.
+A combination of AWD and direct-seeded rice could be beneficial in multiple ways, for saving water, reducing GHG emissions and reducing the risk of sheath blight.
 
@@
 Recently, Lorica *et al.* [-@Lorica2020] have also found that AWD did not affect rodent damage in crops.
-The findings our research along with those of Lorica *et al.* [-@Lorica2020] highlight the need for cross-disciplinary research that examines what the effects of new technologies that are being developed to adapt to and mitigate climate change on the pests and diseases that occur in rice.
-Ultimately these findings are useful as IRRI promotes AWD as water-saving technologies because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
+The findings of our research along with those of Lorica *et al.* [-@Lorica2020] highlight the need for cross-disciplinary research that examines what the effects of new technologies that are being developed to adapt to and mitigate climate change on the pests and diseases that occur in rice.
+Ultimately these findings are useful as many countries promote AWD as water-saving technologies because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
 
 Climate change is predicted to decrease sheath blight risk over the longer term [@Kim2015].
-However, over the next 10 to 20 years the risk is predicted to remain the same as from 2000 to 2010 in research that has been conducted on the matter to date [@Kim2015].
-Therefore, it is likely to remain an important disease into the near future with little resistance available in currently available varieties.
+However, over the next 10 to 20 years the risk is predicted to remain the same as during the period from 2000 to 2010 in research that has been conducted on the matter to date [@Kim2015].
+Therefore, it is likely to remain an important disease for the near future with little resistance available in currently available varieties.
 Given the results of the N treatments showing clear effects, in most cases increasing the amount and severity of the disease, we would argue that this suggests that there is no reason AWD could not be adopted as we were unable to detect any clear differences due to irrigation management in most of the cases.

### 2020-08-11 analysis/paper/paper.Rmd
Cite Ole's references in-text

@@
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
-However, it should be noted that often it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season.
+However, it should be noted that often it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season [@Sriphirom2019; @Sander2017; @Sander2020].
 Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy field reducing the moisture for the fungus to infect and disperse the infective propagules.

### 2020-08-11 analysis/paper/paper.Rmd
Another edit from Ole that I missed

@@
 The findings of our research along with those of Lorica *et al.* [-@Lorica2020] highlight the need for cross-disciplinary research that examines what the effects of new technologies that are being developed to adapt to and mitigate climate change on the pests and diseases that occur in rice.
-Ultimately these findings are useful as many countries promote AWD as water-saving technologies because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
+Ultimately these findings are useful as many countries promote AWD as water-saving technology because farmers can be assured that the changes will not increase the risks from these pests and pathogens.
 

### 2020-08-11 analysis/paper/paper.Rmd
Edits for clarity based on Ole's comments and add conclusion section

@@
 
+The interaction of N100 and N120 with the water management treatment were undecided.
+
 ## 2016 Experiment {-}
@@
 The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure&nbsp;\@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-3).
-As in the 2015 study, water management treatment was undecided with no clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
+As in the 2015 study, water management treatment and the interaction of N rate and water management were undecided with no clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
 
@@
 However the water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-2)).
+
+However, the interaction of the water management and N rate, AWD and N180 were clearly different and lower than traditional puddling and N60.
 
@@
 
-By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment improved the experiment by decreasing the variability in the results leading to more clear differences in the observations.
+By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment improved the experiment by decreasing the variability in the data collected.
 The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
-The use of different levels of N did provide information about the effects of N on the disease, but it reduced the statistical power to find the effects of the irrigation.
-Using a high rate of N, _e.g._ 180&nbsp;k/ha, for the entire study would help ensure that enough disease occurs to be able to detect differences in the irrigation treatments.
+
+While the use of different levels of N did provide information about the effects of N on the disease, it reduced the statistical power to find the effects of the irrigation [@Bradley1998].
+Using a high rate of N, _e.g._ 180&nbsp;k/ha, for the entire study would help ensure that enough disease occurs to be able to detect differences in the irrigation treatments with a more simple trial statistical design.
+
 We would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the data.
@@
 However, it should be noted that often it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season [@Sriphirom2019; @Sander2017; @Sander2020].
-Still, sheath blight remains an issue in both seasons and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of reduced water in the paddy field reducing the moisture for the fungus to infect and disperse the infective propagules.
+Still, sheath blight remains an issue in both seasons [@Savary2001] and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of less water in the paddy field than in traditional systems, reducing the moisture for the fungus to disperse the infective propagules and infect.
 
@@
 However, over the next 10 to 20 years the risk is predicted to remain the same as during the period from 2000 to 2010 in research that has been conducted on the matter to date [@Kim2015].
-Therefore, it is likely to remain an important disease for the near future with little resistance available in currently available varieties.
-Given the results of the N treatments showing clear effects, in most cases increasing the amount and severity of the disease, we would argue that this suggests that there is no reason AWD could not be adopted as we were unable to detect any clear differences due to irrigation management in most of the cases.
+Therefore, it is likely to remain an important disease for the near future with little resistance available in currently available varieties [@Srinivasachary2011].
+
+# Conclusion {-}
+
+We argue that that there is no reason AWD could not be adopted as we were unable to detect any statistically clear differences due to irrigation management in any of the sheath blight measurements made.
+Whereas, in the presence of excess N the treatments showed clear effects, increasing the amount and severity of the disease, suggesting that the studies were capable of demonstrating differences in the selected treatments as applied.
 Therefore, based on these studies the use of AWD technologies would not appear to be a factor that increases the incidence or severity of rice sheath blight disease and should be adopted given the other benefits that it provides.

### 2020-08-11 analysis/paper/paper.Rmd
Delete text on interactions, not modelled

@@
 
-The interaction of N100 and N120 with the water management treatment were undecided.
-
 ## 2016 Experiment {-}
@@
 The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure&nbsp;\@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-3).
-As in the 2015 study, water management treatment and the interaction of N rate and water management were undecided with no clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
+As in the 2015 study, water management treatment was undecided with no clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
 
@@
 However the water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-2)).
-
-However, the interaction of the water management and N rate, AWD and N180 were clearly different and lower than traditional puddling and N60.
 

### 2020-08-12 analysis/paper/paper.Rmd
Edit highlights
Remove interactions, add info on N rates

@@
 highlights: |
-  * The effects of AWD on sheath blight disease incidence and severity were investigated.
+  * The effects of alternate wetting and drying and nitrogen fertilisation rates on sheath blight disease incidence and severity were investigated.
+  * Increasing rates of nitrogen led to increased levels of sheath blight incidence and sheath blight severity.
   * AWD had no detectable effect on either sheath blight incidence or sheath blight severity.
-  * The interaction of AWD and nitrogen management had no detectable effect on either sheath blight incidence or sheath blight severity.
-  * The adoption of AWD technologies will not lead to increased sheath blight incidence or sheath blight severity.
+  * The adoption of AWD technologies does not appear to lead to increased sheath blight incidence or sheath blight severity.
 ---

### 2020-08-12 analysis/paper/paper.Rmd
Edit statement on possibility of reducing disease in Discussion

@@
 However, it should be noted that often it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season [@Sriphirom2019; @Sander2017; @Sander2020].
-Still, sheath blight remains an issue in both seasons [@Savary2001] and the use of AWD would not appear to increase the disease but may be effective in reducing it in some cases because of less water in the paddy field than in traditional systems, reducing the moisture for the fungus to disperse the infective propagules and infect.
+Sheath blight still remains an issue in both seasons [@Savary2001] and the use of AWD would not appear to increase the disease but might be effective in reducing it in some cases because of less water in the paddy field than in traditional systems by reducing the moisture for the fungus to disperse the infective propagules and infect.
 

### 2020-08-12 analysis/paper/paper.Rmd
Edit statement about future design not being split plot

@@
 
-While the use of different levels of N did provide information about the effects of N on the disease, it reduced the statistical power to find the effects of the irrigation [@Bradley1998].
-Using a high rate of N, _e.g._ 180&nbsp;k/ha, for the entire study would help ensure that enough disease occurs to be able to detect differences in the irrigation treatments with a more simple trial statistical design.
-
-We would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the data.
+While the use of different levels of N did provide information about the effects of N on the disease, this effect was already known [@Castilla1996; @Tang2007], and it reduced the statistical power to find the effects in the main plot of the irrigation.
+Designing a future experiment as a randomised complete block with two treatments, puddled or AWD and using a single high rate of N, _e.g._ 180&nbsp;k/ha would help ensure that disease occurs and increase the precision of measurements for the irrigation treatments.
+Therefore, we would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the quality of data.
 

### 2020-08-12 analysis/paper/paper.Rmd
Edit sentence for flow with other sentences in same paragraph

@@
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
-However, it should be noted that often it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season [@Sriphirom2019; @Sander2017; @Sander2020].
+However, it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season [@Sriphirom2019; @Sander2017; @Sander2020].
 Sheath blight still remains an issue in both seasons [@Savary2001] and the use of AWD would not appear to increase the disease but might be effective in reducing it in some cases because of less water in the paddy field than in traditional systems by reducing the moisture for the fungus to disperse the infective propagules and infect.

### 2020-08-12 analysis/paper/paper.Rmd
Edits to highlights. Spell out AWD

@@
   * Increasing rates of nitrogen led to increased levels of sheath blight incidence and sheath blight severity.
-  * AWD had no detectable effect on either sheath blight incidence or sheath blight severity.
-  * The adoption of AWD technologies does not appear to lead to increased sheath blight incidence or sheath blight severity.
+  * Alternate wetting and drying had no detectable effect on either sheath blight incidence or sheath blight severity.
+  * The adoption of alternate wetting and drying technology does not appear to lead to increased sheath blight incidence or sheath blight severity.
 ---

### 2020-08-12 analysis/paper/paper.Rmd
Edit introduction for flow, add new refs

@@
 Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress.
-As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50 \% [@Yan2005; @Sander2015].
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50\% [@Yan2005; @Sander2015].
 
@@
 Various countries, *e.g.* Bangladesh, Vietnam, Thailand and Philippines, plan to widely apply AWD to rice production [@MOEF2015].
-However, a change like this in the water regime in rice fields on a large scale could trigger unintended effects, for example, changes in disease incidence or severity.
 
-Many studies have been conducted *in silico* that examine how diseases may change with a changing climate.
+Studies have been conducted *in silico* that examine how diseases may change with a changing climate.
 Rice blast is perhaps the most frequently studied rice disease in regards to the effects of climate change [@Luo1995; @Luo1998; @Kim2015; @Duku2016; @Viswanath2017].
@@
 
-While the effects of climate change directly on rice disease have been studied, the effects of mitigation practices have not.
-Rice farmers may be hesitant to adopt water-saving technologies because changing rice production practices could have unintended effects on the pests and diseases that occur in the rice crop.
-This is a reasonable concern because of the well-documented effects of N [@Slaton2003; @Tang2007] and the effects of alternating wet and dry periods [@Castilla1996] on sheath blight.
+*In-situ* studies of the effects of changing crop management practices also exist.
+Chapagain *et al.* [-@Chapagain] reported slightly higher grain yields and reduces pests and diseases.
+Van Buyten *et al.* [-@VanBuyten2012] studied *Pythium* species found in aerobic rice production that were found to negatively affect rice yields in the Philippines.
+They found that unlike the traditional paddy system where the pathogen is inhibited due to puddling, aerobic conditions promote pathogen growth and it can inhibit rice seedlings.
+Furthermore, nitrogen rates [@Slaton2003; @Tang2007] and alternating wet and dry periods (not to be confused with AWD irrigation technology) also have both been shown to affect rice sheath blight [@Castilla1996].
+
+While the effects of climate change directly on rice diseases have been conducted, studies on on the effects of mitigation strategies are less common, other than .
+A change like this in the water management in rice fields on a large scale could trigger unintended effects, for example, increasing disease incidence or severity.
+Because of this, rice farmers may be hesitant to adopt water-saving technologies because changing rice production practices could have unintended effects on the pests and diseases that occur in the rice crop.
+
 To gain a better understanding of what the effects of adopting AWD on rice sheath blight could have, we established field experiments that incorporated irrigation technology and N fertilisation to create a conducive environment for the disease to develop.
@@
 
-While the use of different levels of N did provide information about the effects of N on the disease, this effect was already known [@Castilla1996; @Tang2007], and it reduced the statistical power to find the effects in the main plot of the irrigation.
+While the use of different levels of N did provide information about the effects of N on the disease, this effect was already known [@Castilla1996; @Slaton2003; @Tang2007; @Tang2007], and it reduced the statistical power to find the effects in the main plot of the irrigation.
 Designing a future experiment as a randomised complete block with two treatments, puddled or AWD and using a single high rate of N, _e.g._ 180&nbsp;k/ha would help ensure that disease occurs and increase the precision of measurements for the irrigation treatments.
@@
 
-# Conclusion {-}
-
-We argue that that there is no reason AWD could not be adopted as we were unable to detect any statistically clear differences due to irrigation management in any of the sheath blight measurements made.
+Our findings here indicate that there is no reason AWD could not be adopted as we were unable to detect any statistically clear differences due to irrigation management in any of the sheath blight measurements made.
 Whereas, in the presence of excess N the treatments showed clear effects, increasing the amount and severity of the disease, suggesting that the studies were capable of demonstrating differences in the selected treatments as applied.

### 2020-08-12 analysis/paper/paper.Rmd
Edit introduction with prior studies and fix grammar throughout

@@
 To understand how different combinations of water and nitrogen management affect sheath blight epidemics, we conducted two separate split-plot experiments with a water-saving (alternate wetting and drying) regime and a traditional puddled regime combined with differing nitrogen treatments in the dry seasons of 2015 and 2016.
-Disease was scored using the same methodology in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers was counted per hill.
+The disease was scored using the same methodology in both experiments using a sheath blight assessment scale for field evaluation developed at the International Rice Research Institute to assess the severity on infected sheaths and leaves while sheath blight incidence on tillers was counted per hill.
 We were unable to detect any clear differences in the incidence or severity of tiller sheath blight due to irrigation treatment.
-Leaf severity for the AWD treatment was clearly lower than traditional puddling in the 2015 trial but we were unable to detect any clear differences in 2016.
+Leaf severity for the AWD treatment was clearly lower than traditional puddled treatment in the 2015 trial but we were unable to detect any clear differences in 2016.
 However, the level of disease severity remained low in both years, < 1&nbsp;%.
-Our findings indicate that farmers can adopt water-saving technologies without risking increased sheath blight incidence.
+In these studies, our findings indicate that farmers can adopt water-saving technologies without risking increased sheath blight incidence.
 We suggest that further cross-disciplinary research in this area is warranted.
@@
 
-Some *in-situ* studies of the effects of climate change on rice diseases have focused on the effects of temperature on bacterial blight [@Webb2010] and the effects of drought [@Dossa2017].
-
-*In-situ* studies of the effects of changing crop management practices also exist.
-Chapagain *et al.* [-@Chapagain] reported slightly higher grain yields and reduces pests and diseases.
-Van Buyten *et al.* [-@VanBuyten2012] studied *Pythium* species found in aerobic rice production that were found to negatively affect rice yields in the Philippines.
-They found that unlike the traditional paddy system where the pathogen is inhibited due to puddling, aerobic conditions promote pathogen growth and it can inhibit rice seedlings.
+*In-situ* studies of the direct effects that climate change and adaptation or mitigation strategies have on rice diseases have also been conducted.
+Looking into the disease bacterial blight (*Xanthomonas oryzae* pv.
+*oryzae*), Webb *et al.* [-@Webb2010] examined the effects of increasing temperature while Dossa *et al.* [-@Dossa2017] studied the effects of drought on the disease.
+While Van Buyten *et al.* [-@VanBuyten2012] found that unlike the traditional paddy system where *Pythium* is inhibited due to puddling, aerobic conditions promote pathogen growth and it can inhibit rice seedlings.
+Conversely, Chapagain *et al.* [-@Chapagain2011] reported slightly higher grain yields and reduced incidence of insect pests and diseases through the use of AWD.
 Furthermore, nitrogen rates [@Slaton2003; @Tang2007] and alternating wet and dry periods (not to be confused with AWD irrigation technology) also have both been shown to affect rice sheath blight [@Castilla1996].
 
-While the effects of climate change directly on rice diseases have been conducted, studies on on the effects of mitigation strategies are less common, other than .
-A change like this in the water management in rice fields on a large scale could trigger unintended effects, for example, increasing disease incidence or severity.
-Because of this, rice farmers may be hesitant to adopt water-saving technologies because changing rice production practices could have unintended effects on the pests and diseases that occur in the rice crop.
+These studies suggest that a change like this in the water management in rice fields on a large scale could trigger unintended negative effects but also positive effects may result.
+Because of this, rice farmers may be hesitant to adopt water-saving technologies because changing rice production practices without good information about what the changes in the management will mean for other parts of the cropping system.
 
@@
 In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Figure&nbsp;\@ref(fig:fig-1)a; Table&nbsp;\@ref(tab:Table-2)).
-Water management was undecided in the test for equivalency (Figure&nbsp;\@ref(fig:fig-3)a; Table&nbsp;\@ref(tab:Table-2)) between the AWD and puddled treatments.
+Water management was undecided not showing any clear difference in the test for equivalency (Figure&nbsp;\@ref(fig:fig-3)a; Table&nbsp;\@ref(tab:Table-2)) between the AWD and puddled treatments.
 However, the effect of the N treatments of both N100 and N120 on tiller incidence were higher and clearly different when compared with the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)a, \@ref(tab:Table-2)).
@@
 As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values that were clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
-The AWD water management treatment was again undecided (Figure&nbsp;\@ref(fig:fig-3)e; Table&nbsp;\@ref(tab:Table-2)).
+The AWD water management treatment was again undecided with no clear difference between the control puddled and AWD treatments (Figure&nbsp;\@ref(fig:fig-3)e; Table&nbsp;\@ref(tab:Table-2)).
 
@@
 The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure&nbsp;\@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-3).
-As in the 2015 study, water management treatment was undecided with no clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
+As in the 2015 study, water management treatment was undecided not showing a clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
 
@@
 In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Figure&nbsp;\@ref(fig:fig-4)d; Table&nbsp;\@ref(tab:Table-3)).
-The AWD water management did not show statistically clear differences from the puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
+The AWD water management result was undecided and did not show statistically clear differences from the control puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
 
 In 2016 the higher N rate, N180, were clearly different, higher, than the control treatments, N60.
-However the water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-2)).
+However the water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-2)) with no clear differences from the puddled treatment.
 
@@
 Designing a future experiment as a randomised complete block with two treatments, puddled or AWD and using a single high rate of N, _e.g._ 180&nbsp;k/ha would help ensure that disease occurs and increase the precision of measurements for the irrigation treatments.
-Therefore, we would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the quality of data.
+Therefore, we would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer while using the larger plot size and inoculation methods used in 2016 that improved the quality of data.
 
@@
 However, it is only practical to implement AWD in the dry season due to the inability to completely drain the paddy fields in the wet season [@Sriphirom2019; @Sander2017; @Sander2020].
-Sheath blight still remains an issue in both seasons [@Savary2001] and the use of AWD would not appear to increase the disease but might be effective in reducing it in some cases because of less water in the paddy field than in traditional systems by reducing the moisture for the fungus to disperse the infective propagules and infect.
+Sheath blight remains an issue in both seasons [@Savary2001] and the use of AWD would not appear to increase the disease but might be effective in reducing it in some cases because of less water in the paddy field than in traditional systems by reducing the moisture for the fungus to disperse the infective propagules and infect.
 

### 2020-10-15 analysis/paper/paper.Rmd
Halting any work on this. Decided not to publish

@@
 output:
-  bookdown::word_document2:
+  officedown::rdocx_document:
+    reference_docx: "../templates/template.docx"
     toc: no
     fig_caption: yes
-    reference_docx: "../templates/template.docx"
+    tables:
+      layout: autofit
+      width: 1.0
+      caption:
+        style: Table Caption
+        pre: 'Table '
+        sep: ': '
+      conditional:
+        first_row: true
+        first_column: false
+        last_row: false
+        last_column: false
+        no_hband: false
+        no_vband: true
     pandoc_args:
@@
       - '--lua-filter=author-info-blocks.lua'
+      - '--lua-filter=pagebreak.lua'
 csl: "../templates/plant_disease.csl" # Insert path for the bib-style
@@
 Leaf severity for the AWD treatment was clearly lower than traditional puddled treatment in the 2015 trial but we were unable to detect any clear differences in 2016.
-However, the level of disease severity remained low in both years, < 1&nbsp;%.
+However, the level of disease severity remained low in both years, < 1%.
 In these studies, our findings indicate that farmers can adopt water-saving technologies without risking increased sheath blight incidence.
@@
   * Alternate wetting and drying had no detectable effect on either sheath blight incidence or sheath blight severity.
-  * The adoption of alternate wetting and drying technology does not appear to lead to increased sheath blight incidence or sheath blight severity.
+  * The adoption of alternate wetting and drying technology does not appear to lead to increased sheath blight incidence or sheath blight severity
 ---
@@
 
-##### pagebreak
+\newpage
 
-# Introduction {-}
+# Introduction {.unnumbered}
 
-Rice is mainly produced in Asia with over 90&nbsp;% of production occurring there [@GRiSP2013] and uses the largest amount of any agricultural commodity [@Dawe2005; @GRiSP2013].
+Rice is mainly produced in Asia with over 90% of production occurring there [@GRiSP2013] and uses the largest amount of any agricultural commodity [@Dawe2005; @GRiSP2013].
 
@@
 anastomosis group 1 IA, of rice, is an economically important disease worldwide throughout tropical and temperate production areas.
-Under conducive conditions, the disease can cause up to 50\% yield losses [@Marchetti1991].
-Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10\% annually.
+Under conducive conditions, the disease can cause up to 50% yield losses [@Marchetti1991].
+Studies by Savary *et al.* [-@Savary2000] estimated normal yield losses in tropical irrigated lowland rice in Asia at 5 to 10% annually.
 The disease is best managed through an integrated disease management approach, which includes resistance [@Kumar2009; @Srinivasachary2011], fungicide applications where affordable [@Rush1983; @Groth2008], nitrogen (N) management [@Slaton2003; @Castilla1996; @Tang2007] and water management [@Castilla1996].
 
-Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 to 40\% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
+Alternate wetting and drying (AWD) is an irrigation technique for rice (*Oryza sativa* L.) developed by the International Rice Research Institute (IRRI) and its partners that saves about 15 to 40% of irrigation water while not affecting yield [@Bouman2001; @Feng2007].
 In AWD rice, fields are exposed to several dry phases during the growing season without exposing the plants to water stress.
 To avoid yield decline under AWD, "safe" thresholds have been developed.
-Under safe AWD irrigation water is applied when the field water level reaches 15&nbsp;cm below the soil surface [@Richards2014].
+Under safe AWD irrigation water is applied when the field water level reaches 15 cm below the soil surface [@Richards2014].
 Fields are furthermore kept puddled with water standing during the flowering period to avoid plant stress.
-As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50\% [@Yan2005; @Sander2015].
+As an added benefit to saving water, AWD also reduces greenhouse gas (GHG) emissions of rice fields, which are a substantial factor in the GHG budget of rice-producing countries, by around 50% [@Yan2005; @Sander2015].
 
@@
 
-# Materials and Methods {-}
+# Materials and Methods {.unnumbered}
 
-## Experimental Site {-}
+## Experimental Site {.unnumbered}
 
-Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14&deg;&nbsp;11'&nbsp;N, longitude 121&deg;&nbsp;15'&nbsp;E).
+Two experiments were conducted at the International Rice Research Institute's (IRRI) Ziegler Experiment Station in Los Baños, Calabarzon, Philippines (latitude 14° 11' N, longitude 121° 15' E).
 The climate is classified as humid-tropical with the wet season starting in early June to December and dry season between December and late May.
@@
 
-## Pathogen {-}
+## Pathogen {.unnumbered}
 
-An isolate of _Thanatephorus cucumeris_ (strain AG1-IA) infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
-The isolate was transferred to 90&nbsp;mm Petri dishes containing PDA and incubated a room temperature (20 to 27&deg;C) for five days.
+An isolate of *Thanatephorus cucumeris* (strain AG1-IA) infected lowland rice was maintained on potato dextrose agar (PDA) medium slants.
+The isolate was transferred to 90 mm Petri dishes containing PDA and incubated a room temperature (20 to 27°C) for five days.
 Glass bottles of autoclaved rice grain and hull substrate (1/5, w/w) were prepared and plugs of the culture were transferred from Petri dishes to the autoclaved substrate and incubated at room temperature for two weeks and used to inoculate the plots [@Castilla1996].
 
-## Host Plant {-}
+## Host Plant {.unnumbered}
 
@@
 
-## 2015 Experimental Design {-}
+## 2015 Experimental Design {.unnumbered}
 
@@
 The main plot treatments were alternate wetting and drying (AWD) and continuously puddled or farmers' practice as the control treatment.
-The main plot size was 12&nbsp;m x 12&nbsp;m (144&nbsp;m^2^), with a split-plot size of 5&nbsp;m&nbsp;x&nbsp;5&nbsp;m (25&nbsp;m^2^).
-Replication size was 12&nbsp;m&nbsp;x&nbsp;24&nbsp;m (288&nbsp;m^2^) with a buffer of 1&nbsp;m per split-plot for a whole experiment size of 1,152&nbsp;m^2^.
+The main plot size was 12 m x 12 m (144 m^2^), with a split-plot size of 5 m x 5 m (25 m^2^).
+Replication size was 12 m x 24 m (288 m^2^) with a buffer of 1 m per split-plot for a whole experiment size of 1,152 m^2^.
 
-Irrigation in AWD plots was determined by the water level in plots, *i.e.* when the water level reached 15&nbsp;cm below the soil surface irrigation water was applied to a level of 5&nbsp;cm.
-In puddled plots, a standing water layer of 3 to 5&nbsp;cm was maintained throughout the growing season.
+Irrigation in AWD plots was determined by the water level in plots, *i.e.* when the water level reached 15 cm below the soil surface irrigation water was applied to a level of 5 cm.
+In puddled plots, a standing water layer of 3 to 5 cm was maintained throughout the growing season.
 
-The split-plot treatment rates of N were N0 (no N supply), N100 (100&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) and N120 (120&nbsp;kg&nbsp;per&nbsp;ha applied as urea in three splits) (Table&nbsp;\@ref(tab:Table-1)).
+The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits) and N120 (120 kg per ha applied as urea in three splits) (Table \@ref(tab:Tab1)).
 
 Trays of NSIC Rc222 were seeded on 19 December 2014.
-Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20&nbsp;cm within and between rows.
+Plots were established by manually transplanting seedlings on 9 January 2015 in hills with six to eight seedlings per hill and a distance of 20 cm within and between rows.
 
-The plots were inoculated 20 days after transplanting by applying 151&nbsp;g of inoculum over the split-plot area with a 1&nbsp;m buffer on either end (4&nbsp;m x 11&nbsp;m).
+The plots were inoculated 20 days after transplanting by applying 151 g of inoculum over the split-plot area with a 1 m buffer on either end (4 m x 11 m).
 
-## 2016 Experimental Design {-}
+## 2016 Experimental Design {.unnumbered}
 
@@
 However, the plot size was increased and due to these changes, the replicate sizes are not equal as necessitated by the use of a larger area for the experiment due to differences in the blocks.
-The main plot sizes were: Block 1 (B1) 21&nbsp;m x 20.5&nbsp;m (412.5 sq&nbsp;m) and Block 2 (B2) 20.25&nbsp;m x 21.6&nbsp;m (437.4&nbsp;m^2^).
-The split-plot sizes were B1 21&nbsp;m x 10.25&nbsp;m (215.25&nbsp;m^2^), B2 20.25&nbsp;m x 10.8&nbsp;m (218.7&nbsp;m^2^).
-The replication sizes were B1 -- 42&nbsp;m&nbsp;x&nbsp;20.5&nbsp;m (861&nbsp;m^2^) and B2 -- 40.5&nbsp;m&nbsp;x&nbsp;21.6&nbsp;m (874.8&nbsp;m^2^).
-A buffer 0.5&nbsp;m per split-plot was used and the overall experiment size was 3471.6&nbsp;m^2^.
+The main plot sizes were: Block 1 (B1) 21 m x 20.5 m (412.5 sq m) and Block 2 (B2) 20.25 m x 21.6 m (437.4 m^2^).
+The split-plot sizes were B1 21 m x 10.25 m (215.25 m^2^), B2 20.25 m x 10.8 m (218.7 m^2^).
+The replication sizes were B1 -- 42 m x 20.5 m (861 m^2^) and B2 -- 40.5 m x 21.6 m (874.8 m^2^).
+A buffer 0.5 m per split-plot was used and the overall experiment size was 3471.6 m^2^.
 
-split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60&nbsp;kg/ha as urea split into two applications) and N180 (180&nbsp;kg/ha in three splits) being applied (Table&nbsp;\@ref(tab:Table-1)).
+split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg/ha as urea split into two applications) and N180 (180 kg/ha in three splits) being applied (Table \@ref(tab:Tab1)).
 
 Nurseries of NSIC Rc222 were established on 7 January 2016.
-Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20&nbsp;cm within and between rows.
+Seedlings were manually transplanted from 20 to 22 January 2016 in hills with six to eight seedlings per hill with a distance of 20 cm within and between rows.
 
 Based on the 2015 results, the inoculum application methods were modified in 2016 to increase the amount of inoculum and applied to a smaller area.
-Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1&nbsp;m&nbsp;x&nbsp;1&nbsp;m) per plot, where one bottle contained 151&nbsp;g inoculum.
-A total amount of 1,510&nbsp;g of inoculum was applied to each 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m area.
+Plots were inoculated 41 days after transplanting using ten bottles per one sampling area (1 m x 1 m) per plot, where one bottle contained 151 g inoculum.
+A total amount of 1,510 g of inoculum was applied to each 1 m x 1 m area.
 
-## Data Collection {-}
+## Data Collection {.unnumbered}
 
-In both experiments, two sample areas, sized 1&nbsp;m&nbsp;x&nbsp;1&nbsp;m, per plot were assessed.
+In both experiments, two sample areas, sized 1 m x 1 m, per plot were assessed.
 The total number of tillers per hill and number of tillers with sheath blight (incidence) was measured for nine hills per sample area.
 Tiller sheath severity was measured for four tillers per hill and six leaves tiller using a disease assessment rating scale for field evaluation developed at IRRI.
-The scale is an unequally spaced categorical scale where (i) 0 -- no disease; (ii) 1 -- trace to 1\% severity; (iii) 2 -- 1 to 5\% severity; (iv) 3 -- 5 to 15\% severity; (v) 4 -- 15 to 50\% severity; and (vi) 5 -- 50 to 100\% severity.
+The scale is an unequally spaced categorical scale where (i) 0 -- no disease; (ii) 1 -- trace to 1% severity; (iii) 2 -- 1 to 5% severity; (iv) 3 -- 5 to 15% severity; (v) 4 -- 15 to 50% severity; and (vi) 5 -- 50 to 100% severity.
 Severity was considered to be the amount of leaf or sheath tissue covered by sheath blight lesions.
-A leaf was considered living if at least 50&nbsp;% of its area was not brown or dark brown due to natural senescence.
+A leaf was considered living if at least 50% of its area was not brown or dark brown due to natural senescence.
 A leaf that was yellow-green or light green due to a disease, such as tungro or N deficiency was still considered a living leaf.
@@
 
-## Statistical Analysis {-}
+## Statistical Analysis {.unnumbered}
 
@@
 The "Test for Practical Equivalence" is based on the Highest Density Interval (HDI) plus the Region of Practical Equivalence (ROPE) decision rule [@Kruschke2014; @Kruschke2018], *HDI+ROPE decision rule* and checks whether parameter values should be accepted or rejected against the null hypothesis, the ROPE.
-To do this, it checks the percentage of the 89&nbsp;% HDI that is in the null region ROPE.
+To do this, it checks the percentage of the 89% HDI that is in the null region ROPE.
 If this amount is sufficiently low, the null hypothesis is rejected.
@@
 
-## Hypothesis {-}
+## Hypothesis {.unnumbered}
 
@@
 
-# Results {-}
+# Results {.unnumbered}
 
-## 2015 Experiment {-}
+## 2015 Experiment {.unnumbered}
 
-In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Figure&nbsp;\@ref(fig:fig-1)a; Table&nbsp;\@ref(tab:Table-2)).
-Water management was undecided not showing any clear difference in the test for equivalency (Figure&nbsp;\@ref(fig:fig-3)a; Table&nbsp;\@ref(tab:Table-2)) between the AWD and puddled treatments.
-However, the effect of the N treatments of both N100 and N120 on tiller incidence were higher and clearly different when compared with the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)a, \@ref(tab:Table-2)).
+In 2015 the incidence of tiller sheath blight remained low throughout the growing season (Figure \@ref(fig:fig-1)a; Table \@ref(tab:Tab2)).
+Water management was undecided not showing any clear difference in the test for equivalency (Figure \@ref(fig:fig-3)a; Table \@ref(tab:Tab2)) between the AWD and puddled treatments.
+However, the effect of the N treatments of both N100 and N120 on tiller incidence were higher and clearly different when compared with the control N0 treatment (Figure \@ref(fig:fig-4)a, \@ref(tab:Tab2)).
 
-Tiller sheath blight severity remained below 2\% (Figure&nbsp;\@ref(fig:fig-1)c, \@ref(fig:fig-2)c).
-Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Figure&nbsp;\@ref(fig:fig-4)c; Table&nbsp;\@ref(tab:Table-2)).
-However, the AWD water management was undecided whether it was different than the puddled treatment (Figure&nbsp;\@ref(fig:fig-3)c; Table&nbsp;\@ref(tab:Table-2)).
+Tiller sheath blight severity remained below 2% (Figure \@ref(fig:fig-1)c, \@ref(fig:fig-2)c).
+Both the N100 and N120 treatment effects caused the tiller severity to be higher and were clearly different than the control N0 treatment (Figure \@ref(fig:fig-4)c; Table \@ref(tab:Tab2)).
+However, the AWD water management was undecided whether it was different than the puddled treatment (Figure \@ref(fig:fig-3)c; Table \@ref(tab:Tab2)).
 
-The severity of leaf sheath blight remained low, less than 0.4&nbsp;% across all treatments (Figure&nbsp;\@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
-As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values that were clearly different than the N0 treatment (Figure&nbsp;\@ref(fig:fig-4)e; Table&nbsp;\@ref(tab:Table-2)).
-The AWD water management treatment was again undecided with no clear difference between the control puddled and AWD treatments (Figure&nbsp;\@ref(fig:fig-3)e; Table&nbsp;\@ref(tab:Table-2)).
+The severity of leaf sheath blight remained low, less than 0.4% across all treatments (Figure \@ref(fig:fig-1)e, \@ref(fig:fig-2)e).
+As with the tiller incidence and severity, the effects of both the N100 and N120 treatments on leaf severity resulted in higher values that were clearly different than the N0 treatment (Figure \@ref(fig:fig-4)e; Table \@ref(tab:Tab2)).
+The AWD water management treatment was again undecided with no clear difference between the control puddled and AWD treatments (Figure \@ref(fig:fig-3)e; Table \@ref(tab:Tab2)).
 
-## 2016 Experiment {-}
+## 2016 Experiment {.unnumbered}
 
-The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98&nbsp;% incidence at the third observation (Figure&nbsp;\@ref(fig:fig-2)b).
-The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure&nbsp;\@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-3).
-As in the 2015 study, water management treatment was undecided not showing a clear difference between the treatments (Figure&nbsp;\@ref(fig:fig-3)b; Table&nbsp;\@ref(tab:Table-3)).
+The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Figure \@ref(fig:fig-2)b).
+The N treatment N180 value was higher and clearly different than the control N60 treatment (Figure \@ref(fig:fig-4)b; Table \@ref(tab:Tab3).
+As in the 2015 study, water management treatment was undecided not showing a clear difference between the treatments (Figure \@ref(fig:fig-3)b; Table \@ref(tab:Tab3)).
 
-As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Figure&nbsp;\@ref(fig:fig-2)d).
-In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Figure&nbsp;\@ref(fig:fig-4)d; Table&nbsp;\@ref(tab:Table-3)).
-The AWD water management result was undecided and did not show statistically clear differences from the control puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-3)).
+As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the puddled treatment (Figure \@ref(fig:fig-2)d).
+In 2016 the N180 treatment was again higher and clearly different from the N60 treatment, with N180 severity being higher (Figure \@ref(fig:fig-4)d; Table \@ref(tab:Tab3)).
+The AWD water management result was undecided and did not show statistically clear differences from the control puddled treatment (Figure \@ref(fig:fig-3)d; Table \@ref(tab:Tab3)).
 
 In 2016 the higher N rate, N180, were clearly different, higher, than the control treatments, N60.
-However the water management treatment was undecided (Figure&nbsp;\@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table&nbsp;\@ref(tab:Table-2)) with no clear differences from the puddled treatment.
+However the water management treatment was undecided (Figure \@ref(fig:fig-3)f, \@ref(fig:fig-4)b; Table \@ref(tab:Tab2)) with no clear differences from the puddled treatment.
 
-# Discussion {-}
+# Discussion {.unnumbered}
 
 In both experiments, we were unable to detect any statistically clear effect of AWD on sheath blight that led to increases in the disease that could hinder adoption of the technology, or decreases that would favour it except in one case.
-In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure&nbsp;\@ref(fig:fig-3)d; Table&nbsp;\@ref(tab:Table-2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
+In the 2016 experiment the tiller sheath blight severity was clearly lower for the AWD treatment than puddled treatment (Figure \@ref(fig:fig-3)d; Table \@ref(tab:Tab2)), indicating a possible adverse effect of using AWD on tiller sheath blight severity under high sheath blight disease pressure.
 In all other cases, no significant differences were observed.
 
-The findings of the effects of N rates on sheath blight were as expected in both experiments.
-Higher rates of N caused an increase in disease incidence and severity in all of the cases examined.
+The findings of the effects of N rates on sheath blight were as expected in both experiments. Higher rates of N caused an increase in disease incidence and severity in all of the cases examined.
 
 By increasing the plot size and increasing inoculum amount applied to a smaller area, the changes made for the 2016 experiment improved the experiment by decreasing the variability in the data collected.
-The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure&nbsp;\@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
+The sheath blight incidence increased and the variability of sheath blight in the plots decreased (Figure \@ref(fig:fig-1)a:b, \@ref(fig:fig-2)c:d, \@ref(fig:fig-3)a:b, \@ref(fig:fig-4)c:d).
 
 While the use of different levels of N did provide information about the effects of N on the disease, this effect was already known [@Castilla1996; @Slaton2003; @Tang2007; @Tang2007], and it reduced the statistical power to find the effects in the main plot of the irrigation.
-Designing a future experiment as a randomised complete block with two treatments, puddled or AWD and using a single high rate of N, _e.g._ 180&nbsp;k/ha would help ensure that disease occurs and increase the precision of measurements for the irrigation treatments.
+Designing a future experiment as a randomised complete block with two treatments, puddled or AWD and using a single high rate of N, *e.g.* 180 k/ha would help ensure that disease occurs and increase the precision of measurements for the irrigation treatments.
 Therefore, we would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer while using the larger plot size and inoculation methods used in 2016 that improved the quality of data.
 
-It should be noted that the levels of leaf severity remained low (<&nbsp;1\%) throughout the growing season in all treatments for both years.
+It should be noted that the levels of leaf severity remained low (\< 1%) throughout the growing season in all treatments for both years.
 Therefore, the sheath blight disease levels in these studies may be lower than they would be if conducted in the wet season.
@@
 
-# Acknowledgments {-}
+# Acknowledgments {.unnumbered}
 
@@
 <!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line. -->
-##### pagebreak
 
-# Literature Cited {-}
+\newpage
+
+# Literature Cited {.unnumbered}
+
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document: -->
 
-<div id="refs"></div>
+::: {#refs}
+:::
 
-# Author-Recommended Internet Resources {-}
+# Author-Recommended Internet Resources {.unnumbered}
 
@@
 
-##### pagebreak
+\newpage
 
-# Tables {-}
+# Tables {.unnumbered}
 
-```{r Table-1}
+```{r Tab1, tab.id="Tab1", tab.cap = "Nitrogen application rates for 2015 and 2016 experiments in kilograms per hectare.
+Five different nitrogen treatments were applied depending on the experiment.
+In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg/ha N (N100) and 180 kg/ha N (N120).
+In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg/ha N (N60) and 180 kg/ha N (N180).
+Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications."}
 N_rates <- N_rates[, -1]
@@
 x <- fontsize(x, size = 10)
-x <-
-  set_caption (x,
-               caption = 
-    "(\\#tab:Table-1) Nitrogen application rates for 2015 and 2016 experiments in kilograms per hectare.
-Five different nitrogen treatments were applied depending on the experiment.
-In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100 kg/ha N (N100) and 180 kg/ha N (N120).
-In the 2016 experiment, two nitrogen rate treatments were applied: 60 kg/ha N (N60) and 180 kg/ha N (N180).
-Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications."
-    )
 x
@@
 
-##### pagebreak
+\newpage
 
-```{r Table-2}
+```{r Tab2, tab.id="Tab2", tab.cap="An 89 % test for practical equivalence for 2015 experiment.
+Response variables are shown as T.
+Inc., Tiller Incidence; T.
+Sev., Tiller Severity; L.
+Sev., Leaf Severity.
+The parameters are WMGTAWD, irrigation treatment AWD; NRTEN100, nitrogen rate of 100 k/ha; NRTEN120 kg/ha.
+ROPE low and ROPE high provide the limits of the Region of Practical Equivalence (ROPE).
+ROPE Percentage is the proportion of the Highest Density Interval (HDI) that lies inside the ROPE.
+All points within this interval have a higher probability of density than points outside the interval.
+ROPE Equivalence is the test result, either \"rejected\", \"accepted\" or \"undecided\".
+\"HDI Low\" and \"HDI High\" are the lower and upper HDI limits for the parameters."}
 x <- rbind(
@@
 x <- autofit(x)
-x <- set_caption(x, 
-  "(\\#tab:Table-2) An 89 % test for practical equivalence for 2015 experiment.
+x
+```
+
+\newpage
+
+```{r Tab3, tab.id="Tab3", tab.cap="An 89 % test for practical equivalence for 2015 experiment.
 Response variables are shown as T.
@@
 Sev., Leaf Severity.
-The parameters are WMGTAWD, irrigation treatment AWD; NRTEN100, nitrogen rate of 100 k/ha; NRTEN120 kg/ha.
+The parameters are WMGTAWD, irrigation treatment AWD; and NRTEN180, nitrogen rate of 180 k/ha.
 ROPE low and ROPE high provide the limits of the Region of Practical Equivalence (ROPE).
@@
 ROPE Equivalence is the test result, either \"rejected\", \"accepted\" or \"undecided\".
-\"HDI Low\" and \"HDI High\" are the lower and upper HDI limits for the parameters."
-  )
-x
-```
-
-##### pagebreak
-
-```{r Table-3}
+\"HDI Low\" and \"HDI High\" are the lower and upper HDI limits for the parameters."}
 x <- rbind(equivalence_test(TInc16),
@@
 x <- autofit(x)
-x <- set_caption(x, 
-  "(\\#tab:Table-3) An 89 % test for practical equivalence for 2015 experiment.
-Response variables are shown as T.
-Inc., Tiller Incidence; T.
-Sev., Tiller Severity; L.
-Sev., Leaf Severity.
-The parameters are WMGTAWD, irrigation treatment AWD; and NRTEN180, nitrogen rate of 180 k/ha.
-ROPE low and ROPE high provide the limits of the Region of Practical Equivalence (ROPE).
-ROPE Percentage is the proportion of the Highest Density Interval (HDI) that lies inside the ROPE.
-All points within this interval have a higher probability of density than points outside the interval.
-ROPE Equivalence is the test result, either \"rejected\", \"accepted\" or \"undecided\".
-\"HDI Low\" and \"HDI High\" are the lower and upper HDI limits for the parameters.")
 x
@@
 
-##### pagebreak
+\newpage
 
-# Figures {-}
+# Figures {.unnumbered}
 
@@
 
-<!-- Use for MS Word ##### pagebreak -->
-
-# Colophon {-}
+# Colophon {.unnumbered}
 
